\part{The Ghost Hacker}
\chapter{}
\emph{Boom!}

``Star dust!'' Haruto cursed as he pushed away his VECD screen. The clean chamber filling with dark smoke every passing second. ``No, no, no, no, \emph{no}!'' He chanted as he leaped across the workbench. Grabbing the edge of the metal vacuum valve, he ignored the searing pain as he flipped it open. The low rumble of the motor powered vacuum sounded moments after causing the smoke to pour out from the VECD chamber and into his face.

``Cough. Cough.'' Haruto choked as he pulled back from the growing cloud of putrid smoke.

\emph{Buzz. Buzz.}

Haruto looked down at his vibrating BISM as a warning message appeared on the screen.

\textbf{\textsc{Injury detected! Injury detected! Please, stop current activity.}}

``Yeah, yeah, yeah,'' he mocked the generic message as he flicked the screen off. ``I'm stopping. I'm stopping.'' He continued under his breath. Really he ought to figure out how to disable the warnings altogether. He knew he was injured, he hardly needed his guidance chip to tell him that! If the damned thing would actually heal him without all the fuss. Now that would be helpful, \emph{useful} even.

Moving to activate his own first aid program, Haruto didn't get very far before the sound of loud high-pitched beeping goes off.

\emph{Beep! Beep! Beep!}

Letting out a great sigh as the smoke detector began to wail, he turned his head upwards. \emph{`The Gods must be laughing at me today. I'm sure of it.'} He thought as he climbed onto his good chair. Blissful, wonderful silence greeted him as he disconnected the power. He'd have to remember to turn the damned thing back on, but that was for another time.

Collapsing into the chair a wave of pain hit him. His burn throbbed an angry reminder to activate his first aid program. The burn relief protocol top of the list.

``Hhhhhhhhhhhaaaaaahhh.'' Haruto sighed in relief, his eyes fluttering shut as the pain meds took effect. After a moment more, he let out a reluctant groan. This was the thirteen burn this week. There was no way he wasn't running on 'E'. A quick glance at his BISM screen confirmed his initial assessment. Burn, cuts, and bruises were all low. Dangerously so. Although radiation looked good.

\emph{`See, a plus side to everything.'} He thought to himself. Although, the Healers were hardly going to welcome him with open arms for another refill. He'd been warned not to show up for another two more weeks. The regular check-up time for radiation refills. \emph{`Yeah, they're going to be sooo happy to see me.'} He thought sarcastically. 

His mind's eyes already picturing their pinched faces. He wasn't sure why they weren't on first name bases yet. They probably saw more of him than any other fourth year student. Haruto smiled at the thought, he really should consider stocking up properly. Seo-Jun hardly needed all of his. One too large inhalation turned into a coughing fit as smoke filled his lungs.

\emph{`Right smoke still everywhere.'} He thought as he pushed himself out of his seat to the window. Throwing it open, he stuck his head outside and took a deep breath of smoke-free air.

With a long sigh he rested his head on the window seal looking out over Solas. There really was no better view.

The noise from the central plaza filtered up even here at Haruto's apartment on the edge of Solas. People packed the streets. The occasional android among them. Overhead, was nearly as busy. Not like it used to be, but still droids zipping here and there. Tilting his head upward, Haruto caught sight of a patchwork robot, working on the catwalks. And just to the right, was the observatory deck. Currently open, giving Haruto a view of stars for miles.

KTS Kanopos was by far the best God Chaser class ship out there. Bar none. And Solas, his city, was the gem of the Jade Empire.

\emph{`And I've got the best view of it all.'} He thought as his eyes turned back to the observatory and the millions of stars. \emph{`Well, maybe not the best view.'} He continued in thought. After all, his best friend's room lay right under the observatory deck. While she couldn't see Solas like he could, he could see the stars much clearer than anyone else. Assuming she wasn't stuck listening to a bunch of old farts.

\emph{Buzz. Buzz.}

``Speaking of friends,'' Haruto muttered to himself as he looked down at his BISM to see the waiting message.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: Distract me please.
  }
\end{quote}

Haruto smiled widely as he began typing back.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    GhostHacker: It's 1413. That's class time.\\
    MPrincess: There's a 66\% chance your not even there. Add in your current AIM project and that turns to 98\%. We both know you get kicked out of class at a significantly higher rate when you're thinking of something else.\\
    GhostHacker: That's because no one needs to know about the history of some outdated battle.\\
    MPrincess: The Battle of Teckon cemented the power dynamics of the Jade Empire today.\\
    GhostHacker: Blab, blab, blab, blab...
  }
\end{quote}

Haruto knew his best friend was holding back a sigh. His grin widened as he stepped back inside his apartment.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: This is only mildly more entertaining than my tutors, Haru.\\
    GhostHacker: I was just pulling your SKIM. Class or no class, you're way more interesting. Besides, I need a break.
  }
\end{quote}

There was short pause. Haruto stressed at the thought of the total meltdown sitting in his VECD. Completely unsalvageable.

\emph{Buzz. Buzz.}
\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: You'll get it soon.
  }
\end{quote}

He didn't know how she knew. But it was mildly comforting nevertheless.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    GhostHacker: Not if I blow through all of my CG16 chips. You know how hard it was to get the box.\\
    MPrincess: Yes, and I know that the warehouse in the Zh\`{u}r\'{o}ng sector is currently on high alert. So, I wouldn't recommend going back.\\
    GhostHacker: Why does the old man need to rotate threat level drills anyway?\\
    MPrincess: We've been over this.\\
    GhostHacker: So, doesn't mean I've got to like it.\\
    MPrincess: Stop pouting. Besides, you shouldn't be seen in the Zh\r{u}r\'{o}ng sector anyway.\\
    GhostHacker: I've got an arrest on sight just about in every sector, Princess.
  }
\end{quote}

There was a long pause, where Haruto knew she was giving him the mental eye.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    GhostHacker: Okay, okay, okay. So maybe the Zh\`{u}r\'{o}ng sector is a special case.\\
    MPrincess: My Uncle is still fighting the backlash for that unique prank, Haru. \emph{Special} case is not how I would put it.\\
    GhostHacker: It's not my fault they can't take a joke.\\
    MPrincess: It was funny. And really, they should have known better than to simulink all of their SKIMs like that.\\
    GhostHacker: See! My point exactly. I did them a \emph{favor}, exposing that weakness.\\
    MPrincess: Yes, I'm sure that's how they saw the SKIM virus too.
  }
\end{quote}

Haruto could feel the sass even through his BISM. It was after all an old argument they'd had. He'd comment on how simulinks like that were for babies, and she'd counter that a virus was illegal no matter the intent behind it. But in the end, they'd agree that it was funny and as long as no one got hurt the Princess didn't need to turn him in to her Uncle. Which is how all of their pranking related arguments went.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    GhostHacker: Anyway, I just don't see why Guardian Inugami can't just give me one of his beta AIMs?\\
    MPrincess: Besides the fact that it's an act of treason?\\
    GhostHacker: The old man wouldn't care \emph{that} much.\\
    MPrincess: No, but the Council would. And they're not exactly your biggest fans.\\
    GhostHacker: No one would have to know. The Guardians have dozens of them just laying around.\\
    MPrincess: And they also have a full medical unit too.
  }
\end{quote}

His friend didn't give him any time to counter.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: They're beta AIMs for a reason, Haru.\\
    GhostHacker: So is SB3-QB9, but you don't complain about that.\\
    MPrincess: You know SB3-QB9 didn't make it out of beta testing because of health risks.\\
    GhostHacker: Come on Princess, no one would be the wiser if one AIM went missing.\\
    MPrincess: And how would you get past regular inspections? SB3-QB9 is 30 years old and thus unclassified. The same can not be said for the five models in Guardian beta testing.
  }
\end{quote}

Haruto sulked at his friend's rationale. Yes, he'd probably get in trouble for having the beta chip, but the old man would get him out of it. He always did. \emph{`If only I knew where the Guardians' base of operations was...'} he thought dejectedly. He'd have liberated a chip or two for himself without having to implicate Guardian Inugami. The Princess would be able to get behind that.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: I'm not going to give you the location of the Guardians base of operations.
  }
\end{quote}

Haruto didn't have a response to that.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: What's the real problem, Haru?
  }
\end{quote}

Haruto paused in his reply.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    GhostHacker: I've only got two left, Princess. \\
    MPrincess: The CG16's are meant for practice. They're expendable. And we both know you've been making progress.\\
    GhostHacker: But, what if it's not enough? What if I can't do it?\\
    MPrincess: Can't? The infamous Ghost Hacker can't do something?\\
    GhostHacker: Those hacks were mostly software driven. Viruses, low-key patches. This is different.
  }
\end{quote}

There was a long pause. Long enough that Haruto thought he'd lost his friend to her tutors.

\emph{Buzz. Buzz.}
\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: Haru, if there's anyone who can challenge an AI like the SB3 series, then it's you.\\
    MPrincess: You've proven time and time again, that you can do the impossible. And this is no different.\\
    MPrincess: You're going to finish patching SB2-QB9. And use your unique skills to pass the OCI exam.\\
    GhostHacker: Yeah, and somehow get a passing score for academic excellence. Right Princess?
  }
\end{quote}

Even Haruto didn't believe that last statement. OCI was a pipe dream and they both knew it. Without a unique AIM, he'd do poorly on the showcase too. And that didn't even touch on the exams.

\emph{Buzz. Buzz.}

Haruto jumped slightly in his SKIM, the buzzing of his BISM catching him by surprise.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: You can do anything, Haru.\\
    GhostHacker: Thanks Princess.\\
    MPrincess: I have to go. Try to eat something other than MINOS, please.\\
    GhostHacker: No promises.
  }
\end{quote}

\chapter{}

Haruto carefully opened the next CG16 chip under his clean chamber. Switching over to his VECD system, he began the tedious work of damaging the chip.

His VECD was off by a couple of picometers, and eventually he'd given up trying to fix the calibration. \emph{`But what can you expect from a toy?'} He thought bitterly. The VECD, or Vacuum Environment for Creative Design, was marketed for children ages 6 to 12. And as the Princess liked to point out, discontinued 25 years ago for sparking and alignment issues. But the latest models were out of their agreed upon price range for gifts, so he was stuck with it.

Sitting back, Haruto took a look at his work. Comparing the damage to the similarly broken SB3 model in his homemade anti-chamber. ``Alright you piece of junk, now how am I going to fix you?''

The problem, really, was the on-board power. No matter how he approached the problem, the thing just blow up in his face. Even now, as he stared at the circuitry under the fine microscope of the VECD system, he just couldn't see a way of successfully fixing the dang thing without crossing wires.

\emph{`I've got to disconnect the power, but how?'} He thought as he eyed the on-board power supply. ``Disconnect, and it blows.'' He muttered to himself. ``So I've got to keep the power running.'' Haruto mull over the idea for a moment longer.

``A secondary source, maybe?'' He said aloud. An idea sparked in his mind as he reached for the last CG16 chip. Opening it up in the clean chamber. He sat it next to its identical brother, and smiled.

Half an hour later he was carefully diverting the power from one chip to the other using a slapped together protoboard. With the power diverted from the damaged chip, Haruto began the process of bridging the copper wiring around the damage portion. A smile stuck on his face as he worked. Humming to himself, he started on the last bridge when his hand slipped just slightly to the VECD default alignment.

``Star du...'' A spark followed closely by smoke cut his curse short as the duel-linked CG16 chips shorted together. ``All that work...''

Sighing deeply. He cleaned up the mess. Still it \emph{had} worked. \emph{`Up until I messed up.'} He thought with a forlorn look at his almost success. Clapping his hands together he focus. ``Right. I've got this.'' Punching the air for good measure he hopped in place as he pumped himself up for the next steps.

``All I've got to do is build a mock power supply similar to SB3 on a new protoboard to connect them, bridge the damaged portions. Hope they still have redundancy. And not blow anything up.'' He hopped up and down some more. ``Yeah, no problem. No problem at all.''

Sitting back down he got back to work.

\starbreak

Hours later he sat back from his work. The light in his apartment had automatically turned on sometime while he'd been working. As he had it set to offset the fading light from KTS Kanopos, he wasn't sure exactly what time it was, but that hardly mattered now. It was done. SB3-QB9 should be fixed now. The SKIM around his hands hardened as he reached for the patched up AIM. He'd noticed it did that whenever he touched a functioning AIM. Some line of code in his BISM programming probably. All it meant for him was that he didn't need to remember to put on static free gloves.

It was small, all of them were. But this was the first time when he really considered its size. This thing was going to change his life. Holding back a sigh, he put the chip back down. It would be just his luck to get some small particle in it right before he put it in his body.

\emph{`I guess it's now or never, huh.'}

Opening his BISM, he popped out the basic guidance chip in there. Model 000256 given to every child born on KTS Kanopos during his first breath year, and while it wasn't an AIM it did keep him online and connected to Kanopos. \emph{Safe}. He closed his eyes as he gently held it. He felt cold without it. He wasn't sure if that was because he was now offline, his BISM no longer monitoring the temperature of his SKIM, or some other reason. But he felt cold.

\emph{`For a fourteen year old chip, you don't look half as bad as I thought you would. Seeing how much I put you through.'} He thought. And he had a lot of memories with this chip. He felt a little misty eyed, and immediately pushed the thoughts of the past away. He didn't know why he was being like this, he knew for a fact that all of the students from Clans in his class at KANP didn't have their 000256 guidance chip anymore. The Clans never kept their baby chips for long. Not to mention this was always going to happen. He was due for an upgrade in two years. Either the pilot AIM or the civilian guidance chip. And he didn't want either one, so this, \emph{this} was bound to happen sooner or later.

\emph{`All of the Clans have their own models. Better models, and so will I.'} Haruto thought as he gently placed his childhood guidance chip into the anti-static vacuum chamber that SB3-QB9 chip had been resting in hours before.

Picking up the SB3-QB9 chip again, he hesitated above his BISM. \emph{`What's the worst that could happen if this goes wrong?'} He thought.

``I could short circuit my BISM, and destroy it and possibly blow off my arm, which I guess isn't the worst thing in the universe.'' Haruto answered his question aloud, ``Unless, I've crossed the wrong wire, then it could possibly overload my heart and kill me when it starts up.''

He paused for a moment in thought, ``Man that would suck.'' Popping the chip in place he shrugged, ``Oh well, you only live once,''\ he continued as he snapped the BISM closed and the power re-routed back into it.

Shutting his eyes tightly he tensed in anticipation.

\emph{Buzz, buzz, buzzzzzz!}

Haruto's arm vibrated as he looked down at his BISM screen coming back online.

\textbf{\textsc{Hello Cadet H\={e}id\`{o}ng Haruto.}}

\textbf{\textsc{My name is SB3-QB9.}}

The words flashed across his screen in simple characters just long enough for him to read.

\textbf{\textsc{I will be connecting to your Bio-Interactive System Monitor now.}}

Haruto felt a sharp tingle, and then the screen went blank, and he waited, and waited, and \emph{waited}. ``Oh come on! How long does it ta...''

\textbf{\sffamily{Oi, will you shut up, kid!}} A deep voice sounded in his head. \textbf{\sffamily{I'm trying to think.}}

``Oh...''\ Haruto let out in surprise. He didn't know it would do that. A grin slowly formed on his face. He was going to have the time of his life with SB3-QB9.

%%  LocalWords:  VECD
