\chapter{}
The KTS Kanopos' artificial light slowly brighten the ship.
This close to the observatory, Haruto could just make out the Nebula star system.
A handful of small droids littered the air, but not nearly as many as a couple of years ago.
Small things like that worried him.
Things were starting to break faster than they could be fixed. \emph{`Still, if the old man wasn't worried, then I shouldn't be either.'}

Turning his attention away from the observatory, Haruto let his eyes fall on the nearby park.
Although technically it was the KANP training grounds, it still had real trees and a small pond made of recycled water, which were all things that made up the parks of Kanopos. 
So, Haruto didn't see why the old man differentiated it from any other park.

\emph{`Not as pretty as Sanctuary Park, but really nothing else is.'} He thought as he closed his eyes to imagine the small birds and other extincted species that called Sanctuary Park home. As the center piece of Pray Alley and his best friend's Clan sector, there wasn't another park that could compare. All in all, it wasn't all that surprising as the Gento Clan was known for it's patronage of the arts and conservation efforts. The Princess could go on for days about that stuff.

The thought brought a small smile to his face. He quickly wiped it off, and waited, but his new AIM was strangely silent. Haruto relaxed at having his own thoughts to himself for as short as he knew it would be. QB would go out like this periodically as the AIM seemed to still by calibrating itself. It was only during times like these when he needed worry about QB using anything Haruto thought about against him. And QB mostly seemed to want to use the Princess. 

Haruto couldn't get a thought about her in edgewise without QB bombarding him with questions about her. Questions he just wasn't ready to answer. It wasn't like he was hiding her or anything. 
It was just that for the four years they'd been friends, it had always been just them. And Haruto wasn't sure he was ready to share. That and the AIM was proving to be less than useless.

The Princess had warned him that the SB3 series was the closest Artificial Interface Module every developed to having functional artificial intelligence. At the time, Haruto had only cared about the theoretical performance. How else was he going to get an AIM that preformed on the same level as the Zh\`{u}r\'{o}ng Clan's or even the Princess' AIM?
But so far all SB3-QB9 wanted to do was get its own body, and the thing didn't talking about getting one in a nice way. But somehow he was going to have to make this work.

Turning his attention to the world outside, he couldn't help but picture himself in Sanctuary Park, minutes away from the Princess. There, life just seemed to be better. Little birds would play within the tallest trees of KTS Kanopos. Blues, blacks, oranges, pinks, every color of the spectrum. He'd seen a vivid purple bird once, fluttering amongst the leaves. Singing sweet songs. The thought taunted Haruto with endless possibilities just out of his reach. 

\emph{`Why am I even here, again?'} He questioned himself. Nothing the Lieutenants taught in class would be on the test. Half the time, Haruto was sure the Lieutenants were purposely skipping material that the students from the Clan's already seemed to know. While he couldn't prove it enough to go to the old man, every time Akihiko so much as turned his head to the window, the Lieutenant in charge would change topics.

And the Gods forbid if he asked a question. That never ended well for him or any of the other non-clan members. \emph{`Well mostly,'} His eyes fell onto the silver haired girl one row in front of him. Tomorrow it would probably be light pink again as the Helian heir seemed to change hair colors faster than her mood swings. Cadet Helian Aeliana was the only exception to the non-clan members no asking questions rule. When he'd told the Princess about it, she'd mentioned something to do with politics after which he'd toned the rest of her explanation out.

Haruto looked down at his tablet. He knew better than to look over at someone else's knowing it was a quick way to detention. Still, out of the corner of his eyes he saw holograms playing. On his was just a dense set of words, all in the ancient tongue.

He tried not to let the bitterness seep through. He should be lucky enough to have this tablet even if it was ancient. The loaner tablet, while several decades old was free and it worked. Sure, all it showed was the dense text, which he \emph{was} supposed to know by now. And yeah, halograms were like a billion times more exciting to watch. But free was free. And he needed all the practice he could get in the ancient tongue if he was going to be a successful Pilot, anyway.

All of the ZenKZ created by the great Jade Empire used the ancestors' language. So of course all of KTS Kanopos' Pilots used it too. But despite the nearly four years he'd spent at KANP, Haruto still struggled with it. The Princess had tried to help, but her method of learning the language had been to spend hours upon hours for years studying it. He didn't have that kind of time or patience.

\textbf{\sffamily{Oh stop feeling sorry for yourself, brat.}}  QB answered causing Haruto to nearly jump out of his SKIM. \textbf{\sffamily{At least you have a body.}}

\emph{`Dang it, QB stop doing that. Give a guy a warning or something.'} Haruto replied startled.

\textbf{\sffamily{My name is SB3-QB9, you may call my that or QB9, nothing else you ungrateful brat!}} QB9 answered back. \textbf{\sffamily{You seem to forget I am in control of your bodily functions.}}

Haruto snorted. \emph{`Yeah, and if I die you die.'}

\textbf{\sffamily{I never said anything about dying...}}

His wrist buzzed and an image of soiled SKIM flashed quickly. Haruto flushed at the thought, \emph{`You won't dare.'}

\textbf{\sffamily{Try me, brat.}} QB9 answered. Haruto was really going to need to figure out some kind of compromise with the AIM.

\emph{`Stupid program doing whatever it freaking feels like.'} He thought darkly, luckily QB9 didn't bother to respond. He'd probably get what he wanted, if Haruto couldn't figure out an alternative. \emph{`What kind of name was QB9 anyway?'}

\textbf{\sffamily{Doctor Fumagawa had a mind far more brilliant than yours.}} QB9 challenged. \textbf{\sffamily{H\={e}id\`{o}ng, however. Trying hard aren't we?}}

\emph{`The Princess says the H\={e}id\`{o}ng's were an elite Clan that once mastered time and space.'} Haruto countered.

\textbf{\sffamily{Clan?}} QB9 replied in disbelief.

Haruto flushed, \emph{`Well I didn't say they were a Kanopos Clan.'} He added quickly. Haruto felt an amusement not his own settle.

\textbf{\sffamily{And who in the Gods' name is this \emph{Princess}?}} QB9 questioned. \textbf{\sffamily{You've been thinking about her constantly since I was activated.}}

Haruto ignored the jab at the end focusing on the new information, \emph{`I suppose I should just tell him, but...'}

\textbf{\sffamily{Answer the question, brat.}} QB9 growled out.

\emph{`I don't know, QB9. You haven't been all that nice to me.'} Haruto responded teasingly as a feeling of anger not his own built within him. \emph{`How about we make it a game?'}

\textbf{\sffamily{A \emph{game}, boy? I don't play games!}} QB9 responded in a low growl of frustration.

\emph{`You've been around for like ten seconds. Who would you know if you play games.'} Haruto thought in response. The anger inside of him raged to a new level so Haruto changed tactics. \emph{'Look, I'm bored and you want an answer that only I can give you,'} Haruto taunted. \emph{`Seems to me like you don't have a choice.'} 

Waiting the new rage released all at once, followed closely by a feeling Haruto could only identify as resignation. With a smile on his face, Haruto continued. \emph{`I'll give you one hint, and only one hint to the Princess' identity. And if you can't guess her name with that one hint, then I get to call you QB.'}

\textbf{\sffamily{And if I win?}} QB9 questioned. Haruto paused in thought, not entirely sure what an AI would even want. \textbf{\sffamily{My freedom.}} QB9 answered for him. \textbf{\sffamily{I want my freedom.}}

Haruto rolled his eyes at the dramatics. It wasn't as if he was holding the AIM captive or anything. The thing \emph{was} an AIM after all. \emph{`Sure, why not.'} Haruto replied. \emph{'If you win, I'll get you a body of your own as soon as I can. Build it if I have to.'}

Satisfaction bubbled up from within him. \textbf{\sffamily{The hint, brat.}} QB9 demanded.

\emph{`She's from a Clan.'} Haruto smiled. \emph{`Hey, I never said it would be a good hint.'}

\textbf{\sffamily{Brat, you underestimate my skills!}} QB9 challenged. \textbf{\sffamily{That is more than enough for me.}}

\emph{`Prove it.'} Haruto replied. As far as he was concerned this was a win-win-win. He got to entertain himself, and he wasn't going to have to do anything he wouldn't have already agreed to do if the AIM had given him half a chance.

\textbf{\sffamily{Well you've got a pretty smug feeling about you, so the nickname isn't for just shits and giggles. If she's in a Clan that rules out a great many girls, including that Helian. Really kid, you shouldn't have given my the gender.}}

\emph{`I'm hearing a lot of talk.'} Haruto replied. There was a long pause as Haruto could feel QB9 processing. \emph{`You give up?'} Haruto questioned as he kept his mind thinking of the trees outside and imaginary birds.

\textbf{\sffamily{Impossible!}} QB9 spat out a moment later.

\emph{`So is that your way of saying you failed?'} Haruto questioned.

\textbf{\sffamily{Of course not, brat!}} QB9 responded. \textbf{\sffamily{My conclusion is simply impossible, even for you.}}

\emph{`Either you give a guess or you give up QB9. Those are the rules of the game.'}

\textbf{\sffamily{I believe this is her.}}

\emph{Buzz. Buzz.}

Looking down at his BISM screen, Haruto found his Princess staring back at him in her formal Moon Princess coveralls. He smiled disappointingly, \emph{`Yeah, that's her. My best friend.'}

\textbf{\sffamily{Then I win.}} QB9 gloated.

\emph{`Hey now, that wasn't part of the game.'} Confusion laced his thoughts but Haruto continued before QB9 could interrupt him properly, \emph{`Her name, QB9.'} He smiled at the blank response. \emph{`You're supposed to guess her name.'}

\textbf{\sffamily{She's the Gento heir, the K\={o}taishi,}} QB9 huffs in frustration. \textbf{\sffamily{You don't have access to the kind of information that would allow me to know more.}}

\emph{`That's only because I have to clear our chat history weekly.'} Haruto replied cheekily. \emph{`Well QB9?'}

\textbf{\sffamily{You already knew I wouldn't be able to get her name didn't you.}} QB9 growled out. \textbf{\sffamily{You played me!}} He roared in anger.

\emph{`Hey now, don't get mad. You actually got more than I thought you would.'} Haruto paused in thought seeing how this could go badly for him. \emph{`Look, why don't we call it a draw. I'll still help you out.'}

\textbf{\sffamily{You're not calling me, QB.}} QB9 responded. 

Haruto shrugged. \emph{`No big deal.'} QB9 settled down at his response.

Haruto leaned back in his chair as the Lieutenant continued to drone on at the front of the classroom. He wasn't entirely sure what they were supposed to be learning and frankly he didn't really care. Heck, he hadn't even bothered to remember his Lieutenant's name, and he'd had the man for months now.

\textbf{\sffamily{The Clans.}}

``Huh?'' Haruto questioned under his breath.

\textbf{\sffamily{Lieutenant \emph{Cho} is discussing the Clans.}} QB9 replied, sass heavy in his deep voice.

Haruto forced himself not to bang his head on his desk at the answer. \emph{`Why am I even here?'}

\textbf{\sffamily{Don't be overly dramatic, brat. This is important information.}}

\emph{`For you maybe, but nearly a quarter of this class is in the Clan. And I've known all about them for ages.'} Feeling QB9's disbelief, Haruto continued as he looked to the front row. \emph{`The blond up front is Ilia the Amur Clan heir. I think they do mind control or something. I can't really remember. But I do know that they're involved in a lot of enhanced interrogations and the likes.'} Haruto looked over to Helian. \emph{`Side note, I'm pretty sure they're dating.'}

\textbf{\sffamily{How do you know any of that?}} QB9 questioned. \textbf{\sffamily{You don't have access to that kind of information.}} QB9 continued in accusing tone.

\emph{`Best friends with the Gento heir remember.'} Haruto replied cheekily. Although he was sure the Princess had said significantly more on the topic of the Amur Clan, not that it mattered now. \emph{`Anyway, sitting next to her napping is Kur-ram. Cool guy and killer at Komi.'}

\textbf{\sffamily{Kur-ram is not a Clan.}} QB9 replied shortly.

\emph{`Oh, yeah. He's the Krai heir. And the big guy next to him is Kenta the Sakhalin heir. They have the best food anywhere onboard.'}

\textbf{\sffamily{How is that relevant?}} QB9 demanded.

\emph{`How is it not relevant?'} Haruto countered. Before QB9 could answered he continued. \emph{`Anyway, the Princess says the three of them are like really old family friends and will be a Pilot unit together after OCI.'} Turning slightly in his seat his eyes landed on Akihiko. \emph{`That brooding guy with the pinched face is the second son to the Zh\`{u}r\'{o}ng head family. Which apparently makes him as useful as a eleventh finger.'}

QB9 snorted in amusement. \emph{`The kid with the symbiote on his head is Seo-Jun from the Gonsaeng head family. Solid guy to have at your back during a prank. Also cheats on every test.'}

Haruto seat back as he found himself lost in some of his favorite pranks with Seo-Jun.

\textbf{\sffamily{And the kid in the back? With the goggles?}} QB9 questioned as a buzz came from his BISM. \textbf{\sffamily{He must be from the Haibeu Clan.}}

\emph{`Who?'} Haruto questioned as he looked at the stock picture on his BISM. Not recognizing the Cadet.

\textbf{\sffamily{He is literately sitting in the back right now.}} QB9 growled anger leaking into his voice.

Turning his head quick, Haruto looked and sure enough they were there. \emph{`Well what do you know.'} Haruto commented as he sat back to face the front. \emph{`I guess that must be Ji-Min the Haibeu heir. The Princess mentioned they were in the class. Must have blocked them out again.'} Haruto added with a small shiver. \emph{`Those guys give me the creeps.'}

QB9 was not amused. \textbf{\sffamily{There's only one of \emph{him}.}}

\emph{`Yeah, but since they're some kind of hive-mind, the correct pronoun is they/them.'} Haruto replied easily.

\textbf{\sffamily{I suppose your \emph{Princess} told you all of that too.}}

\emph{`More or less.'} Haruto replied. \emph{`Honestly though, if you get in a game of Komi with Kur-ram he's an open book. The Sakhalin Clan are really nice and will feed just about anyone who shows up at their family get togethers no questions asked.'} He continued for QB9's benefit.

He'd followed Seo-Jun to the Gongsaeng sector too many times to count. Haruto still remembered his failed attempts to get Seo-Jun's sister to give him one of her symbiotes. And if QB9 wanted to hear a biased opinion on the Zh`{u}r\'{o}ng Clan, then all Haruto had to do was insult Akihiko.

\textbf{\sffamily{Is that is? Just the seven Clans if you count your Princess?}} QB9 questioned skeptically pulling Haruto from his thoughts.

\emph{`Oh, well no. There's twelve in total, and...'} Haruto sighed. He really didn't want to have to explain them all. \emph{`Give me a second, would you?'}

Picking up his tablet, he tuned out Helian as she answered \emph{another} question like her life depended on it. Personally, he thought she needed to learn a lesson in fun, but that was just him. Angling the tablet just right so the Lieutenant wouldn't see him accessing his BISM, he began to hack into his neighbor's tablet.

A moment later and he had the direct feeds from the Lieutenant's notes.

\textbf{\sffamily{Oh, nice...}} QB9 murmured as he downloaded and sorted though the data on the Clans. From the flashes coming across his BISM screen, he could tell QB9 was also following secure links to even more data.

Haruto turned his attention back to the window as he waited.

``...the Gento...''

Haruto's attention was drawn to the Lieutenant at the front of the class at the sound of his best friend's Clan name. While he liked to think of himself as an expert on the Clan, partly due to being best friend's with the Princess and partly due to his continuous run-in with the Keepers, it never hurt to see if there was more to learn.

``As you all should have read last night, the Gento are one of the big four, and the one of the two original founders of our mighty KTS class ship,'' the Lieutenant spoke.

\emph{`There was homework?'} Haruto thought absentmindedly as the Lieutenant plowed on.

``What was not included in that reading; however, was the difficulty in getting the Gento Clan to join. The Sakhalin were all too happy to join in the cause. And the Zh\`{u}r\'{o}ng instantly saw the benefits of helping the shaping of a KTS class ship, which would be the first and only such ship within the Jade Empire.'' The Lieutenant chuckled at the comment. ``It would seem that Empire, great as it is, always seems to be last to the party.'' He chuckled again at some random inside joke.

\emph{`Tell me something I don't know.'} Haruto thought as his mind began to wonder. The Princess used to tell him bedtime stories about her Clan when he'd had trouble sleeping. The time of the Honorable Hanza, her great, great, great, great, grandfather, was one of her favorites.

``But the Gento, a powerhouse in their own right were reluctant to join their enemy.'' The Lieutenant tapped his own tablet sending information to the class. Haruto looked down at his only to see another block of dense text.

\emph{`Hard pass.'} He thought, \emph{`Besides, I've heard the story a dozen times now.'}

QB9 was quiet as he continued to processed the new data.

``Their blood feud with the Fujimi, as you can see, is something out of the history books. Some of the greatest battles of that were recorded were between the honorable Fujimi Hoshizora and Gento Hanza.''

Haruto let his eyes drift back to the world outside the classroom as murmurs erupted from the class.

``Lucky for us, a fabled friendship between the first Sakr\'{a} and the Honorable Hanza greatly aided the alliance process.''

``What was the feud about?'' Seo-Jun asked the Lieutenant. 

Haruto answered for him, ``Really Seo-Jun?'' he commented. ``Everyone knows that the Fujimi and Gento Clans were Pilots for hire and normally on opposite sides of battles during the Warring Stations period.'' He continued. ``There was so much bloodshed, so much death...'' he trailed off as he remembered the Princess' words. The pain heavy underneath them.

``A time where children younger than us fought and died.'' He added lowly. ``That's why KTS Kanopos is so important. We're here,'' Haruto nodded to the classroom, ``Until we're ready to be out there.'' He tilted his head to the window in the general direction of the observatory deck.

There was silence before Helian interrupted, ``How do you know any of that?'' Her words were accusatory. ``It wasn't in the reading, or in open records.'' She continued.

Akihiko interrupted before the Lieutenant or Haruto could reply. ``With the power of the Zh\`{u}r\'{o}ng Clan, there should have been no problem in defending and building the KTS ship. No reason to team up with the \emph{Gento}.''

Haruto leaned forward anger at the disrespect to the Gento Clan on his friend's behalf. ``Like the Zh\`{u}r\'{o}ng could afford the expense or the man power?'' Haruto already knew the answer. ``The Gento put up half. \emph{Half}. The construction cost of the KTS Kanopos. Gave up half their own ships, brethren, many who died in the defense of this great ship during construction. No profit, nothing gained but the honor of their Clan.'' Haruto paused as he looked around at the stunned faces. ``And we all know the Zh\`{u}r\'{o}ng aren't well know for their \emph{honor}.''

Akihiko's nose flared, ``How dare you...''

Haruto cut him off, ``Without the Gento Clan, stick up their SKIM in all, KTS Kanopos would still be a dream of two young friends.''

``That's enough, Cadet H\={e}id\`{o}ng.'' The Lieutenant interrupted. ``While you have some facts amazingly correct, you're wrong on several counts. Most glaringly your claims on the Gento Clan's investment, which was not half of the funds and man power, but initially only half the funds. If not for the constant respect and fair treatment that the First Sakr\'{a} showed the Honorable Hanza, it's very possible that the Gento Clan may have never joined.''

Haruto opened his mouth to correct him, but the glare of the Lieutenant caused him to shut it. He didn't often get warnings before being kicked out of class, but even Haruto knew one when he saw it.

``Now, if I may teach my class without further interruption.'' The Lieutenant snapped as he looked around the room. ``Can anyone tell me about the terms of the treaty that the Gento Clan signed?''

Haruto watched as Helian shot her hand up into the air.

``Cadet Helian,'' Lieutenant acknowledged her with a nod.

``The Gento Clan were given the protection of KTS Kanopos forming the Keepers in exchange for never having one of their Clan members become the Sakr\'{a},'' she answered swiftly. ``They have since grown to be the most prominent Clan within Kanopos,'' Akihiko snorted at the answer, but it would seem that Helian wasn't done, ``For example, the K\={o}taishi is already considered a ranking officer despite being our age.''

\emph{`Wow now, the Princess never mentioned that.'} Haruto thought. He'd have to ask her about it later. \emph{`Did she even need to go to OCI?'} Because if she didn't, that changed \emph{everything}.

``I see someone has done extra reading.'' The Lieutenant replied gripping Haruto attention. ``Cadet Helian is correct. When the Gento Clan joined KTS Kanopos, their treaty gave them the exclusive right to maintain and control the Keepers of the Peace that keeps watch over our great ship, in exchange for never having the ultimate power of the Sakr\'{a}.''

``Wait a second.'' Haruto interrupted accidentally. ``In the initial treaty?''

Lieutenant tightened his lips. ``Are you hard of hearing too? Hard to believe with those ears.''

Haruto flushed in embarrassment. ``No, it just the Keepers weren't even mentioned in the initial Gento-Kanopos Treaty. That was added like fifty years after the completion of the ship.'' Haruto leaned forward as he continued. ``\emph{And} the Gento didn't join the Kanopos because of fairness and respect.'' Haruto added not seeing how anyone could believe that. ``Honorable Hanza had already made a deal with...''

``Enough H\={e}id\`{o}ng!'' The Lieutenant yelled. ``I don't know where you think you're getting this information, but it's all wrong. The official record states...''

``\emph{I'm} getting this information from the Princess, eh Moon Princess, herself. And some how I think the heir of the Gento Clan would know her own history.'' Haruto countered angrily.

The Lieutenant looked pissed for a second before his face returned to a blank mask. Haruto was sure he was about to get kicked out, but before the Lieutenant could speak Helian did.

``The Gento heir?'' She questioned. ``Moon Princess? You call the K\={o}taishi by her ZenKZ's name?''

``Well it's a nickname actually. She's got one for me too...''

``One for you?'' Seo-Jun questioned his symbiote squeaked on his head. ``What are you on man, because there's no way your friends with the K\={o}taishi.''

Haruto crossed his arms in defense. ``We're best friends. We talk all the time.''

``Sure you do, idiot.'' Akihiko answered with sarcasm. ``Because the K\={o}taishi is friends with the dead last, Clanless orphan.''

``The H\={e}id\`{o}ng was a powerful Clan...'' Haruto started to counter, but was interrupted as the entire room burst into a fit of laughter.

``But not a Kanopos Clan, which is why they're all but dead.'' The Lieutenant interrupted calmly as the laughter died down. ``And Cadet,'' he continued looking at Haruto, ``if you're going to lie make it a better one next time.'' The Lieutenant shook his head in disappointment. ``Best friends with the K\={o}taishi.''

``I'm not lying.'' Haruto tried to defend.

``The door, Cadet.'' The Lieutenant pointed to the door. Staring Haruto down as he gathered his things.

With a huff Haruto slowly rose from his seat before walking out of the classroom. \emph{`See if I care if they get the whole story wrong anyway.'} He thought as he closed the door behind him.

Still, this went a little further than normal. And the Ghost Hacker of Kanopos didn't let anyone get away with laughing at him.

\chapter{}

No one would say that Haruto had patience for much of anything. And even he had to admit that was mostly true. So far, he'd found only one exception, pranks. 

Hacking into the feeds of one of the Zh\`{u}r\'{o}ng mechanical birds. As if anyone believed they were for anything but spying. Haruto took control of it and sent it hovering just outside of his classroom. Within moments the feed was running over his left retina. The first time he'd done this, he'd thrown up his lunch. Now, though the odd sensation of looking at the KANP training grounds in one eye and his classroom in another just made him a little nausea.

Sitting back, he leaned on the wall of the rooftop exit of the nearby building. And waited.

\textbf{\sffamily{You really going to sit here and wait?}} QB9 questioned skepticism heavy in his voice.

\emph{`Welcome back to the living QB9.'} Haruto replied jokingly.

\textbf{\sffamily{Seriously kid. There's a good half an hour before the lunch break. And your little girlfriend doesn't break for lunch for another forty-five minutes.}} QB9 growled out in disbelief. \textbf{\sffamily{You can't even wait the three minutes it takes to heat up that stuff you insist on calling food.}}

\emph{`First, MINOS is a gift from the Gods. Second, this is a prank.'} Haruto replied, but he could still feel a disbelief that was not his own so he continued, \emph{`Just watch and learn, QB9.'} Turning his attention to his BISM. It was time to prepare.

With quick fingers, Haruto had his programming logs up. As a log file, the Keepers never gave it more than a glance. Hidden within the log was a crude access point that would get him access to the GH mainframe, or rather allow him to bounce off the numerous amplify using his Hacker signature as the encryption password to get to the GH mainframe located in the basement of a building in Red Sector of Lower Level.

\textbf{\sffamily{Surely someone would find it there.}} QB9 commented.

Haruto held back a snort at the comment, \emph{`It's abandoned, and I promise you no one's going near that place.'} Haruto shivered at the risk he'd taken putting the thing in there, but he could still feel QB9's skepticism. \emph{`Look, the building it's in is right next to the crazy, scary lady's place, well apartment building I think.'} Haruto continued. 

Haruto thought she was either a former prostitute or a Pilot. Either way, the rumors that followed her meant that her property had an invisible barrier around it.

\textbf{\sffamily{No one's that scary.}} QB9 commented at his unspoken thoughts.

\emph{`Yeah, well when you get a body of your own, you can test out that theory.'} Haruto answered shortly as he started scrolling through his programs and viruses. \emph{`There it is.'} He thought as he landed on the SKIM virus he'd used to great effect on the Zh\`{u}r\'{o}ng oh so long ago. 

It would need modification if he wanted it to work, but he was sure he'd get in done within the thirty minutes before lunch.
And it would have to be during the lunch break as this Lieutenant was smart enough to keep his notes on him at nearly all times. It was just too bad that he was paranoid enough not to flush his system with the little drive on him. That would have made things even easier.

\textbf{\sffamily{Really? The bathroom?}} QB9 questioned.

\emph{`There was one Lieutenant that should have been a little nicer to me.'} Haruto thought in reply.

\textbf{\sffamily{That's why they have a separate flush system?}} QB9 continued more to himself than anyone else.

Haruto nodded even so, as he watched his classmates rush out of the room for lunch. \emph{`Not that it matters. Since I gave myself administrative access to the staff system.'} He continued in thought as he counted the last student. ``Whatcha waiting for Lieutenant?'' Haruto muttered under his breath as he continued to wait for the man to exit as well.

Haruto's eyes went back to his BISM as he flipped to his encrypted master routine list. Under \textbf{KANP Lt. YEAR 4} Haruto found his random generator: \textbf{\textsc{Flush, eat}}.

\emph{`Good, I won't have to wait long.'} He thought as his left eye watched the Lieutenant exit the room.

Exiting the little mechanical bird's vision so as to avoid running into a wall due to split vision, Haruto hopped off the rooftop heading back to KANP.

\textbf{\sffamily{Wait a second. How did you get the man's randomized generator program? And all those other ones!}} QB9 demanded.

\emph{`A lot of time and patience.'} Haruto replied as he stealthily made his way back into the empty classroom. \emph{`Hey, give me three minutes.'} He asked.

\textbf{\sffamily{I'm not your damn clock.}} QB9 growled back in response.

Haruto held back a sigh as he entered his own count down. \textbf{\textsc{176..175..174..}}

Lieutenant Cho, as QB9 had reminded him earlier, kept his drive in a secure box, multi-layer encryption. The kind of encryption that would normally take Haruto anywhere from twenty to thirty minutes to crack. In fact, he'd cracked this one in twenty-eight minutes and fifteen seconds, 10 weeks ago during a lunch break. Plugging in the encryption key, he was a little disappointed when it popped right open without needing any modifications.

\emph{`No one ever bothers to update these things,'} He thought with a sigh.
\textbf{\textsc{165..164..163..}}

\textbf{\sffamily{Stop complaining. We don't have time for modifications.}}

\emph{`What? You saying you couldn't have broken a new multiple-level encryption in less than a minute? Where's that AI brilliance?'} Haruto replied cheekily. QB9 growled in response.

Leaving the AIM alone, Haruto moved on to the next part, which was just as easy. Popping the device into his BISM, Haruto took the extra minute and a half to bypass the drive's encryption. Double layered security was all well and good, Haruto personally ascribed to it. Even so, if the inner layer wasn't either equal in difficulty or harder to crack, there really wasn't much of a point to it.

\textbf{\textsc{63..62..61..}}

Popping out the drive, Haruto placed it back in its protective box and was out the window with a minute to spare. 

\starbreak

Perched back on the top of the nearby rooftop. Haruto waited comfortable as he hopped from one mechanical bird to another. In this way, he spent the remainder of lunch with a bird's eye view of Kanopos. And the other eye, blissfully closed.

Without warning, his vision was abruptly switched to a bird monitoring the classroom, which was already filling with his classmates. \emph{`Oh, it's starting.'} He thought.

\textbf{\sffamily{A `thank you' would be nice.}} QB9 complained.

``Thanks.'' Haruto replied dismissively, but his attention was more on the classroom as the Lieutenant finally arrived. Pulling up the rear of a group of students. Moving to the front, the man pulled out his virsus containing thumb-drive and connected it to his BISM without a care in the worlds.

A smile tugged at Haruto's lips in success. Now, it was just a waiting game. And he didn't have to wait long. One by one, the class looked down at their own BISM in confusion. 

``What the...'' Someone called out finally putting a voice to the general confusion in the room.

\emph{`That would be the virus taking over your SKIM.'} Haruto answered darkly in his head as he continued watching with glee as the Lieutenant frantically tapping on his own BISM as if that would stop it a Ghost Hacker prank.

``No, \emph{no}, no, nonono, \emph{NO}!'' The Lieutenant chanted from the front right before the room locked down.

``Oh, that's new.'' Haruto responded as he watched the battle alert flashers descended from the ceiling.

\textbf{\sffamily{Kid, is it supposed to do that?}} QB9 questioned anxiously.

\emph{`No. The higher ups must have changed the threat response.'} Haruto replied as the lights in the room began to flash red followed closely by the high pitched battle station alert sound. From here he could see the flood lights illuminating the floor as the emergency window exits popped open.

``Oh well.'' Haruto replied with a shrug. The higher response level wouldn't effect his prank.

``Code Red, Systems on lock-down. Kanopos Academy for Novice Pilots room 13 under....'' The female automatic voice crackled off as Haruto's BISM buzzed in warning. 

\textbf{\textsc{This is not a drill.}} Flashed in bright red blocks of letter for a brief moment. ``What do you know. They send that thing out to everyone regardless of location.'' Haruto spoke aloud as QB9 overwrote the warning.

Deep cold laughter replaced the automatic voice causing Haruto to look up in surprise. ``QB...''

\textbf{\sffamily{It's QB9, brat.}} QB9 replied.

\emph{`I don't care what you want to be called. Why's your voice going off in the classroom?! Did you do something to my program?'} Haruto thought wishing he could pull up the program to check. But he knew that soon enough his prank would actually take into effect and he didn't want to miss a second of it.

\textbf{\sffamily{I didn't remove your hacker signature if that's what you're asking.}} QB9 replied dodging the actual question.

\emph{`That is not what I asked!'} Haruto thought as QB9's deep laughter continued to fill his classroom. \emph{`What part of that program did you write, huh?'} He continued.

The first of the SKIMs began to flicker as QB9 replied. \textbf{\sffamily{It went through me didn't it. That should be enough.}}

Haruto shook his head as his class' SKIMs started to change colors. Haruto smiled despite QB9's additions as the green and pink began to make a pattern. In his head he replied, \emph{`We will be talking about what equates to contributions to a prank later.'}

The front room camera went off capturing the moment for all to see on the blackboard.

``How troublesome.'' Kur-ram's voiced, clearly the first to see the big f-u he'd given the class. A hand gesture he'd learned in the Red Sector of LL that the old man had made him promise never to repeat. 

\emph{`Well, technically I'm not.'} He thought as laughter began to bubble up from inside him. Looking down at his BISM, he was pleased to see the picture had turned out splendidly.

Sending it off to his friend, he wasn't at all surprised by the instant fox face she'd sent back in reply. He nearly opened a new chat with her when sounds from his hacked bird caught his attention.

``What is the meaning of...'' The Lieutenant began, but the sound of the rest of the KANP building entering Red alert drowned him out. Followed by more of QB9's dark laughter echoed off the walls.

Haruto paused in horror. ``Star dust!'' He cursed. \emph{`QB9 is this you?'} He questioned.

\textbf{\sffamily{Don't look at me, brat.}} The AIM growled out in confusion.

Haruto flew the bird back and forth as each class seemed to be triggered exponentially fast. QB9 switched the camera back to his classroom as the Lieutenant looked around him in increasing horror. ``No. Heavens above no. This \emph{can't} be happening.'' The man's fingers jabbed at his BISM futilely.

``Well,'' Haruto spoke aloud. ``This just got real serious.''

``H\={e}id\`{o}ng \emph{HARUTO}!'' The Lieutenant yelled at the top of his lungs.

``Star dust!'' Haruto cursed again as he pulled hastily from the mechanical bird. Taking off from the rooftop at top speed. He bolted for his exit. One class and the old man would probably have a laugh with him. Two or three and he'd get a stern lecture. But the whole school?

\textbf{\sffamily{I'd suggest running faster.}} QB9 added unhelpfully.

``\uppercase{H\={e}id\`{o}ng}!'' The Lieutenant yelled far to close for comfort.

\emph{`Rookie mistaking staying too long. What was I thinking?'} He admonished himself as his feet took him across the rooftops.

Hopping off the building, Haruto flung himself around the corner and into the bustling crowd. He blended into the hectic group as he weaved his way across the Market Plaza. He just needed to make it through this crowd and he'd be home free.

\emph{`Of course nothing is ever that easy.'} Haruto thought as he felt the tug of a soft link connecting his SKIM to someone else. Pulled backwards, his gaze met two sets of pale eyes missing their irises. \emph{`Gento, Keeper Gento.'} He thought darkly. \emph{`Just my luck.'}

\textbf{\sffamily{Are they allowed to just link with you like this?}} QB9 questioned mildly concerned.

``Keeper Gento, Keeper Gento,'' Haruto greeted each Keeper warmly. ``So, nice to see you,'' he continued. To QB9 he added, \emph{`Well yes and no.'} 

QB9's frustration at his answer was palatable as one of the Gento Keepers gripped his bicep hard. At the same time, the soft link dissolved. \emph{`See, I kinda have an arrest on sight order out on me. So it's technically allowed as long as they don't keep it.'}

\textbf{\sffamily{Figures.}} QB9 muttered.

``Cadet H\={e}id\`{o}ng, shouldn't you be in class,'' questioned the Gento that still had him in a vice grip.

``Well, you see. I was just on my way back to class, so if you could...'' he began pointing to the left as he edged towards the right. Visual misdirection sometimes worked wonders, but it wasn't helping him here.

Catching sight of his Lieutenant frantically searching for him out of the corner of his eye, Haruto silently cursed himself. The Gods' really had it out for him today.

The Keeper holding him turned slightly to his left in the opposite direction of his frantic Lieutenant. ``Sir?'' He answered hesitantly, loosening his grip in the process. Haruto had an idea about what that call was for and didn't plan on staying long enough to prove himself correct. Pulling himself out of the Keeper's grasp, Haruto made a run for it disappearing in the adjacent alleyway.

``Stop him!'' A male voice called after him, but Haruto was only meters away from his destination.

Skidding to a halt in front of a the Market Plaza Central Terminal, Haruto flipped open the control panel as he hastily connected his BISM to the system. It shimmered as it began to start up, before blinking out.

``Star dust!'' He cursed. \emph{`The old man has got to keep at least the Market Terminal in working order!'} He thought harshly as his mind raced through his options. \emph{`I could bypass the damaged circuitry with my BISM, but that will take at least five minutes.'}

\textbf{\sffamily{We don't have time for this.}} QB9 growled out harshly.

Frustration flashed across Haruto's eyes. As if he didn't know already. Before he could complain aloud, the Terminal screen blinked back to life.

``Thanks,'' Haruto murmured as his fingers danced along the screen as he forced the Terminal into command console instead of normal boot. A moment later and he'd forced his \texttt{Portal Jump} program through the system. ``Come on, come on, come on.'' Haruto chanted to himself as he watched line after line of code pass along his BISM screen.

\textbf{\sffamily{Any day now, kid. Any day, would be nice.}} QB9 replied his sarcasm tinted with worry.

\emph{`I'd like to see you go faster!'} Haruto countered.

Feeling QB9's annoyance, Haruto was unsurprised when the AIM spoke again. \textbf{\sffamily{I'm optimizing your programs as soon as we're out of this mess.}}

``Code Yellow, MPCT under cyber attack.'' A light female modulated voice boomed from the aerial speakers above, giving away his position to the angry Lieutenant behind him. Big black letters flashing on the Terminal's screen. \textbf{\textsc{ACCESS DENIED.}} Blinking over and over again.

\emph{`Yeah, yeah, yeah.'} Haruto thought just as the screen turned green. \textbf{\textsc{ACCESS GRANTED.}} Flashed quickly on the screen, silencing the alarms in the process. In another moment, he had the Terminal service entrance opened.

\emph{Buzz. Buzz.}

``What now?'' He asked aloud as he stepped into the service tunnel. QB9, helpful for once, opened the message for him.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: Are you alright?
  }
\end{quote}

Haruto didn't know how she knew that the KANP prank had gone a little overboard already, but honestly wasn't all that surprised. 

``\emph{H\={e}id\`{o}ng!}'' Haruto heard his name called from what might have been his out of breath Lieutenant as his fingers typed his response.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    GhostHacker: Yeah, I'm good. KANP just got a little exciting for once.\\
    GhostHacker: Talk to you later, okay. I've got to go dark, now.
  }
\end{quote}

The service entrance closed as the Lieutenant's irate face came into view. Haruto waved goodbye with a huge smile.

\emph{Buzz. Buzz.}

Haruto was surprised when QB9 opened the message without begin asked.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: Don't get caught.
  }
\end{quote}

Well, that was one warning he didn't need saying twice.

%%  LocalWords:  KANP Tlacopan Kur Komi Seo Ppalgan Zh ng Hoshizora
%%  LocalWords:  Hanza Sakr Akihiko's Aeliana's Haruto's taishi OCI
%%  LocalWords:  ng's Whatcha multi SKIMs MPCT MPrincess GhostHacker
