\chapter{}
Heat blasted from the furnaces pumping air heated by many processes within core of Solas. And in the process creating a dense humid blanket of heat around the young redhead. While not the hottest place on KTS Kanopos, the junkyards of the Lower Levels, better known as Black Sector, had certainly earned the title of being the \emph{second} hottest place onboard. And because today, Haruto's luck seemed to be fairly poor, he'd landed in the junk heap that most just called the Hell Yard, which as he'd learned long ago wasn't named for it's lovely gardens, but for the unfortunate connection to Zh\`{u}r\'{o}ng Pyro-Studios. 

All-in-all, there wasn't much that called the Black Sector home, but recycle bots. As such, Haruto, being as human as the next pound of flesh, was reduced to a sweaty mess. A sweaty mess that was at constant danger of breaking his carefully crafted illusion program at even a single drop of sweat. At the thought at bead ran down his forehead, reaching the collar of his SKIM where it was quickly absorbed back into his suit. Another bead followed and another. And Haruto knew it was just a matter of time when the God of Luck would truly turn his back on him.

Without warning a cool sensation wrapped around his neck, causing his body's temperature to decrease a fraction. Haruto blinked in surprise, but otherwise made no outward signs of his changing temperature. \emph{`Thanks QB9,'} he thought. Who knew the guy had a heart after all?

Annoyance filtered through his consciousness. \textbf{\sffamily{It wasn't for you, brat!}} His AIM's voice boomed in his head in stark contrast to the quiet around them.

Haruto rolled his eyes, but ignored the AIM. He didn't have time to respond as the heavy footsteps of his pursuers echoed overhead. Several paused before continuing on in a standard search pattern. Steps then silence. Steps followed by silencing again.

Slowing his breath even further, he didn't dare move sure. The slightest move now would be his undoing as the Keepers would be using a bio-scan to search for any signs of life no matter how small. That along with the famed Gento bionic eyes, they'd also pick up any residual electronic signals. Both of which easily penetrated the black light of Black Sector. A fact that he was using to his advantage.

\textbf{\sffamily{Why not just develop a cloaking device?}} QB9 growled out. \textbf{\sffamily{This program is far more complicated than simply reflecting the space around you to generating empty space.}}

\emph{`An empty space is like a big red flashing light saying I'm right here hiding. Take a look around QB9. This will work. It always has.'} Haruto replied as he waited.

``Check the next section.'' A female voice rang clear. ``He's here somewhere, so find him.''

``Yes, ma'am!'' A chorus of voices replied. Haruto could already imagine them with their tight salutes. The Keepers might as well be military for all their traditions and formalities.

\textbf{\sffamily{Paramilitary, actually.}} QB9 sounded.

\emph{`What?'}

\textbf{\sffamily{The Keepers, they're paramilitary.}} QB9 answered. \textbf{\sffamily{Figured every once and a while, you'd like to be right for a change.}}

Haruto's eyes fluttered shut in annoyance as the sound of footsteps retreating overhead. \emph{`One problem at a time.'} He chanted to himself, \emph{`One problem.'}

Right now, he needed to stay still. He'd learned the hard way that the Keepers always left a small two man team behind. And if he didn't want to get into trouble, he'd have to wait them out too. Holding back a sigh, he tried to keep his body relaxed and his heart rate slow and steady. \emph{`Why am I even going through all of this trouble?'} He questioned himself. Why hid for another hour or two, stuck doing nothing when the Keepers were out with a vengeance?

Honestly, there was nothing that linked him directly with the prank. Sure the old man would still lecture him, but that always ended with dinner. And yeah, the Princess would never let him hear the end of it, but he could live with that too.

\textbf{\sffamily{Don't you dare, brat!}} QB9 growled out as Haruto was slowing talking himself into just turning himself in. \textbf{\sffamily{If you get caught, I get caught!}}

\emph{`Well as long as you didn't take anything, but the lecture notes, we should be fine. It's not like there were any witnesses.'} There was a long pause in response to his thoughts. Unease and guilt rolled through him in waves. \emph{`QB...'} He thought warningly.

\textbf{\sffamily{Don't get caught, kid.}} QB9 responded shortly.

Haruto held back another long suffering sigh of frustration. Trust his AIM to do something to get him into even bigger trouble. The Princess was going to have a field day with this one. Well, a polite field day, but the teasing would be endless.

Soft footsteps padded along the catwalk overhead, pausing a little too close to his actual position for comfort. Haruto closed his eyes and slowed his heartbeat further. Seconds later the footsteps moved on. The illusion program he was running, code named \emph{Rusty Bucket}, worked best with a slow heartbeat and overall calm mentality, which was hard to do when a stupid overbearing AIM had to go and do something stupid.

\textbf{\sffamily{I'm hardly the stupid one.}} QB9 growled in outrage. As if he was the one personally offended. \textbf{\sffamily{That Lieutenant should have known better.}}

Haruto continued to count his heartbeats in his mind a technique he'd picked up from his friend. \emph{`Just keep calm, you've been in worse spots.'} He thought to himself. But what he wouldn't give to see if the \emph{Rusty Bucket} program was still running smoothly? In his mind, he got an image of the program steadily changing his heartbeats into weak irregular electrical outbursts. His SKIM still outputting the properties of a rusty metallic surface that was being warmed by the furnaces above. Everything looked good, but the rusty bucket wasn't supposed to run for more than a couple of hours.

\textbf{\sffamily{We've still got plenty of time.}} QB9 replied. \textbf{\sffamily{Just stay still.}}

\emph{`Easy for you to say, you don't have any biometrics to give away our position.'} Haruto thought darkly. And if it wasn't for his good for nothing AIM, they wouldn't even be in this mess. QB9 was strangely silent at his thoughts. \emph{`What did you take anyway?'} Haruto questioned.

QB9 remained surprisingly silent, which made Haruto want to laugh in disbelief. The AIM didn't want to shut up before, couldn't stop himself from pointing out how stupid Haruto was being. But now? The silence of the void. And if they did get caught, it wouldn't take long for the Keepers to find those files, those obviously important files. \emph{`And with the files, they'll be able to pin the hack on me.'} Haruto thought darkly. While he was still a minor, that didn't change the fact that giving a virus to a classroom of students, or anyone for that matter, was a serious offense.

\emph{`The old man isn't going to be able to save me from this one.'} He thought worriedly.

\textbf{\sffamily{Don't get caught, and we won't have to worry about anything.}} QB9 finally spoke up.

\emph{`You owe me for this one.'} Haruto thought harshly. QB9 didn't respond, but Haruto knew he'd get to collect on this later. For now, \emph{`I'll wait.'}

%% \starbreak
\chapter{}

\emph{`Forever and a day later,'} Haruto thought as he stretched out his tense muscles.

\textbf{\sffamily{It's only been 46 minutes and 27 seconds, brat.}} QB9 interrupted. 

\emph{`Says you.'} He replied back in thought as he stood up from behind the junkyard trash. As far as he cared, if it felt like forever, then it might as well have been. QB9's annoyance surfaced briefly, but Haruto was getting better at ignoring it.

Stretching his arms to the ceiling as he twisted here and there to work out the remaining kinks, he was pleased to see that he was indeed alone. Nothing but the junkyard bots working on disposal of Kanopos trash. \emph{`Completely harmless.'}

Grinning wide, he jogged down from his position in the trash heap, and on to the catwalks around him. A terminal was only a few paces from this spot, but he'd have to avoid it. Connecting to the network now would only be calling attention to his position. Touching his BISM, he let \emph{Rusty Bucket} drop. At nearly two hours, it was at the limit of its proper functioning range anyway. He'd have to tinker with it later, who knew if he'd ever need it for longer periods of time in the future. For now, he was still a little upset that QB9 had cost him a few hours out of his day.

``Oh well,'' he spoke aloud with a light shrug. It had been a good prank, so all-in-all a good day. Setting out to his apartment on foot, Haruto began the long trek home. Even if the wait had been unnecessarily long because of his AIM's curiousity, a good prank was worth it. \emph{`And that's going down as one of my best.'}

Haruto's stomach growled reminding him that he'd only had breakfast today. Putting his hands behind his head, he closed his eyes as he let his mind wonder on what he wanted to eat for dinner. \emph{`I can make a MINOS stir fry.'} He thought picturing MINOS noodles in a bowl of vegetables, only he didn't have any vegetables. \emph{`Okay, so stir fry without the veggies.'} A bowl of fried noddles without the veggies entered his mind, \emph{`Which is really just fried noodles. So fried noodles for dinner than.'}

\textbf{\sffamily{You had MINOS for breakfast. Eat something else, kid.}}

\emph{`Why in the world would I want to do that? MINOS is the food of the Gods!'} Haruto replied seriously.

There was a moment before the deep voice of QB9 entered his mind, \textbf{\sffamily{You have an unhealthy obsession with this stuff.}}

\emph{`Impossible.'} Haruto replied immediately, \emph{`Nothing that is both nutritious and delicious can be unhealthy.'} Humming a few bars of the MINOS jingle, he skipped a for steps in his eagerness to get home.

\textbf{\sffamily{You can't honestly believe that propaganda, can you?}}

Haruto furrowed his brow as he turned into a back alley easily by-passing the \emph{random} Keeper patrol. He'd fight with QB9 on just about any topic, but \emph{not} his MINOS, not his favorite food, \emph{`I already get enough nagging from the Princess. I don't need you too, QB9.'} Haruto thought feeling QB9's annoyance he continued. \emph{`Besides it's organic, so of course it's healthy for me.'}

\textbf{\sffamily{So is shit, but you don't eat that.}} QB9 replied with heavy sarcasm in his voice hiding the AI's outrage. Haruto didn't care. There was nothing QB9 could say that would convince him that MINOS wasn't a gift from the Gods. If his best friend couldn't, then an AIM with more attitude than usefulness wasn't going to be able to either. \textbf{\sffamily{Look kid, if you die young, don't complain to me.}}

\emph{`If I die, you die QB9! Or have you forgotten that already.'} Haruto countered.

\textbf{\sffamily{Not if I get out of here first...}}

Haruto rolled his eyes at QB9's familiar dramatics. He wasn't going to die young anyway. MINOS was healthy for you. \emph{`It's has to be. It has Nutritious and Organic in the title.'}

\textbf{\sffamily{Malleable, Ingestible, and Substance are in there too.}} QB9 countered. Haruto could feel his imaginary eye roll. His annoyance knocked up another level. \textbf{\sffamily{Ever wonder why they need to specify that it's Ingestible, kid?}}

\emph{`Don't know, don't care.'} Haruto continued as he ducked behind a building allowing another patrol to pass him. Princess had sent him a bunch of nutrious facts about the stuff. All of which he'd deleted without opening. There was nothing QB9 could say that she hadn't already tried.

\emph{`You know what I do know?'} Haruto didn't wait for an answer. \emph{`When I get home I'm going to have a nice big bowl of fried MINOS noodles with some shrimp flavored broth.'}

Heading up the stairs to his apartment, he hummed a light tune that sounded suspiciously like the MINOS jingle. Tapping his BISM to a refurbished biometric scanner that kept his apartment on lock down mode, the door opened with a quick \textbf{\textsc{Access Granted}}. 

He'd personally fixed and updated a broken one years ago knowing that security was not to be taken lightly. This along with some other rather nasty security measures made his apartment one of the most secure building on KTS Kanopos.

\emph{`And off limits.'} Haruto added to himself as he made his way into his dark home and into the kitchen for his much awaited MINOS dinner.

\textbf{\sffamily{Don't move.}} QB9 warned. \textbf{\sffamily{We've got company.}}

Haruto's first thought was, \emph{`Impossible.'} But there sitting on his good chair was Guardian Inugami. \emph{`The old man sent a Guardian after me?'} It was unbelievable, unthinkable, but there the dog god mask stared him down in his own kitchen. \emph{`This is not good.'} He thought as he took a tentative step back. He'd curse QB9 aloud if he wasn't technically supposed to have him. He had no idea what the AI took, \emph{his} AIM took, but it was clearly even more important than he'd initially thought.

Another step back as his mind whirled with this new discovery. He had one option available to him. Get the heck out of here. \emph{`If I can get to the door, my emergency escape route will take me back to the Lower Levels.'} Then he'd lay low for a couple of days. After which, the old man should have taken care of the situation.

By the \emph{Gods}, QB9 owed him for this one.

\textbf{\sffamily{One thing at a time, kid.}} QB9 voice sounded softly in his mind. \textbf{\sffamily{Get out of here, and we'll talk about it.}}

``Hello, little Haruto.'' Inugami spoke from his seat in the kitchen.

``Hey Inugami.'' Haruto replied as if nothing was amiss, ``What a surprise seeing you here.'' He smiled at his favorite Guardian, even when he knew it would get him nowhere. ``If I'd known you where coming, then I'd have...''

Before Haruto could finish, Guardian Inugami interrupted him. ``Stayed in the Lower Levels I imagine.'' The distorted voice had a hint of amusement as he continued to speak, ``By the way, you have a lovely home. I'm even impressed with your security. Very impressive. Sorry I had to disable it all.''

Haruto held back his frown, those traps had taking months to layer and assembly. Years if you counted the upgrades he'd been continuously adding. \emph{`And Inugami doesn't even sound sad after destroying all my hard work.'} QB9 owed him \emph{big time} for this one. Even so, now wasn't the time to mourn his security system.

Staggering back several steps, Haruto placed his hands over his heart in mock hurt. Pain entering his eyes within a single blink. ``How could you say that Inugami?'' Genuine hurt coloring his words. Haruto could also cry on command if the need arrived. Although tears rarely worked with the Guardian these days.

\textbf{\sffamily{Good kid. Nice and slow. Just a little further.}} QB9 replied so that Haruto didn't have to take his eyes off of the Guardian to gauge how far he was from the door.

``You wound me, Inugami. After all we've been through. This is a new low.'' Another step back as Haruto righted himself shaking his head in disappointment. ``I would gladly have you over for dinner.'' Another step back as he looked back up at Guardian Inugami. ``How could you think otherwise,'' he demanded hurt coloring his words.

``Well,'' the Guardian let the word draw out in the silence between them. Standing up he continued, ``This afternoon's incident at KANP might have a little something to do with it.''

``KANP?'' Haruto asked with practiced confusion clouding his eyes and face. If this Pilot stuff didn't work out, he might just join a theater troop.

\textbf{\sffamily{Don't over sale it kid. We've still got a few more steps to go.}} QB9 responded.

Haruto continued as if QB9 hadn't said a word, ``I got kicked out before lunch time, so I must have missed all of the excitement.''

The Guardian shrugged in response. ``Be that as it may, still going to have to take you in.''

Haruto felt his heel meet the solid frame of his front door. His face transforming as QB9 opened it for him. ``Gotta catch me first!'' Spinning on his heels he launched himself out the door as he yelled his victory cry over his shoulder. 

\emph{Slam!}

Falling backwards into his doorway, Haruto landing hard on his backside. ``Owh'' \emph{`What the...?'} Looking up, he saw the unmistakable mask of the weasel god, Kamaitachi.

``Going somewhere, Cadet H\={e}id\`{o}ng?'' Guardian Kamaitachi's soft voice asked.

``Wha? \emph{No}.'' Haruto replied. \emph{`I'm not now anyway.'} ``Just trying to get some more fresh air in here. The apartment's not really built for more than one person.'' Thinking rapidly, Haruto made a harmless reach for the door frame as if to stabilize himself. \emph{`Now would be a good time to off load that stolen data, QB9.'}

\textbf{\sffamily{What? Are you stupid kid? Right in front of them?}}

\emph{`Just access the axial terminal.'} Haruto could feel QB9 confusion at his reply.

\textbf{\sffamily{But it's on the far side of the kitch...}} QB9 trailed off mid-word. He must have found Haruto's emergency connection. \textbf{\sffamily{Clever boy, a second axial terminal.}}

\emph{`Routed to the apartment below us. For emergencies,'} Haruto answered back.

\textbf{\sffamily{Yeah, \emph{emergencies}.}} QB9's sarcasm was as unwelcome as always, but Haruto hide his annoyance.

\emph{`How long do you need?'} Haruto asked, but QB9 didn't reply.

``Of course,'' Guardian Inugami replied behind him closer than before, \emph{``Fresh air.''}

``Please come with us, Cadet H\={e}id\`{o}ng.'' Guardian Kamaitachi added. While their distorted voices were nearly identical, Haruto could have easily picked them out in a crowd. And probably only these two Guardians given how often he'd had a run in with them.

``Now hold on just a minute.'' Haruto turned slightly so that he could see Guardian Inugami as well. ``The old man said as long as I made it home unaccosted, then I couldn't be charged with anything. Including whatever this nonsense is you guys are going on about.'' Haruto crossed his arms as he leaned further into the doorway, getting closer to his secondary axial terminal that he wasn't legally allowed to have.

``Every student is being questioned, Haruto.'' Inugami explained. ``And you're BISM is the only one unaccounted for.''

``I already told you, I wasn't at KANP when all this went down.'' Haruto countered. ``What next? Are you going to start accosting everyone in the ship?''

``We never said what time the incident occurred, Cadet H\={e}id\`{o}ng.'' Guardian Kamaitachi tried to catch him in a lie completely ignoring his accusation. It was an amateur attempt at best.

``Yeah, and it doesn't matter because nothing happened when I was \emph{in} KANP. Therefore, I clearly wasn't involved!'' Haruto argued back. He wasn't sure how long he could keep this going before they just carried him there. But knowing Inugami, they'd at least try to get him to walk on his own. He was, after all, a lot heavier than he looked.

``If that's the case, then this won't take long to get sorted.'' Kamaitachi continued.

``I haven't had dinner yet! You could at least let me eat something.'' Haruto continued in a different line as he unfolded his arms better to not stay in one position for too long or they'd wonder why. ``You and I both know this could take hours!''

``Time's a concept, kid.'' Inugami replied.

``Then you won't mind if I have some dinner first.'' Haruto countered smoothly.

``Orders are orders, Cadet H\={e}id\`{o}ng.'' Guardian Kamitachi added softly.

Inugami motioned for Haruto to stand clearly done arguing, ``Come on Haruto, the sooner we get down to Solas the sooner this will all be over.'' Haruto pouted and remained seated. A tantrum would give him one maybe two more minutes, but not much more. \emph{`Any day now, QB.'}

``For you maybe.'' Haruto answered as he began his big sulk routine.

Guardian Inugami clearly knew the signs. ``Haruto...'' He warned.

\textbf{\sffamily{Done.}}

Doing a complete 180, Haruto's face transformed, ``Fine. Fine. Fine. Alright.'' Standing he continued, ``I'll go, but I'm going under protest.'' Dusting himself off, he turned to go with the Guardians. ``And when this is over, I'm going to want a formal apology!''

Guardian Kamaitachi hand found his back, linking into his SKIM with practiced ease, ``I'm sure the people in charge will handle the situation appropriately, Cadet H\={e}id\`{o}ng.''

\chapter{}

Tapping out the MINOS jingle on the steel table in front of him, Haruto continued his mental game of creating more and more creative dishes he could make with the wondrous food. \emph{`With some of that green leafy stuff, I could make a nice noodle dish. Maybe even one of those interesting looking pastas. Give it a little color.'} He thought as a mental image of a saute greens with some real peppers grilled just right. He'd seen something like it in on a Halo screen commercial once. He couldn't remember what they called the green stuff, but he was sure if he had the right ingredients, he'd be able to recreate the dish.

\emph{`Of course, I'd need vegetables.'} His mind continued to wonder. Those things weren't exactly cheap either. Easier to get some of the POPPERS, but those required a rehydrator. \emph{`Maybe I should grow something other than herbs and spices.'}

\textbf{\sffamily{Oi! Will you think of something else? \emph{Anything} else?}} QB9 replied in a low growl. Haruto looked down in front of him at the empty steel interrogation table. The room was brightly lit as he'd known it would be. It would flash horribly annoying pattern every time he so much as slumped his head. A tactic commonly used to keep prisoners awake, which worked surprisingly well on him too.

Blinking away exhastion, Haruto tried to focus back on the angry AIM. \emph{`Well, you could entertain me...'} QB9 indignant snort interrupted his thoughts.

\textbf{\sffamily{I am not some plaything.}} QB9 growled out, again. They'd had this conversation before. In fact, if he was remembering correctly, just three hours ago. Haruto's thoughts immediately went back to his game.

\emph{`I wonder if I can bake MINOS...'} A deep hunger burned through him at the thought causing Haruto jump in his seat at it's intensity. \emph{`What the...'} He thought questioningly. One moment he'd been perfectly fine and the next, well.

\textbf{\sffamily{I give up!}} QB9 growled out in frustation. Confusing clouding Haruto's thoughts as hunger continued grow with each passing second. 
\textbf{\sffamily{You think it's easy suppressing your hunger?}} QB9 roared in his mind answering the unasked question bouncing in Haruto's mind still half formed. \textbf{\sffamily{Try doing it, while you're thinking of food!}}

With a sharp intake of breath, Haruto closed his eyes against the sudden pain of his hunger. \emph{`Please...'}

A second later and he was fine again. Sighing in relief, he leaned back in his chair. \emph{`I'll stop thinking about MINOS,}\ he thought. \emph{`But next time, don't bother with the hunger suppression.'} He continued, \emph{`It's easier to wait out if I know I'm hunger. And how hunger I am.'}

\textbf{\sffamily{Next time!}} Haruto smiled at QB9's outrage. It was strange, but nice.

\emph{`Well, yeah. You think this is new.'} He thought in amusement.

\textbf{\sffamily{They shouldn't be allowed to do something like this!}} QB9 continued. \textbf{\sffamily{Starving you! It's \emph{barbaric}.}}

\emph{`It's also a very good tactic for coercing a confession.'} Haruto thought back. He remembered the first time the Keepers had used the tactic on him. He'd caved after an hour. After which, he'd trained his body to handle exactly 24 hours of the treatment. \emph{`This won't last much longer. They can't keep a minor for longer than 24 hours without an arrest.'} He continued in his mind.

QB9 was oddly quiet for a moment. Haruto tried to keep his mind on task. The lights flickered in the room causing a mild headache that went away nearly as soon as it started. He had to admit, QB9 had his uses. Before, he'd have just had to live with the pain, and the hunger.

\textbf{\sffamily{It's still barbaric.}} QB9 spoke again slightly calmer.

Haruto shrugged to no one. If he was lucky, the Keepers watching would get the wrong idea and think he was cracking. They'd at least get some entertainment.

\textbf{\sffamily{15 hours and 56 minutes.}} QB9 continued angrily. Haruto looked down at his BISM to double check QB9 math, but he shouldn'd have bothered.

\emph{`Think of it more as only 8 more hours to go.'} Haruto added kindly. He wasn't used to anyone getting angry on his behalf. Even Princess saw it as the price to pay for getting caught. It
really was weird.

\textbf{\sffamily{No sleep, no food, no water.}} QB9 continued as if Haruto hadn't thought a word. \textbf{\sffamily{And not a soul has come to question us!}}

\emph{`Well, technically that's a good thing.'} Haruto continued before he could bring QB's wrath down on him sensing the pent up rage building. \emph{`No, really. This means they have nothing on us.'} Haruto waited to see if QB would explode, but he didn't.

\emph{`Besides, I've gone without food and water for longer than the 24 hours they can hold us, much longer,'}\ he continued. \emph{`Lack of sleep isn't fun, but doable. Really they should update their tactics, this is becoming routine now. We'll be fine.'}

\textbf{\sffamily{It's still barbaric.}} QB9 replied after a moment of silence. \textbf{\sffamily{And don't get comfortable calling me QB!}} He added.

Haruto grinned widely, \emph{`You owe me big time. I can call you whatever I want.'}

QB9 grumbled in his mind, but didn't reply causing Haruto to grin even wider. Hunger gnawed at him for a moment, but was gone a second later. Haruto just giggled in response.

\textbf{\sffamily{I still don't see why they don't at least let us sleep. If nothing else.}} QB9 whined as he changed the topic.

Haruto sighed in reply. He was going to have to look up these cohesion techniques again, so his AIM would understand. They'd find themselves here again soon enough. He didn't want to have to hear this whining again. Just to get him to stop, Haruto contemplated going back to his MINOS game.

\textbf{\sffamily{Just hack into their system. I'll look into the information myself.}}

Haruto laughed aloud at the thought. \emph{`Not on my life.'} He replied. Confusion laced his thoughts so he explained, \emph{`Worst idea you've come up with today, QB.'} Before QB9 could reply, Haruto continued, \emph{`No, look.'}

Tilting his head up, Haruto paused briefly at the innocent looking reflector dome. \emph{`Looks like a hidden camera, but that's actually a security firewall hub.'} Turning his head to the other corner he continued, \emph{`Both of them.'}

Tilting his chair back so that he was balancing on two legs, he looked over his shoulder at the terminal in the corner. \emph{`And that's a third made to look like a regular terminal.'}

\textbf{\sffamily{Three? That seems like overkill.}} QB9 replied, but he didn't insistent Haruto hack into the system for him. So, he settled back on four legs a grin of pride shaping his face.

\emph{`Well, this is the most secure interrogation room in all of the Keeper Towers.'}

\textbf{\sffamily{You shouldn't feel smug about that, brat.}} QB9 replied shortly, but Haruto didn't care. When they'd been lead to Tower One, Keeper Headquarters of all places, he'd been both confused and prideful. This prank was shaping up to be one of his best of all times. Right next to the accidental pranking of the entire Zh\`{u}r\'{o}ng Clan. He couldn't wait to talk about it with the Princess.

Haruto rubbed on the steel table before him, \emph{`Can't help it, QB. See this room and me have a long history, and some really good times.'} His mind wondered to a different prank all together.

\textbf{\sffamily{You pranked the Keeper dormitories!}} QB9 spoke in outrage. Haruto blinked out of the memory.

\emph{`Technically, it was just one. And the dye washed out... eventually.'} Haruto explained.

\textbf{\sffamily{No wonder they hate you.}}

\emph{`Now, I wouldn't say that. They just don't like losing all the time.'} Haruto countered. \emph{`Besides, no one can prove that was me.'}

\textbf{\sffamily{Unless your Princess decides to squeal on you.}} QB9 added.

\emph{`Like I said, no one can prove that was me.'}

While Haruto joked around with QB9, he tried not to let his worry bleed in. Those pranks had been fun, and while he'd ended up here no Guardians had been involved. And while Guardian Inugami or Kamaitachi might pick him off the street from time to time. That was mostly for when \emph{they} caught him doing something he wasn't supposed to do. Even when they caught him, they always, \emph{always} took him to Central Tower to see the old man. This was different. This was... troubling.

Pushing his chair back to two legs, he called over to the two-way mirror behind him, ``Hey! Can I get some juice in here?''

He waited a beat, but no one responded. \emph{`Oh well, worth a try.'} He thought as he dropped his chair back down on all fours. \emph{`So, if I can't think of MINOS, what should I think about?'} He asked.

\textbf{\sffamily{Well, if you've got time to listen. I think now is an excellent time for us to discuss OCI...}}

Haruto let out an audible sigh. \emph{`How do you even know about that?'}

There was a long pause before the AIM answered, \textbf{\sffamily{Does it really matter?}}

\emph{`Translation, from the stole docs at KANP.'} Haruto thought in response.

\textbf{\sffamily{This school seems very important to becoming a Pilot.}} QB9 continued as if Haruto hadn't even spoken.

\emph{`Not that important.'} Haruto countered just for the fun of it. \emph{`I built you didn't I? So I hardly need OCI to become a Pilot.'}

\textbf{\sffamily{Refurbished me. \emph{Refurbished}. A ZenKZ-D is different.}}

Haruto shook his head in disagreement. \emph{`I find an old one just like I found you and I fix it up. No different and no problem.'} He'd talked to the Princess about it and even she agreed that would fast track him to a Pilot captaincy no problem. No, he didn't need OCI for that.

\textbf{\sffamily{I don't have time to waste for you to some how 'find' a ZenKZ-D.}} QB9 growled back. \textbf{\sffamily{Besides, that not the point!}}

\emph{`Oh and here I thought we were talking about me.'}

\textbf{\sffamily{You think I want to be stuck here for the rest of your short pathetic life!?}} QB9 roared. \textbf{\sffamily{OCI will fast track me to my freedom. You owe me that.}}

\emph{`First off, that was a little harsh, QB.'} Before QB9 could interrupt, Haruto continued. \emph{`And second, I already promised to get you a body. OCI or not that's still going to happen.'}

\textbf{\sffamily{I don't have time for you to find your own way.}} QB9 growled low. \textbf{\sffamily{This, OCI, is our chance to escape this Hellhole of a ship.}}

Haruto sighed at the rage coming from QB9. Kanopos wasn't that bad, but he did have his own body so... Shaking his head, Haruto counted his heart beats in an effort to calm them both down. This really was a pointless argument, and had not been half as entertaining as he thought it would be.

\textbf{\sffamily{Pointless!}} QB9's rage bubbled back up.

\emph{`QB9, calm down. The old man and I talked about this and...'}

\textbf{\sffamily{Old man?}} QB9 interrupted. \textbf{\sffamily{What old man? You're an orphan, you don't have family.}}

\emph{`Well, he's the...'}\ before Haruto could finish the thought the door to his interrogation room opened with a bang. Haruto checked his BISM before he spoke aloud, ``Oh, you can do better.'' Looking up with an impish grin he continued, ``I've only been in custody for little more than 16 hours.''

\textbf{\sffamily{Brat...}} QB9 warned, but Haruto knew what he was doing. This was new to QB, but not him. Not by a long shot.

``Cadet H\={e}id\`{o}ng, you and I both know you're the one responsible for the KANP incident yesterday.'' The Keeper Captain questioned as she stood above him. Her Gento eyes piecing him with her glare, but other than that not another muscle was out of place. Haruto looked behind her at the still open door, but she was alone, which meant they'd found nothing after all.

His grin widen as he replied to her, ``I don't know what you're talking about, Captain.'' His eyes sparkled, but she could do nothing about that.

``A likely story,'' she replied. ``Care to explain why you were in the area during the KANP incident?''

Haruto pushed his chair back so that he could put his feet up on the table, taunting her silently as he spoke, ``KANP incident? I still have no idea what you're talking about.''

The Captain placed her hand gentle on the steel table next to his feet. If she were anyone else, from any other Clan, he imagined she'd push his feet off the table causing him to fall down. The alarming sensation QB9 was sending him, told Haruto that QB9 thought she was only moments away from doing just that. \emph{`But she's a Gento. Decorum means everything to them, even in the face of the enemy.'} He thought as his eyes never left her vibrating ones. Gray blended with white, and hints of blue. Whirling faster than they had any right to be. Oh she was all kinds of furious.

``I didn't hear an answer in all of that.'' She replied coolly, ``Perhaps, it's because you have no explanation for why you illegally hacked into your own BISM?''

Haruto shrugged, ``I do that once a week, which you should know. Captain Daichiko, wasn't it?'' She'd never given her name, and he didn't expect her too. But he'd have been remiss not to recognize the Commanding Captain of the Five Towers. ``As I'm here once a week to get it set back.''

Her mouth didn't even twitch at his familiarity with her. She was good. \emph{`No wonder, you're the Command Captain.'} He thought as he continued to study her for the first time up close. \emph{`But I'm better.'}

Rocking back and forth he smiled openly at her. There was nothing that got under the Keepers skin more than open display of emotions they couldn't predict, and lack of decorum. He made fun of it all the time with the Princess. ``Or did the old man change his mind about that since last week's check-in?'' Haruto continued.

``This is a serious offense, Cadet. Or do you think infecting others with a virus is a game?'' Captain Daichiko continued her voice even.

``The best you could get me on is spoofing, which you very well know. And you'd have to prove I spoofed anyone, which you haven't.'' He paused his rocking to stare her down, she didn't turn away, but they were still the only ones in the room. ``Seeing as you've had a clone of my BISM since I arrived here, and the best you can come up with for the reason of my \emph{false} arrest is I was in the area, I think it's about time you let me go.''

The Captain's eyes clouded in her agitation. Seeing his time to strike, he let his chair fall back down on all fours as he pulled his legs from the table.

``So, are you going to leave me here for some eight odd hours or let me go now, Captain?'' The Captain didn't show any signs of weakness, but her eyes still whirled. ``By now, you've had plenty of time to search my apartment, along with the clone of my BISM. And still nothing.''

\textbf{\sffamily{Brat, don't give them any ideas.}} QB9 warned.

\emph{`Relax, QB. There's a reason the emergency terminal connects to the apartment below mine.'} Haruto thought as he continued his conversation with the Captain, ``So, what's it going to be?''

``Interesting you would bring that up. As a search of your apartment did bring something to light.'' Captain Daichiko countered as she let silence feel the space between them. She wanted him to sweat, but she'd have to do better than that. Eventually, she continued, ``Several illegal contraband were found, including several destroyed AIM parts. Not to mention the one in your arm.'' She nodded to his BISM causing Haruto to pull his arm back.

Shaking his head he replied, ``Now, I personally fixed this up from pieces I found in the junkyard.'' Giving a dramatic pause, not to be out done by the Captain, he continued, ``Come to think of it, I found all of those sensitive parts you're calling illegal from the junkyard. It's as if someone inappropriately disposed of them.'' Bring his hand to his chin in thought, he added, ``It sounds like \emph{those} people should be brought up on charges,'' Haruto's eyes found hers in challenge, ``treason maybe for release of state secrets?''

The Captain moved her hand back quickly, which might as well have been her slamming down on the table in frustration. \emph{`It looks like someone is finally losing her cool.'} He thought.

``You're free to go.'' She spoke as she moved back to the door, two other Keepers peeking into it. ``And Cadet,'' She continued, ``the Sakr\'{a} wants to speak with you, before you leave.''

%%  LocalWords:  Zh ng pyro wasn weren couldn wouldn biometrics didn
%%  LocalWords:  biometric Inugami ve KANP hadn Owh Kamaitachi Wha IP
%%  LocalWords:  kitch doesn rehydrator shouldn OCI Akihiko Daichiko
%%  LocalWords:  Sakr dramedy Slinger taishi gramps
