\chapter{}
The chamber used as a waiting room in Tower One was as interesting as a blank wall. In fact, it might as well have been a blank wall, or at least four of them. No place to sit, no Halo screens for entertainment or just commercials. \emph{`Man, I love to watch commercials.'} Haruto thought as he began to hum the MINOS jingle.

\textbf{\sffamily{Don't you dare start that now.}} QB9 voice growled low in warning.

\emph{`Yeah, yeah, yeah. Hunger and stuff.'} He thought back as he turned his mind away from his lunch options. \emph{`Maybe I'll get the old man to buy me something...'}

\textbf{\sffamily{That includes thoughts of any kind of food, brat.}}

Haruto waved away QB9 comment with his hand as he leaned against one of the blank walls. With this much free time on his hands, and nothing to do with his imagination, he couldn't help but think about something more troubling. He'd gotten picked up at his house. The old man had never allowed that before. But now... \emph{`This sounds like a dangerous precedent.'}

\textbf{\sffamily{You never did tell me who this 'old man' was.}} QB9 asked again.

Haruto considered the question, but before he could answer, a section in the blank walls slide away as someone entered. \emph{`No, not just someone.'} Haruto thought. This \emph{someone} he'd recognize anywhere.

``Hiya, Princess. They didn't get you too?'' He asked, ``Just can't imagine, you in the interrogation rooms.'' He continued. \emph{`Like, no one in their right mind would interrogate Kanopos' princess.'} Of course, he never said the Keepers were always in their \emph{right} mind, so...

``Fortunately, no. Ghost Hacker,'' she replied as she made her way towards him leaning on the wall next to him. ``Although given your familiarity with the place it can't be all that bad.''

\emph{Buzz. Buzz.} Haruto's BISM vibrated with a new message.

``Ghost Hacker? Never met the guy, or girl.'' He added as he tilted his head down to look at his BISM, but a movement of the Princess' hand stopped him. Haruto gave her a questioning look in return. Her cloudy eyes met his blue ones before turning to the room at large as if to say we are not alone.

``Perhaps you are correct.'' She spoke aloud. ``The Ghost Hacker would never have been caught.'' She continued a hint of amusement coloring her words. Haruto rolled his eyes in return at the long standing joke they had.

Turning to the matter at hand, he had no idea how he was supposed to read her message without looking down at his BISM, and QB9 wasn't being helpful either. \emph{`What a surprise.'} He thought sarcastically.

``The Ghost Hacker is a fairy tale Princess.'' Haruto answered. ``Us real folks have to interact with society.'' He continued knowing she'd read between the lines.

\emph{Buzz. Buzz.} His BISM went off again, and now Haruto knew it was the Princess sending him messages. How, well he had no idea. Her hands were in sight laying against the wall behind her. For once not in her formal coveralls, something he knew her tutors and father would not have approved of.

When his eyes returned to hers, all he got in answer was a challenging look before her eyes drifted back to his BISM. ``Perhaps, but I find the ability to be in more than one place essential for a Pilot.''

\emph{`Oh! Pilots, her AIM. Of course they can do hands free messaging.'} Haruto looked at his own BISM with some heat. \emph{`Well, that's assuming they have a useful AIM.'} QB9 didn't so much as flinch at the comment.

\textbf{\sffamily{I'm not a toy, brat.}} QB9 replied calmly.

\emph{`Yeah, a toy would at least be useful.'} Haruto answered. Pausing for a split second he continued, \emph{`Come on QB9, please.'}

There was another moment when Haruto was sure the AIM would ignore him, but a second later and words appeared in his left-hand vision.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: I warned you not to get caught.\\
    MPrincess: See, you figured it out.
  }
\end{quote}

Haruto shrugged as he changed the topic, ``So not held against your will. Can't imagine you're here for the Keeper's Famous hospitality.'' In his head he continued, \emph{`QB, how to do I reply?'}

\textbf{\sffamily{Just think it and I'll do the rest, kid.}} QB9 replied helpfully as the Princess' lips tightened as she held back a smile.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    GhostHacker: Princess meet QB9. The AIM with his own opinions on everything.\\
    MPrincess: A pleasure, SB3-QB9.
  }
\end{quote}

``I've never had a problem with the hospitality.'' The Princess answered amusement tinging her voice. ``Of course, I've always been on the right side of the interrogation rooms, so...''

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: Why that's very forward of you. But if Haru hasn't told you yet, then I'm not sure I should.
  }
\end{quote}

\emph{`Hey! What the heck are you asking her?'}

\textbf{\sffamily{Haru?}} QB9 questioned instead causing Haruto flush.

``Ha!'' Haruto's bark laugh was more forced than it would have been otherwise. ``You've got me there.''

\emph{`You didn't answer the question.'}

\textbf{\sffamily{None of your business, pipsqueak.}} QB9 answered.

``I'm waiting for my Honorable Father.'' The Princess answered.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    GhostHacker: Not the words I'd use to describe him.\\
    MPrincess: Haruto...
  }
\end{quote}

``It would seem that the KANP incident had a very large reach. Although not the normal Ghost Hacker MO.'' The Princess continued, a slight question in her voice.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    GhostHacker: Blame that on QB9. Someone had to get sticky fingers.
  }
\end{quote}

\textbf{\sffamily{Seeing as I have no fingers, I hardly see how that comparison is relevant.}}

``Well, I'm sorry to hear that. I wish I could help, or I did before spending more than 16 hours in room 4.'' Haruto replied aloud ignoring QB9.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: Only 16? The Captain must be going soft.
  }
\end{quote}

\textbf{\sffamily{Soft!? You call that soft? We're starving here!}} QB9 complained.

In one smooth motion, the Princess reached into her coveralls and pulled out a protein bar.

``By the Gods, be praised!'' Haruto praised in thanks as he ripped the bar out of it's packaging and shoved it down his throat. ``Mmmmmmmm.''

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: I'm glad you like it.
  }
\end{quote}

``You're welcome.'' The Princess said aloud as she handed him another one. This one he ate slower.

\textbf{\sffamily{Will wonders never cease. You do know how to chew.}} QB9 commented drily.
    
\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: Although, if you hadn't gotten caught, you wouldn't have had to endure the standard enhanced interrogation tactics.\\
    GhostHacker: I told him as much, but QB decided to suppress our hunger, which just made routine interrogation painful.\\
    MPrincess: I didn't know AIMs could suppress hunger.
  }
\end{quote}

\textbf{\sffamily{I'm hardly your average AIM.}} QB9 replied. The Princess nodded her head slightly in agreement.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    GhostHacker: \emph{Anyway.} I'll have you know we didn't get caught per se. The Guardians just showed up at my place.\\
    MPrincess: I'm not surprised to hear that. Classified documents went missing.
  }
\end{quote}

\textbf{\sffamily{If they didn't want it stolen, then Lieutenant Cho shouldn't have been linked to the secure database.}} QB9 responded. \textbf{\sffamily{They should be glad it was just us and not someone else taking advantage of his stupidity.}}

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: I agree.\\
    GhostHacker: Of course you do. You're not the one who had to waste nearly a day because your AIM couldn't stick to the unclassified stuff.\\
    MPrincess: Somehow, I doubt SB3-QB9 instigated the KANP prank.
  }
\end{quote}

Haruto blushed as he started to lick the wrapper.

\textbf{\sffamily{Ha! See not my fault.}} QB9 answered. \textbf{\sffamily{And don't lick the dang thing. Have some manners.}}

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: I think I like SB3-QB9.\\
    GhostHacker: You're not stuck with him every second of everyday.
  }
\end{quote}

``So eh...'' Haruto began aloud not sure what he could say. The Princess just tilted her head slightly in response. Clearly not going to help. QB9 also seemed amused. ``Yeah, speaking of KANP, you never...'' Haruto cut himself off to rephrase his question, ``I didn't know you had an officer ranking already.''

\begin{quote}
  {\fontfamily{cmss}\selectfont
    GhostHacker: Do you even need to go to OCI?
  }
\end{quote}

``It's ceremonial at best.'' The Princess answered aloud.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: Nothing has changed, Haru.
  }
\end{quote}

\textbf{\sffamily{Changed?}} QB9 questioned.

``Ah, that's too bad. I guess you can't put in a good word for me, then?'' Haruto continued ignoring QB9 for the moment.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: Perhaps you will be able to assist Haru in this endeavor.\\
    GhostHacker: Later, Princess.
  }
\end{quote}

\textbf{\sffamily{Later? Later what?}} QB9 demanded confused.

``After the KANP incident, I'm afraid my word would have little weight.'' The Princess answered.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: And Uncle was extremely upset about the whole thing. If you're trying to look for alternatives, Haru, this is not the way.
  }
\end{quote}

``Now, I don't know anything about this KANP incident talk. Must have missed all the excitement.'' Haruto replied aloud.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    GhostHacker: Was worth the shot.
  }
\end{quote}

The Princess sent an image of an eye roll.

``Even so, your reputation proceeds you. And unfortunately, solid recommendations are hard to give to a renown prankster.''

``Prankster? Me?'' Haruto asked as he bat his eyes at her. ``I've since changed my prankster ways. Now, I'm a serious KANP student.''

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: Laying it on thick, aren't you?
  }
\end{quote}

``If that's so, then I'm sure you'll manage OCI on your own merits.'' The Princess answered aloud.

\textbf{\sffamily{You know, while this conversation's all shooting stars and star bursts. What's stopping you, oh so lofty Moon Princess, from telling on us. Classified documents and all.}} QB9 interrupted their banter.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    GhostHacker: QB! How dare you!
  }
\end{quote}

The Moon Princess tilted her head in their direction clearly having received the message.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: Haruto is my best friend. I trust him with my life.\\
    GhostHacker: Hey, you don't have to explain anything to him.
  }
\end{quote}

Haruto was going to have words with the AIM later about his disrespect.

\textbf{\sffamily{If you're such great \emph{friends}, why are you hiding it now.}} QB9 challenged.

Before the Princess could respond, the wall panel slide open. ``K\={o}taishi,'' the biggest pain in Haruto's SKIM called out.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: You're making that face again. Stop Haru. He's not that bad.\\
    GhostHacker: Says you.
  }
\end{quote}

QB9's thoughts questioned their conversation, but the Princess soon answered it, ``Honorable Father,'' she took her hands off the wall placing them in their place within her coveralls.

\textbf{\sffamily{What kind of father calls his offspring by a title?}} QB9 questioned still confused.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    GhostHacker: That asshole, that's who.\\
    MPrincess: I'd like to remind you both that he is still my father.
  }
\end{quote}

``We don't have time for you to engage in ideal chic-chat.'' The cold man continued eyes already turned to the door. Haruto never seemed to exist with this man.

The Princess turned her head in Haruto's direction, ``I'll see you around Haruto, but hopefully not here again.'' She called out easily causing a smile to appear on Haruto's lips.

Gento Yozora's eyes pierced Haruto as he waved goodbye.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: And SB3-QB9, I never said for Haru to pretend we weren't friends. He did that on his own.
  }
\end{quote}

The connection dropped as his friend left. Leaving him red in the face. \emph{`I swear she's got a game out of making me blush'} He thought.

\textbf{\sffamily{I hate to admit this, but she might be a keeper.}} QB growled in his head. \textbf{\sffamily{No, not that kind of Keeper, kid.}} QB continued in Haruto's confusion. \textbf{\sffamily{You know what, never mind.}}

\emph{Buzz. Buzz.}

Opening the message normally, Haruto wasn't all that surprised to see that it was the Princess again.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: One down, Haru.
  }
\end{quote}

QB9's confusion was palatable. Before Haruto could explain, the side panel reopened. Walking in was an elderly looking man in the ceremonial white coveralls of the Sakr\'{a}. The white cloth was layered in a flowing garment that Haruto knew from experience hide body armor. Some of the most powerful on Kanopos, or so he was told.

``Haruto,'' the Sakr\'{a} sighed as he took Haruto's appearance in.

``I swear I didn't do it, Gramps.'' Haruto lied easily.

\textbf{\sffamily{GRAMPS!}} Haruto flinched at the sound, which the old man seemed to take for something else. \textbf{\sffamily{The Sakr\'{a} is the \emph{old man}!}}

``Yes, I'm sure,'' the Sakr\'{a} replied not even trying to hold his disbelief. Beckoning him out of the waiting room, they made their way out of Tower One. ``What I'm not happy about is you being kicked out of KANP again. How will you become a Pilot if you don't pass school?'' The old man continued.

\emph{`It's really not that big of a deal, QB.'} Haruto answered the AIM as he kicked at the ground. He knew the speech that awaited him. He'd heard it hundreds of times now. Stay in school, don't get into trouble, and study hard. 

\textbf{\sffamily{The leader of this rickety old ship is your \emph{Gramps}.}} QB9 continued in a disbelieving tone. \textbf{\sffamily{That's something you lead with.}}

\emph{`Yeah, well I don't.'} Haruto replied in thought. QB9 growled in annoyance causing Haruto to stifle a sigh. \emph{`We're not related by blood or anything, so really not that big a deal. Besides, I think you'll prefer stuff about the Princess.'}

\textbf{\sffamily{Why? Only one of us has a crush on her.}} QB9 replied.

\emph{`First off, we're friends. And second, the reason why I said our discussion earlier about OCI was pointless...'} Haruto was interrupted by QB9.

\textbf{\sffamily{This again, kid.}} QB9 started, \textbf{\sffamily{OCI is...}}

\emph{`Will you just give me a second to explain.'} Haruto waited for silence. \emph{`It's pointless because I'm already planning to go.'} He finished.

\textbf{\sffamily{Then why...}} QB9 trailed off.

\emph{`I was bored and you just assumed.'} Haruto answered.

\textbf{\sffamily{Then you lied.}} QB9 answer bubbling up. \textbf{\sffamily{You do need OCI.}}

\emph{`I didn't lie. I don't need OCI to become a Pilot.'} Haruto continued over QB9's anger. \emph{`But it is the only place me and the Princess can be partners together. We've been planning this since we were ten. That's what OCI means to me. To us.'}

\textbf{\sffamily{And one down? What's that supposed to mean?}} QB9 questioned.

\emph{`The test, the big bad final exam.'} Haruto replied as he swung his feet at the floor as he followed the still lecturing Sakr\'{a}. \emph{`There's two parts, well three, but I'm gifted at the simulators so.'}

\textbf{\sffamily{I'm for the Showcase.}} QB9 answered following the conversation. \textbf{\sffamily{A unique AIM.}}

\emph{`Yeah, pretty much.'} Haruto answered. \emph{`That's why I made you anyway. To get into OCI, to become a Pilot.'}

\textbf{\sffamily{And the Practical. How will you pass that?}} QB9 questioned.

\emph{`That's part two, and I'm still working on that one.'} Haruto replied. QB9 was contemplative at the answer. \emph{`Hey now, make no mistake, even if this doesn't work I'm still going to become a Pilot and together the Ghost Hacker and the Moon Princess will make history.'}

\textbf{\sffamily{There's three Pilots to a Unit, kid.}}

Haruto shrugged at the response, not really caring.

``And you haven't heard a word I've said, have you little Haruto?'' The old man questioned as he smiled down on him.

Haruto smiled back sheepishly as he ran a hand through his hair. ``Sorry Gramps. I guess I'm just too hungry to concentrate.''

A light pat to his shoulder, ``Why don't I take you to lunch. You can tell me how you've been. My treat.''

``Woo hoo!'' Haruto shouted as he jumped into the air taking the lead. He was going to get MINOS after all.

\chapter{}

Exiting the high arches of Sanctuary Park's main entrance, Haruto dipped onto Shinodake Main, aka the northern section of Gento Sector. \emph{`Better known as Prayer Alley, QB.'} Haruto spoke to his AIM as they continued to familiarize the AI with Kanopos proper.

\textbf{\sffamily{I don't see the point of this running around.}} QB9 replied. \textbf{\sffamily{I have the layouts of the ship from public and KANP classified records. This is just excessive.}}

Haruto rolled his eyes before ducking down a side street. \emph{`Was this on it?'} He questioned already knowing the answer. QB9's grumble brought a smile to Haruto's face. \emph{`That's what I thought.'} He continued, but the prickle of QB9's frustration didn't go away, so he rephrased his response. \emph{`Look QB, this ship, the great Kanopos, is just as alive as you are.'} 

\textbf{\sffamily{Some how I doubt that.'}} QB9 snapped back.

\emph{`Well, not like that.'} Haruto sighed in reply. Some times QB9 was difficult just to be difficult. \emph{`But the results are the same.'} He continued he feet running down another off the record back alley. \emph{`Sections fall apart, Sectors grow, change, morph with the growing people who live in them. Upgrades, legal and illegal both take up empty spaces creating new walkways in the process.'} Stopping above a grate he stomped on it, \emph{`And tunnels, all of which are illegal and 60\% unaccounted for.'}

Moving on he couldn't help the love and appreciated he had for \emph{his} ship. Each Sector was alive even if QB9 could never understand. It grow and shrank, changing to it's own rhythm. Kanopos was \emph{alive}. At least in all the ways that counted. And there was no one who knew it like he did. Not even the Princess with all her special access.

\textbf{\sffamily{60\%? How do you even know that?}} QB9 growled in frustration. Haruto blushed in response. \textbf{\sffamily{Of course it has to do with your Princess. At least someone is taking the security of this ship seriously.}}

\emph{`Hey! Gramps does what he can, but he's got bigger worries as do the Keepers. Besides, the tunnels are small and the majority of them have overheated since their creation.'} Haruto responded. He'd argued the same thing to the Princess. They'd come to a compromise. They didn't give up his detailed knowledge of Kanopos, while he helped her generate up-to-date maps of the ship.

\textbf{\sffamily{Why can't I just use the Princess' map?}} QB9 whined. \textbf{\sffamily{Then we can actually do something productive.}}

\emph{`Because the files are too big, and the transfer times are ridiculous.'} Haruto replied absentmindedly as he stopped by one of his old terminals long since decommissioned. \emph{`We can't risk it.'}

\textbf{\sffamily{Hump.}} QB9 replied as they entered silence. \textbf{\sffamily{I take it you used to play around here.}} Came his soft reply to unmasked nostalgia.

\emph{`Something like that.'} Haruto replied as he turned down the street to a main road, T\={o}ji Avenue. Taking in the large building he continued. \emph{`I used to live here.'}

\textbf{\sffamily{Solstice. One of the thirteen Gento sponsored Orphanages.}} QB9 supplied unnecessarily.

\emph{`You can't imagine how much trouble I got into back in the day.'} Haruto continued.

\textbf{\sffamily{I supposed that explains why Sanctuary Park is the first place you take me too.}} QB9 replied.

Haruto ignored the tune. \emph{`If you follow this street and take a left, small alley you can't miss it, you'll make it to Sanctuary Academy. Most of the Keeper brats end up there.'} And if not for meeting the Princess, he'd probably have gone too. Maybe end up a Keeper, maybe not. The old man had been pushing KANP pretty heavily back then too.

\textbf{\sffamily{Keeper brat?}} QB9 questioned, but before Haruto could answer he was interrupted by a familiar shout.

``Haruto? Hey!'' Turning to the voice, Haruto was meet with an all to familiar face. ``I figured you'd be hanging out with one of your fellow Cadets on your off day and not walking around the Sanctuary?'' She questioned politely.

Haruto snorted in response. ``And get teased endlessly about being the only Cadet \emph{helping} with KANP security? The Gods help you, Naomi.'' The young woman smiled amusingly back at him.

``It's an honor to get to serve so closely with the three DOMAINE High Commanders. The Sakr\'{a} surly smiles upon you Cadet \emph{H\={e}id\`{o}ng}.'' The emphasize on his family name was part bitter, part longing.

\textbf{\sffamily{Why?}} QB9 questioned. \textbf{\sffamily{You're both orphans.}}

\emph{`More than that, we're both Keeper brats.'} Haruto added. \emph{`But they call her Ensign Naomi for a reason.'} Haruto could still feel QB9's confusion so he elaborated. \emph{`Most orphans are without a family name, QB.'}

\textbf{\sffamily{I have no family name. That doesn't make me any less than you.}} QB9 replied sharply.

\emph{`Not to me or the Princess, no. But she'll never know her ancestors. Even you know that.'} Haruto wasn't sure how he could explain more so instead he spoke to Naomi. ``We both know me helping out at KANP six days out of the week isn't an honor position. Maybe for a Techie like you, but for me?'' Haruto shook his head. ``The old man is unjustly punishing me. For a crime I didn't commit!''

Naomi relaxed minutely showing she'd been a Keeper brat much longer than he had. ``You mean a crime no one can \emph{prove} you committed.'' She corrected.

Haruto shrugged easily in response. ``Same difference.''

``Still you aught to be grateful for the opportunity. Commander Lee is the top of her field.'' Naomi continued.

``Yeah, I'm sure of it, but that doesn't change the fact that all I'm allowed to do is move some stuff around.'' Haruto hopped in disbelief. ``My genius wasted on manual labor!''

Naomi smiled openly, ``Like anyone would let you near a terminal or console.''

Spreading out his arms as to say, what can you do about it, he turned his attention to Solstice. \emph{`Still, it would have been nice to work with Commander Chin\={o} instead. There was so much we could have done to help with cyber security.'}

\textbf{\sffamily{I'm surprise you care so much.}} QB9 commented. \textbf{\sffamily{Doesn't this mean we'll have an easier time regaining access to the KANP system.}}

\emph{`Yeah, but it's not the same.'} Aloud he spoke to Naomi, ``Anyway, I thought you were from Wayward?''

``Mentorship program.'' Naomi answered easily. ``It's still pretty new.'' 

Haruto looked at her in confusion. \emph{`Then why haven't I heard of it.'} 

She continued before he could voice his thoughts. ``I'm sure your reputation is why you haven't been asked to join.''

Folding his arms across his chest, ``I'd make a great big brother!'' Puffing up he chest he continued. ``Us Keeper brats got to stick together.''

Naomi let out an undignified snort, ``You barely count.''

``I'll have you know, I've probably spent more time with the Keepers than even a Keeper Cadet.'' He countered with a large grin.

A full laugh escaped from Naomi's reserve stance, ``I bet you have.'' There was a small pause before she continued, ``What are you doing today, anyway? You're going in the wrong direction for Sanctuary Park.''

\textbf{\sffamily{Ask her directions to a place of knowledge gathering.}} QB9 replied. \textbf{\sffamily{The Princess wasn't sure which Archives was open access. And I don't want to have to go by all of them.}}

Haruto's lips tensed. \emph{He'd} not been apart of that conversation, which meant QB9 was talking to \emph{his} best friend without him.

\textbf{\sffamily{Oh get over it. We need to study if we're going to make it into OCI, and I don't see you seeking out the information.}} QB9 paused for a split second. \textbf{\sffamily{Honestly, I'm not sure we'll be able to do it using the Princess' curriculum.}}

``Actually,'' Haruto spoke aloud admitting defeat to QB9, ``I'm looking for, well like a place to study and like get knowledge and stuff.'' He trailed off uncertain. \emph{`There's got to be a place like that, yeah?'}

Naomi raised an eyebrow all other facial features like worked steel. ``You mean a library?''

``A what?'' Haruto questioned. Even QB9 seemed stumped by the term. The confusion lining his face caused a glint to appear in Naomi's eyes.

``Dear Goddess. You better hope this Pilot stuff works out for you, because you'd make a poor Techie.''

Haruto blushed at the comment, his lips jutted in a pout, which just caused Naomi's lips to turn into a slight smile. ``Do you know a place or not?''

``Of course I do,'' she replied wiping the smile from her lips, but her eyes still held lingering amusement. Bumping his BISM with her own, she blinked into a frown. ``By the Goddess, what type of encryption do you have on this thing?''

Haruto ignored the question. \emph{`QB, could you open a link, please.'} QB9 grumbled but opened the link without any fuss. The Princess might be on to something with this being nice to the AIM thing.

Naomi eyed him, but her fingers tapped on her BISM all the same. ``Here, the coordinates to KOAL. Honestly, though you should already have it's location on file. It is, after all the biggest library on Kanopos.''

``Thanks,'' he muttered as QB9 showed him the location. 

``It's a great place to study. Just be careful. The old woman guarding the place isn't one to cross. We're all pretty sure she's a retired Guardian or something.'' Naomi warned.

Haruto waved her off as he turned to leave, he knew how to handle Guardians. ``Have fun baby sitting.''

``Good luck, Haruto. We're all routing for you.'' Her eyes saying what he already knew. Keeper brat or not, if he made it into OCI, he'd be the first orphan to do so in more than a decade.

Haruto gave her two thumbs up before disappearing into the nearby alleyway. \emph{`Yeah, no pressure.'}

\chapter{}
Kanopos Open Access Library was hard to miss. In fact, Haruto had passed it a bunch of times on his way to and from KANP. Or at least when he wasn't running late and could take Main.

\textbf{\sffamily{When are you ever \emph{not} running late, kid?}} QB9 added sarcastically.

Haruto flushed in embarrassment at the realization he'd not passed it once since obtaining the AIM. \emph{`This week's been rough.'} He replied.

QB9 gave an undignified snort in response. \textbf{\sffamily{How did you not know about this building?}}

\emph{`I don't usually use the front door to public buildings, QB.'} Haruto replied as he started towards said front door. Even now, it felt wrong. But that might have had more to do with the look of the building. 

\textbf{\sffamily{Look?}}

\emph{`I've been banded from all public Farms, since I was eleven. I thought this was one of them.'} He continued in thought. Given the size of it, he would have been hesitant to break his band for a Farm.

\textbf{\sffamily{Farms?}} QB9 questioned bring up an image of the Krai's breeding Nags.

\emph{`No, not that kind of farm. A Console Farms.'} Haruto paused a meter from the door to pull up an image for QB9 to review. \emph{`Buildings with wall to wall Halo screens and virtual consoles. Lockers of some really impressive tech, tablets with more power than the basic KANP stuff I get assigned.'}

The image went blank as QB9's attention returned to Haruto. \textbf{\sffamily{Do I even want to know how an eleven year old gets banded from all these so called \emph{Farms}?}}

\emph{`Too much imagination.'} Haruto supplied as he continued towards the door. At QB9's annoyance he elaborated. \emph{`I accidentally uploaded a virus to the network. And let's just say Gramps wasn't too happy that he had to replace a tenth of the Kanopos operational network.'}

QB9 snorted in mild approval. Standing in front of the KOAL doors, Haruto was surprised when they slide open for him. \emph{`I guess this really isn't a Farm.'} Haruto thought as his eyes found the bio-scan from habit.

Walking into the building expecting at any moment for an alarm to go off, Haruto hesitantly took in his surrounds. A handful of Halo screens, plenty of desk space and access lines. But several sections seemed to be dark with \textbf{\textsc{Down for Maintenance}} signs plastered in front of them.

\emph{`Well this is a little bit of a let down.'} Haruto thought feeling QB9's silent agreement as he continued into the building properly passing the front desk without a backwards glance.

``And just where do you think you're going, Cadet H\={e}id\`{o}ng?'' An aging woman with sharp eyes peered at him from behind specs. A crooked, wrinkled finger pointed in his direction stopping him in his tracks. 

\emph{`Like who even wears specs these days?'} Haruto questioned in surprise. Eye sight could be fixed in half a second. 

``We don't have anything for you to steal and this building has the highest security of all Archival spaces.''

Haruto looked around again spotting only second rate surveillance tech. \emph{`Sure, and I'm a lost Prince.'} He thought sarcastically, QB9's amusement lingered at the back of his mind. ``Then it's a good thing I'm here to learn.'' Haruto replied as he continued on his way.

``Not so fast.'' She continued directing him to her desk at the front. ``If you're really here to \emph{study} then you'll have register your BISM for access.''

``Ah... okay.'' Haruto walked hesitantly to her desk her eyes gleaming like a predatory.

``And you'll need to sign, these, read these, and complete several tests about proper KOAL usage.'' Her eyes glanced at him. ``And that's assuming you only want archival access.'' Batting her eyes challenging, a dark smile crossed her lips.

``Ah...'' \emph{`You've got to be kidding me.'} Haruto thought as his eyes glanced at the dense text of just once of the documents placed in front of him.

\textbf{\sffamily{Just do it kid.}} QB9 encouraged lightly.

\emph{`Easy for you to say. You're not the one signing your soul to this she-devil.'} Haruto countered eyeing the paperwork as if it were cursed by Tsukiyomi himself. And if any fairy tale hand taught him anything, it was never to make a deal with the devil.

``Of course,'' the old woman purred, ``If that's too much work for you. You know the way out.''

A frown touched Haruto's lips at the woman's trumpet. As if a little paperwork would be enough to send him away. Pulling the documents to him, he set to work. \emph{`QB9 reads these, and makes sure everything's on the up and up.'} He demanded with no complaint from the AIM. He'd never backed down from a challenge and he wasn't going to start today.

Two hours later and Haruto was done with the ridiculous tests and paperwork. Pulling his BISM from the registration system, Haruto stared down the old woman daring her to deny him entry now. ``And remember \emph{Cadet}, if you so much as blink in the wrong way. Not even the Sakr\'{a} will be able to save you.''

``Blinking's not against the rules.'' Haruto snapped back at her as he hurried away.
\emph{`Remind me to prank her later, QB.'}

\textbf{\sffamily{With pleasure.}}

They walk over to a desk and Haruto takes out his KANP tablet and hooks it up to an access point. Signing into the KOAL network too nearly all day. But the real kicker was trying to access the archives.

\emph{`This is ridiculous.'} Haruto thought.

\textbf{\sffamily{It's not that bad.}} QB9 answered.

\emph{`This connection speed is a joke.'} Haruto

QB9 was silent for a moment, \textbf{\sffamily{I've tested it, and it should be fine. How many firewalls does your tablet have?}}

\emph{`Not that many.'} Haruto placed the tablet down on the table. With a sigh he continued. \emph{`But the wireless adapter is ancient in this thing.'}

\textbf{\sffamily{Console?}} Looking over, while the place wasn't wall to wall, it was pretty busy. \textbf{\sffamily{There in the back.}} Haruto turned his head in the direction QB9 indicated.

A set of four consoles were completely undisturbed despite the busy place. It was odd. \emph{`Perhaps they're broken.'} Walking over to them, Haruto sat in the farthest one and logged on. Fractions of a second later and he was staring at the archives home page.

``By the Gods,'' Haruto cursed as he sat down fully. \emph{`That has got to be the fastest connection time, I have every had the pleasure of using.'} Haruto looked around at the rest. All state of the art, maybe even beta type machines.

QB9 voiced Haruto's question, \textbf{\sffamily{I'm not sure why these aren't being used. They're clearly the best this library has to offer.}}

\emph{`Gift horse, QB.'} Haruto replied as he downloaded the Princess' curriculum to get started.

\textbf{\sffamily{What's that supposed to mean, kid?}}

\emph{`Beats me,'} Haruto thought turning his focus on the console. \emph{`The Princess said it once, even explained it. But it started with a battle so I tuned it out.'}

QB9 tisted in annoyance. \textbf{\sffamily{Of course you did.}}

Haruto sighed at the dense text in front of him. At least it was in the common tongue, but the Gods only knew how he'd rather be playing or chatting with the Princess.

\textbf{\sffamily{Focus kid.}} QB9 commanded.

\emph{`Easy for you to say, apparently you talk to the Princess all the time without me.'} Haruto whined.

\textbf{\sffamily{You know we can't now. There's no point in senseless whining.}}

Haruto grumbled but nodded all the same. QB9 was right, the Princess was busy preparing for her big trip. \emph{`I still don't see why she's got to be gone for so long. Her dad's just punishing us, again.'}

\textbf{\sffamily{You should be glad it's only six months. A full trip through the Empire can take years.}} 

\emph{`Not helping, QB. Not helping.'} The last thing Haruto needed was for her old fart of a dad to keep her off ship for that long. Official transmissions sucked. They took ages and were always screened before hand. What if he did an awesome prank? How was he supposed to fill her in? What if her dad bored her to death? How was he supposed to distract her?

\textbf{\sffamily{The Princess is made of tougher stuff than that. You'll both be fine.}} QB9 countered interrupting his death spiral. \textbf{\sffamily{Besides, this way you'll actually stick to a studying schedule.}}

Looking at the dense text, he wasn't sure about that.

\starbreak

\emph{`Why would anyone need to know trade agreements for the Kanopos Clans?'} Haruto questioned as he skipped the rest of the document.

\textbf{\sffamily{She \emph{is} a Clan heir.}} QB9 supplied, but Haruto could feel his slight desperation at their situations. QB9 couldn't seem to help but pull up the study guide, which was just a condensed list of everything the Princess had learned in the last four plus years that she thought might be KANP related. Haruto knew for a fact she'd taken out all of her internal Clan politics. She'd ranted at him enough about it that he was sure he could recite the dynamics and their origins in his sleep.

\emph{`What are we going to do, QB?'} Haruto asked as he scrolled down the document. \emph{`We don't have...'}

Haruto's thoughts were interrupted by the harsh sound of his name from a familiar voice. ``H\={e}id\`{o}ng.''

Blinking up in confusion, Haruto spotted Helian Aeliana standing beside him looking unusually annoyed. \emph{`Does she want something?'} He thought as he voiced the question. ``Helian? You need something?'' He asked.

\textbf{\sffamily{Wasn't her hair silver earlier this week?}} QB9 questioned. As the fellow Cadet's bright pink hair. 

\emph{`I told you she changes hair colors faster than her mood swings.'} Haruto thought. ``And clearly her mood has changed.'' He commented under his breath at the increasingly annoyed look crossing the girl's face.

``You're sitting at my console.'' She replied tensely arms crossed. ``Surely you wondered why no one was sitting at it?''

Haruto looked around at the empty seats next to him, before looking back at the annoyed girl. \emph{`She can't be serious.'} ``Ah...'' He started to reply, but QB9 interrupted him.

\textbf{\sffamily{Don't be stupid brat. She's the Guild heir, try not to insult her.}}

\emph{`Try not to... QB, there are three seat next to me. She can use one of those.'} Haruto countered.

\textbf{\sffamily{Boy, you must be a fool.}} Haruto went to correct him, but QB9 talked over him. \textbf{\sffamily{State-of-the-art equipment. Everyone else is using the old versions. \emph{Everyone else}.}}

Haruto looked again at the other occupants logged on to different consoles. \emph{`So what? I'm just supposed to give up the console because she's having a bad day.'}

\textbf{\sffamily{Yes.}} QB9 continued over Haruto's objectives. \textbf{\sffamily{Think of it this way, we move to the next seat, and she doesn't use mommy and daddy to get us kicked out.}} QB9 paused to let the thought sink in. \textbf{\sffamily{Think carefully, kid.}}

Haruto nodded minutely as he turned back to the console to log off. Hopping off the seat, he moved to the console next to it hoping Helian hadn't claimed them all. When she made no move to stop him, he relaxed and logged in to the new console. ``All yours.'' He called over his shoulder as she seemed frozen to the spot.

At his voice, Helian settled down next to him so Haruto went back to work. \emph{`You think there's some way to use those KANP documents you liberated to cross-references the Princess' study guide?'} He questioned as he began the process of generating all of his previous archive searches.

\textbf{\sffamily{Not without sending all kinds of alerts.}} QB9 answered. At his unspoken thoughts he continued. \textbf{\sffamily{And I can't use the network at home or the GH network either. The Keepers will pick up even the hint of those document signatures.}}

\emph{`Well dang.'} Haruto thought as he continued to bring up window after window. Beside him, he was a little surprised to hear nothing but even breathing. Helian was well known for her study habits. She also happened to be ranked first in their Cadet class in just about every category. 

``You just going to stare at the screen all day?'' Haruto questioned as his fingers flew across his keyboard absentmindedly. ``'Cause that would make me moving kinda pointless.''

\textbf{\sffamily{What are you thinking kid? You're all over the place.}} QB9 questioned.

\emph{`I can't just be friendly?'} Haruto thought. QB9 answered with palatable disbelief.

``I'm just thinking.'' Helian answered.

Haruto snorted in reply, ``What do you even need to study for anyway?'' He continued. ``Don't you already know it all?''

``I've never claimed to know everything.'' She snapped in frustration. ``\emph{Some} of us have to study and review to even have a chance at getting into OCI.'' She continued with a bite that surprised him, ``We can't all be born into a \emph{Clan}.''

Haruto shrugged in response grateful for once that QB9 was letting his mind run wild. The frustration Helian expressed wasn't new, but for the first time he really took a look at it. Her. She had a desperation about her that was surprisingly familiar. Even so, he had doubts that her concerns were real. ``You all seem the same to me with the only exception I find being the Princess. But you're no Moon Princess, are you, Helian?'' 

At her silence, he looked over at her briefly to see her lost in thought. Searching.

\textbf{\sffamily{What makes you think she'll help us?}} QB9 questioned. 

\emph{`Because if she's truly worried about getting into OCI. Ranked number one in our class, and all. Then it's because she's not from a Clan, QB.'}

\textbf{\sffamily{The Showcase?}} QB9 questioned as Haruto turned back to his screen. \textbf{\sffamily{You think we could help?}}

\emph{`I made you didn't I?'} Haruto replied.

``Thanks.'' She called out abruptly.

\textbf{\sffamily{For what? You didn't do anything?}}

\emph{`Didn't I?'} Haruto countered as she moved to type on the screen. 
``No problem.'' The Princess called him a conductor of light all the time. But QB9 still scoffed at his thoughts. \emph{`You got to understand people, QB.'} He told the AIM. To Helian, he continued ``Besides, I could tell you were having a bad day.''

``Can I ask why you're even here?'' She questioned hesitantly. ``I mean, not to sound rude, but you've never taken your studies seriously before, so...'' She trailed off the question obvious in her voice.

\emph{What are you doing here?}

And for once, it was a question he would gladly answer. With a large grin in place, he held up a finger, ``First off, if you've got to say `not to be rude', then you're definitely about to be rude.'' 

\textbf{\sffamily{Kid, really? Now's the time when you want to joke.}}

\emph{`Everyone likes a good joke, QB. Everyone.'} Haruto replied with an even wider grin. Holding up another finger he continued. ``And second,'' he paused for dramatic effect as if sharing a secret. ``I've got to get into OCI, too.''

``You? OCI?'' She questioned. His smile turned mischievous at her doubt. 

``Yup!'' Turning back around he started typing once again, ``No matter what it take!''

Not even a half a second later, she spoke again. ``You'd need a 92\% on the next six ranking exams to break even. And that's assuming they don't raise the test score average from 70\% to 75\%.'' 

\textbf{\sffamily{Did she just calculate all of that in her head?}} QB9 sounded impressed. Haruto grinned even wider, his smile recognizing a kindred spirit. ``Whatever it takes, right?''

Helian shook her head in disbelief, but a small smile founds it's way to her lips. ``Yeah, whatever it takes,'' she parroted softly, but Haruto knew he just might have found his answer.

If there was anyone who knew the KANP curriculum it would be Helian. And it would seem they had a similar goal in mind.

QB9 chuckled darkly as Haruto begin to skim the next article. The Princess would be proud.

