\chapter{}

%% Haruto walking with Aeliana to the nice part of Blue Sector.

%% Keeper patrol passes them giving him a long hard look, but otherwise leaving him unmolested. 

%% The Keeper on the right nodded at Aeliana as they passed. A soft ``Cadet Helian'' following in their wake. It was beyond unnerving. He still half expected for the Keepers to turn around and arrest him.

%% \emph{`Any moment now.'} He thought hesitantly. But they didn't even blink back in their direction. Just like the last three patrols they'd passed. ``Where are we going again?'' Haruto questions. 

%% Aeliana gave a long low sigh as they passed another of the increasingly fancy warehouses of Blue Sector. He'd never been anywhere near this section of Blue Sector. And for good reason, as Keepers patrol were barely five minutes apart.

%% \textbf{\sffamily{Surely the great Ghost Hacker can get passed them.}} QB9 replied.



Arriving at RL2 warehouse, Aeliana led Haruto to the side door. Hooking her BISM into it, the door slid open seconds later. \emph{`I'll have to remember to add Haruto onto the access list.'} She thought as she made her way up the stairs in the dark. Her hand trailing the wall as she traced her steps into the side office.

While she'd never been to this particular warehouse, all of the RLs had the same layouts. Bring back memories of following her father around on his warehouse rounds. Everything was so big back than. She'd thought, she would be the next Guild leader. Be just like her father.

\emph{`At least on paper.'} She added in her head as she found the lights and flicked them on. Haruto hovered at the door entrance his steps unsure for once. His eyes took in the empty little room.

``Ah?'' He began confusion in his voice. ``This is ah, great place.'' He continued.

She sighed as she rolled her eyes. ``Turn around.''

He did so, and his eyes lit up in excitement. While the boy was generally annoying, his face was unusually expressive. Even when he was simply playing a role, he seemed to buzz with pent up energy. When he was mad about something, it showed. And so, his pure excitement wasn't hidden under a well maintained emotionless mask. It was these times why she wondered why they needed to hid their feelings. Masking them only half as well as the Gento Clan.

Dismissing the thought for a later time. She felt a small smile edge at her lips as she joined the loud redhead at the doorway. The warehouse laid out before them. ``Welcome to warehouse RL2. Currently not in circulation.'' She couldn't help the smug sound of her voice. RLs were the largest warehouses the Guild owned in Kanopos. They would not lack for room here.

Haruto turned to her with a hint of worry, ``And you're sure your folks can spare the place?'' He asked. ``I mean, look at it?'' His arms waved to take in the empty space below them. His face a mask of disbelief. She looked down on it again from his eyes. All that empty space on a ship were space was one of the most valuable commodities right behind oxygen and water. From his perspective, it would be incomprehensible how they could pay for this space and not use it.

\emph{`But we are using it.'} Aeliana thought. Knowing of the histories of the Helian's use of empty warehouses. Given what she was beginning to suspect about her parents and the Guild, she could not ignore the difference between this warehouse on paper and in real life. But Haruto didn't need to know about that side of the Guild. So she choose a different response. The official response.

She shrugged away his question she answered without looking him in the eyes, ``It's an emergency warehouse. We have them all over the Kanopos, just in case something goes wrong. The Guild has a reputation to uphold, so warehouses like these are maintained, empty.'' Finally she turned to look him in the eyes. ``And if all goes well, then it should never get used.'' She continued. ``And if it doesn't, there are two more emergency RL warehouses in the Lower Level ready to use as backup. So we should be fine.'' She added as she made her way out of the small office. 

Three backup RL warehouses were all that her father had managed to obtain here on Kanopos. It wasn't an ideal situation given the number of warehouses in active circulation, but the Clans had put their foot down on her father buying more for worse case scenarios. The KTS was, after all, limited in space. Even so, Aeliana knew that outside of a catastrophe, the Guild merchandise would be alright. \emph{`And mother has plans to off load what can't be stored.'} The Guild would take a hit, selling in such a hurry, but not a big one.

Haruto's footsteps were surprisingly light as she scrambled down to the main room. Jumping down in his haste as she continued leisurely down the stairs. Of course, if something like that happened. Aeliana was sure that her mother wouldn't bother storing much at all here given the KTS class as a war ship. No, even if something that devastating happened on Kanopos, the Guild would not be using all three RL backup warehouses. Maybe not even two of them. So three was probably overkill, but it was also their lucky number and constantly used as a measure for the number of backups. Aeliana herself kept three backup copies of her notes in three separate locations. \emph{`Better to be safe than sorry.'} She thought, her father's words coming to her automatically. And the Helian's were never sorry about anything.

As Aeliana stepped off the stairs, she turned away from the soft harried footsteps of her newest companion. With the light, she easily located the access panel. Plugging her BISM, her biometrics opened all access to the compartments not listed on any blueprint anywhere. She'd secure it on her way out. Tapping on her BISM, she made a note to get Tommy to update the system here for her use, and take it off the Guild network. The last thing they needed was for someone in the Guild to use RL2 to store something off the books. \emph{`Better to just take it completely off the list, than risk Haruto getting involved the Guild business.'} The kid was already a target by the Keepers. The Guild would do best if they stayed clear of him altogether.

``What you doing!?''

Aeliana jumped nearly out of her SKIM at the loud voice to her left. Placing her hand over her racing heart she counted backwards from twenty. A technique she'd needed to master after working with the redhead. ``Haruto.'' She began opening her eyes to see him fiddling with the access panel. ``Dang it Haruto, stop that.'' She swatted at his hands. ``You don't have the access clearance yet.''

Haruto gave her a look that said he was confident that wouldn't matter at the end. She hesitated. Not sure how regular security clearance was given to other Guild members. Not wanting to find out, she took Haruto by the elbow and marched him away from temptation.

She didn't let him go until they were in the middle of the main room. Spinning around she let Haruto take it all in, ``What you can see now is everything on every blueprint of the warehouse.'' She started. ``It has the latest air filtration system that recycles oxygen 70\% more efficient than the mega filtration system used by KTS Kanopos.'' She continued. ``Although that's not really hard.'' She muttered under her breath. Aeliana grabbed Haruto before he go off and pull the whole thing apart. ``And no you can't take a look at it.'' She added harshly seeing the red deflate.

Walking over to the nearest wall, she continued. ``Every RL backup warehouse is also equipped with a separate generator and climate control. All Guild patented tech.'' She didn't hid the smugness from her voice as Haruto looked around in awe. Now in her element, she couldn't help but continue bragging about the Guild tier one warehouses, which but even the best the Gento clan had to shame. ``Built on shock absorbers. Nothing that happens to the ship will effect this room.''

Finally arrive at the wall she traced the panels looking for the right section. She knew it only by location, and her mind had was fiercely calculating the polar coordinates to the hidden panel as she spoke. ``The walls are noted to have composite insulation, which is the cheapest, most reliable tech currently on the market.'' \emph{`There.'} She thought as she pushed hard on the wall.

Haruto took a sharp intake of breath as the panel moved to reveal an empty space. ``But Guild tech has designed a slightly more expensive version that's takes up a forth of the space leaving room for these hidden compartments.''

Haruto poked his head into the space as his hands moved over the hidden compartment. Aeliana stood back and watched. His face moving as if he were currently having an in-depth conversation. The guy was just short tempered enough to be arguing with himself. His mind moved faster than she'd ever expected. It was just a pity he couldn't focus it. \emph{`Not that he'd every be as quick witted as me, but he could really do some damage if he could just focus for five minutes.'} He thought as he seemed to have won some kind of argument turning back to face her.

``We'll use thing to hid our grayish things when we're done.''

Haruto nodded in agreement, ``Like you blaster.'' He pointed to her waist. Hidden as it was she was a little surprised he knew it was there.

``Actually, I had something else in mind.'' She replied. Ignoring the fact that the blaster would be a little more blackish than gray with regards to legality.

``Yeah?'' He questioned clearly confused.

She sighed. ``The books about the relics.''

Haruto still looked confused, ``Why would you need to hid those?''

She closed her eyes and counted backwards from twenty. ``You do know it's illegal to talk about let aloud read about other Gods.'' She continued when she'd calmed down. ``Which is why I don't talk about it at the library.''

Comprehension seemed to dawn on him. ``Oh.''

``Yeah, \emph{oh}.'' She mocked him. Shaking her head. ``Haruto it's basic knowledge that the other Gods are heretical topics. If we're caught with those books, well...'' She trailed off. He father could possibly get her out of that kind of mess, but she'd never be able to return to the Jade Empire at least not as Helian Aeliana. As for Haruto, she had no idea what would happen to him.

``What happens if a Keeper just happens upon the wall?'' Haruto asked a slight frown to his face. ``There doesn't appear to be a lot of secure to this.''

Aeliana shook her head. ``That's what I was doing earlier. Opening up all of the hidden panels. Normally, it's closed, or only one panel is open at a time. But I figured it was best to show you where they all were.'' Haruto looked to ask another question but she stopped him. ``And no one from the Guild is accidentally going to come in here. I'm taking this warehouse of the network.''

``And your positive none of these secret compartments are on any blueprint, even unofficial ones.'' Haruto continued to question his eyes surprisingly serious.

She shook her head in answer. ``We keep only one set of blueprints and that are the official ones.'' Turning to the panel she closed it. ``Either you know where they are or you don't. We keep no record of their location. Someone has to show you where they are, which is what I'm doing now.'' Aeliana moved along the wall as she continued her mental location. Technically what she was saying was true. But there was a formula to their position, so while she'd only been shown the formula and warehouse RL3, she could calculate where the others where based on the position of the corner office.

``Here's another.'' She said as she stopped.

Haruto waved away her silent request to continue showing him the locations of the hidden panels. ``I'll figure them all out later.'' He replied as he looked away, clearly deep in thought.

``You'll need high level security access to open them, so I'll have Tommy add you to the system.'' She continued.

``Huh? What?'' Haruto asked coming back to the world around him. ``Security access?''

\emph{``Yeah.''} She replied. ``Otherwise, you won't be able to use them.'' She shook her head. Sometimes he was a little slow.

``Oh, no. Don't do that.'' He replied. She gave him a look. ``Look, if you give me security access to them, the the Keepers might be able to use my level of access to find them.''

``The Keepers? Really?'' She responded with a roll of her eyes. \emph{`They'd have to be daft to try and search this place.'} She thought, but aloud she simply said, ``I don't think well have to worry about them here.''

``Just in case. Better safe than sorry. And I'm sure I'll find my own way into the system.'' He replied as he looked in the direction of the box.

Just the thought of him hacking into the Guild network was a scary prospect, especially if her mother ever found out. ``Haruto. I swear if you make a mess of the Guild's system, you'll live to regret it.'' She swear only to have Haruto wave her off. ``I'm serious. If my parents find out you hacked the \emph{security} system, then we're both in trouble.'' Haruto finally looked over at her. ``And if I get in trouble for this, \emph{you} will be the one to regret it.''

``Alright, alright, alright.'' Haruto replied giving her a surprisingly good Keepers'{} salute. ``It'll be like I was never there.'' He continued. ``I'd hate to get on the wrong side of the Guild.'' Haruto paused. ``That's not supposed to be good for one's health.'' He continued in a low mutter.

``Anyway.'' Aeliana continued. ``It shouldn't take long for use to get settled here. Tommy can have everything we need in within a day or two once he knows what he's ordering.'' She turned as she looked at the open space. \emph{`I should put in a gun range, too. Better than shooting in the house.'} She thought. She'd have to figure out a way to get it hidden, but she was sure there would be a way.

Door opened suddenly causing both her and Haruto to spin in that direction. Blond hair popped out with hands raised. ``Hey now little Stargazer, don't shot.'' Erik replied as he made his way inside the warehouse. ``Tommy said you where here.''

Aeliana relaxed as she made her way over to the man who was like a brother to her. ``Erik, your back.'' She smiled as she wrapped him in a hug.

``Alright, alright.'' He replied pushing her off of him. ``Enough of that, your going to make me all tear eye and stuff.'' Turning to Haruto he nodded in his direction. ``So who's the little man? Always figured you had a height requirement.''

``Hey!'' Haruto replied glaring at Erik. Aeliana rolled her eyes at them.

``Erik, meet H\={e}id\`{o}ng Haruto. Number one prankster in Kanopos and my current study partner.'' She replied. ``Haruto, meet, J\o rgensen Erik. Pretty much my older brother, although not by blood.''

``The body's mostly water anyway. Bonds of loyalty are much stronger than that.'' Erik replied with a smile. ``Nice to met you shorty.''

Haruto shuffled his feet around but didn't respond with more than a grumble.

Pulling Erik aside and away from the grumbling redhead, she spoke. ``Sorry about him, while he wasn't raised in a barn he might as well have been.'' She spoke.

``Nah, it's alright. I know guys like him. You could even say I was one, once upon a time.'' Erik replied with a mischievous smile. ``Anyway, wanted to be the first to tell you the old man's going to be home for dinner.''

Aeliana clapped her hands together in her excitement, ``Really? Dad's back?'' Erik nodded his smile even larger.

``Stuck with paperwork and the like, but he'll be properly free come dinner time.'' Erik's smile turned a hint smug clearly with holding information.

``Did he?'' She asked.

``Yup! Two relics from Water Country.'' Erik roughly messed up her hair. ``And I've even got a couple of stuffy old tomes to go with them. Tommy's making digital backups as we speak.''

Aeliana didn't even care that Erik had ruined her hair. This was the best news yet. ``When will can you move them here?''

``Got to get the proper transfer papers, but then I'll have them moved from the docks. Shouldn't be too long.''

Aeliana smiled until she heard a crack noise of panels shifting. Turning sharply she'd completely forgotten about Haruto, who had managed to find another hidden panel. ``Ahhh, don't mind me.''

She rolled her eyes as he quickly closed the panel. Best to get him out of the way for a little while. ``Why don't you go make a list of the things you want in the warehouse?'' She asked. Her eyes adding, the get out of here part. For once, Haruto seemed to get the message.

``Sure, be back in a jiffy.'' He replied as hurried out of the warehouse.

``He's not so bad.'' Erik replied.

``No, I suppose not.'' She replied as Erik gave her a sideways hug.

``Didn't say he was a replacement. Just that sometimes it helps to be around people, is all.'' He continued.

Aeliana didn't respond. Instead her eyes looked at a hidden panel she'd used once years ago. It seemed silly now, how much she'd wanted, no needed, to know about the Nordic Gods. On the surface a way to be closer to her adoptive brother, but in reality she'd wanted to know about Ilia, whose blonde hair was even brighter than Erik's. It had been a waste of time, of course, as she knew now that the Amur clan had no ties to the Nordic Kingdom. But had lead to her and Ilia bonding over it after she confessed about the illegal activity.

Erik squeezed her again pulling her out of the memory. ``Hey nice blaster, by the way.''

``Not you too.'' She replied as she pushed him off her. Pulling the gun out of its hiding place she held it out to Erik's waiting hand. ``How did you even know I was wearing it?''

``Its the way you hold yourself.'' Erik said as he examined the blaster holding it out to fire. He locked it back up before handing it back. ``Good work on that one. My first one wasn't nearly as balanced.''

She couldn't hold back the smug smile she had at the compliment. Even so, she didn't respond. Patting her shoulder lightly he surveyed her warehouse. ``I'll have something installed. You'll want to practice in an actual range.''

She nodded. As she followed him around, imagining the place in full swing.

``And don't worry. This,'' he nodded to the blaster she'd put back into her makeshift holster. ``Will remain between the two of us. No need to tell the old folks about everything.''

She nodded in agreement. The less her parents knew, the better.

\chapter{}

This chapter is pretty much filler if I can't think of something to place here.

What to do? What to do?

Something to do with the Heidong Effect?

Maybe meet Anko and build relationship between him and Iruka?

I'm just not sure how I can fit it into the timeline. Other than random chance in Red sector.

Haruto's eyes feel onto the room at large. There were more people here than he'd thought would bother on an off day.

QB9 - give me access to KOAL and I'll have all their information in a heart beat

\emph{`I'm not hacking into the system. I don't know any of their weak points and we just spent hours getting access to the place.'}

* In KOAL, Haruto observes people...

Haruto rolled his eyes. \emph{`Look, QB. There are two ways a master hacker like myself gets information.'} He replied. \emph{`The first of course is to hack into the system, but that needs days of prep to do successfully.'} Sitting down at a empty table, Haruto pulled out his KANP tablet and logged onto the KOAL network. \emph{`Strategy number two, while it sounds easy is just as hard. Listen.'}

\textbf{\sffamily{Listen!?}} QB9 raged back, but Haruto was only half listening to him. \textbf{\sffamily{I listen \emph{just} fine.}}

Haruto waited a beat longer as he continued to listen to the students around him.

\textbf{\sffamily{\emph{You} are the one with the \emph{listening} problem!}} QB9 continued, getting angrier by the second.

\emph{`Did you know that those six students are sixth years KANP cadets?'} Haruto replied.

\textbf{\sffamily{What?}} QB9 spoke, his rage settling.

\emph{`And those three are from the same Gento orphanage program.'} Haruto nodded his head in the direction of three student, two boys and a girl huddled together over one Haloscreen.

QB9 paused briefly, \textbf{\sffamily{How can you possible know that?}} He questioned darkly.

\emph{`Body language, coveralls, size and height.'} Haruto could tell he had QB's attention so he continued. \emph{`See that group over there, four girls all with the same badge on their coveralls?'} Knowing he had QB9 attention he continued. \emph{`They're orphans, but live together in one of the apartments at the end of Solas. Closer to the Sakhalin sector than the Gento sector.'}

\textbf{\sffamily{How could you possible know that without hacking their BISM, or the KOAL register?}} QB9 questioned.

\emph{`Easy. That badge is for orphanage 5A in the Sakhalin sector, which can only hold a small number of kids. All orphanages prioritize the younger children, which means those girls live in group.'} Haruto replied. \emph{`And before you ask. I know they live together because of their familiarity with each other. They laugh ease, brush each other SKIMs without thinking about it. That's group life.'} 

There was a long pause. \textbf{\sffamily{Why don't you live in a group home?}} QB9 questioned. 

\emph{`I was born in Kanopos, or so the old man tells me, but my mom, she was a Heidong. Our clan, just like that Haibeu and the Gento took genetic modification to for space travel to the extreme.'} Haruto pulled up a picture of a smiling blue-eyed red haired woman. Her ears pointed, eyes slanted, and nose just a little sharp, animalistic markings on her face. \emph{`I look different, scare to some. And without a Clan to share in my oddity, well...'}

\textbf{\sffamily{She was a very beautiful woman.}}

Haruto's hand traced her face, \emph{`Yeah, she was.'}

