\chapter{}
Haruto twirled a thumb drive between his fingers as he walked down the streets of Blue Sector on his way to his newest hangout, the warehouse. Given the time of day, he was more than sure she'd be there. \emph{`Think she won't mind the additional requests?'} Haruto thought. 

\textbf{\sffamily{If you'd just let my write the food list from the begin, we would have already had everything by now.}} QB9's rough growl was cut off by Haruto's own thoughts.

\emph{`Yeah? And let you forget the MINOS.'} Haruto replied just has hotly shaking his head hard. \emph{`Besides, I wasn't sure that was included.'}

\textbf{\sffamily{And I said, it didn't hurt to be prepared.}} QB9 replied. \textbf{\sffamily{But no one listens to me.}}




``Anything.'' Haruto countered aloud. \emph{`Look, I still don't know if this is really a blank check, you know. And we can't be greedy about this.'} Haruto continued in his head as he turned down a sketchy street. His eyes scanned the shadows, moving away from a lump pile. 

Given his face, he tried to avoid places that weren't heavily patrolled. But as he'd yet to install roof access to the warehouse, he'd was forced to travel by street.

\textbf{\sffamily{Look kid. If you don't ask for it, then we can't get it.}} QB9 added grumpily. \textbf{\sffamily{What's the worse that can happen?}} \textbf{\sffamily{She says no.}}

\emph{`Aeliana decides I'm not worth the effort.'} Haruto countered. \emph{`Honestly, I don't see what she get's from this arrangement.'}

QB9 was silent for a moment. \textbf{\sffamily{Kid, you did read the requirements to get into OCI. Right?}} Haruto hesitated in his response. \textbf{\sffamily{Right!?}}

\emph{`Well, you see...'} Haruto began, but was stopped by the a wave of fury washing over him. \emph{`Honestly, QB I was going to read it, but I got distracted.'}

\textbf{\sffamily{It's a paragraph of text...}}

``Not the way Aeliana describes it.'' Haruto muttered.

Haruto could feel QB9's disapproval. \textbf{\sffamily{Creativity.}}

\emph{`Huh?'}

\textbf{\sffamily{Why the Helian girl needs your help.}} QB9 grumbled out. \textbf{\sffamily{Just be glad she's got no other options.}} He continued. \textbf{\sffamily{Force is the only reason}} \textbf{\sffamily{anyone would spend any length of time with your incompetence.}}

\emph{`Hey!'} Haruto thought slightly hurt. \emph{`The Moon Princess likes my just fine.'}

QB9 snorted. \textbf{\sffamily{You still haven't even asked her name.}}

Haruto blushed in embarrassment. \emph{`I'll do it in my own time.'} He replied.

\textbf{\sffamily{Yeah, right after you build my body.}} QB9 replied harshly.

\emph{`If, I build you a body. If!'} Haruto replied.

\textbf{\sffamily{I thought that was why your taking that stupid Trade course.}} QB9 growled. \textbf{\sffamily{That's the only reason I agreed to it.}}

\emph{`Keep your SKIM on. If I build you a body, then it will help.'} Haruto moves across the street to avoid a group of lurking individuals. Playing some game, but he didn't want to try his luck. \emph{`I could always drop out, or never show.'} He continued.

\textbf{\sffamily{You wouldn't.}} QB9 replied.

\emph{`Try me.'} Feeling like he had the upper hand once more, his thoughts turned to a different concern. First, he'd need to install roof access to the warehouse, then he could work on creating his own false compartment. He'd only heard stories about the Guild. Impossible to avoid in LL. \emph{`Still better safe than sorry.'} QB9's approval filtered through his senses.

A shift in the air caused Haruto to dodge right. Rolling to he bounced off a building to a nearby trash can. The metal rang in the alleyway as Haruto continued to dodge a heavy fist. No time to think, he continued up the side of the building. \emph{`Three, no four of them.'} Jumping over to the next building he continued.

\textbf{Left. Right. Duck.}

The thoughts, not his own, came to him without full comprehension, but he didn't have time to analyze it. \emph{`Roof?'}

\textbf{\sffamily{Terminal around the corner.}} QB9 replied. \textbf{\sffamily{Accessing now.}}

Dodging to the right of a large fist, Haruto used his momentum to jump onto the scowling man's head. Another jump and he was nearly home free. Hands on the edge, Haruto pulled himself into the roof. One foot on the rooftop. 

\textbf{\sffamily{Right!}}

But the warning was too late. Haruto just managed to get his arms up to protect again serious damage. The force of the hit was clearly from a military grade SKIM enhancement. \emph{`Star dust!'} Haruto thought as he rolled with his momentum.

\textbf{\sffamily{Just get to the edge, kid.}} QB9 replied as the roll slowed.

Using his momentum, Haruto pushed off into a front flip. \textbf{Above.} Turning the flip into a slide was easier said than done, but some how he managed. The fist aiming for his center mass passed centimeters above his hair.

\textbf{\sffamily{Two meters kid.}} 

Without pause, Haruto jumped out of his slide and rolled to the right. In a dead sprint, he took four steps before sliding again to the edge of the rooftop.

``Ahhh!'' The man voice from behind him screamed out as his hand just brushed Haruto's shoulder. A smile began as he let the ships artificial gravity do the rest.

Yank!

\emph{`Oh no.'} Haruto thought as he hang in mid-air over the ledge. \emph{`A SKIM linker, but those are government use only.'}

``The old man's not going to like what I've going to tell him about his.'' Haruto began as he was pulled back onto the roof. The original four men huffing a meter back.

``Well it's a good thing I don't work for him anymore.'' The voice was familiar. Haruto looked up and tried to place him. \textbf{\sffamily{A disgruntled Guardian?}} QB9 questioned.

\emph{`No, not the right built.'} Haruto replied in his head eyes still search.

``You never said he'd be this hard to catch.'' One of the other four wheezed out.

Another shook out his fist. ``Yeah, the kid made me hit a wall.'' The man grimaced in pain before the bruising in his head disappeared. ``Those units are coming out of your pay.''

``Yeah, yeah.'' The man hold him replied dismissively. Turning back to Haruto he continued. ``Don't tell me you've forgotten me already.''

The face was familiar, could it be? ``Sergeant?''

``Bingo!'' Turning to his men he continued, ``Boys looks like I did make an impression. Wasn't sure after all that class he missed.''

``Like I give a damn.'' One of the men replied. They all seemed to have gained their breath.

``How have you been, Sergeant?'' Haruto tried a friendly voice.

\textbf{\sffamily{That's right. Talk your way out of this.}} QB9 voice rumbled gently.

``Sergeant?'' Haruto's once teacher questioned, his voice had a hard edge to it. ``No one calls me that anymore.'' The man ran the fingers of his free hand through his short hair. Eyes closed in some kind of memory, before snapping open. A burning hatred Haruto had seen before. ``Not after I was fired, anyway.''

``Fired?'' Haruto questioned, ``You were a great Sergeant.'' He continued voice as genuine as possible.

The other man, whose name, even now, Haruto could not remember, gave a cold hard bark of a laugh. ``Ha! Can you believe the stones of this kid?'' He tossed back.

``He's kinda funny, if you asked me.'' One of the lugs answered. 

``Yeah, from everything I've heard. You sucked at it.'' Another continued.

``And let's not forget the KANP incident. The whole ships still talking about that one.'' 

Haruto's old Sergeant turned to him, shaking him roughly, ``And I have \emph{you} to thank.'' He spat. ``You, no name, no good, demon!'' He shook with rage. ``You ruined my life!''

\textbf{\sffamily{Technically, he was stupid enough to link to the KANP center hub.}} QB9 added.

\emph{`Not helping!'}

``Because of the prank?'' Haruto questioned.

``BECAUSE OF THE PRANK!'' He roared. ``Data went missing, and someone had to be blamed.''

``I'm so sorry, Sergeant.'' Haruto gave his best innocent eyes. ``But I had nothing to do with that prank. The Guardians and the Keepers heavily reviewed my involvement and had to apologize for their treatment.'' Which was all only technically true as the Guardians hadn't done much outside of deliver him to the Keepers, but the Sergeant, or ex-Sergeant didn't need to know that.

The ex-Sergeant's arm drooped and for a moment, Haruto thought he might have talked his way out of a beating.

``The thing is, I don't care what the Keepers, or \emph{Guardians}, can prove. You did it. I \emph{know} you did.'' The ex-Sergeant continued. ``For months, I've just been trying to stay tethered.'' Cold laugh, ``but no one will hire me. Well, no one legitimate. No offense guys.''

``None taken.''

``And I've dreamed of this moment. What I'd do once, I found you out where you don't belong.'' The ex-Sergeant pulled him closer to his face. ``Where no Keepers can keep you \emph{safe}.''

``Really, we don't have to do this.'' Haruto add. His hands up in surrender.

There was a long pause as the ex-Sergeant just stared at him. ``It's now or never, Cho.'' A man called out. Haruto didn't turn to find out.

\emph{`QB, please tell me you have a way to get me unlinked.'}

\textbf{\sffamily{I need another ten maybe fifteen minutes, kid.}}

\emph{`I don't even have one.'}

``You see, I honestly had given up on this. We leaving tomorrow, and I almost didn't get to return the favor.'' Before Haruto could reply, Cho shook him silent. ``No, you've talked long enough. Listen for once!'' He waited and Haruto shut his mouth. 

\emph{`Please work faster, QB.'} Haruto thought.

Cho hand caressed Haruto's face as he spoke. ``I'm going to enjoy this.''

``Star dust.'' Haruto cursed. This was going to hurt.

\chapter{}

It was the shooting pain he recognized first. Then the struggle to breath. Groaning, Haruto attempted to open his eyes, but they were slow to listen to him.

\textbf{\sffamily{Easy, now. Easy.}} QB9's voice sounded gently in his head.

Slowly he opened his eyes, well really mostly his left eye seeing as his right seemed to be too swollen to see much of anything from. The soft red of the Lower Level junkyard greeted him. Soon enough the sharp edges of metal bins long past their time made their presence known. The warmth from the unnatural heat of the furnaces was a surprisingly welcome relief from the possible alternatives.

\emph{`Well, that could have gone better.'} He thought as he shut his eyes again. He was beyond tired and just wanted to sleep a little longer.

\textbf{\sffamily{I expected a little more, I don't know... concern about nearly dying.}} QB9's sarcasm echoed in his head bring Haruto's attention to the sharp pain coming from his nose.

Carefully lifting the arm he deemed less injured to his face, he let his fingers feel the damage to his nose. \emph{`Could have been worse.'} Haruto replied just before he sharply straightened out his broken nose. Taking a quick intake of breath at the pain only caused more of it.

``Can't you do something about my broken ribs?'' Haruto asked aloud in nothing more than a bare whisper.

\textbf{\sffamily{No. You've run out of medicine, and I had other priorities to think about.}} QB9 replied angrily. For once, Haruto could tell the anger wasn't direct at him.

Laying back down, Haruto tried not to think about how bad he must have been in to run through all of the medicine in his BISM. Especially seeing as he still felt like crap. And every breath was a nightmare of twisting pain. One of his lungs was probably still clasped, but it wasn't anything he couldn't live through.

\textbf{\sffamily{You can't go around with empty medicine vials kid.}} QB9 continued worry clear in his voice. \textbf{\sffamily{And seeing as we won't be back to KANP for four weeks,}} \textbf{\sffamily{I don't see how we get around hospice and the Keepers.}}

\emph{`Don't worry QB. I've got extra supplies for rainy days like this.'} Haruto thought. \emph{`You every wonder why they call them rainy days? I wonder if...'} A loud grinding sound interrupted his thoughts as the pile of junk his was currently on top of started moving. \emph{`Great, they couldn't have tossed me on a different pile.'}

\textbf{\sffamily{I might have made them think you were dead. And bodies tend to smell when not}} \textbf{\sffamily{disposed of quickly.}} QB9 answered. There was something under his tone that Haruto couldn't quiet figure out. As he was starting to get a pounding headache, he decided to leave it for another time. The moving trash pile more of a concern.

Attempting to sit up, the pain in his ribs discouraged any further action, so Haruto returned to his prone position.

\textbf{\sffamily{Kid, come on. We can't stay here. Not if we don't want to end up as space junk.}} QB9 spoke softly aware of his pounding headache.

``Give me a moment, okay.'' Haruto replied as he breath slowly in and out. The pile of junk slowly moving beneath him. Opening his eyes, he gently turned his head to each side hoping against all odds that he was somewhere close to some old coveralls. \emph{`I ought to start wearing them, if for only this reason.'}

\textbf{\sffamily{Kid...}} QB9 warned softly as their trash pile continued to shrink. \textbf{\sffamily{We don't have time for whatever you're thinking.}}

``Going to have to make time, QB.'' Haruto as he spotted a piece of coverall fabric within reach. Extending his arm, he could feel QB9's anxiety. \emph{`Don't worry, QB. I've got this.'}

\textbf{\sffamily{You've still got to get down, kid. Any you haven't even tried to stand up yet.}} QB9 voiced his worry.

Haruto ignored it for now. Instead, he gently wrapped the warn and dirty coverall around his waist. Tightening it to secure his broken ribs. Taking a deep breath for the first time, he relaxed back into the pile for a moment to rest.

\textbf{\sffamily{Kid, you're killing me here.}} QB9 whined in a deep warning.

``Alright, alright, alright. Just give me a second.'' Haruto complained.

\textbf{\sffamily{We don't have a second.}} He growled back.

\emph{`No, we've got plenty of time.'} Haruto replied as he started the painful process of curling into a ball. His hands around his neck in protection, finally the AIM seemed to understand how he planned to get down.

Rolling in the opposition direction of the junk compressor, Haruto tried to keep his arms and legs in place to avoid further damage to his ribs or a painful break of his neck. Soon enough he was at the bottom of the trash heap. The tumble down drew in his legs deep into the junk, but Haruto had a good grasp of the catwalk that he was sure he could pull himself out. \emph{`But man is this going to hurt.'} He thought as he steadied his hands on the ledge.

With a groan he slowly pulled his legs out of the trash, and pushed his tired body onto the catwalk. The metal clanged as he slumped back down onto his back the warmth from the furnaces lulling him to sleep. \emph{`I think I've earned a break.'}

Haruto blinked away, unsure how much time had passed, or what woke him.

\textbf{\sffamily{Hey kid. I know you need your beauty rest, but the dock ships leave at noon.}}

Haruto hummed in acknowledgment, but didn't move from his place. QB could wait a moment or two. Feeling a restlessness not of his own, he opened his eyes with a sigh. Fiddling in his SKIM, Haruto pulled out his lucky fox foot. Using the silver ring, he twirled it a little with a small smile.

\emph{`Hey QB, do you think she liked the dream catcher?'} Haruto asked.

There was a short pause before the deep grumbling voice of his AIM followed. \textbf{\sffamily{Sure, why not?}}

Letting his hand drop on his chest, he tried not to take too deep of a breath in frustration. ``You're a whole lot of help, you know.''

\textbf{\sffamily{Look kid. I don't study human interactions all that much. They're boring. So, give me a}} \textbf{\sffamily{break.}} QB9 replied. \textbf{\sffamily{I'm sure since you gave it to her, she liked it. The girl's way}} \textbf{\sffamily{smarter than you, so I'm sure she gets the importance without it needing to be explained.}}

Haruto was hesitate to see it QB's way. \emph{`Is that supposed to be reassuring?'}

QB9 growled in his mind reminding Haruto of his headache. \textbf{\sffamily{Kid, we don't have all day here. And as much as I hate to admit needing you, my plan would}} \textbf{\sffamily{benefit from a pair of hands.}}

Putting the gift from his friend away, Haruto rolled over to his stomach. Getting his knees under him, he pushed up to a seated position. Taking stock of his injuries for the first time, Haruto went through his limps. A swollen ankle, but he had meds that would decrease inflammation at home. His legs seemed fine, but his right arm might have a hairline fracture. \emph{`Do I have more osteo-regeneration serum?'} He thought.

Not able to remember, he shrugged it off.

\textbf{\sffamily{I'll give you this. Not just anyone could shrug off those injuries. From everything I know}} \textbf{\sffamily{about human biology, you shouldn't be able to walk.}} QB9 added. Haruto could feel him holding back. Given how injured he was when he woke up, it was more likely he'd be dead.

\emph{`But, they always underestimate me.'} He thought. ``Always.'' He muttered to himself. Letting his hands move to his pain coming from his ears, he spoke aloud to QB. ``Didn't anyone ever tell you, QB?'' slight pause, ``I'm a monster.''

Straightening out the little bones in his ear, he held back a yell of pain. At least now they'd heal correctly.

\textbf{\sffamily{You're no more monster than I.}} QB added after a moment. \textbf{\sffamily{Just a little}} \textbf{\sffamily{different.}}

``Maybe.'' Haruto replied after a few seconds of rest. Fixing a broken nose? No problem, but his ears. They throbbed worse than before, but if they grow back incorrectly, the KANP medics would have to re-break them. All cadets had to be in fighting shape based on biology. Haruto would sooner have cut them off, if the old man hadn't given his big spiel about family and legacies.

With a heave, he stood up leaning heavily on his uninjured foot. ``Alright, now what do you need me for?''

\textbf{\sffamily{Only for a little payback.}} The malice behind the words were startling.

``Against Name?''

\textbf{\sffamily{And his new friends.}} QB9 added. \textbf{\sffamily{I was able to hack into the theta dock, where their ship is located, while you were resting.}} \textbf{\sffamily{Surprisingly poor security.}}

``It's theta dock. Of course their security sucks.'' Haruto replied as he began to limp out of the junkyard. ``You still haven't gotten to me, yet.''

\textbf{\sffamily{I'm getting there.}} QB replied. \textbf{\sffamily{I've got the schematics of their ship. It won't}} \textbf{\sffamily{take much to cross wire the fusion core to the thrusters.}} He added. \textbf{\sffamily{And than once they}} \textbf{\sffamily{leave port. BANG!}}

``What?'' Haruto paused sharply. ``I'm not \emph{killing} anyone!''

\textbf{\sffamily{What? Now you're against murder?}} QB9 replied. \textbf{\sffamily{You're training to become}} \textbf{\sffamily{a pilot.}}

``Pilots \emph{protect} people, they don't kill them.'' Haruto countered. ``Haven't you read Mizumi's Dream?'' He muttered under his breath.

\textbf{\sffamily{Come now, you can't believe that romanticized piece of fiction is the pilot life?}} QB9 sarcastic disbelief.

``Look, QB. I don't care if it's real or not. \emph{I'm} not killing anyone.'' Haruto continued. There was already too much death in the world for him to be adding to it.

\textbf{\sffamily{Fine. I'll do it myself.}} QB9 replied.

At QB's reply, Haruto could just imagine the mess of a hack. Closing his eyes in frustration, knowing his AIM would do this with or without him. ``Alright, I'll help.'' QB9 pleased feeling. ``But, I'm not going to kill anyone.''

He could feel his AIM's displeasure. \emph{`Do you still have the documents you acquired from KANP?'} Haruto continued without waiting for QB9's agreement.

\textbf{\sffamily{Yes. Why do you want to originals?}} QB9 questioned, not quiet seeing where Haruto was going with it.

\emph{`I think it's time to give the Keepers what they want.'} He thought to QB9. ``Don't you?'' He finished aloud.

With that, he continued limping his way home. Sure that his body wouldn't be able to stand a trip in the tubes. Cold dark laughter feeling his head.

\starbreak

A couple of hours later, found Haruto sipping a nice cold drink of a type of fruit punch. 

\textbf{\sffamily{You know it's mostly sugar, kid. It's not actually made of real fruit.}} QB9 commented.

\emph{`Don't care.'} He replied. When something tasted this good, why complain about it's fruit content. Now that his face looked less like someone had tried to manually rearrange it, he was going to enjoy the finer things in life. \emph{`Like artificial flavoring.'} 

Slurping away, he pulled his docker hat down a little lower on his head. His docker coveralls, hand-stitched, would help him blended in with the rest of the people in theta dock, but that was as long as no one caught sight of his ears. 

Another little tug to keep the hat in place, he knew he was just another dock kid taking a break from a long morning of work. Haruto pulled out his KANP tablet. With the help of his tunneling program run through his BISM, it didn't take long before he'd found the ship he was looking for. 

The security of GC Samaritan was laughable compared to the dock security, which was saying something as theta dock had the worst security, both internal and external, of all the docks in KTS Kanopos. Seconds later, Haruto was in the network. 

\emph{`There's the cameras.'} He thought as the feeds started showing up on his screen. The captain of the ship a short balding man with a pudgy stomach was drinking something at the helm as his navigation crew worked on the consoles. Haruto flipped through their screens next. \emph{`Basic diagnostics, huh.'}

\textbf{\sffamily{They're nearly finished, kid. You need to stall them a little longer.}} QB replied. Looking at the time, he had to agree. Hacking in, he placed a small bug into the navigation system. Nothing out of the ordinary, but it'd take them an extra ten minutes before they were ready for launch.

``What's taking so long?'' The Captain snapped at his crew.

``Nothing we can't handle, sir.'' One answered.

``We'll be ready to launch in ten minutes.'' Another said. The Captain nodded as he turned to his own console, probably reviewing their route.

\emph{`Not that it will matter.'} Haruto thought. They weren't going anywhere if all went according to plan.

\textbf{\sffamily{It's not to late to just blow them up.}} QB commented.

\emph{`I'm not a killer.'} Haruto replied. QB9 didn't reply, but Haruto could feel his mild irritation all the same. \emph{`We do this my way, QB. You agreed.'}

\textbf{\sffamily{Yeah, yeah, yeah. Just get on with it.}}

Five minutes later and the sounds of sirens could be heard. Looking up, Haruto watched as the flashing yellow lights of a Keeper unit rushed down the docks. \emph{`Right on time.'}

\textbf{\sffamily{There's a first for everything.}} QB9 commented.

Rolling his eyes, Haruto monitored the video feeds of GC Samaritan. Finding the ex-Sergeant Cho easily enough, he watched the scene unfold.

The Captain rose as the Keepers strolled onto his command deck. ``What is the meaning of this?'' He demanded.

Ignoring the question the lead Keeper spoke, ``Summon your crew at once.'' Turning to his partner he continued, ``Scan them into the database when they arrive. I don't want to miss anyone.''

The Captain frowned but did as he was told, ``All of my people are registered, and so is my paperwork. You're making a big mistake here.''

The Keeper didn't even acknowledge his presence as they waited for the ship crew to emerge. \emph{`There, that looks like everyone.'}

The Keepers nodded to each other as the last of the Samaritan crew filed on deck. Tilting his head, the Keeper began to speak, ``Captain, this is team two, we have the crew. Ship is ready to be secured.''

``What!?'' The Samaritan ship Captain shouted. ``I demand to know what's going on.''

Haruto watched as a Keeper program took control of the ship remotely. Smiling all the while.

``You are being charged with aiding and abetting the transfer of classified documents.''

``What? I'd never...''

``This is God Chaser Samaritan, ID number 256DW13X?''

``Yes, but...''

``And you recently hired Civilian Cho Joon-Woo,'' The Keeper nodded to the man in question. ``Last stationed at the Kanopos Academy of Novice Pilots?''

``Yes, but...''

Nodding the Keeper motioned to his partner, ``Ready for booking.'' The crew flew to their knees, arms twisted behind them as their SKIMs glared bright red.

\emph{`Man, I didn't know that could do that.'}

\textbf{\sffamily{Their SKIMs are all linked to the ship, kid. Look.}} QB9 spoke in his low gravel.

Sure enough, Haruto could see that each BISM was duel linked to GC Samaritan. 

``You can't do this!'' Cho yelled out. ``I've done nothing wrong.''

``Save that for the Sakr\'{a}.'' The Keeper replied, a hard tone to his voice. 

``I demand to know the charges!'' Cho continued.

``Treason.'' The Keeper's partner answered. The crew gave a collected hush.

``Hey, now.'' The Captain replied from the flour of his own deck. ``I don't know anything about any treason. I hired him because he was cheap. Take him, I'll give you everything I have on him.''

``You'll give us what we want regardless.'' The lead Keeper replied.

``I have rights!'' The Captain continued. ``As a member of the Guild, all complains and concerns must go through their legal department!''

\emph{`Uh oh, didn't know that.'} Haruto thought as he immediately began navigating into the ship's Guild's registration.

``Command, can you confirm Guild membership?'' The Keeper asked.

\emph{`Just a second, just a second.'} He thought as he frantically typed. \emph{`There!'} Leaning back he smiled as the Keeper's face darkened.

``Nice try,'' the Keeper's partner answered as he began the prisoners to the mobile flat.

``Next time you want to use Guild membership, you might want to keep said membership current.''

``What? That's impossible. I renewed my membership months ago.'' The Captain yelled.

``Your registration says otherwise.'' The lead Keeper replied as they got to Cho.

``Wait, wait.'' Cho yelled. ``I still don't know what I'm accused off.'' He continued as he tried to pull away.

``Did you really think you'd get away with this?'' Keeper asked. ``That the Keepers of the Peace wouldn't get to the bottom of the theft of thousands of classified documents?''

``I...'' Cho began confusion written on his face. ``That was H\={e}id\`{o}ng! Everyone knows that.''

``No, the prank was H\={e}id\`{o}ng.'' The Keeper countered. ``But the recent transfer of said files from this ship to the nearby Kumo satellite gave the plot away.''

``You steal classified documents during H\={e}id\`{o}ng's prank. With his history everyone blames him for the theft, while you get yourself kicked out of KANP so it seems like you have no other options.'' His partner continued. ``It was almost perfect.''

``But I.'' Cho continued, ``this is H\={e}id\`{o}ng! Can't you see he's framing me!?''

``Oh will you shut up Cho.'' The Captain snapped. ``H\={e}id\`{o}ng's a prankster, not some manipulative mastermind.'' He continued as he sat down on the mobile transporter, his hands locking to the metal surface.

``Now,'' the Keeper's partner continued. ``Will you come quietly?'' He eyes showed he hoped the answer was no.

As if the Gods were looking down on Haruto, Cho knocked the Keeper away. Probably using his illegal SKIM linker to override the Keeper's control before Haruto could even begin to help the ex-Sergeant.

The Keeper's eyes condensed and the diamond shape of the Gento nanites activation took form. The Keeper dropped into the Simply Grace fighting style his Clan was famous for and in a blare of movement, Cho collapsed. Blood spit from his mouth as his body twitched. An electric current coursed through his SKIM.

``Illegal SKIM linker deactivated.'' The Keeper replied.

``You know,'' one of the navigation crew began, ``he was kind of a dick anyway.''

Haruto held back a laugh as he disconnected from GC Samaritan. His once Sergeant would have a very hard time getting out treason charges.

\textbf{\sffamily{I still think we should have killed him.}} QB9 commended, but Haruto could feel his approval.

``Would have been too quick.'' Haruto replied. ``Now, he'll never see the new moon.''

%%  LocalWords:  RL RLs wasn couldn didn doesn wouldn biometrics ve
%%  LocalWords:  absorbers shouldn rgensen Ahhh KANP rehydrator meds
%%  LocalWords:  hadn Mizumi GC ng weren OCI Cho DW Joon SKIMs Sakr
%%  LocalWords:  Kumo
