\chapter{}
Aeliana chapter, invitation to Koutaishi breathing day party...

\chapter{}

The heavily clank of the 'students'{} around him and QB9 quite reminder had Haruto putting weight into his every step. Joining the noise as they walked across the catwalk above the 'heart'{} of ZPS. Or at least that's what Head Tech Suio was calling it.

``Now, this is where we build all of the gravity independent weaponry.'' The Head Tech pointed below them pausing as he talked. Haruto took several steps over the to side to get a better look. Hands on the railing he leaned over.

Large machinery was casting what looked to be both plastic and metallic forms. \emph{`It almost looks like fire.'} He thought, but knew better.

``Now you might not be away yet, but our patented chemical flame that you see at work down there is five times hotter than actual fire. And burns without the consumption of oxygen.'' The Tech paused, amusement in his voice. ``Now, don't ask me anymore question about it.'' He continued as if someone had asked about it to begin with. Given that Haruto was in a group of quiet ones that was nearly impossible. ``I'd have to kill you if I told you any more. It's that sot after.''

Haruto leaned more over the railing. \emph{`Is that sulfur? Could I replicate it?'} He thought.

\textbf{\sffamily{Not on your life, kid.}} QB9 responded bitterly. \textbf{\sffamily{Now if you just let me at their systems. I could have the recipe in minutes.}}

Haruto snorted as he tuned out the rest of the Head Tech's speech about the chemical flame. It was mostly just boasting and not worth his attention. \emph{`As if I'd let you anywhere near it. One KANP incident is good enough for me.'} He thought back. He was still looking over his shoulder for that one, well he used to looking over his shoulder for that one. For now, the ex-Sergeant was paying for his crimes.

QB9 mood seem to darken, but Haruto didn't think it was because he'd been denied a hacking opportunity. Haruto had deny him plenty of them while they trained QB at better techniques. Whatever his problem, Haruto wasn't sure he needed to know about it.

``Hey, kid,'' Haruto felt a pull at the back of his temperature cover all. Fighting his instinct to run, he went with the movement returning to the catwalk proper. ``Ah,'' The Head Tech looked at him hard searchingly.

``Kim.'' Haruto supplied the name.

``Yeah, Kim.'' He parried back, but Haruto could already see recognition leaving him. ``Try not to fall down there. Wouldn't want to have to explain to the Sakr\'{a} how I lost one of you guys to the flames.'' He replied with a small smile.

Haruto nodded slightly in understanding, but chose not to speak. Tomorrow Head Tech Suio would have already forgotten about him, at least that was the plan.

``And has anyone, um.'' He looked lost for words, ``I mean have you considered changing you hair or something.'' He looked over in the direction of the two other Kims in the class.

``Sorry?'' Haruto asked innocently.

``Ah, never mind.'' He pulled back. ``It's like a freaking uniform or requirement or something.'' He murmured under his breath. Cause Haruto to fight back a large grin. Kim Min-jun, was the most common name for his year group and the two years born before and after him. That year also had a surprising about of orphans. From Aeliana's notes, he'd learned that was because of some micro-battle.

\textbf{\sffamily{As if mortal combat can be considered micro.}} QB9 complained as they continued their end of day tour. Haruto had been preparing all week for \emph{this} tour.

\emph{`I don't make up the names for these.'} He answered QB9 as he looked further ahead. They were almost at the way station for pryo district of ZPS. \emph{`Besides, didn't Aeliana explain it was called that because no other major power was involved?'}

It was the one thing he'd picked up from their history lesson that had supposedly happened three years ago. Although he was sure he'd have remembered something so exciting. It wasn't everyday that Kanopos was attacked by rogue pilot ships.

\textbf{\sffamily{Kid, they were only rogue because they failed.}} QB9 commented. Haruto could feel annoyance and hatred at the thought. \textbf{\sffamily{Humans.}} Was added as an afterthought. \textbf{\sffamily{You'll kill anything, and everything in the end.}}

\emph{`I don't think its that bleak, QB.'} Haruto responded as they finally arrived to the way station. QB9 snorted in his head.

\textbf{\sffamily{That's because you're naive, and too trusting.}}

Now that was going too far. He didn't think he was that trusting after all.

``Now, my future techs just give me a moment while I log in to the system.''

Haruto moved toward a terminal as he waited for the Head Tech to log in. The ZPS, or really the Zh\`{u}r\'{o}ng in general had learned several valuable lessons from his pranks. Chief among them was never linking systems together, which meant that if he wanted those beautiful weapons specs, he was going to need to access \emph{this} terminal. \emph{`And we won't be coming back.'}

The Head Tech stepped back as the Halo screen lit up with some of the more basic weapons modules. \emph{`Go time.'} He thought as he plugged in his BISM to the terminal behind him.

``Why don't we start with the basics?'' He pointed to the screen as he continued. ``The Zh\`{u}r\'{o}ng Pyrotechnic Studios is the leading supplier of weaponry to the Kanopos pilots program, which includes all of us little people.'' He smiled around as he cycled through another set of basic blasters, long ranged and short ranged.

Looking at his tablet, ZPS propriety. Haruto appeared to be taking notes, but instead he was directing his hack into the weapons files.

\textbf{\sffamily{I'd be ten times faster than this.}} QB9 complained.

\emph{`And you'd also announce to the world that we were in the system.'} He thought as he downloaded a set of long ranged blasters. \emph{`We've talked about this. Once you're as good as I am at hacking without leaving a footprint, then you can start hacking real targets again.'} Haruto was not having another KANP incident.

``This blaster can penetrate armor at grade ten level, which is just a step below ZenKZ.'' The Head Tech pulled up the schematic of another blaster that was nearly as big as Haruto was himself.

\emph{`But can anyone pick it up?'} He thought.

\textbf{\sffamily{Just take the schematic. Aeliana could use more diversity.}}

Putting it into the file, Haruto dumped another ten other heavy armor penetrating files. Some of them looked experimental, or well most of them.

\textbf{\sffamily{All but that one on the screen kid. Won't matter when we get our hands on them.}}

``Now, what you've all been waiting for.'' The Head Tech gave them a big small as he pulled up another schematic from his BISM. ``The gravity depended weaponry.''

What looked like a armor penetrating blaster took the screen followed shortly by a ZenKZ to put it to scale.

\emph{`Well, dang that's big.}

``We also supply Kanopos with all manors of ZenKZ and ship weaponry.'' He pulled up another. ``This little baby will be installed in Kanopos next week as an upgrade.''

\textbf{\sffamily{Get those kid!}}

Haruto pulled up the file and downloaded the whole lot.

The Head Tech looked around before pulling up another schematic, ``But this is my baby.'' He replied. ``A master work of hydraulic power for the first time being placed in a ZenKZ.''

Haruto looked long and hard at the weapon, he was hard place to describe it was so unique. He'd only heard rumors of it's creation, but had come prepared just in case it was true.

``But isn't hydraulic power to large for a ZenKZ, let alone a side arm?'' Came the question from another Kim Min-jun. Haruto wasn't surprised to hear it as he'd paid him to ask it.

\emph{`And money well spent.'} He thought as the Head Tech immediately pulled up a sophisticated algorithm.

``We used a series of compressions to get into to power a new model of weaponry. In fact, it's so impressive, it will be going into the Zh\`{u}r\'{o}ng heir's ZenKZ. Master Itachi has already demonstrated it's power to a small showing.''

Haruto switched folders as he pulled up the algorithms. He wasn't stupid enough to try to get past the firewalls that would be surrounding anything the heir himself would be using. But no one ever really thought of giving the same level of protection to the mathematical formulas that made said weapons. And he was not disappointed now, as he downloaded the whole folder.

``So,'' The Head Tech closed out of the schematic leaving only the ZPS trademark fireballs moving up and down the screen. ``that's pretty much it for the weaponry tour. Any questions?'' He asked already knowing there wouldn't be.

\emph{`Blast.'} Haruto thought as he hurriedly exited the terminal. He still needed to clean up his download history. As he'd piggybacked onto the Head Tech Suio's log on, no one would think twice of him looking at these weapons files. They would, however, wonder why he needed to download any of those files, which meant Haruto needed to permanently erase that history. And he needed to do it while Suio was still logged in.

``Good,'' he continued. ``Now, as a general rule, if it explodes or lights up than ZPS was apart of that.'' The Head Tech's hand hovered of his BISM as he was in thought.

\emph{`Come on, come on, come on.'} Haruto chanted.

``Well, expect for the Keepers equipment. They like to keep things in house.'' The Head Tech continued.

\textbf{\sffamily{Brat, you need to do something.}}

\emph{`I know.'}

So Haruto broke his stay quiet rule and said the first thing that came to mind, ``Does that include the Moon Festival?''

``Huh?'' The Head Tech looked in his direction, but couldn't figure out which one of the three student all looking down said it. Out of the corner of his eyes, Haruto could see his hand moving away from his BISM. ``The Moon Festival?'' He questioned. ``Yes. Yes.'' He continued nodding his head. ``While the Gento would like to take credit for everything that happens during the Moon Festival, it is us the great House of Fire here at the ZPS that does all of the fireworks indoor and out.''

The Head Tech smiled at something, ``Of course, we don't have to pay for the oxygen burned. Now that alone the Gento's pay for.''

Just as the Head Tech was finishing, his tablet screen blinked off as he pulled out clean from the terminal.

``We also do the fairy lights.'' The Head Tech continued as he closed out of his BISM pointing the students back the way they came. ``Which is a great segue for next week's project. Now that you all have learned the basics of what it means to by a pyrotech here at ZPS.''

Herding them along, Haruto shuffled into the middle of the pack. Blinding in with the rest. They made it to the clean room as they disrobed from their coveralls. ``Now, the Corporal are all looking forward to your visit. They've got a lot planned for your last two weeks here, and I'm told the first assignment will be fairy lights.'' He continued as he looked at his BISM screen. ``Here's the information.''

Haruto looked at his own BISM as if he'd received the information with the rest of the small class. As he was technically Kim Min-jun, or at least one of them. Haruto had to bounce his signal through three different BISM before it came to him encrypted. And not half a minute later, the assignment appeared.

``Now, study hard, and maybe someday, you'll count yourself a member of the ZPS.'' The Head Tech dismissed them.

Haruto followed the flow of exiting teens as he seamlessly blended in with his surrounding. The other Kim nodded to him as they parted ways. Haruto moving with the crowd who didn't so much as give him a second glance. Despite that he couldn't help but look to the rooftops. 

\textbf{\sffamily{Focus kid,}} QB9 began. \textbf{\sffamily{The rooftops are being watched. Stick with the plan.}}

Haruto knew QB was right. They'd been walking out of the ZPS building for two weeks now with no problems. He just couldn't shake the feeling of uneasy walking around the Zh\`{u}r\'{o}ng district like this. 

\textbf{\sffamily{Nothing's going to happen while you look like this kid.}} QB9 continued surprisingly soothingly.

Haruto nodded as he weaved his way through the crowd at a brisk walk. There was no point in tempting fate. Breathing a sigh of relief once he'd exited the Zh\`{u}r\'{o}ng district, Haruto turned into a back alley. Shedding his face paint and prosthetic ears in one swift motion, he toss them in a nearby trash dispensary. It was a pity they were one time use objects.

Climbing up the side of the building, Haruto was finally at peace as he looked down at the little people from the rooftops. With a wide smile, he was off to LL and his new home base, the RL2 warehouse. From the rooftops, the trip back to the warehouse was a breeze.

\emph{`My new home away from home,'} Haruto thought as he kneeled over his recently installed hatch. Aeliana had not been happy about the new installation when she'd first seen it. And, admittedly, he might have wanted to run it by her before he made modifications on the warehouse. But in his defense, every building aught to have rooftop access, so really he was doing her a favor. \emph{`And it's a more secure entrance than the front door, so really, she has nothing to complain about.'} He thought. 

Feeling QB9's agreement, Haruto popped the hatch open with a flash of his BISM. \emph{`1024-bit arthorization key that re-generated every week. What's to complain about?'} He continued in his head. Jumping down he answered his own question, ``Nothing.''

\emph{Zing. Zing, zing, zing. Clink.}

The sounds of Aeliana at her firing range greeting Haruto. Turning to the mini-fridge, he grapped a pouch of water and a fresh energy pack. While not MINOS, the stuff tasted okay.

\textbf{\sffamily{And it's actually health for you.}} QB9 growled out. Haruto rolled his eyes in response. 

\emph{`We're not having that argument again.'} He thought as he popped open the water pouch. Taking a deep sip, he exhaled in wonder. The stuff was like magic or something. Absolutely delicious. Real water was just, well it \emph{had} a taste to it. And it was just something that even the synthetic stuff couldn't touch. Not that he'd had much opportunity to drink synthetic anyway. No orphan could.

The energy pack, which QB assured him was fruits, vegatables and nuts mashed together, downed as quickly as he could manage. \textbf{\sffamily{Quality food could hit you in the face and you still wouldn't appricated it.}} QB9 complained.

\emph{`I'll have you know,'} Haruto begin in his head as he headed out of the staff room to the main warehouse floor below. \emph{`I have a fresh garden, so I know what this stuff is supposed to taste like.'} He took another long sip of his water before continuing, ``And this is not it.''

\textbf{\sffamily{Better this than MINOS.}} QB9 countered.

Haruto ignored him knowing that a response would only devolve into an hour long argument at minimam. Instead, he serveyed the latest additions to the room. \emph{`Are those PX-10000's?'} He thought as he looked over the three new shiny consoles. \emph{`I didn't even know these were on the market.'}

\textbf{\sffamily{Perks of being an Helian, I take it.}} QB9 replied, but he also sounded impressed.

Haruto spent the next ten minutes inspecting it. \emph{`No, this won't due.'}

\textbf{\sffamily{It shouldn't be that hard to disconnect them from the Kanopos network.}} QB9 commented.

Sitting back on his heels he nodded in agreement, \emph{`No, but it must have cost a fortune to connect three of them.'} Haruto pointed to a thick bundle of wires. \emph{`See that's archival access and it's linked to all three of them.'}

\textbf{\sffamily{Can't they get their money back for it? It's not like we need three anyway.}} QB9 replied, grumpiness returning to his voice.

Haruto shrugged, \emph{`Beats me.'} Turning to the firing range, he yelled out, ``Hey, do you mind if I disconnect one of these from the network.''

Aeliana finished her target, before turning to him, ``What?''

Pointing to the console in question he continued, ``Disconnect it.''

Aeliana gave him a look before returning to her firing range. For a moment, he thought she was going to ignore him, but surprisingly she pressed a button or two on her BISM and the whole range disassembled itself, collasping into the far wall. \emph{`That was not there yesterday.'} He thought, but said nothing as Aeliana harnessed her blaster and walked toward him.

``Why would you want to disconnect from the network?'' She questioned, her arms crossed in wieriness.

``Do you really want to know the answer to that question?'' Haruto countered. She looked at him for a long moment, before shaking her head.

``Nothing you do better land back on the Guild. I'm serious Haruto.'' She replied harshly.

Haruto crossed himself as he responded, ``That's why I need an offline computer.''

She sighed as she relaxed her position, ``You know without access you can do virtually nothing.''

``Nothing that can be traced.'' Haruto replied evasively.

She shook her head, but nodded the okay. Haruto smiled as he kneeled in the back of the console setup already pulling out the network wiring.

``Don't touch any of the other ones.'' She continued. 

``No problem,'' his reply was muffled as he started the re-wiring process. \emph{`No, I'm going to want this re-routed here...'}

``And try not to break it.'' She added. ``I don't want to have to explain to my mother why I need another one.''

``Uh ah,'' Haruto replied. \emph{`And this should go there...'}

``And this better not interfere with the warehouse security network.'' She continued. ``I swear I have someone check that you didn't just log into the Guild network.''

``Yeah,'' he replied absentmindly. \emph{`I think that should do it.'}

\textbf{\sffamily{I have no complains.}} QB9 confirmed.

``I'm serious, Haruto.'' Aeliana continued.

Haruto pulled himself out from behind the console. ``I got that from the 101 demands.'' Padding her softly on the shoulder he turned to the now offline console. ``But honestly, nothing's going to go wrong. I have my console offline just like this one.'' He added. ``Nothing's gone wrong with that one.''

``Yet,'' she muttered under her breath, but the console started up just fine. And more importantly, offline.

\emph{`Good now I can work without worries.'} He thought already thinking of his latest biodegradable project.

\textbf{\sffamily{I still don't see why you need a chip that disappears.}} QB9 growl out.

\emph{`You will in time.'} He thought as he sat down at the console and started setting up the security.

He could feel Aeliana's eyes on him, but she didn't say a word. She was like that keeping most of her thoughts to herself. He was just grateful she didn't seem bothered about his currently dyed hair.

``Before you get distracted, I got something for you,'' Aeliana spoke catching Haruto's attention.

\emph{`More stuff?'} He thought.

\textbf{\sffamily{Don't question gifts, kid.}} QB9 replied.

``Here,'' she handed him a new XP3 tablet. ``Don't break it, alright. And no, it doesn't have my lecture notes on them. That doesn't seem to be helping you all that much so I put Interactive History modules on them.''

Taking the tablet gentle he smiled, ``Cool.''

She snorted, ``They're technically for little kids, but given you have an attention span of a four year old, I figured it was the only thing that would really work. If you're actually serious about OCI.''

``Completely,'' Haruto answered as he looked her in the eyes, ``and thanks.''

``Don't thank me yet. It's in basic characters, so you still might have trouble on the tests. But Sergeant Sang-eo seems nice enough to let you take the exams in basic, so yeah.'' She finished.

``Still, thank you.'' Haruto replied seriously. He looked over at his computer before stepping away from it. ``You know, if you need help with your relic stuff, I'm free now.''

She shook her head, ``No, I've got a thing with my parents tonight. We'll work on it tomorrow.''

Haruto nodded as he sat back down. Aeliana turning to go, she paused, ``Oh, Tommy was able to locate a local source for that MINOS stuff you asked for. He should have it in later this week.''

Haruto whole face transformed, ``Yosh!'' He yelled as he fist pumped. Today just kept getting better.

Aeliana shook her head with a small smile, ``I'm not touching that stuff, just so you know.'' She replied. She turned back around and started heading for the door.  ``Anything that needs to tell you it's eatable probably isn't.'' She called over her shoulder.

Haruto was going to argue with her, but she was already out of ear shout.

\textbf{\sffamily{I'm really starting to like this Helian girl.}} QB9 commented. Clear pleasure in his voice.

``Oh, shut up you.'' Haruto muttered to himself as he turned back to what was to be his console. \emph{`Firewalls first, then a little Interactive History.'} He continued in his head. He was going to be very busy tonight.

%%  LocalWords:  Suio KANP didn wasn Wouldn ve isn Itachi wouldn ZPS
%%  LocalWords:  couldn Sakr Kims pryo Zh ng compressions pyrotech RL
%%  LocalWords:  autobot Heya hadn doesn MODs shouldn outshined OCI
%%  LocalWords:  Tsuyomi taishi Masaru Akihiko ngd
