\part{The Guild Princess}
\chapter{}
Aeliana tried not to tug on the synthetic cotton sleeve of her coverall. She hated wearing coveralls of any kind over her SKIM. No matter what material her parents bought for her, she always ended up with some kind of irritation. As such, she preferred the pilot fashion of wearing only MODs on her SKIM. And no matter how her time at KANP ended, she had no plans to join the current fashion of the Emperor's court and wear these ridiculous coveralls.

A steady hand came to her elbow as her mother gentle squeezed. ``Dear please, it's only for the night.'' She spoke softly in her ear before letting go.

Her father took her place with a reassuring smile and gentle pat on the back, ``Don't worry Stargazer, I've got Tommy preparing a nice bath for you when you get back. Should take care of the irritation.''

She nodded at her father before forcing her hands away from the breathy material. \emph{`I can do this.'} She chanted in her head. \emph{`Just a few hours, and I can leave.'} She looked at the looming ship as they continued to approach. Flashing balls of fire in all kinds of colors lighting up space a signature of the Zh\`{u}r\'{o}ng clan. Why was she here again. Tugging on her father's elbow, careful not to rip his dress coveralls she asked. ``Why do you need me again?''

Her mother answered in his stead, ``Dear we're hardly going to have you moping about the house. Tommy can only take so much of it.''

``Than I'll go to the warehouse.'' She replied already looking forward to getting her coveralls off.

Her father smiled at her but shook his head, ``I happened to mention to Lord Yuri*(Noble of Fire Nation) that you were on vacation. Even if you have no interest in the business.'' Aeliana moved to correct him but he hushed her with a gentle smile. ``I know my little Stargazer, but we all must play the Game.''

Aeliana sighed heavily. \emph{`Best to get it out now.'} She thought. The Game would not allow for such behavior.

``Get your jitters out too, and remember your training.'' Her mother added as they pod slowed upon its approach. ``They are all the enemy. And we,''

``Show no weakness to the enemy.'' Aeliana continued. Her mother nodded pride clear in her eyes and small smile. Aeliana returned it as she shook out her body. A method her father had showed her in preparation for the Game. He too was shaking his body. Rolling his shoulders, and taking deep breaths. She copied him while her mother looked on. Mother was a natural at the Game. Aeliana just hoped she wouldn't need to play it often.

Once their pod docked, she heard the shift of pressure as their pod sync with the main ship, but felt nothing as her SKIM reacted to equalize pressure. Gravity must have shifted as well because the hard clank of her SKIM boots attaching themselves to the metal of the pod rang clear. They waited a moment longer before the door opened. \emph{`6.2 sec decompress.'} She thought as she followed her parents into the ship. \emph{`That put this ship as an E class cruiser. Not bad for the Zh\`{u}r\'{o}ng, but probably their best merchant ship.'}

They feet continued to clang as they walked. Not everyone could afford gravity in greeting chambers, she knew even the Sakhalin clan didn't use them, but that wasn't from lack of money. Some how, she got the sense that if the Zh\`{u}r\'{o}ng could afford it, then at least \emph{this} ship would have then installed.

She looked at her father, to see him slightly green. He had a weak stomach, so all of their main ships had to have them, which was a small expense for her father's comfort as far as she was concerned. She mother held his arm gentle as they reached the anti-chamber. A second decompress and reintroduction to gravity and that door opened to a lift. A stiff looking Zh\`{u}r\'{o}ng grabbed man greeted them.

``Invitation.'' The requested wasn't really a question, but Aeliana was hardly surprised.

Her mother held out her BISM for the man to scan before he activated the lift. Less than a second later, soft music greeted them as they stepped out into the main hall and the party proper.

``Enjoy the party, Master and Mistress Helian.'' He replied just as stiffly before the lift shut and so her only exit.

The room was lavishly decorated. Clearly no expense had been spared for the event. She followed closely behind her parents as they moved into the thick of it. Her mother believed in being fashionable late to these kinds of things. Nothing begins until the Helian have arrived. At least not when it came to the business of the Guild. And this was no exception.

As soon as they arrived, business associates streamed to her mother as if this was a Helian event. Without conscious effort, the hoard around her mother pushed both her and her father to the side. Her father wasn't the little bit upset either. \emph{`And why would dad be? He hates these things as much as I do. Maybe more.'} She thought as she absently grabbed one of the metal cups from a passing server, human server. The bore expression on his face wasn't as devoid of emotions as he'd probably intended.

Bring the cup her lips he father halted her, ``You're not going to like it.'' He spoke under his breath. She wrinkled her brow in question. ``They try, but always second best when it comes to the clans.'' He looked around, but seeing that mother was still engaged relaxed.

She took a small sip and understood at once his meaning. And knew he shouldn't have voiced it aloud. At least now \emph{here}. In the cup, was a water. Something that would pass for real water to those who drank synthetic or recycled on the regular. But that was not her. ``Dad.'' She admonished. He nearly shrugged before remembering that they were supposed to be playing the Game. He gave a goofy smile instead.

``It's true.'' He continued. ``Always a step behind, or two.'' There was a little malicious in his voice, but Aeliana wrote it off for his discomfort at playing the Game.

He was right of course. She would be sipping on this cup of water for the rest of the night. As nothing could compare to the real stuff, but the Zh\`{u}r\'{o}ng would have the majority of their guest fooled and those they didn't wouldn't matter as they were beyond the reach of the Zh\`{u}r\'{o}ng. Because no matter how hard they tried, the Zh\`{u}r\'{o}ng would always play second fiddle to the Gento. Their servers could try to copy the Gento mannerism all they liked, but they would fall short. Just as this party would likely be outshined by anything the Gento would have.

``Are the Gento clan having an event?'' She asked her father. It would be just like the Zh\`{u}r\'{o}ng to rush a party so that their could happen first. Or to at least capitalize on envoys that were hear for a Gento event. She'd gotten a glimpse of the royal envoy just a moment ago. Looking around now, she found the woman talking animatedly with her mother. There wasn't a single occasion that would have the Royal Envoy here for the Zh\`{u}r\'{o}ng outside of being in the area.

``Not this cycle.'' He caught her eye line. ``Oh no, Tsuyomi is here for the K\={o}taishi's fourteen birthday.'' Her father answered her unasked question. ``I'm surprised she had time for this event. She must have arrived early this year.'' His eyes took on a look of sudden understanding as he looked around again. She wondered if he would mention it here, but doubted it. Whatever it was, would be discussed later with her mother as part of Guild business.

The pair fell into silence as the servers bought around elaborate dishes that Aeliana was sure would be an imitation of the real thing. Her father took sampling pieces and tried not to make a face at any of it. With any luck, the Zh\`{u}r\'{o}ng would follow the norm and have a buffet as well with at least a few simpler dishes. \emph{`Those should be impossible to mess up.'} She thought as took a small sip of her fake water.

*Gong sound.*

Aeliana looked for it. A path formed in the mingling crowd as the drumming continued. The famous Fire Troop made their way to the stage.

``Ah finally,'' her father muttered as he shifted to the stage. She'd seen them only once and from a far. Ilia had never been impressed with them and had seen no reason to watch their performances during festivals. So they always watched the Gento Clan's Moon Troop instead.

Personally, she liked them both equally. And on rare events, the Fire Troop was known to use real fire. Although she'd never seen it. The Fire Troop preforms using real fire. Aeliana is impressed. Masaru appear on stage to give a speech. Her father leans over to whisper in her ear.

``I wonder how much that cost them?''

She tried to do the calculation in her head, but forgot the current market price for oxygen. Embarrassed at the lost of information she just gave her father a small smile. \emph{`I can't believe I've forgotten the price of oxygen.'} She thought as he tuned back into the Zh\`{u}r\'{o}ng clan head's speech. \emph{`I'll have to remember to go over the market price for the essentials. I can't let my studies get in the way for finances.'} She could just see the horror on her mother's face if she knew.

Aeliana was so lost in her thoughts, she missed the end of Masaru's speech. ``Alright my little Stargazer, I better get out there and socialize or I'll hear about it later tonight. Try to stay out of trouble.'' He squeezed her arm before moving into the thick of it.

Aeliana moved to where she could see servers pulling out the buffet. Half way too it, she was stopped by none other than Akihiko.

``Hey.'' He gave her a small smiled that looked more like a smirk. ``Your parents drag you to this too?''

She looked briefly to the buffet table and the long line forming, knowing she'd missed her chance. Turning to Akihiko she gave him a small smile that didn't reach her eyes. ``Unfortunately. Vacation time, can't really get out of it.''

He nodded as he took a sip of his drink. His eyes finding his father and older brother across the room. ``Father expects me here during vacation as well.''

``At least I don't have to go to the Clan events too. This cycle is packed with them it seems.'' Aeliana added without thought. Her mind on Ilia's Clan schedule despite herself. Thinks about what Ilia would be doing now. Remembers she has eight events during her vacation, although none today (one tomorrow).

``Not as much as you'd think.'' Akihiko replied snapping her out of her thoughts of Ilia. She turned to see his eyes still on his father and brother.

``No?'' She questioned.

``As the second son, father only expects me to go to these business events.'' He continued. Aeliana could read between the lines. His father didn't want him at the clan events. She wasn't sure what to say to that so her eyes went down.

A sickly green screen flashed on Akihiko's BISM as he clinched his fist. She blinked in surprised. \emph{`That almost looked like the symbol Hermes had.'} She thought, \emph{`But someone like Akihiko wouldn't need help from someone like him.'}

Looking at his BISM screen now, the Zh\`{u}r\'{o}ng fire balls bounced back and forth. It was probably nothing. A trick of the light.

``I'm to be the good little boy. Go to OCI, pilot for five or so years, then retire and work for the business.'' Akihiko continued lost in his own thoughts. ``But I'll show him.'' He spoke with a firm determination as he eyes met hers. ``We'll show people like that. Prove them the fool for underestimating \emph{us}.''

Aeliana smiled tightly in response. \emph{`As if we are even close to being in the same position.'} She thought darkly. He had some nerve comparing their situations, but she had her Game face on now and would not make the mistake of showing her true feelings now. \emph{`Everyone is the enemy'} She chanted her mother's words back.

``Anyway,'' he smiled at her a little more openly. ``I don't think I've gotten to the chance to say how sorry I am about your break with Cadet Amur.''

Aeliana took a sip of water to stop her initial reaction at the comment. \emph{`Maybe because I avoid you like the plague at KANP.'} She thought bitterly. Her voice was light when she spoke, ``It happens. People change, and grow in different directions.''

Akihiko shrugged as if no one had taught him how to play the Game. ``Still, I'm sorry.'' He continued, ``I know what it's like to be alone. And can understand why you would choose the company of those less desirable to loneliness.''

Aeliana took another sip of water to cool her temper. Sure sometimes she wanted to strangle Haruto for any number of reasons, but he was hardly 'undesirable'{} because of it. ``Cadet H\={e}id\`{o}ng is a surprisingly great study pattern.'' She replied instead of something nastier.

Akihiko snorted at her comment. ``Come on, it's just us. You don't have to pretend.'' He replied with a roll of his eyes. ``I just want to say that even someone like Amur wasn't good enough for someone with your talents and pedigree.'' He puffed up his chest probably unconsciously as Aeliana imagined ten different ways to disembowel him as she continued to give him a soft smile.

``You flatter me.'' She replied airily. As she made a mental note to buy several cut outs of him for her gun range. \emph{`I can't want to shot that smug smile off your face tomorrow.'}

``I'm only speaking the truth. Someone like you should align yourself with someone more prestigious. Someone with weight to his family name, with connections that matter.'' He continued smug smile never leaving his face.

``I try not to chose my friends for their family name.'' She replied with a smile on her face and a soft laugh to soften her otherwise harsh words.

``Considering your situation, you might reconsider it.'' Akihiko replied.

``I'm sorry?'' Aeliana questioned politely.

``OCI and getting into pilot school.'' Akihiko replied shortly. She could not hid the dark light to her eyes that Akihiko clearly caught as he continued. ``At this point, connections matter more than skill, which is why if I were you, I'd spend less time with the dead last, and more time with those that matter.''

Ignoring some of his statements, ``Cadet H\={e}id\`{o}ng is hardly dead-last now.''

Akihiko snorted, ``No, but it would be nearly impossible for him to get his grades up enough for passing.'' Akihiko countered.

Aeliana tilted her head as if in agreement. \emph{`Only a fool underestimates Haruto.'} She thought. ``What are you proposing?''

``Simple.'' He started. ``Something Amur probably didn't even think to offer.''

``\emph{Cadet} Amur?'' Aeliana corrected as if in question.

Akihiko frowned but continued. ``Yes, Cadet Amur's family is small and depended on the grace of the Sakhalin clan. I, however, can use my father's power and influence to get you into pilot school.''

Aeliana raised her eyebrows in question, ``In exchange for?''

``Five or maybe three years if my career lunges well, of you as \emph{my} head tech.'' Akihiko answered forcing Aeliana to sip at her nearly empty cup of fake water to hid her initial reaction. ``Together,'' he continued, ``we'd be an unstoppable force. And once I've made a name for myself, my father will want me to continue as a pilot to bring great honor to our clan. It will be only a matter of whispering to the right people to get you into an OCI program.''

He looked at her expectantly, ``That is assuming I don't get into OCI on my own.''

He nodded, ``Giving you talents and abilities, it really is a pity that you were born in my year.''

``That also assumes that if I don't get into OCI, I won't simply turn my attention to the Guild.'' She continued.

He tilted his head in acknowledgment. ``That would be a waste of your talents, but always an option.'' Before she could reply he continued. ``I don't want you to think you must have an answer now. Something should be considered with great weight.'' He clinched his fist as he spoke, but Aeliana did not see that sickly green again in his BISM. ``No, this is an open invitation. I can wait for your answer up until I have to go to OCI.''

And there was no doubt in his voice that \emph{he} and not she would be going. She held back a sigh as she finished her fake water. ``Then I will have to think about it.''

``Of course.'' He replied. A small smile creep onto his face as he continued, ``And if you'd like proper company for lunch, I would be pleased to replace Amur's company.'' He looked her up and down with a predatory look. ``I'm sure I will make better company in that regard as well.''

Unable to control her frown, she held her metal cup, for once glad that the Zh\`{u}r\'{o}ng clan could not afford glass, to cover her mouth as if she were flustered at his advance. Inside she was seething. As if \emph{anyone} could replace Ilia. She wanted to spit in his face. To rage at his audacity, to think that she would want him in that way. But she couldn't for this was still the Game so instead she said. ``If I can pull myself from my much needed study given my natural disadvantage, then I will have to consider it.''

He smiled as if she'd said yes. Probably to him everything was a yes. He bowed slightly to her, ``I must be going. Socializing.'' He spoke as if they were sharing a secret.

Raining her face in she pulled the metal cup way with a weak smile, ``See you around, Cadet.''

Suddenly having lost her appetite, she looked for a server to replace her cup of water. What she wouldn't give for something stronger? But she knew that any party that served 'real'{} water, would not have the budget for liquor of the same quality. With another cup of the nasty stuff in hand, her eyes scanned the room. She was not surprised to find Akihiko in the middle of a group of girls around their age. They didn't have class with him six days out of the week.

He caught her eye and waved. She waved back as was expected of her. \emph{`I hope my mother didn't see that.'} She thought to herself. If there was one person, who would find this whole situation even more displeasing then it would be her mother, and Aeliana was not in the mood to deal with her mother in her Game face.

A light touch to her elbow caused her to turn into her mother's waiting eyes. But fate seemed to have other plans for her tonight. ``Mother is the Royal Envoy doing well?'' Aeliana asked trying to put off the inevitable conversation.

``Little Tsuyomi is happy to have the honor of attending the K\={o}taishi's fourteen birthday in the name of the Sh\`{a}ngd\`{i} again this year.'' Her mother replied easily. ``I see that you've spoke to Masaru's second son. I'm told he has a head for business. Is that true?''

Her mother guided her to a more crowded section of the party as she spoke. Aeliana felt her BISM buzz.

``Ah,'' Looking down at it, she was surprised to see a message from her mother.

\textbf{\textsc{I'm moving us to a more private place to talk.}}

The loud crowd meant that her mother had to lean in to her to be heard, but still this was hardly the place \emph{she} would have considered 'private'{}. She messaged her mother back not sure when the woman had even written her something. 'Do we have to do this now?' She wrote.

``Aeliana, dear. Your mother is talking to you. Can your little friends not wait a moment?'' Her mother replied as she gentle pulled Aeliana's arm down. Her arm buzzed again, but her mother had a firm grip on her wrist. A flash of light pulled her to the metal pillar glossed for the party tonight. Her mother angled her arm, and suddenly she saw the new message in the reflection.

\textbf{\textsc{The Game, dear. And yes. I need to know if I need to put out some fires before your father finds out about his.}}

``I'm sorry mother. What was it that you were saying?'' Aeliana replied as her mother let her wrist go.

``It's just that you and Cadet Zh\`{u}r\'{o}ng seem to be getting along well. I wondered if you knew if this rumor was true or not.'' Her mother said. A buzz and new message said another story.

\textbf{\textsc{Of all the people to replace Amur, you had to pick him?}}

``Cadet Zh\`{u}r\'{o}ng and I were just sharing are boredom together. Honestly mother, you know I spend all of my time studying. I couldn't tell you anything personal about most of my classmates including Cadet Zh\`{u}r\'{o}ng. Well,'' she paused in thought, ``at least not outside whatever one else knows. He ranks second in our class behind only myself.''

``He is such a nice young man, I'm surprised you don't spend more time with him.'' Her mother replied. Aeliana didn't need her mother's next message to read between those lines.

``He's a natural, while I must spend hours studying. We don't really cross paths except for tonight.'' Aeliana said aloud, and hoped that her mother heard the underlining meaning. \emph{`And only tonight.'}

``Well do try to talk to others as well.'' Her mother said it as a suggestion, but Aeliana knew it to be a command. 'Akihiko can't be the only one you talk to tonight.' Was implied from her tone.

``Of course mother. Please don't let me keep you.''

Her mother gave her a wide smile before moving on. A buzz told her, however, that she was not done.

\textbf{\textsc{And if you must associate with a Clan, I'd prefer it was that Amur girl. As nothing good ever comes from aligning oneself with the Zh\`{u}r\'{o}ng.}} Aeliana read the message without the use of the reflective surface now that her mother had gone. She tightened her jaw in frustrations. Opening a new box to send a message to...

Closing it quickly, she turned to the room in search of people in her age group. \emph{`I will not start messaging Ilia, just because my mother is being overly pushy.'} Aeliana thought as she made her way across the room. And the last thing she wanted to do was socialize with girls who would talk about only boys and the latest fashion. Not when it made her think of the last time she'd been to one of these events.

Then, she'd spent the whole time messaging Ilia. They'd done that for each other. Aeliana would bar herself in her room waiting for Ilia to complain about her Clan events, and Ilia would do the same during one of Aeliana's civilian events. She'd been able to get through anything and everything like that. But now...

\emph{`Now, I've just got to entertain myself.'} She thought as she smiled and nodded to the conversation going on around her. For a moment she considered messaging Haruto, but dismissed the thought. It just felt wrong for some reason. Haruto was a friend, yes. But he wasn't Ilia. \emph{`At least he wasn't trying to replace her either.'}

He had his own thing going on with the K\={o}taishi, his Princess, anyway. \emph{`And perhaps, I should stop pretending that what Ilia and I had was just friendship.'} She thought. ``Perhaps,'' she whispered under her breath. No one paid any attention to her though.

\chapter{}
Helian New Years Party, Haruto is invited.

Haruto meets Aeliana's parents?? That would work here, but I'm not sure House of Fire works for the title. Might have to try to work in something else entirely?

A dinner date with Anko and Iruka? Got to get a gift for his best friend? No myster over why security has been increased, by-the-by.

Probably talking to Hinata during one of her important meetings. That would be cool here!! Like a mirror of what Aeliana had with Ilia.

Could try a different day, where the Uchiha's have to show up. Hinata's actual breathing day? Good way to introduce breathing day. Although Haruto now needs a gift...

Should be some teasing about the prank Haruto plans to pull. Back and forth with Hinata.

(Must end with a proper introduction to the Guild Princess. (Meeting Aeliana's parents is the best way.)

\chapter{}
Aeliana and Ilia are walking toward the warehouse. Ilia is jealous of all the time Aeliana spends with Haruto, so Aeliana is showing her the place.

-here I want to talk about the SKIMs

-I also want a little bit of an arguement about the DOMAINE

maybe some other stuff...

once there get there, Haruto turns things down, and moves to leave...

Aeliana asks him to fix her BISM, interference (easier than going to a Keeper Tower)

-Haruto forgot to tell the Princess about it...

-Aeliana mad, because this is not a footnote activity...

...here we get into the other network... Aeliana will look into it... (speak to Erik, but he won't take her seriously)
