\chapter{}
<Aeliana's point-of-view>

Haruto rushed into the classroom just as Sergeant Sang-eo was returning. Setting back into his seat, he could help the smile that graced his lips.

``Man, what did you have massive diarrhea?'' Seo-Jun asked.

``Ha!'' Haruto laughed at the easy way out. ``I wouldn't go in there if I were you, is all I'm saying.'' Haruto replied in a non-answer.

\textbf{\sffamily{Good kid, make that alibi stronger.}} QB9 replied as Haruto surveyed the room. Seo-Jun was already looking away with a shake of his head. Only Aeliana was giving him a search look. He smiled back at her just as Sergeant Sang-eo started class.

Haruto tuned out most of it as he looked out the window. He did this so often, no one would think anything off about it. But today, he wasn't looking out at Sanctuary Park. No, his eyes lay squarely at the observation deck. Soon enough his prank would take into effect. 

\emph{`Hey, how long do you think it will take.'} He questioned.

\textbf{\sffamily{It'll take as long as it'll take. Now quiet, I'm trying to record the lecture. Someone has to}} \textbf{\sffamily{make sure you have comprehensible notes.}} QB9 growled.

``...which is why we have the OCI program to begin with.'' Sergeant Sang-eo paused in his lecture probably to gather his thoughts as the man lacked any form of dramatics that could make his lectures interesting. ``Now, today the OCI...'' He continued, but was interrupted as the class locked down.

\emph{`And it begins.'} Haruto thought as he masked his face in surprise. Looking around like everyone as the emergency Halo screen begin to descend. 

``What's going on?'' Someone muttered. The class erupting into confusion and concern. As the old man's face showed long and solemn. Movement out the windowed showed that the Commander's Halo was also descending. 

\emph{`This is just perfect.'} Haruto thought as he continued to look shocked with the rest of the class.

``I don't have a drill scheduled. Do you Y\'{u}?'' Sergeant Sang-eo asked to Sergeant Y\'{u}.

``No, Sang-eo. Something must be wrong.'' Sergeant Y\'{u} replied.

\textbf{\textsc{This is not a joke, or a game.}} The screen flickered as the old man continued. \textbf{\textsc{Ready yourself.}} Haruto had taken a recording of the old man during his weekly lectures to splice together this piece of art.

Sergeant Y\'{u} turned to the class in response. ``Prepare to enter battle stations, Cadets.''

``Yes, sir.'' Haruto replied along with the rest of class trying to hold back his own smile. 

On cue, QB9's laughter rang low and clear. \emph{`See!'} Haruto thought pointedly. \emph{`I told you, you sound menacing on the regular.'}

\textbf{\sffamily{I can hardly change my voice to suit you.}} QB9 replied, but Haruto could feel his pleasure as the faces in his class gave him a withering look as they all immediately disconnected from the KANP network with light curses muttered under their breath. Haruto maintained his innocent one knowing it would probably fool no one.

\emph{`As if I'd hit the same system over again.'} Haruto thought in disbelief. Even Aeliana was disconnecting. \emph{`Surely she knows that's a pranking rule!'} He continued in his head.

\textbf{\sffamily{I thought you called those training rules...}} QB9 replied.

\emph{`Wha? Of course, I meant training.'} Haruto quickly covered up, but he could feel that QB9 didn't believe him.

\textbf{\sffamily{They must think you're pretty good, to hack back into the KANP network after all of those}} \textbf{\sffamily{security enhancements.}}

Haruto eventually decided it might look weird if he was the only one still logged into the network, so disconnected with the rest of class. \emph{`Well, technically we did.'} He replied to QB9.

\textbf{\sffamily{The bathroom?}} QB9 questioned. \textbf{\sffamily{That hardly counts.}} He added bitterly.

\emph{`Don't be mad, I didn't let you do the hack.'} Haruto replied as Kur-ram was giving him a hard look before turning to his BISM, probably to run a diagnostic on it. Amur looked at him briefly before taking Kenta's BISM and connecting it to hers likely to run her own diagnostics. \emph{`The terminal was your test. As long as that goes well than we can talk.'}

\textbf{\sffamily{IF it goes well.}} QB9 raged. \textbf{\sffamily{My side was perfect, and ten, no hundred times}} \textbf{\sffamily{faster than anything you could do!}} He continued. \textbf{\sffamily{You should be begging me to do all}} \textbf{\sffamily{of the hacks!}}

\emph{`You every well no I'm not taking any chances.'} Haruto replied back completely forgetting about the class around him. \emph{`If we're caught, do you know how many felonies we, I commented?'}

\textbf{\sffamily{The only reason we get caught is because your human body left some clue to our involvement.}} QB9 countered.

Their argument was was interrupted by the screen door opening revealing a pair of Keepers. Haruto turned his attention and was a little surprised he'd miss the change from the old man's face to his signature black-hole on the emergency screen.

``Excuse us Sergeant,'' the closer Keeper spoke short on breath. ``But is Cadet H\={e}id\`{o}ng here?'' He continued as he managed to catch his breath.

\emph{`Finally,'}\ Haruto thought as he turned his attention to he practiced words he'd prepared for this encounter.

``Yes, Cadet H\={e}id\`{o}ng is here,'' Sergeant Sang-eo responded hesitantly still not used to Haruto's pranking ways interrupting class time. Haruto was sure the man would get better at it as he never knew when he'd have to pull a smaller prank on some rude shopkeeper. 

``What's the idiot done this time?'' Akihiko questioned, his arrogant voice loud among the mostly silent classroom. 

Now normally, Haruto dislike the other boy with a passion, he was rather moody and detached. Seemed to be bothering Aeliana all of the time. But for the first time, Haruto actually want to thank the Gods for his birth. Maybe even kiss him for all the help. Haruto didn't even care if the asshole calling him names in the process.

``Despite the stick up his butt, \emph{Akihiko}'s managed to ask a good question.'' Haruto responded trying to control his predatory smile. ``Will wonders never cease?''

``Why you...'' Akihiko growled out, but Haruto continued over him.

``What are you accusing me of doing? Falsely might I add now in front of all of these witnesses.'' He continued as he looked around the room. Puffing his chest out as he stood letting his classmates act as a jury. 

\textbf{\sffamily{Kid, if this OCI stuff doesn't work out. You might want to take up acting. Or legal}} \textbf{\sffamily{counsel or something.}} QB9 commented. \textbf{\sffamily{Even I'm starting to believe you, and I helped}} \textbf{\sffamily{with the prank.}}

``Cadet H\={e}id\`{o}ng, we have a warrant for your arrest for the involvement of the illegal hack of the Commander's Halo. A capital offense as you know.'' The Keeper answered.

``If you come without a fight will make a note in your defense.'' A second Keeper made her presence known at that moment as they both moved into the room.

``Now, wait just a minute. I've been sitting here, with the rest of the class trying to not fall asleep to Sergeant Sang-eo's lecture.'' Haruto turned to the coloring Sergeant as he continued, ``Sorry Sergeant, but you're a snooze fest.'' He replied with a good-natured smiled, gaining a small grin from the Sergeant in question. 

``I'll have to work on that then, Cadet H\={e}id\`{o}ng.'' He replied. Haruto would mark that as another point in the man's favor later.

Haruto nodded to the man before turning back to the Keepers, ``So, I've been here. I watched this prank happen with everybody else.'' He took this moment to point to his classmates as he spun in place. ``So, clearly I couldn't have done it.'' He continued crossing his arms in dramatic protest. ``I know my rights. You have to have some cause before you can arrest me.'' He finished with a flourish.

``I think the H\={e}id\`{o}ng black-hole will work in this instance,'' the female Keeper countered. 

\emph{`Okay, so you're the smart one.'}

\textbf{\sffamily{They still don't have anything on us.}} QB9 countered.

\emph{`The black-hole is enough for an arrest, though.'}

\textbf{\sffamily{Why use it if you knew they could arrest us for it.}} QB9 growled.

\emph{`Arrest, sure. But they can't hold me for it.'} He replied. Aloud he continued his protest, although weakly. ``Everyone knows that's my Clan symbol. It's public record.''

``But it's enough.'' She continued.

``You'd be surprised how easily the Sakr\'{a} gives warrants for your arrest when you've written your name all over the prank.'' The man Keeper added sarcastically.

Haruto placed his hands dramatically over his heart. ``You wound me. The old man loves me more than that.'' He continued, but he knew he was just buy time. For what? Nothing, but the fun of it. 

``Will you come willingly, Cadet?'' The male Keeper asked his voice saying he hoped Haruto didn't.

``Wait let me get this straight.'' Seo-Jun interrupted taking his feet off the desk in front of him, ``You think Haruto did \emph{that},'' he pointed to the Commander's Halo which still showed the H\={e}id\`{o}ng black-hole. ``Like I get how everything is normally Haruto's fault, but no way he can do that in less than five minutes.'' Seo-Jun continued. ``Sorry bro, but you're not \emph{that} good.''

``Never said I was.'' Haruto replied with a little bow. ``So, I ask again. How can you arrest me, when I was having lunch with Seo-Jun during the time it would have taken to 'hack'{} the old man's big screen?'' He continued.

``That is not for us to determine. The warrant has already been issued.'' The female Keeper replied with the Keeper monotone. She was good. Haruto would give her that. He imagined she'd be bumped from her patrol unit soon enough despite how poorly this was going to go for the Keepers.

``Man that's messed up. The dude couldn't have been in two places at one like some kinda ghost hacker or like rider or something.'' Seo-Jun replied as he leaned back in his chair turning to address Haruto directly he shook his head in bewilderment. ``I can't believe they can just take you up for nothing, bro.'' He continued in deep thought. ``Mom's going to hear about this for sure. I'll make sure they don't keep you long.'' He continued. Haruto couldn't hold his surprise. While he ate lunch and did some smaller pranks with Seo-Jun every once in a while, he never really considered them close.

\textbf{\sffamily{Don't be so surprised you have more than one friend kid.}} QB9 grumbled out. \textbf{\sffamily{Even I'm starting to like you.}} Haruto smiled in response. \textbf{\sffamily{Hey, don't go soft on}} \textbf{\sffamily{me or anything. I'm still getting my own body.}}

Aloud Haruto spoke to both of them, ``Thanks.''

Before he could say more; however, the female Keeper moved the conversation along. ``I'm sure you will be called to testify about the Cadet's whereabouts later, for now.'' The female Keeper gestured for Haruto to follow them. ``If you will?''

``Alright, alright. I know when I've been beat. But I'll expect compensation for this unjustifiable arrest.'' Haruto replied knowing the old man would get him something nice on the Keepers units.

As he was going willingly, Haruto didn't expect them to SKIM link him. So, he was a little surprised when they reached the KANP arches and the male Keeper linked their SKIMs together.

``Just in case.'' He replied. Looking up he continued, ``We got him Captain. ETA five minutes.'' The pair nodded to some command before they were off.

A handful of seconds later and everything went black. ``Star dust!'' Haruto cursed.

``Language, Cadet.'' The female Keeper admonished him.

\textbf{\sffamily{Was that suppose to happen?}} QB9 questioned.

\emph{`Heck no.'} Haruto replied. A hard rumble reaches Haruto's sensitive ears as the backup generates kick in. The lights flicker back on but the Commander's Halo flickers off. \emph{`What in the world did they just do?'}

``Yes, ma'am. We'll take it at a run.'' The female Keeper replied as Haruto was lifted off the ground by mister grumpy.

``You've really done it now H\={e}id\`{o}ng.'' The man replied his voice giving away his anger.

\emph{`And he'll be on patrol for the rest of his career.'} Haruto thought as he was held away. Today was going to be a long night no matter what Seo-Jun told his mom. \emph{`Hey, QB?'}

\textbf{\sffamily{What kid?}}

\emph{`I kinda of like the Ghost Rider.'} He continued as he remembered what Seo-Jun had called the it. He could feel QB9's irritation causing Haruto to smile widely as he was manhandled to Tower One. Yeah, this prank was already topping the KANP incident.

%%  LocalWords:  KANP wasn ng wouldn ve couldn eo Kur Seo weren didn
%%  LocalWords:  awesomest Sakr Kenta Akihiko Gongsaeng hoo OCI Wha
%%  LocalWords:  SKIMs

