\chapter{}
Aeliana was weightless. Every nerve seemed to be firing at a rapid concession. She was heavy and light, muscles straining but working in effortless form. It was exhilarating.

The feeling wasn't new to her. No, every day she had the opportunity to experience the dueling sensations. Here, as an extension of her ZenKZ, a deadly beauty fit for the Helian heir, she was a fighter, a \emph{Pilot} for the Jade Empire. 

The weightless effect dueling feelings from the limited gravity within her ZenKZ-D, but also the mental heaviness associated with harnessing its great power. Her nerves were on fire because their were extended into her machines interface system. Her arms were no longer her arms, her body just an extension of something bigger, stronger, faster, than anything it could achieve even with enhancements. Every muscle strained under the pressure of 50 kilos of force. And it all felt \emph{so} good.

``Foreign signatures incoming, ma'am,'' a static female voice relayed over her comms system.

``Roger. Moving into position,'' Aeliana responded as she moved her elegant machine into a group of asteroid debris. She was, after all, on patrol near the Nahua border for a reason. The Sakr\'{a} didn't send his Ace Pilots just anywhere.

``One moment, ma'am. Commander H\={e}id\`{o}ng must have missed a few, because I'm reading three additional signatures,'' the woman, who was clearly Aeliana's Head Technician, static voice relayed over the comms. ``We'll need to recalculate maneuvers.''

\emph{`Figures Haruto let some get away.'} Aeliana thought. To her Technician she replied, ``No time, I'll adjust on my end.''

``But ma'am,'' the woman protested, her name escaping Aeliana, but she didn't have time to question it as the signatures were finally showing up on her radar.

``I've got this, trust me.'' Aeliana answered as she adjusted her position slightly to stay out of radar signal. Just like a game of Komi, she used the asteroid debris to maneuver her opponents into vulnerable positions. Her mind already re-creating their positions in a mental 3D grid.

\emph{`Yeah, that should work.'} She thought as she let half the force pass her position. \emph{`3, 2, 1. Let's go!'}

Shooting out of cover, she disabled the first to ships before they had time to raise their shields. The next two had enough time to release a laser defense grid, but she hadn't planned to bring the fighting in close. Dodging the opposing fire, she charged her rail gun as she maneuvered the two ships into a linear path.

\emph{`There!'} Fire! The blasted them to pieces.

Her last three ships, surrounded her. Class E fighters weren't anything to snuff at. \emph{`No wonder Haruto had so much trouble.'} She thought.

She dances around the laser fire. \emph{`Intense.'} She thought as a laser clipped her. At this rate, she was going to end up in pieces. \emph{`I've got to think of something.'}

Doing some quick course calculation, she comes up with a plan. Uses the asteroid debris to misdirect, and is able to take the fighters out one at a time.

``Amazing!'' Aeliana hears over the comms as the fighting dies down.

Aeliana smiles, but doesn't degrade herself by using one of Haruto's one-liners. ``Returning to base. My baby's going to need some repairs.''

``Oh, of course.'' The woman replied. Aeliana could hear her flush in embarrassment. \emph{`Yeah, this is the life.'}

A moment later and Aeliana found herself striding down the main hall of her support ship. Ahead of her, she entered the main deck. ``Commander present!'' Someone called out as everyone came to attention.

``At ease.'' Aeliana replied turning to the closest Tech. ``Is Commander H\={e}id\`{o}ng back yet?''

``No ma'am, he's still out on a patrol run.'' Aeliana nodded at the information before taking a seat at the helm. As the top ranked Pilot, she captained this ship. 

``Status report,'' she commanded.

``Ma'am!'' Man came to salute in front of her. Holding a tablet he read off, ``Your Head Tech is currently leading repairs on your ZenKZ, ma'am. She reported that you should be back out there in a matter of days.''

Aeliana nodded, ``Good. Make sure she runs balances adjustments. She felt a bit off today.''

``Yes, ma'am!'' He replied as he tapped away. ``And..'' He trailed off.

``What is it?'' She asked curiously.

``Well,'' he said with a bright smile that he shared with the crew. ``The rankings are in, and we,'' he somehow straightened even more, ``are the proud crew of the number one ranked Pilot for the third straight year.''

The crew whooped in excitement.

``Settle down, settle down.'' Aeliana commanded with a small smile. ``If you guys get this excited every time I get an award, you'll be drunk every day.'' The crew hollered louder at that. ``Drinks on me tonight.'' She addressed the man debriefing her before standing up. The crew got more done with her out of the room, honestly.

``It's an honor to be working with someone with your credentials,'' the man continued as he saluted her off the deck. Aeliana nodded in response. It was probably true. \emph{`Top of my KANP and OCI class, now the number one ranked Pilot of KTS Kanopos. I really have come far.'} She thought as she made her way off the deck floor.

``Please tell me you didn't start a party without me.'' Haruto's voice sounded in her ears.

``I thought you were still on patrol.'' Aeliana answered back smoothly.

``QB's handling it.'' He replied easily, ``And you didn't answer me. What's going on in there.''

``Rankings got in,'' Aeliana replied smugly, ``You can't blame me if they go wild for me.''

Haruto snorted in response. ``That's what we're calling it now, huh?'' He chuckled at the idea. ``Anyway, can you write up the report for this one? Meet with the old man and everything. I've got a thing, when we make it back.''

``Yeah, a \emph{thing}.'' She parroted knowing his \emph{thing} was probably a date with his Princess. ``Yeah, why not.''

``Yatta!'' He yelled back, ``You're such a life saver. I owe you big time for this.''

``Hey,'' She says before he can close the comm-link. ``Do you know if...''

Even now, she couldn't finish the sentence. She and Ilia hadn't been, well anything for so long, but after getting into OCI had made things worse if possible. Now, well. She was glad that they had vastly different flight schedules. And hoped it wasn't by choice. Haruto would know all this, but more importantly because of his close connection with the K\={o}taishi, he'd also knew everyone's schedules. His Princess sure seemed to anyway.

``Ah, give me a sec.'' He replied and half a second later he replied, ``Yeah, their ship is supposed to be docked for, huh?''

``Huh?'' Worry entered her voice.

``Well doesn't give a leave date. Maybe there're in transition or something.'' He replied optimistically.

``Yeah, maybe.'' She replied, but her voice was hallow, ``Hey, don't let me keep you.'' She continued before cutting off there link. Turning into her room, she braced herself on the wall. The worst case surrounding her thoughts. 

\emph{`Transition?'} Not for the famous Amur-Krai-Sakhalin ship formation. The only other reason for a missing departure date, was... 

``Goddess protect her.'' Aeliana whispered in pray as she closed her eyes.

Opening them, she found herself stumbling out of a bar. ``Yeah, know.'' She slurred. ``You know, they won't even let me on the flotilla!''

``Yeah, I know.'' Haruto replied softly as he helped her up. 

``How,'' hiccup, ``dare they,'' She continued. ``I'm her, I'm her,'' She stumbled but Haruto held her upright.

``Yeah, I know.''

``What have I done?'' She whispered. ``If only.'' She shook her head, ``If I was \emph{there}.''

``You couldn't have known.'' Haruto replied. ``And you know they wouldn't break up the Amur-Krai-Sakhalin formation.''

``Yes, but,'' hiccup. ``If I'd just been her Head Tech.'' She whined. ``I could, I could've,'' she stumbled again tears building at the corner of her eyes. ``They wouldn't even let me go to the ceremony.'' She cried.

``Yeah, I know.'' Haruto replied sympathetically, ``But you can't place the blame on yourself.''

``If I were, if I were her Head Tech,'' she tried to counter, but Haruto interrupted.

``You'd have had to go to that Tech school. Would you have rather never be a Pilot just because there was a possibility you could have saved her.'' Haruto shook his head.

``Yes!'' She cried out. ``Because I could've, \emph{would} have.'' She continued. ``And we would have had so much more \emph{time}.''

\emph{Beep, beep, beep, beep.} A buzzing sounded.

``You couldn't have known, Aeliana.'' Haruto continued. ``Come on, let's get you home.''

\emph{Beep, beep, beep, beep.}

``No, no!'' Aeliana pulled herself up, ``I just need one more drink.'' Haruto looked skeptical, ``For the fallen. Just one more.''

\emph{Beep, beep, beep, beep.}

``Alright, but let's do this at my house.'' He replied. She closed her eyes as she nodded.

\emph{Beep, beep, beep, beep.}

``What is that noise?'' She called out, but when she opened her eyes she was alone. ``Haruto?''

\emph{Beep, beep, beep, beep.}

``Ah,'' Aeliana woke in a dry sweat.

\emph{Beep, beep, beep, beep.}

``What in the world?'' She questioned to no one as she rubbed the sleep from her eyes. Half expecting the beeping to continue, she was surprised not to hear anything more. ``Well, I'm not getting back to sleep after \emph{that}.'' She said aloud as she pulled herself out of bed. \emph{`I might as well get a drink of water.'} She thought as she exited her room. \emph{`Or ask Tommy for a Stargazer Special.'}

Pausing at the top of the stairs, she tilted her head in concentration. 

``Y... I...'' Murmured conversation reached her.

\emph{`Is someone at the door?'} She thought still trying to clear her mind of sleep. ``Goddess, what time is it?''

\textbf{\textsc{0313}}

Heading down the stairs, the voices grew louder. \emph{`Who's stupid enough to bother us at 3 in the morning?'} She thought. Looking around she continued until she found her parents huddled together at the front door. \emph{`And not get invited in? I guess it's not a Guild issues than.'}

She caught Tommy looking anxious in the kitchen doorway. Her mother looking close to vivid.

``Do you understand what time it is?'' She whispered harshly. A clear warning someone was losing their job later.

``Yes ma'am, but...''

``Mom, dad?'' Aeliana stepped up closer to try to peek outside. ``What's going on?''

``Oh sweetheart,'' her mother immediately dropped her anger, ``did the door bell wake you.'' (mother looks like she'd been up for hours, which was extremely unlikely as her father still had bed hair)

Aeliana looked past her parents to two young looking Keepers. ``Yes, I was just getting some water.'' She answered turning to her father she continued, ``Dad, what are Keepers doing here? It's three in the morning.''

``Well, Stargazer. That's what we're trying to figure out.'' He replied to her before turning to the two young Keepers standing outside their door. ``Now, young men, why did you think it was a good idea to ring the bell at this hour?'' Her father asked reasonable. It was unfortunate for the Keepers that there was no right answer to that questions.

``Sir.'' The one on the left turned to her father, ``As we were trying to say, we have a warrant to search warehouse registered as a class RL, license 57G...''

``Yes, one of the reserve warehouses.'' Her mother interrupted. ``Child, that is a Guild warehouse and doesn't answer the question my husband asked you.''

``Ah, well.'' He swallowed heavily, the other sweating thickly. ``You see justice sleeps for no one.'' He continued weakly. 

\emph{`Goddess, how long has he been holding that one in?'} Aeliana thought as the pieces were starting to fall into place. This had nothing to do directly with her parents, but with Haruto. Aeliana sighed, this wasn't going to end well.

``A warrant?'' Her father asked calmly, but Aeliana recognized the warning in his voice.

``Yes sir,'' the partner spoke for the first time as he handed it over.

``So, if you could have some of your men let us in that would be great.'' The first one continued a little bit stronger.

Her mother read the warrant over her father's shoulder. ``You can't be serious.'' She questioned.

``Yes ma'am,'' the second Keeper added cautiously. ``The Sakr\'{a}'s signature is at the bottom. It's legal.''

``It's a blanket search order,'' her father continued his voice growing softer.

The first Keeper straightened as he answered. ``Yes sir. We have the power to search all properties related to Cadet H\={e}id\`{o}ng Haruto as part of the investigation into the hacking of the Commander's Halo and subsequent generator failures.'' He answered in one breath. ``All very serious crimes.'' He added.

``And in violation of civilian ethics laws.'' Her father continued his voice having gone cold.

``Uh,'' the first one hesitated. ``The Sakr\'{a}...''

``Did not approve a search of \emph{Guild} property,'' her father interrupted. ``In fact, why don't I just call and asking him now.''

Horror crossed both Keepers faces as her father tapped his BISM, ``Wha? No that's all...''

``Yes, Hwasan. Yes I know what time it is. Two young men, Keepers with unit,'' her father paused.

``F7, dear,'' her mother answer.

``F7 are outside our door. Yes. Because justice waits for no one.'' Her father paused as the Keepers grew paler by the second. ``No get him on the call too. I'd like to ask Yonaka why his Keepers are bothering my family - waking my daughter, my \emph{heir} - in the middle of the night.'' 

Aeliana looked at her mother's smug smile as she padded her father on the shoulder before turning to go, ``Let's go back inside sweetheart. You're father can handle this.''

Aeliana followed her mother further inside the house shaking her head at the ruined careers of those two Keepers. \emph{`Some how I don't think they'll live the ire of the Sakr\'{a} and High Commander of the Keepers.'}

``Yes Yonaka at my home,'' was the last thing she heard her father say before she was too far away. Her mother sitting them down in the sitting room, probably to wait for her father to finish talking to the High Commander and the Sakr\'{a}. 

``A Stargazer Special for you, young Mistress,'' Tommy announced as he set down her hot chocolate, ``And lemongrass tea for you, my beautiful Mistress.''

``Oh Tommy,'' her mother replied with a smile taking a sip of her tea, ``you are such a flirt. What will we every do with you?''

``Perhaps a new kitchen, or new legs attachments. I saw a nice model in the monthly catalog?'' He asked. Her mother smiling in a way that suggested he was probably going to get everything he asked for right now. ``Why don't I get the paperwork in order for the Guild lawyers to look over at a more reasonable time?''

Her mother nodded prompting Tommy to wheel away, ``Thank you Tommy.'' Her mother called after him, ``He is such a dear. We'll have to get him something nice after all this is over.'' 

Aeliana took a sip of her own drink, \emph{`Um, perfect as always.'} She thought.

``I still can't believe any Keeper would ring at the middle of the night,'' Aeliana.

``And I'm sure it will never happen again.'' Her mother replied as calmly as if they were talking about galactic weather. Aeliana agreed.

\chapter{}

Aeliana blinked her eyes open. Pulling herself into the here and now. Birds chirped in the background. The low murmur of her classmates joining the sounds of animals. Even from here, she could hear the sounds of the Park's cycling river.

``Your move, Cadet Helian.'' The voice of Cadet Haibeu brought her to the game at hand.

Her eyes scanned the 3D board of their Komi game. Her pieces unfortunately surrounded after a series of increasingly bad moves. Now, she was running out of options to salvage this game. ``A moment more, please.'' She spoke aloud.

\emph{`If I can even salvage this game.'} She continued to scan the board, reviewing option after option. And the best strategy she could come up with was losing with a slightly smaller margin. She held back a grimace. ``White to level 3, G7.''

Her white stone appeared in the region linking the group of stones, which in the end wouldn't change the course of the game. And as she was losing, birds chirped in the background. Nightmares and early morning visitors combined, seemed to be the start of a very odd day.

``Awe, we see your strategy.'' Cadet Haibeu replied as he took a handful of seconds to review the play. ``But the end will not change. Why do you ask? Because despite your skill in the wonder strategic game of Komi, you have been playing absentmindedly.'' He continued. ``Black to level 2, J9.''

The move was expected even if she could have done without the commentary even if it was true. As such, she attempted to focus. There was still several points on the board before this game became pointless. ``White to level 1, A3.'' She countered.

``Commendable. We did not see that option.'' He buzzed. ``We find that it is good that you have returned to the game. We find no pleasure in winning when you were thoughts were with space.''

\emph{`Oh, just shut up and move.'} Aeliana thought as she ignored her growing headache. Honestly, if it wouldn't hurt her pride, she'd have just resigned now. She wasn't going to win anyway. Looking away, her eyes found the majority of her classmates clumped together in groups talking. It was rare of them to have class away from KANP, but completely unheard of to have it mostly unsupervised. 

Why they didn't just call off all the classes instead of the first and second years class was beyond her. But here she was in Sanctuary Park, the sixth years on the other side of the river probably doing the exact same thing as them. Both Sergeants Y\'{u} and Sang-eo in an out all day. She wasn't even sure what they were doing, playing round after round of Komi, could really be called a learning experience.

\emph{`I can't believe I'm even thinking this, but I would rather be home, sleeping.'} She thought as she eyes found a new four legged animal she'd never seen before. It leaned down to eat the synthetic grass, unaware or unafraid of the many intruders on its land. It was surprisingly beautiful in its simplicity.

``Cadet Helian.'' Cadet Haibeu voice snapped her out of her thoughts. ``We have moved some time ago.''

``Oh, sorry.'' Looking back at the board, Cadet Haibeu had indeed made a new move strengthening his motion in the left quadrant. The move left Aeliana with only one real options to gain points. ``White to level 4, C4.''

``We pass this round.'' Cadet Haibeu replied.

Aeliana let out a sigh, ``I pass as well.''

A moment later, and their scores were automatically calculated. Although Aeliana didn't need a computer to tell her the outcome. \emph{`413 to 587'}

\textbf{\textsc{Winner black, 587 to white 413.}}

``We would say good game, but that seems pointless. Why do you ask? Because for the majority of the bout you, Cadet Helian, were otherwise occupied with outside thoughts, for which we cannot speculate. As such, your game of play suffered.'' Cadet Haibeu replied as he moved to stand. ``We find this most unsatisfying, but understand outside pressures can effect otherwise ordinary life. As such, we offer our support in whatever ills you.''

``Ah, thanks. But I'll be fine.'' Aeliana answered as she stretched out of their seated position.

Cadet Haibeu nodded before heading over to the only other game still going. Looking around, she could guess it was Kur-ram's game still going, which was odd, because even she had a hard time making a game of Komi last with him. \emph{`At least on my good days.'} She thought pausing in her steps. While her parents probably wouldn't have cared that she'd lost to Cadet Haibeu for the first time. She did. 

Komi was one of the only family games where her parents never seemed to mention the Guild, or anything else. A game she'd been playing since she could reach her father's knee. And when she was on top of her game, she could challenge Kur-ram on even footing. Of course, even then their games were often still short. What was the point of continuing for hours when they both knew the other would make no mistakes. And while their boards would be bare, they always knew who had won within the first twenty moves. 

In fact, the only person who could take this long was Haruto, who frustratingly continued his games while passed the point of no return. \emph{`And yet, sometimes, some how, he manages to turn the tables.'} She thought, a small shake to her head. Even so, she doubted the Cadet playing against Kur-ram was Haruto. Continuing forward she walked into the growing crowd, although careful to avoid Cadet Haibeu. 

While they were a good Cadet and probably sincere in their support, Cadet Haibeu could and often did use five sentences when a couple of words would have sufficed. \emph{`That and I'd like to keep my own problems to myself, and not share them with a whole Clan.'} She thought as she pushed her way to the front knowing most were just standing around to look busy for when the Sergeants returned.

Making her to the front, Aeliana is surprised to find none other than the K\={o}taishi playing against Kur-ram. \emph{`Well, that explains the crowd at least.'} She thought.

``You'd think they'd never seen a game of Komi before,'' came the soft whisper of Ilia directly into Aeliana's ear as if nothing between them had changed. Aeliana hummed in agreement, even as her eyes fluttered close, her mouth suddenly dry.

A deep breath later and she has control again of her ability to speak. Tilting her head to the right to eye Ilia standing next to her a small smile on her lips. ``It's a close game. I'd love to review the game play.''

``I'm sure you would.'' Ilia replied amusement in her voice. ``If there's one thing Kur-ram complains about,'' Ilia tilts her head in Aeliana's direction as she rolls her eyes, ``as if he's not complaining about something \emph{all} of the time.'' She continued drawing a sharp laugh from Aeliana unwillingly.

Aeliana turns it into a cough, covering her mouth as she turned back to the game in front of her.

``He complains about how he doesn't get to play against you nearly as much as if that's my fault.'' Ilia continued.

``Isn't it?'' Aeliana replied her eyes focused on the Kur-ram's game. From the board, she could tell it was already over. The K\={o}taishi might be gifted, but she wasn't winning this round.

``Aeli, please.'' Ilia pleaded. ``Surly we can talk, if nothing else.''

``I...'' Aeliana looked away from Ilia not sure when she'd turned to face her in the first place. ``I think this game is over.''

``I resign.'' The K\={o}taishi replied a moment later. Causing a round of clapping to break out. Aeliana turned away from the game, pushing her way back to her table.

``Great,'' Sergeant Y\'{u}'s voice rang clear. ``It looks like I'm back just in time.'' He looked at his BISM as he continued to speak, ``Why don't we do two more rounds? Then the best of the best can go against the sixth years.'' Without waiting for a response, he pressed his BISM. ``Your next partners should be assigned to you.''

\emph{Buzz.}

\textbf{\textsc{Black, game board 6.}}

\emph{`Why am I not surprised, I haven't moved?'} Aeliana thought as she turned to focus on her re-setting game board. Sergeant Y\'{u} was somewhat predictable. For the students with the most influence, her, Akihiko, even Kenta, he bent himself over backwards to accommodate them. She should be grateful for the change, but the treatment left a bad taste in her mouth. Sergeant Sang-eo didn't have that problem. Unfortunately for her, the other Sergeant seemed to be absent even more so than Sergeant Y\'{u}.

``May I join you?'' The soft, steady voice of the K\={o}taishi broke into her thoughts. Aeliana jumped out of her seat in surprise. 

``Yes, yes. Of course, please.'' Aeliana replied as she motioned for the K\={o}taishi to sit.

They played the opening in silence before Aeliana could contain her curiosity no longer. ``I've got to ask, and I don't mean any disrespect or anything, but,'' Aeliana paused in search of the correct phrasing and was mildly surprised that the K\={o}taishi didn't interrupt her. ``I understand why we're,'' she pointed to her classmates, ``are here. The Sakr\'{a} redirected power away from KANP temporarily while they fix the generator problem.''

K\={o}taishi nodded, ``White to level 2, D3.''

``But why are you here?'' Realizing how that could sound Aeliana quickly amended, ``I mean, how does Haruto's prank effect your tutelage?'' Turning to the board she continued, ``Black to level 2, P16.''

``Alleged. White to level 3, O15.'' She replied. Aeliana looked on with confusion. ``Cadet H\={e}id\`{o}ng's involvement is alleged.'' She continued nodding to the board.

``Oh, yes 'alleged'{}. Black to level 3, Q15.'' Aeliana replied. \emph{`Although how you believe that is beyond me.'} She added to herself.

``As for your question, my tutors specialize in critical systems effected by the incident.'' The K\={o}taishi responded. 

Aeliana waited a moment longer, but the K\={o}taishi neither added to her comment or made a move. \emph{`Well, now I know why their game took forever.'} She thought privately. Still she found the answer weird. Two or three of her tutors, sure, but \emph{all} of them busy helping with Haruto's 'alleged'{} mess. That just seemed unlikely. Even so, she didn't know the Gento heir well enough to question her about it. 

Searching for something to break up the silence that wouldn't also possibly be offensive, she said the first thing that popped up in her mind, ``Who was your birthday? Tsuyomi didn't have a change to stop by after the event.''

``The party was as expected.'' The K\={o}taishi responded. ``Black to level 4, R14.''

``Ah, great.'' Aeliana replied shortly. ``White to level 2, P13.''

``Cadet Haruto's gift was very thoughtful.'' The K\={o}taishi continued. ``May I assume your progress with relic technology has increased satisfactory?'' She added. ``Black to level 5, P16.''

``Yeah. Satisfactory.'' She looked at the board as the K\={o}taishi's words caught up to her. ``Wait, Haruto got you a birthday gift and it was appropriate? Thoughtful?''

``Is that surprising?'' The K\={o}taishi questioned her voice flat as if asking about galactic weather patterns.

\emph{`Honestly, kinda.'} She thought thinking of the number of Akihiko heads with remarkable likeness. While thoughtful, she'd hardly call them appropriate. ``Well, Haruto \emph{is} full of surprises. White to level 5, R4.'' Shaking her head she added, ``You should see some of the things he's gotten me.''

\chapter{}

\emph{Bang!}

``Cough, cough, cough.'' Aeliana waved away the smoke as she sat back leaning away from the mess before her. 

\emph{`That makes thirteen.'} She thought as Charlie wheeled into the room. 

``Another one Mistress Aeliana?'' He asked as he began to clean up the ruined chips before she could even begin to move.

``Unfortunately,'' Aeliana replied. As she watched her work be dumped into a recycling bin. ``I was sure having three in parallel would help.'' She muttered to herself as she pulled out her nearby tablet to review her calculations. All estimates based on heuristic modeling. The amount of power needed to run even the tiniest maneuvering program for her relics was simply staggering. ``Honestly, I'm not sure how AIM tech does it.'' She continued aloud.

``Perhaps Young Haruto can assist.'' Charlie replied her work bench looking nearly brand new after his cleaning. His head swiveled around as if just the words would summon Haruto. And normally, the would. Haruto seemed to have a second sense for when he was wanted.

``Yeah, that was my idea. Only,'' looking up she spread her hands, helpless to the situation. Haruto was the only person she knew with an AIM that wasn't produced by a Clan. If there was anyone who could help her develop a guidance chip that could run a relic system, it was him.

``Oh dear, is the Young Master still begin detained?'' Charlie questioned real concern on his synthetic features.

``Probably,'' she sighed as she turned away from the autobot. Thinking of Haruto wasn't going to improve her day. Pushing her tablet away from her, she stretched in her seat. \emph{`Although the lawyers will probably have a field day with this.'} She thought.

``Isn't it past the 48 hour hold?'' Charlie questioned. Aeliana nodded in response. ``Isn't that illegal?'' He looked into space for a moment before answering his own question. ``Yes, it's against rule 37.''

``That's civilian law, Charlie.'' Aeliana replied as she stood. ``Besides, if they over step, mother and father will have him out of there.'' She continued turning to face the worried autobot. ``So don't worry so much. He'll be alright.''

\emph{`Not like he isn't used it this anyway.'} She thought to herself, but thought better of sharing it with the autobot. Charlie was still new, and seemed to have a soft spot for Haruto. \emph{`Along with my mother. The two of them could start a Haruto worrying group the way they go on about how much he's eating.'}

``Well, if your sure.'' Charlie replied although his face was still stuck in a worrying expression.

Aeliana nodded as she spoke, ``And since I can't get anything more done, I'm going to go shoot something.''

``Oh yes,'' Charlie replied as he wheeled back to give her space to move. ``Do tell me how firing of your blaster goes. I'm learning new cleaning techniques for the weapons and want to know which work best.'' He continued.

``No problem, Charlie.'' Aeliana replied. Erik had already told her about the new protocols he'd given the autobot. She'd been expecting something from Charlie any day now.

Standing in front of the firing range, she unlocked her blaster. \emph{`What am I doing wrong?'} She thought as readied the weapon. \emph{`Is it the guidance chips?'} She questioned herself. ``Open range.'' She called out.

In one smooth motion, the range appeared from the custom made enclosures in the wall. A gift from Erik. Her current target, Akihiko's head - a gift from Haruto, whirled around the range in a randomized pattern. Even so, her BISM program tracked the floating head easily.

\emph{Pew, pew.} A second head entered the range. \emph{Pew, pew, pew.}

\emph{`Erik can't get me anything better than the guidance chips.'} She thought letting her mind think as she shoot holes into Akihiko's heads.

\emph{Pew, pew.}

It was just unfortunate that Haruto had found SB3-QB9 in a trash heap. Luck like that didn't happen to a person twice.

\emph{Pew, pew, pew.}

``Additional targets please.'' Aeliana called out causing two more heads to enter the field.

\textbf{\textsc{Calculating...}}

Aeliana waited the extra second it took for her BISM to track the movements before she started shooting. 

\emph{Pew, pew, pew, pew.}

One shot, each on the mark. \emph{`What am I going to do?'}

Before she could fire again, red lights flashed in front of her. \textbf{\textsc{Warning, visitors approaching.}}

``Visitors?'' She questioned aloud as she took a step back from the range. \emph{`We don't get visitors.'} ``Charlie?''

``Yes, Mistress?'' He called as he rolled to the edge of the firing range. 

``It seems we're expecting visitors.'' She replied coolly. ``Could you prepare the warehouse?''

``Of course, Mistress Aeliana.'' He replied wheeling away a little faster than normal.

Turning back to her firing range she spoke, ``Close range.''

In a matter of seconds, the firing range returned to normal. Turning to her side, her blaster chest appeared beside her. A set of programs probably designed by Erik. Either way, she had her blaster carefully stored away, while Charlie took care of any loose ends. Although she doubted there were many as she'd yet to see Haruto work with anything illegal. 

\emph{`Well besides whatever he does on his console.'} She thought as she walked back to her own console, powered up to last weeks lecture notes.

As if on cue, she heard Charlie opening the door. ``Good afternoon, Master Helian, guests.''

Aeliana turned her head at the greeting, ``Dad?''

A moment later, her father came into view flanked by a team of Keepers. ``Stargazer.'' He replied warmly. Looking at her open console he continues. ``I'm so sorry to interrupt your studying, but I promised Yonaka I'd let a small group of his Keepers have a look around the warehouse.'' Her father looked at the group of five Keepers.

One stepped up, ``Sorry to intrude, Cadet Helian.'' A woman replied, Aeliana assumed she was the one in charge. ``This will only take a moment.'' The woman nodded to her fellow Keepers who spread out.

``Alright, tell me what I can do to help.'' Aeliana replied as she stood.

The woman walked over to her, ``First we'll need H\={e}id\`{o}ng's security clearance.'' She nodded to the Keepers walking to the warehouse security terminal.

Aeliana crossed her arms as she spoke, ``Haruto doesn't have security clearance.'' She turned to her father feigning confusion. ``Did mom tell them? Surely Haruto would have.''

Her father in turn looked over the woman in charge, ``Yes, well we just needed to double-check. If that's alright.''

Aeliana made her way to the security terminal. Opening it, she pulled up the access levels. ``See, Haruto isn't listed.''

``And this is the official...''\ the Keeper closest to her began, but was cut off by his boss.

``That's fine.'' She replied to Aeliana, ``search the open space, and check against the schematics.''

Aeliana walked back to her father as she waited. She could hear Charlie's voice muffled in the direction of the supply office. There'd be nothing in there. ``You don't happen to know when they'll let Haruto go?'' She asked her father.

``Technically, he's not being held for questioning.'' Her father replied. At her raised eyebrow he continued. ``Young Haruto's there because he's getting something out of it. But the Gongsaeng's are putting up a fuss about it. And you mother's starting to complain.'' He continued. ``They'll have to charge him, or let him go tonight.''

Aeliana nodded, \emph{`Good, because he's got a lot to answer for.'}

``I think your mother wants to have him over for dinner.'' Her father continued.

Aeliana snorted, ``So he can get arrested on the way there again.''

``Hey, that didn't turn out that badly.'' Her father countered. ``But yes, I did mention it was probably not the best idea.''

Before Aeliana could reply, a Keeper called down to them. ``Is this roof access new?''

Before Aeliana could say anything her father spoke, ``It was added to the blueprints several months ago.''

``Of course,'' Leader Keeper replied. ``Which one of these is Cadet H\={e}id\`{o}ng's console.''

``We'll want access to all of them, ma'am.'' The Keeper closest to the console replied.

``Haruto used the middle one, but you won't find anything on that.'' Aeliana answered.

``We'll be the judge of that.'' The Keeper replied as he attempted to log on. ``I thought you said H\={e}id\`{o}ng had no security clearance?''

``He doesn't.'' Aeliana replied sure the only reason her father would have agreed to this search was because of that little fact.

``Then how come we can't access it?''

``Because that one's offline.'' Aeliana answered easily.

``Offline?'' He questioned, but a look at the back of the console proved her statement true. ``Alright, could you log us into these other two.''

``No problem.''

Ten minutes later, and the Keepers were filing out of the room empty handed.

``Don't study too hard, my little Stargazer.'' Her father called out.

\emph{`Yeah, like that could every happen.'}

%%  LocalWords:  Komi couldn KANP OCI comms ve doesn Krai wasn didn
%%  LocalWords:  weren RL Sakr ng hadn taishi wouldn Wha Hwasan eo
%%  LocalWords:  Yonaka Haibeu Kur Kenta Akihiko autobot Isn isn Aeli
