\chapter{}
Serious problem with ship so forces Haruto to sit and review what they know

-this is not an easy task

they make a list, and after some thought she adds Akihiko's new AIM (she should question him about it before hand)

-they must locate the signal...

Haruto takes a minute to argue with QB9, before telling her about his Ghost Hacker Network.

-they argue about this for a minute before Haruto get's her to listen to him

...he can't hack into the GH network because he's still under servillance, but he could use her BISM to do it (and by he, he means QB9)

-They do this and find the location

103.14.6677

\chapter{}
The coordinates from the message was taking her through the red light district. \emph{`This has got to be the stupidest thing I've every done.'} She thought to herself. ``Hey, doesn't it sound like a great idea to follow an anonymous message to the Lower Level?'' She mocked softly to herself. But she was here now. In search of that power, uniqueness. \emph{`My way out.'}

Aeliana startles as empty beer cans roll in front of her. Turning sharply she hears a groan followed shortly be a, well, probably a person push out from under a pile of garbage. Shaking in disgust, she moves quickly past the man? Woman? Not that the next street is any better.

She wasn't sure if it was the smell that put her off, or the fact that around every corner there seemed to be piles of trash. Some of them having people just piling around them. Why anyone would come to the Lower Levels was beyond her comprehension. More importantly, the piles of trash was just a waste of money. Instead of sleeping under it, these 'people'{} would benefit from just selling it to the nearest compostor. 

\emph{`That piles got alumina in it!'} She thought in outrage. Mentally calculating the number of units she could get for it. \emph{`What are these people thinkin...'} Her thoughts were interrupted as she accidentally bumped into someone.

``Oh, I'm sorry.'' Aeliana responded politely.

``Well, what do we have here, boys?'' Dirty man, attract attention to some kind of dice game. \emph{`Gambling? It's that illegal?'}\ she half turned looking around, but saw no Keeper patrols nearby. In fact, she hadn't seen a Keeper patrol in sometime.

``Yeah, what's a pretty little think doing in the slums?'' Another one asked.

``I must have made a wrong turn. Sorry, I'll just be on my way.''

Rough laughter. Hard grip on her bicep. ``Now, now. You just got here.'' He looked at her with a glint in his eyes that was unsettling. ``Wouldn't do, to just let you go. People might think us a rough bunch, not showing you a little hospitality.''

She tried to pull her arm from his grasp, but he held firm, ``No, that's alright. I've really got other places to be.''

``No.'' Gripped her arm tight enough that she felt a slight ting of pain before it was gone. ``I think you're in the right place.''

Assessing the situation, she was sure she could break this man's grip. The problem lay with her unfamiliarity with the territory. Getting away was one thing, staying out of this disgusting man's reach was another. \emph{`I just need to locate a patrol.'} She thought, but her eyes found nothing on a quick scan.

His grip tightened as he pulled her to him. She smelt his breath on her face, rancid as if he'd never heard of personal hygiene. Before he could say anything more, someone throw a metal box at them. Smelly man pulls back giving some much needed space. If he hadn't been probably be unconscious.

``Who did that?'' He roared.

``I'd leave that one alone if I were you.'' A man from across the street motioned toward her. A small crowd of people passing by without a thought.

``Oh yeah? Or what? You gonna do somethin'{} about it.'' He moved to reveal a blaster, an illegal blaster. \emph{`Oh Goddess, what have I gotten myself into?'}

The man across the street shrugged, ``Nope, just given some friendly advice.'' He spit on the ground. ``You're new on board, so you might not recognize danger when you see it.''

The man holding her companions fanned out as if ready for battle. They held themselves in a way that told Aeliana they had blasters as well.

``That sounds more like a threat, and me and my boys don't do \emph{threats}.''

The man across the street didn't blink, ``No, just a friendly warning.'' The man shook his head, ``That girl in your hands is the Helian heir.'' The disgusting man tightened his hold in shock before releasing her. ``Yeah, I figured you didn't want to get on the wrong side of the Guild. They're not really known for play nice.''

The disgusting man frowned but started walking away. ``Too skinny anyway.'' He muttered before calling back, ``Come on boys, lets find us a real beauty. Kanopos supposed to have some real lookers.''

Aeliana turned to thank the man across the street, but he was already gone. Shrugging she moved on. ``Yup. This is the stupidest thing I've ever done.''

A short while later found Aeliana staring up at a derelict looking building. She glanced back at the coordinate again. No matter how she looked at it, this... building, was the correct place. \emph{`Well maybe it looks better on the inside than the outside.'} She thought before finally getting the courage to push through the door.

The lighting was bad, but at least the place smelt better than the streets, so she continued on. There was only one way down the corridor, and better lighting the further she went. She grew more confident with every step. Soon enough she was outside of a door with light pouring out from the crack. It opened instantly on her approach.

``Welcome Cadet Helian.'' Man with white hair and glasses smiled over at her from an impressive looking console. Her family owned one similar that was only two models newer, or rather her mother did. Seeing as that model wasn't even out for public purchase, Aeliana was very impressed with the man's equipment. 

\emph{`This place must be well funded.'} Looking around she saw more of the same, high level tech confirming her thoughts. 

``I see you approve.'' He replied pushing his glasses further up his nose.

Nodding she spoke, ``I was a bit worried, coming from the red light district.'' She answered honestly.

Soft chuckles greeted her statement. ``Sorry, but rent anywhere else is impossible.'' He answered. ``Besides, we can't all have the fortune of the great Helian clan.''

``We're hardly a Clan. Mister?'' Aeliana replied as she took a step further into the room. \emph{`Is that a simulator?'} Her eyes catching a piece of equipment, she'd been sure was only allowed in official KANP studios. She relaxed a little at the sight.

``Hermes please. I'm not much for formalities.'' He replied as he held out his hand to be shaken. It was an gesture more common in the Kumo and Romulus Empires, but one she'd been trained to respond to nevertheless.

Offering her own hand without hesitation she replied. ``Helian Aeliana, but you already seem to know that.''

Pushing his glasses up his nose again, he smiled kindly at her. ``Yes. I take special interests in KANP students that would otherwise be over looked. And you, Cadet Helian,''

``Aeliana please,'' She interrupted.

Nodding he continued. ``Aeliana then.'' Turning to his main console he continued, ``You are by far the most overlooked and deserving of attention from my organization than ever there was a student.'' Picking up a tablet he added, ``Your test scores rival that of the Zh\`{u}r\'{o}ng prodigy, and heir Katsur\={o}. And your battle simulations are stimulating if nothing else.''

``Thank you.'' She replied hesitantly. She'd never heard of a KANP organization that focused on students like her. And if she were honest with herself, she was a little concerned that he seemed to have her full record list from KANP. Affiliated or not, those records were supposed to be classified.

``No, really it is a tragedy the backward nature of KANP these days. It wasn't always like that, but...'' He shrugged as he put the tablet back down. ``What can you do?''

She nodded, ``Right. About that. You said in your message...'' She trailed off, uncertain how she could phrase it without seeming power hungry. That wasn't her. She was just... desperate.

``Power?'' Hermes continued for her, a kind smile and gentle eyes seeming to not judge her for coming. ``I'd hope you were here for that. We, my organization and I, specialize in developing unique technology for optimizing the integration of the biological to the mechanical.'' Fixing his glasses he pierced her with a look, ``In other words, more powerful, more skilled, more daft use of ZenKZ-D.''

Aeliana took a sharp intake in breath. This could be her answer to everything.

``And, Cadet Helian. We want you as our next Pilot. We want to see you in OCI with the rest of the Clan heirs. But more importantly, we want to utilize your natural born skill so that you outshine even the K\={o}taishi.'' He let a long pause settle between them before coughing into his hand. ``That is, if you still want that. Becoming a Pilot, I mean.''

``Yes, of course. I just...'' Aeliana could see her future. A Pilot at last, but something nagged at the back of her mind. Her mother's voice. \emph{`Everything comes with a price.'} She thought as she was finally able to remember the saying. ``What do you want in return?''

``Return?'' Hermes parroted her question in what Aeliana knew was a stalling technique. ``Is not the betterment of Kanopos enough?'' Aeliana gave him a hard disbelieving look, which only caused him to laugh. ``You are right. Astute as your files suggests. There is always something. Isn't there?'' He replied around a smile.

Instead of answering her, however, he turned to a locked anti-chamber. Pulling on specialized gloves, he carefully extracted a chip of some kind. Turning towards her, he held it out for her to see. From Aeliana's untrained eye it looked to by some kind of guidance chip. Too dissimilar to the older AIM chips she'd read about in her studies, but also nothing like anything she'd seen. And the material? She was hard placed to label it, but it looked organic almost, and the strangest green she'd every seen. Sickly almost in color.

``This is the latest AIM, we've developed, and unfortunately, the survival rate is low.''

``AIM's don't have a survival rate.''

``This one does.'' Moving to put it back, he turned around fixing his glasses in the process. ``As I'm sure you were able to tell, the material is something my organization has developed, and is organic in nature. As such, there has been some rejection of the chip.''

``So, if I want this, extremely amazing, life changing power,'' Aeliana began sarcastically, ``All I've got to do in gamble on my life.'' \emph{`What a price!'}

Hermes nodded, ``As you say, there is always a price. But I've been increasing research into reasons for rejection and don't truly believe it will be an issue in your case. Otherwise, I wouldn't have bothered to offer.'' Fixes his glasses, ``You are, after all, the heir of a great empire.''

``I'd hardly call the Guild an empire.'' Aeliana replied tensely.

``But others might, and do.'' Hermes continued. ``If this were to go wrong, my organization would not survive the fall out with the Guild.'' Shaking his head, ``No, that is why I have gone through great lengths to double and triple check your possible compatibility. And the results are high.''

``How high?'' She needed to know all the fact before she agreed to anything.

``80\% success rate.'' Hermes answered easier. ``That's the highest success rate we've every had. So, the real question, I think is how badly do you want this? Being a Pilot?''

Aeliana knew the answer immediately, knew it in her heart. But this felt off, \emph{wrong}. She was missing something. ``Organization.'' She said softly as her mind produced the missing piece. ``You keep saying organization. You don't work for KANP, do you.''

``Alas, no. I am part of a privately funded organization that specializes in training novice Pilots like yourself.'' Hermes replied. ``Although all the equipment you see here is legally obtained.''

She nodded at the non-answer. \emph{`Private organization. Private funding.'} No name in that reply. A warning sign her mother had told her look out for, but did she really have a choice? What other way was she going to make it into OCI? Did she really have the option to decline this offer? She needed more time. Turning to him she smiled as if this were all a part of the Game. Pulling together all of the skills her mother taught her she answered diplomatically. ``This is a lot to take in all at once. I'll need some time to decide. That won't be a problem will it?''

``Of course not.'' Hermes answered easily. Smile just as kind and gentle as when she'd first walked into the room. ``Why don't you take the rest of the week to decide? And if not, that's okay. We have other novice pilots who want this with a passion.''

``Thank you, again.'' Aeliana replied as she made her way out of the building.

``I really do hope to work with you, Aeliana.'' Hermes replied as he waved her way.

Aeliana couldn't honestly say the same back, so she gave one more tight smile before retracing her steps back. \emph{`Do I have a choice?'}\ was her first thought. The next was just as difficult to answer. \emph{`How much of myself am I willing to sale to become a Pilot?'} The answer evaded her.

From the moment Hermes opened his mouth, she'd known she couldn't trust him. The facts about her life, KANP, his 'organization'{}. All left a sour taste in her mouth. She wasn't stupid. There was always more underneath the surface, behind the mask. She could recognize the Game just as easily as she could calculate shipping revenue. In her sleep. And honestly, that had never been in question.

\emph{`Can I sale my loyalty to an unknown organization? And for what? Power?'} The thought brought her up short. She wasn't a power hungry fool. Her parents raised her better than that. How often did her father take advantage of those seeking power like this? Her mother? Even now, she could hear her father's condemnation of those who didn't care who they stepped on to get what they wanted. Those who would betray you just as soon as it proved advantageous to them.

No that wasn't her, and yet... ``Do I even have a choice?'' She questioned aloud. She knew what her father would say. \emph{`There's always a choice, Stargazer.'} But Goddess knew how badly she wanted to be a Pilot. And right now, she didn't see any other way. This just might be her only option.

\emph{`Am I willing to sell my soul for this?'} She thought. \emph{`Play around with an organic AIM?'} For she knew, there'd be no going back. Not from this, not from something that had a mind of its own. 

\emph{`Do I have a choice?'} Before she could answer the question, she was roughly pulled into a back alleyway. The smell of decay abruptly reminding her that she was in the Lower Level, and that perhaps getting lost in her thoughts here was the best idea. 

``Look, you must be new here, but I'm a Helian. Why don't we all just go are separate ways?'' She replied as she turned to go. She didn't have time for this. Unfortunately, her exit was blocked by two very large men.

``Ha ha haa,'' a woman's voice chuckled lightly behind her. ``Do you heard this boys?'' She spoke causing Aeliana to turned back around to the clear leader of the group. ``You must think you're something else, don't you?'' She continued a hard gleam in her eyes.

``Look,'' Aeliana continued more cautiously. ``I don't think either of us wants any trouble. So why don't we just walk away?''

``Well aren't you,'' the woman paused a tight press of her lips giving the lie to her next words, ``\emph{sweet}.'' She nodded her head at her companions. ``Take her,'' she commanded causing her men to grab each of Aeliana's arms. Aeliana struggled for a moment, but the oversized men over powered her quickly.

\emph{`Just great, Helian. How are you going to get out of this one?'} She thought as the woman before her circled her slowly. A predatory glint to her eyes. Pausing in front of her, the woman leaned into her, Aeliana met her head on.

``Now, I wonder,'' she whispered in her ear as her hand caressed Aeliana's face. Aeliana tried to jerk away, but the woman pulls her face towards her. ``I wonder, how much mommy and daddy will pay to get you little snot nosed brat back.'' Aeliana tightened her jaw as she pulled out of the woman's grasp. 

``A lot actually,'' responded a voice Aeliana recognized from behind them. The woman looked up in surprise at the intruder, but it was already too late. The men holding Aeliana slop down in a heap. Unconscious or dead, she didn't know and didn't care.

The woman backpedaled in fright. ``Look, I...''

But the intruder cut her off. ``Not that you're going to find out.'' Erik stepped out of the shadows. His blaster aimed at Aeliana's would-be capturer. He fired in the next second causing the woman to slump over limply. \emph{`Goddess, I hope that was set to stun.'} She thought as she stepped over the down bodies by her feet to move to Erik. Her concern ending with the thought.

``Do I even want to know, why you're down here?'' Erik eyed her pointedly his blaster nowhere to be seen. Aeliana looked away in guilt, but Erik must of took it another way. ``If this is about that Amur kid...''

``Not everything is about \emph{Ilia}, Erik!'' She snapped. Looking up at his sharply. At a time like this, she didn't even want to hear Ilia's name. The last thing she needed was Ilia's voice in her head too. Her parents were disapproving enough.

``Hey, hey,'' Erik replied hands up in defeat. ``What a guy to think? You being down here 'n all?'' He looked around to emphasize his point. ``If you didn't notice, ain't too many options in the Red Light district.'' He continued suggestively.

Aeliana hurried ahead in an attempt to get her blush under control, but Erik's longer strides had him next to her in seconds. ``You're not my minder anymore Erik.'' She replied tensely. ``You don't need to be here.''

Erik pulled out a bag of dried fruit from somewhere in his overalls. Popping one in his mouth, he spoke between bites. ``You think I want to be here?'' He swallowed before continuing, ``at least not on the clock, anyway.'' He raised his eyebrows suggestively as he smiled wide. 

``Try not to get your food everywhere.'' Aeliana replied sarcastically as she continued at her brisk pace, even though she knew she'd never lose Erik. 

His smile never wavering. ``Hey, what happened to not be a kid any more, huh?'' Popping a couple of dried fruits in his mouth he continued, ``Ya tired of 'hat already?'' 

Aeliana walked a little faster. 

``Anyway, I'm over at the docks, when I get message sayin'{} yous in the Lower Level.'' He took another large bite of his food. ``And not 'n the clean part, well,'' shrugged as he corrected himself, ``\emph{cleaner}, part of it.''

``Can we not?'' Aeliana asked, but Erik continued as if she'd not said anything.

``And without Tommy or me. So of course, I've gotta make sure everything's on the up and up.'' He popped another handful of his snacks into his mouth as he looked her over. Searching eyes that caused her to look away. Judgment she could have taken, but worry... ``Ya know, if yous wanted somethin'{} down here. A good time, or whatevers yous kids get up to these days for broken hearts and such, all yous had ta do was ask.''

``I'll remember that for next time.'' Aeliana replied sharply. She just wanted this conversation to be over.

``Hey now, I just want to help.'' Erik replied.

``Well, I don't need it! Not now, not back there.'' She jerked her head as she replied. Knowing her anger was misplaced, but unable to do anything about it.

Erik shrugged unfazed. ``Yeah, yous probably right.'' He popped another fruit in his mouth. ``Yous no kid anymore. Touch as Zoranium metal, yous is.'' He smiled down at her with pride. ``And I wasn't to worried back there. The Guild's support on the rise down here. What with all those new jobs. Those idiots weren't gonna get too far. Not in Kanopos or anywhere 'n the Empire.'' He added just as proudly.

But the smug look bugged her. Here, in this cesspool of Kanopos, she was something. Her name meant \emph{something}. But in Solas? \emph{`I'm a nobody.'} The thought caused her to start laughing uncontrollable forcing them to stop in the middle of the street.

``Man, whatever yous on, I want some.'' Erik added next to her. ``Did ja get the good stuff off of K?''

For whatever reason that caused her to laugh harder. Bent over, tears sprang at the corners of her eyes. Erik patted her back awkwardly. After a moment her laughing fit passed, and they started to walk together. Aeliana giving up on trying to loss him. ``Hey Erik.''

``Yeah.''

``Thanks.'' She smiled sadly back at him.

``Don't mention it.'' Erik replied. ``No really, don't. If ya folks find out about this one.'' He shivered at the thought. ``The old man would have my \emph{head}.''

``You saved me. That's hardly a bad thing.'' Aeliana replied.

``Shouldn't ah had to.'' He bumped his shoulder gently into hers. ``I'm supposed protect ya remember. Make sure ya don't need save'n.''

Aeliana looked away. Her mind back to internal struggle, the reason she'd been down in this dump. Was she willing to sale her future for an impossible dream? To owe another a debt she would eventually be called to pay for? The answer eluded her, so she tried for another. ``Why do we try so hard?'' She questioned aloud.

``Huh?'' Erik asked as he popped another handful of dried fruits in his mouth.

``I mean, what's the point. Of fighting for the impossible. Of trying to be something we're not.'' She elaborated.

Erik looked at her for moment, weighing something in his head before replying, ``For fun I guess.''

Aeliana didn't try to hide her frown. Rolling her eyes, she turned away from him. \emph{`I'm a fool for thinking Erik could be serious for a second.'} She thought bitterly.

``No hear me out.'' Erik continued around a mouthful of food. ``Ya remember that time the old man took us to Sevian Nine?'' Not seeing where this was going, she nodded all the same. ``The old man wanted us all ta take the Sevian track. Big, popular, safe. He'd gone on it a dozen times already. Just couldn't wait ta take us.''

Aeliana remembered. She'd been twelve and her father had decided to use one of her vacation days for a family outing, a day trip to nearby Sevian Nine - the ultimate theme park. They'd been stuck for days near the system from what was supposed to be a routine re-fueling, but had ended up as a major repair stop. In those days, Erik spent more time off ship than on it. A change that had only happened after she'd joined KANP. As such, the few fun days they spent together always stuck with her. ``Yeah, he'd set his heart on it. But Ilia had talked about the advanced track for ages since her parents let her go the year before, and I just had to give it a try.''

Erik nodded as he popped another unrecognizable dried piece of fruit into his mouth. ``Yeah, and we had a blast, did we.'' She nodded in agreement. While she didn't see a connection, it was still a pleasant memory. ``See, it would'a been easy ta go on the Sevian track. And we'da probably have a blast on it too. But you'da been disappointed.'' He nodded to himself as they made it to the outskirts of Solas. ``I fig'ya it's 'cause ya had ta try so hard ta convince da old man ta let us go. 'cause when ya try hard, it means a little bit more when ya succeed. It's like ya win twice, ya know.''

Aeliana nodded hesitantly still not completely sold on the idea. ``And what if you fail? What then?'' She asked.

Erik shrugged. ``Then I guess ya try harder next time, huh?'' He looked around them as he continued to speak. ``Anything worth anything is going ta be real hard ta get, ya know. That's why it's fun. The easy stuff just ain't worth it in my book.''

Erik's BISM buzzed. He pushed his bag of food in his pocket. ``Look I gotta go. Stay outta trouble, kiddo.''

Aeliana waved goodbye, ``Bye Erik.''

``Oh, oh. This never happened. Yeah?'' He added walking backwards.

``Never happened.'' She replied easily. Meaning more than he could possible know. Hermes was offering her an easy path that just didn't \emph{feel} right. An option for someone truly desperate.

With nothing pressing, Aeliana found herself walking aimlessly through Solas. Her thoughts running in circles questioning her own decision. Without Hermes's offer, she was back to square one, no plan of action that would change her future. Even so, she couldn't find it in her to regret her decision. There was desperation and then there was foolishness. And both were trouble.

\emph{`How desperate am I to have even, for a moment, considered putting some unknown possibly sentient material into my body?'} She thought. That answer was perhaps the real problem. All she knew was that she never wanted to feel that desperate again. \emph{`I can't let my happiness be dependent on OCI. I have other options.'} She continued. She was, after all, the heir to the Guild. 

So what if the thought of leading an intergalactic company didn't set her heart racing in the same way piloting a ZenKZ did? It was honest work, well mostly honest. More importantly, it was her family's life work sense the chase into space. Her history, the Guild's legacy, rivaled the Gento Clan's. If that was to be her lot in life, then she'd make it work. Because even now the thought of being someones head Tech was unpalatable. 

Nodding to herself, she looked up, taking in her surrounds. She snorted in disbelief at the building facing her. \emph{`The library, huh?'} A small smile broke out on her face. She couldn't even be surprised her body had taken her here. And what better place to be?

Walking into the building with her head held high, she knew she would not, could not, surrender to her fate just yet. For now, she had one goal; getting into OCI. And if she failed, it wouldn't be because she didn't put her all into it. 

Her will renewed, Aeliana walked to the back of the building away from the foot traffic and to the individual consoles. Her home away from home. Nodding to familiar faces, she was brought to a halt in front of \emph{her} console. Red hair that could only belong to one person in all of Kanopos sat staring at her screen, typing away.

<Should have Haruto get the Kotaishi involved with this.> Seway into next section.
Aeliana suggests they get the Kotaishi involved.
``The what now?'' Haruto.

``The K\={o}taishi!'' Aeliana upset. Buzz from her BISM.

QB9 - The Princess, idiot.

``Oh, yeah. I'll message Yakei now.''

``Yakei?'' Aeliana questioned softly, but Haruto was already in another world.
