\part{The Gento Heir}
\chapter{}
This is a Chapter frome Yakei point of view...

<they use a Haruto prank to get the Keepers there the next day, but already gone>

\chapter{}
This chapter should center around the Guild...

I want to know more about it, and tie in that this is her back up...

Here, there should be a mention of Haruto trying to get the new location of the shadow organization... They are being, much more careful, but Haruto is sure they'll mess up somewhere...

\chapter{}
...end of a session, Aeliana watching, Watai takes her aside... should get lots of banter between the main people in AI head department.

-Lieutenant Commander Q\'{i}sh\`{a}n doesn't like her, should be some hostility

Watai gives Aeliana a TARGET, boss lady wants her to replace (some guy) on Targeting. (Now you're officially a tech - Watai)

Aeliana takes it with her... Boss lady asks about it (mentoring here)

...Aeliana gets to the warehouse and puts it on...

...power was great, wished she could have it...

...or at least have Haruto here so he could copy it and they could make another... she looks over at his console, but doesn't dare go anywhere on it...

...some mention of QB here...

...end with her using it more...

\chapter{}

``Initiating prototype A9Q-ZZ.'' Lieutenant Commander Q\'{i}sh\`{a}n tenor voice called out. 

Aeliana console showing her the dummy ZenKZ in the largest anti-gravity chamber she'd ever laid eyes on. The largest anti-gravity chamber on KTS Kanopos. Numbers running across her screen as the ZenKZ came alive, pilotless.

``Systems online.'' Lieutenant Watai's lighter voice followed as she typed furiously at her console, ``Connecting to guidance system.''

The visual unit within the ZenKZ light up on her screen, as she reviewed her own contribution. \emph{`Everything's looking good so far. Nothing I would change at least.'} Aeliana thought as she connected to the ZenKZ dummy guidance system along with the seven other Technicians on the power terminal. Here, she had important role to play.

\textbf{\textsc{98..99..100}}

``Command connected.'' Q\'{i}sh\`{a}n continued. ``All support systems quality control running.''

A new bar entered her screen as the firing system, targeting system, neural guidance, and so much more came online. Each being micro-tested in real time before the theoretical launch. It was amazing to watch and far more complicated than she could have every imagined. Her own console only covered the targeting systems. The patch she'd worked into its core code the actual reason for this testing.

\emph{`Now, lets just hope I haven't screwed anything up.'} She thought as she ran her diagnostic protocols on the targeting systems. Another Tech would be running diagnostics on firing, and another on the interconnections. Only the Head Technician would monitor all systems function. Something, at this moment, she couldn't imagine doing herself.

\textbf{\textsc{All systems functioning.}} Her diagnostic came back clean, so she connected to the ZenKZ network. ``Targeting coming online and on standby.'' She spoke aloud.

``Good job Targeting.'' High Commander Chin\={o} replied, ``Firing, don't tell me a KANP student can go faster than you.''

``Firing at 92\%, ma'am.'' Lieutenant Kim called out as his head was bowed over his console. 

``Good.'' The High Commander sat at the Head Technician's console eyes monitoring the system. 

Aeliana looked away. When she'd agreed to shadow a Head Technician after Sergeant Sang-eo had strong-armed her into it, she had not been expecting to be under the leadership of arguable the most important Head Technician on Kanopos, High Commander Chin\={o}. As the Head of the Department of Artificial Intelligence, she was one of the three leaders of the DOMAINE.

\emph{`I don't know what kind of pull Sergeant Sang-eo has, but it must be pretty impressive.'} She thought. She would also have to thank the Sergeant for the experience. While she'd been more than skeptical about using her two week vacation to shadow a Techie, Head Technician or not, she'd not been able to argue against the experience.

Every year she did a project to gain the 300 points of extra credit. A fact that Ilia used to tease her about every time. Used too, anyway. After last year, Aeliana hadn't even realized that had been something she could miss. So much so, that she'd contemplated not doing it this year. She didn't need it and she'd been struggling to come up with something interesting to do. Enter Sergeant Sang-eo.

When the Sergeant had confronted her about learning more about Techies as her extra credit project, she'd been in no position to turn him down for a number of reasons, so she still wouldn't admit to herself. \emph{`That and I barely know anything about the profession.'} She added mentally. Her embarrassment over the fact just as fresh as when the Sergeant had quizzed her on the topic. She'd not soon forget not being about to give the acronym for the DOMAINE. Something now, she'd not soon forget. But that had more to do with what the Department of Mechanical, Artificial Intelligence, and Neurological Engineering stood for to her now. What the High Commander Chin\={o} had made it about.

Of course, she'd never planned on needing to know anything about the DOMAINE and the Tech world. But she could hardly imagine telling the Sergeant that. \emph{`Actually, I going to take up the family business if I this OCI stuff doesn't work out.'} She thought mockingly in her head. Suppressing a shake of her head, she could already imagine how that would go down with the Sergeant. His disappointment easy to conjure up.

``Firing online and on standby.'' Kim called out.

``Interconnection, tell me you're not far behind.'' High Commander Chin\={o} questioned.

``Linking now, ma'am,'' Q\'{i}sh\`{a}n answered.

``Neural guidance online. Waiting on standby, ma'am.'' Watai replied.

``Propulsion on standby, ready at you're command.'' 

``Fusion core stabilized.''

``Visuals online, dummy linked and on key monitor.''

The tenor voices sounding off one right after another too fast for Aeliana to track as new to the AI team as she was. Her eyes stayed on her console, sure that they'd be ready for testing soon.

``Do we have audio?'' The High Commander demanded.

``Audio coming online now ma'am,'' the Techie in charge of visual replied, Lieutenant G\u{a}nju\'{e} if Aeliana was remembering his name properly. ``Pairing with visual now.''

``Gyro systems running, ma'am,'' Lieutenant Suyeom added. Aeliana's eyes falling on the breaded man she was pretty sure held some familiar relationship to the Sakhalin Clan given his size and heavily breaded face.

``Interconnection, mechanical online,'' Q\'{i}sh\`{a}n continued, ``Pairing with guidance systems.'' Another second and the Lieutenant Commander looked up, ``All systems ready, ma'am.''

The High Commander turned to the larger Halo screen of the ZenKZ dummy in the anti-gravity chamber. ``Pull up targets so we can get this thing started.''

``Yes ma'am!'' Aeliana coursed with the rest of the group.

As if on cue, a single round target appeared in her viewing screen. \emph{`Okay, this can work.'} She thought.

``All stations on standby, taking control of prototype A9Q-ZZ.'' The High Commander replied, her console transforming before Aeliana's eyes. Each time she watched, she was just as fascinated. Controls she was familiar with during her own KANP Pilot simulations appeared on the Head Tech's console. Minus the helmet and body armor, and Aeliana could have mistaken the High Commander as a Pilot.

Her attention was pulled to the Halo screen as the dummy ZenKZ started do move. Limbs moving in the well taught systems diagnostic test Aeliana had, herself, performed countless times now. Only the High Commander finished in a blink of an eye. Moving at a speed, Aeliana could only hope to achieve in the future.

``Firing protocol begin.'' The High Commander called out as she released her weapon, a single wielding machine.

Just as soon as the High Commander shoot the stationary target, two more popped up. Without waiting, she continued, taking both out with two shoots. Aeliana looked at her screen, \emph{`Dead center. Yes!'} She thought. As two became four and four became eight. Aeliana was impressed at the Commander's speed. \emph{`But how will she handle, 64?'} She thought as the final targets appeared in the field.

Dropping the ZenKZ level blaster, the High Commander continued, ``Command overwrite. Activating ballistics system.''

``Heard Command.'' Kim replied. ``One of four ballistics ready for launch.''

``Launching.'' High Commander Chin\={o} continued, and the ZenKZ transformed again. Aeliana leaned into the screen, never having seen this before. The chest of the ZenKZ opened to reveal a missile launching system. A millisecond later and the rocketed all at once causing the stationary targets to be destroyed in a flurry of explosions. \emph{`Almost like fireworks.'} Aeliana thought as the screen slowly cleared.

``Report.'' The High Commander commanded.

Aeliana looked over the targets, her mind taking in the data. ``100\% accuracy, all targets destroyed.'' Aeliana called out as she looked up in wonder.

The someone near her snorted, ``The Gods be praised, huh?''

Q\'{i}sh\`{a}n voice was unmistakable when he added, ``Impossible, 100\% Cadet, you sure?''

Aeliana turned to the Lieutenant Commander, ``All shots fired hit bullseye. That is unless the targets reporting if off.''

He sneered at her, ``How dare y...''

``Enough.'' The High Commander replied, ``I don't have time for you to bicker, moving on to phase two.''

``Roger!'' The group coursed.

Q\'{i}sh\`{a}n turned back to his console, ``Adjusting randomized programming.'' His hands typing furiously, ``Readying targets, High Commander. Any second now.''

``Good,'' the High Commander replied as she stream leased from the ballistic unit as it closed. She pulled the blaster back out.

Without warning, a target popped out from behind the High Commander shooting off at a velocity significantly faster than Aeliana had every calculated. \emph{`Star dust!'} She cursed mentally as she pulled up the targeting program. With the Commander's skill, the first target was destroyed in seconds, quickly followed by the two after it moving in randomized directions and at speeds Aeliana had not accounted for. By the time, she had the targeting results up, the Commander was already destroying the next four.

\textbf{\textsc{99.8\% accuracy target 1; 97.5\%, 93.2\% accuracy targets 2, 3...}} Her analysis reported.

\emph{`Why didn't I account for asteroid speeds?'} She thought. \emph{`Oh, that's right. No ZenKZ can move that fast.'} She knew that Q\'{i}sh\`{a}n was just getting back at her, but she would not be provide wrong. Typing furiously, Aeliana adjusted her targeting algorithm.

``Command overwrite. Engaging ballistics.'' The High Commander spoke as she moved, but Aeliana didn't look up. At the current velocity, accuracy was bound to fall to 80\% plus or minus 2.6\%. 

``Two of four ballistics ready for launch.'' Kim called out.

But more importantly, she was sure Q\'{i}sh\`{a}n would use the results to not enact her patch. \emph{`Well, I won't let you win.'} She thought as explosions sounded in the background. \emph{`There, updated. Now, do I have time for a simulation?'} She thought as she looked up. But the smoke had cleared.

``Targeting report.'' The High Commander demanded a little breathless. 

Aeliana's eyes reviewed the data, ``Average accuracy dropped to 82.1\%, High Commander. 93.7\% of targets destroyed.'' 

A snorted replied, ``Figures it couldn't handle moving targets.''

``82\% accuracy is still very good,'' Watai replied as she looked over at Aeliana with a smile.

``Yes,'' the High Commander replied as her ballistics cooled down. ``With a few adjustments, it will be battle ready.''

``High Commander Chin\={o}?'' Aeliana called out hesitantly.

``Cadet Helian?''

``I believe I've made the necessary adjustments.'' Aeliana replied.

``Impossible.'' Q\'{i}sh\`{a}n interrupted.

``If you'd let me, I'd like to run it again.'' Aeliana continued stronger this time.

``High Commander, she's just wasting our time.'' Q\'{i}sh\`{a}n replied. Aeliana looked around and all of the other Techies had skeptical looks on their faces. ``No one, can adjust on the fly that quickly. At least not a KANP student ma'am.'' He continued. ``We've humored her enough.''

``Lieutenant Commander Q\'{i}sh\`{a}n, do you make the decision here?'' the High Commander asked.

``Wha? No ma'am.'' He replied stiffly, ``I would never dream of commanding you.''

``Than, I'd like to run the targeting protocol again.'' The High Commander replied. ``Cadet Helian, upload your adjustments. Let's see how close we can get to 100\% accuracy.''

``Yes ma'am!'' Aeliana called out as she turned back to her console. Q\'{i}sh\`{a}n leaned back in his chair, frown on his face, but she ignored him. ``Uploading now.''

``Re-initiating.'' Q\'{i}sh\`{a}n replied in a flat tone. ``All systems ready. Targets coming online, momentarily.''

``Command ready.'' The High Commander responded her blaster at the ready. ``Let's make this good.''

Just as before, the targets at impossible ZenKZ speeds. One, than two, than four destroyed in a matter of seconds. But Aeliana was more concerned with the results. \emph{`Come on, come on. What is it?'} She thought as her screen finally spat out the results.

\textbf{\textsc{100\% accuracy target 1; 100\%, 100\% accuracy targets 2, 3; 99.9\%, 100\%, 100\%, 99.8\% accuracy targets 4, 5, 6, 7...}}

\emph{`Yes!'} She thought as the results flowed on her screen. \emph{`Take that Q\'{i}sh\`{a}n.'}

``Command overwrite. Ballistics online.'' The High Commander called.

``Firing responding, three of four ready for launch, ma'am.''

``Launching!'' The High Commander responded. This time Aeliana's eyes were on the screen as 64 moving targets danced around the High Commander some racing at her. Aeliana was surprised she could move while engaging the ballistics overwrite, but the High Commander dodged racing targets and a millisecond later missiles launched turning the screen into lights and sound.

Aeliana held her breath as the smoke cleared. ``Tell me what we have, Cadet Helian.'' The High Commander replied calmly.

Aeliana smiled as the results came in. Averaging them mentally as they flashed before her screen. ``99.13\% average accuracy, ma'am.'' Looking up she smiled openly, ``100\% of targets destroyed.''

``Wow!'' The majority of Techies cheered.

``Way to go, Cadet Helian,'' Watai cheered her own with a large smile, while Q\'{i}sh\`{a}n remained silent.

``Well, then I'm disengaging.'' The High Commander replied as she began the process of shutting down the dummy ZenKZ. ``Lieutenant Commander Q\'{i}sh\`{a}n, power us down.''

``Yes ma'am.'' Q\'{i}sh\`{a}n replied. Aeliana pushed slightly away from her station. The Lieutenant Commander was the only one needed for this part.

``Good job, Cadet Helian.'' High Commander Chin\={o} replied suddenly by her side. ``I'd say, your little patch is battle ready.''

``Thank you High Commander. If not for your confidence in me...'' Aeliana replied just as softly.

``None of that.'' The High Commander replied. ``A good leader always knows when to push the boundaries of their people. And I'm not sure, I've pushed you far enough yet.''

Aeliana smiled at the complement, but before she could respond slow clapping grabbed their attention. Turning to the testing room entry way, Aeliana was surprised to see the K\={o}taishi. But it was the old Gento standing next to the Gento heir that seemed to have the High Commander's attention.

``Impressive Woong. Your skill at the helm is always something to admire.'' The old man spoke. ``Testing a new targeting patch? Or will it be in the next model of your amazing m-TARGETS technology?'' He continued.

``Gento Genshir\={o}, an honor as always.'' The High Commander responded with a small bow returned in kind. ``And of course, we are honored to have the K\={o}taishi in our presence.'' She added causing the room to murmur in awe. ``But I cannot take the credit for this new targeting patch.'' She continued hand resting on Aeliana's shoulder. ``Cadet Helian Aeliana, one of KANP's finest is with us for the transition season. And she has surprised all of us with her brilliance.''

``You are too kind, High Commander Chin\={o}.'' Aeliana replied softly.

``Helian?'' Gento Genshir\={o} rolled her name in his mind. ``Yes, I'd heard the heir was at KANP.'' The old man pierced her with a look, but Aeliana held his gaze. ``Well than perhaps, you have a bright future in the AI Department.''

``I'm still hoping for OCI.'' Aeliana replied with a easy smile. A technique her mother had taught her disarmed older men.

The tilt of the older Gento was as much as she got in reply. High Commander Chin\={o} interrupted the stare down with a question of her own, ``Now, what brings you to this side of the ship, old friend?''

``The Honorable Yozora has asked that I teach the K\={o}taishi the values of the Technicians.'' He turns to the K\={o}taishi, ``As such, what better place to start but the DOMAINE, the birth place of modern day ZenKZ-D technology.''

\emph{`That's putting it lightly.'} Aeliana thought in reply. As she was coming to learn so much about the DOMAINE and the Tech world. That had surprised her the most. How KANP got away without teaching just the basic history behind the AIM, Aeliana would point to hubris. 

The High Commander gave a full laugh at the declaration. ``If only others saw us in that way, huh. I'd love to stop fighting KANP for funding.''

Genshir\={o} nodded, ``The Honorable Yozora makes it a priority in his council dicussions. As I'm sure the Honorable K\={o}taishi will when she takes her seat.'' 

The K\={o}taishi bowed at the statement. ``It would be my honor for without the advancements of the DOMAINE, KTS Kanopos would not be the envy of the Five Great Empires.'' She responded.

Genshir\={o} nodded as he watched the AI Command positioned Techies leaving the room. Aeliana wasn't sure if she should follow, but given that she'd have to push her away around the High Commander, the K\={o}taishi, and the old Gento, she opted to stay put.

``Speaking of the great and powerful KTS Kanopos,'' the High Commander began. ``Is it true that Guardian Kamaitachi will be the new Guardian Commander?''

``Yes, despite the Clans complaints.'' Genshir\={o} replied stiffly. ``But the man is qualified despite his family. And it's long past time that Guardian Inugami decommission.''

High Commander Chin\={o} nodded, ``Too long in the mask is never good for the psyche.''

``Yes, and the OCI cadets will learn much from him.'' Genshir\={o} added pausing with a distant look. ``It seems Neurological Department is ready for us. It's a pity Octavia is busy with the annual Cram session. The K\={o}taishi could have learned much from her insight.''

``I'm sure there will be another opportunity for High Commander Stone to provide her insights.'' The High Commander commented. ``Please don't hesitate to call if I can be of assistance.''

Genshir\={o} nodded, ``Come K\={o}taishi there is much left for you to learn today.''

The K\={o}taishi nodded at the man before turning to Aeliana, ``Goodbye Cadet Helian.'' 

``Ah, bye. Cadet Gento?'' Aeliana replied weakly with a small wave of her hand as the two left.

The High Commander raised an eyebrow when they were alone, ``You didn't tell me you knew the K\={o}taishi.''

\emph{`Know her?'} Aeliana thought to herself as her eyes found the door. \emph{`Haruto maybe, but me?'} ``I wouldn't quite say know.'' Aeliana replied after a moment in thought. ``We've talked a few times that's all.''

``Still more than most.'' The High Commander replied with a sigh, ``I suppose you both run in the same circle, huh?'' She added.

Aeliana shrugged a yes in a way her mother would have winched at. ``Somewhat I guess.''

High Commander Chin\={o}'s eyes lite up in amusement at her response, a small smile at the edge of her lips. ``Anyway, I've been meaning to talk to you about the future.'' She held her hand out to stop Aeliana from responding, ``And yes, I know your first goal is OCI. What young KANP student doesn't want to be a Pilot?'' She asked rhetorically. ``Honestly, after just a week with you, I'd say us DOMAINE folks won't have a chance to recruit someone of your caliber. But yours is an odd birth year.''

``So everyone keeps saying,'' Aeliana answered bitterly.

``The Clans used to stagger births mostly to keep top marks, but that got lost a two generations ago. An accident or not, your situation is the result.'' High Commander Chin\={o} replied sympathetically. ``Which is why I want you to keep that TARGET in your arm.''

``What?'' Aeliana questioned as her hand hovered over her BISM. ``But, I thought this was just for the remainder of my shadowing program? So I could connect to the system.''

``And so that's what I told you.'' High Commander Chin\={o} responded. ``But there is no shadowing program, Aeliana. Sang-eo called in a favor I couldn't ignore, and I'm glad I didn't try too.'' High Commander Chin\={o} held Aeliana's gaze. ``I'd never intended for you to do anything, but each day your surpassed my expectations. And now that I've only got a few more days with you, I know you were meant to use one of our multi-Thread Adaptive Recognition, Global Emulator \& Tracking System.''

Aeliana didn't know what to say. ``High Commander...'' She began not sure how to tell her that she had no intention of becoming a Tech, begin stuck behind the desk.

``Yeah, I know. Pilot dreams.'' The High Commander replied. ``The thing is KANP isn't what it used to be. Politics what it is.'' The High Commander shook her head. ``Whether you end up at the DOMAINE or not, doesn't matter when it comes to this.'' The High Commander tapped her own BISM as she spoke, ``And I'm sure you've already figured out your little guidance chip can't do even half the stuff the Clan's AIMs can.''

Aeliana nodded. Having struggled with that realization over the past few months. Banking on Haruto to be able to find, steal, or help create an AIM of her own. \emph{`A long shot at the best.'} She thought as she absentmindedly cradled her BISM against her chest.

``So keep it.'' High Commander Chin\={o} continued. Winking at her she turned to leave, ``Besides, the DOMAINE could benefit from the first ever Pilot to use a TARGET instead of an AIM.''

``Thank you, High Commander.'' Aeliana called out as the AI Department Head paused at the door.

``Make us Techies proud, kid.'' She responded before exiting the room.

Aeliana found herself slumping back into her chair. She'd never imagined keeping the TARGET, but now she had in her possession the answer to her most pressing problem. The very first non-Clan ZenKZ-D interface system. The model that all AIMs were generated from. \emph{`A TARGET of my own.'} She thought.

Now only time would tell if her TARGET could keep up with the widely used AIM.

%%  LocalWords:  didn wasn KANP DOMAINE wouldn couldn OCI isn TARGET
%%  LocalWords:  ve ZZ pilotless eo hadn Wha taishi Genshir doesn nju
%%  LocalWords:  multi AIMs Watai Suyeom Woong Kamaitachi
