\chapter{}
Tap. Tap. Tap.

Aeliana's footsteps sounded in the hallway of Tower One. Here, emergency power had returned but every few steps the orange shallow lights would flicker on and off.

Tap. Tap. Tap.

Aeliana slow and steady footsteps grounded her in this unthinkable situation. Beside her came the quick steps of her parents best lawyer and family friend, Lieb Sara. Her soft breathly close and calming. The lights flickered staying off for a second longer than usual. Aeliana paused taking a shallow breath as her eyes fluttered shut.

Sara's hand gentle touched Aeliana's arm. Giving it a comfortable squeeze. Aeliana regained her footing and continued on. Before them the Command Captain Gento Daichiko had not gotten too far ahead of them. The stern looking woman turned slightly waiting for them to catch up, but otherwise showed no signs of well anything. Which, given that she was a Gento, wasn't all that surprising. 

Even so, none of that changed the fact that the Command Captain herself was going to be interrogating her. \emph{`I should be honored.'} Aeliana thought bitterly. 

After a long day at the Jade Festival, she just wanted to go home and relax. There she wouldn't need to worry about any of this.

The group paused as Keepers rushed out of double bolted room. Aeliana looked in to see a strile looking white room. Metal table, metal chair, and black glass. Chains linked from the floor, and two cameras in just the first glance. The door shut and they moved on.

\emph{`So, I'm not being interrogated there, huh.'} She thought as she continued to follow.

``How much longer are you going to parade my client?'' Her lawyer questioned harshly.

Command Captain Daichiko turned her head briefly to respond. ``Not much further.''

``Good, because the kindness of the Helian family can only extend so much. Especial after this very trying day.'' Sara answered in her slightly accented voice.

In response, the Command Captain stopped in front the next door. ``Understandable.'' She replied diplomatically. ``This should be it. Please.'' Motioned them inside as the door opened.

Aeliana stepped into what looked like one of her parents higher end conference rooms. A comfortable looking couch lined the wall, a long circular table in the center surrounded by high quality chairs meant for long meetings. It was something even her mother would approve of, and given the pleased look on Sara face it was acceptable accommadations.

\emph{`If that means anything.'} Aeliana thought. Be it a couch or a hard metal chair, this was still an interrogation. She didn't care what they were trying to called it.

``Thank you again, Cadet Helian for sitting down with us for this interview.'' Command Captain Daichiko replied as she pulled out one of the comfortable chairs for Aeliana to sit in.

Aeliana nodded her head in thanks as she took the offered seat. \emph{`At least the chairs are comfortable.'}

The Command Captain moved to offer Sara a seat as well, but she pulled her own out instead.

A handful of Keepers stood at the open door, the Command Captain motioned to them, ``Can we offer you something to drink, eat? Anything to make you more comfortable?''

Aeliana shook her head in the negative. 

``My client just wants to go home, Captain,'' Sara answered for her.

Aeliana looked away at finding a window with an amazing view of Solas. 

``Of course, then let's get started,'' Command Captain Daichiko began as she took a seat. Tilting her head slight she continued. ``Camera please.''

A panel opened up revealing a camera. The red light blinking open told Aeliana that it was recording. ``For the record, you are Cadet Helian Aeliana born FDY 256 born to...''

``Talia and Atticus Helian, or however you people say it.'' Sara interrupted the Command Captain.

The Command Captain continued as if not interrupted, ``Standing council for Cadet Helian is...''

``Sara Lieb L.\L.\ and a bunch of other titles we don't have time to go over. Please, if we could speed this up.'' Sara added pointedly.

``Cadet Helian, you currently attend KANP with Cadet H\={e}id\`{o}ng Haruto.''

``And six Clan members, four of which are heirs, not to mention another two dozen or so of \emph{regular} folks.'' Sara interrupted. 

``Be that as it may, recently you've spent a great deal of time in Cadet H\={e}id\`{o}ng's company.'' Command Captain Daichiko

Sara leaned in as she spoke for Aeliana, ``And before that Aeliana spent just as much if not more time with Ilia Amur.'' Sara's eyes narrowed. ``What's your point, Captain?''

The Command Captain didn't even flinch at the inapproapiate title. ``It was not Cadet Amur's family name written in Solas, Ms.\ Lieb, but Cadet H\={e}id\`{o}ng.'' She answered. ``For the record, we must describe the connection.''

``Loss connection.'' Sara answered.

``Furthermore, I would like to remind you both,'' Captain Daichiko looked at Aeliana as she spoke. ``This is not an interrogation. Cadet Helian has done nothing wrong. Please understand that you are here to help us find Cadet H\={e}id\`{o}ng Haruto for his crimes...''

``Allegded crimes.'' Sara interrupted.

``Against KTS Kanopos,'' she continued as if not interrupted.

``That hardly explains what my client can do for you.'' Sara responded.

``Currently, Cadet H\={e}id\`{o}ng's whereabouts are unknown. Given your relationship...''

``Which I must again state was no different than for many of her other classmates,'' Sara interrupted.

``Nevertheless, we believe you might have information that will help us locate him.'' Command Captain finished.

``For what?'' Sara demanded, ``So you can illegal detain him for days on end? Arrest him at school or his own home without good cause?'' Sara shifted in her seat as she continued, ``Given your track record, it's no surprise the boy wants to stay out of sight.''

Captain Daichiko's lip twitched very slightly the only outward indencator of her thoughts. ``All arrests made by my Keepers are within the bounds of the law.''

Sara gave a bark of laughter, ``Law? Please spare me the speech as we both know none of those incidents I'm speaking about would hold up in court. You should just be glad I'm not his lawyer, because I'd have sued you ten times over by now.''

Aeliana turned away as the bitter back and forth continued. The Command Captain defending her peoples actions, while Sara roughly dismantled it all. It was all seemingly pointless. \emph{`This is going to take all day if I don't say something.'} She thought.

``And another thing,'' Sara took a breath giving Aeliana the opportunity to cut in. Holding her hand out, the room went silent.

``What's the point?'' Aeliana spoke in the silence. ``Why do you think Haruto would every say anything to you even if you could find him?''

``Note that my client is not suggesting she knows where he is. Only asking what we all want to know the true motives behind this interrogation desguished as an interview.'' Sara

Command Captain Daichiko paused looking off slightly in the distance. Listening to something only she could hear. A slight nod and she turned to face Aeliana directly. ``This is not prank...''

-gives a big speech about how badly the prank damaged the ship. It will take months maybe even a year to fix the problems... the blackouts aren't going away. What they need is a starting point to speed up the process. They hope they can implore Haruto to give up how he attacked the Towers so that they can fix the problem.

-Aeliana shakes her head, knowing that's not going to work on Haruto. ``I really don't know him that well. He's either at the warehouse, his apartment, or Santuarary Park.''

``All places you've already searched.''

Daichiko looks at Aeliana as if seeing if she's telling the truth. And she was, Haruto spent time in the Pray Alley because that was here his Princess was at. ``Honestly, I don't even know where his apartment is.''

-Lawyer gets up to go. says something about how their done here

-Daichiko shakes the Lawyers offered hand, if you remember anything that could help. Please contact us.

-We have your number. (guides Aeliana out of the room)

They leave and Sara switches languages, it takes a second for Aeliana to remember (her mother's tongue).

``You did great, kid.''

``It helps that I don't actually know where he would be.''

Sara snorts and pinches her cheek. ``You think that matters.'' Aeliana brushes her hand away as they make their way out of Tower One. ``Anyway, Talia owes me a drink for this one. Your little friend's probably comitted some four maybe even five different felonies.''

``Allegelly, right?''

Sara shrugged, remaining silent as a couple of Keepers passed them. ``Your boy's hacker signature was all over it. Honestly, I could probably put him away for less.''

``That's not what you said back there.''

Sara waved her concern away, ``The Keepers are sloppy, and don't really know what their doing when it comes to domestic issues. That's the problem with these paramilitary types.''

They pause at the door. ``Oh.''

``Come on, let's get you home.'' Sara said as her hand lay gently on her back.

Stepping out into Solas properly, Aeliana looked off in the direction of Lower Level. If Haruto was anywhere it would be in those twisted streets, but the Keepers would, should, know that. \emph{`Stay out of trouble Haruto.'} She thought before moving forward.

\chapter{}
The first time Tatsuki had left her alone. If she was going to warn, Haruto, and she must warn Haruto, then she would have to do it now.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    MPrincess: Don't show you're face, Haru.\\
    GhostHacker: I'll be okay, Princess.\\
    MPrincess: Haruto this is serious. The council is involved.\\
    GhostHacker: The council gets involved when I have a hang nail.\\
    MPrincess: But this time, Father personally wants your head.\\
    MPrincess: You humilated Uncle. You humilated the Clan.\\
  }
\end{quote}

There was along pause when the Gento heir was left alone with her thoughts.

\begin{quote}
  {\fontfamily{cmss}\selectfont
    GhostHacker: Yakei...\\
    Foxy999: I'll watch out for the kid. No worries Princess.\\
    MPrincess: Thank you, SB3-QB9.
  }
\end{quote}


Interrupted.

Part two of blackout... Not sure what should go here... This is in Yakei's point of view.

Will start with her, and her perspective of the Blackout.
