\chapter{}
The pale moonlight was bright in the night sky illuminating the world beneath it. Stationary buildings reflecting the soft light left the area in a strange eerie glow. Its penetrating white light illuminating the resting inhabitants within the confines of each imposing structure.

Yakei slept peacefully under the pale glow of the moon. The slow steady flow of her breathing went undisturbed as time ticked by slowly. One invariable breath after another. One unfaltering heart beat after another. She slept on. Suddenly, without visible change and without any noticeable indicators, her eyes snapped open. And she awoke.

Staring at the plain tiled ceiling above her, Yakei made no move to rise. She held still. Gazing motionlessly at the ceiling, she did not bother to look around. After all, she had little reason to, long ago having memorized the simple layout of her quarters. Besides the oak desk pressed against the far wall, there was nothing of note within the confines of her space. No elaborate paintings to gaze upon. No colorful decorations to break the endless expanse of monotony. Not even a clock placed high upon a wall or low upon the small bedside table. There was nothing.

Of course, she'd long ago come to terms with the lack of d\`{e}cor. As Honorable Father always said, the world was filled with distraction. There was no need to bring it into one's only calm space. Of course, now that she was older, she also realized the political reasons for living minimally. In a ninja village within a prominent ninja clan, those of power and wealth were frowned upon if they highlighted their elevated status with petty displays of frivolous artifacts. A leader must always put the needs of their people above the needs of their own. As such, interesting artifacts and paintings had no place within the main house manor, much less her own quarters.

It wasn't as if she had need for any such articles. She'd spent so little time in her room that paintings and decorations were a waste of resources. She had little use for those types of trinkets and babbles. Additionally, a clock would be another such unnecessary object as she hadn't needed one to aid her in discerning the time for many years. As she'd never been allow the use of one, she'd developed her own means of telling time.

Whether Honorable Father had intended for her to become wholly independent of time devices, a theory she was more than willing to accept given his constant insistence that she be independent in all ways. Or perhaps he had simply wanted to reinforce the importance of patience, she did not know. However, it was because of Honorable Father's strict directives that there would be no visible clocks within the compound that had enabled her to learn the much-valued skill. As such, she currently held no use for the objects.

Inhaling deeply, Yakei estimated the time. 0447. She had another thirteen minutes before she was to begin her day. Thirteen minutes before everything changed, and she wasn't quite sure how she should feel about that. Today would not be like any other day. And unfortunately, she lacked the luxury of knowing that all would return to the same familiar schedule she'd grown so accustomed to tomorrow, or even the next day.

No, today was the beginning of a new stage in her life. Today, she would begin the process of becoming a Genin. Today, she would be one step closer to taking over her clan. One step closer to taking her rightful place within the village. She knew she was ready to take this step. However, that knowledge did not stop the small amount of anxiety from running through her veins.

For almost as long as she could remember, she'd been on a strict routine. It had varied little within the last eight years. And now. Now, that routine would be shattered completely. While she was sure she could force some sort of structure onto her new life, she knew that it would not be the same. There would be no one to usher her from one activity to the next. There would be very little one on one instruction. There would be less time spent under Honorable Father's heavy, analytical gaze. In the eyes of the village and in the eyes of the clan, she would be an adult. She would be officially responsible for her actions as well as the actions of her future teammates.

While she was confident that she would succeed in her future endeavors, these were the tasks that she'd been instructed in for the last eight years, she could not shake the small amount of anxiety that whispered in her ears that she might falter in her path to success. She might stumble on the way and while that would be a minor setback, such a misstep would disappoint Honorable Father. And she could not disappoint him.

She could not disappoint the man that had taken so much of his personal time to painstakingly instruct her in the ways of the clan. Even if she struggled to master a clan technique, he had not given up on her. He had pushed and pushed until she'd gotten it correct, and then he had pushed further so that it was not only executed perfectly, but ingrained in her every movement. No matter what, she could not disappoint him.

Of course she realized that these worries were unfounded. Given what she knew of the Ninja Academy training which was quite a lot due to the fact that she'd spent half a year studying and evaluating the Hyuuga Academy, Police Academy and the Ninja Academy training regiments, she would be hard pressed to disappoint Honorable Father today. All the same, it would have been nice if she had someone to talk to about these fears. However, she was Yotsugi, and the Yotsugi does not fear, at least she doesn't show it.

Of course she might be able to confide in Captain Tatsuki, her only confidant within an endless sea of people, but even here she hesitated. She would always be Yotsugi, and as such she would always have certain standards to maintain even with her only confidant. And really, this small anxiety was beneath her. Moreover, she would not be the only person affected by the changes that this day represented. Her routine was not the only one changing today. More so than anyone else in the entire clan holdings, Captain Tatsuki's routine would be drastically effected by this inevitable next step.

Yakei could still remember the last time she'd changed her retainer's routine. She'd been six years old and accustomed to her usual wake up time. Thinking she would save Captain Tatsuki the trouble of waking her for the day, she had gotten up and ready for the day all by herself. She'd been so proud of her accomplishment that she'd nearly missed the cast fallen look on her retainer's face. Even at such a young age she'd been aware that she'd done something wrong.

It had been then, at the tender age of six, that she'd learned that her actions had consequences. She'd learned that she had to consider all possible outcomes when deciding what to do. She'd realized that just because she could do something, didn't always mean that she should. And she'd taken that knowledge to heart.

It was the reason Yakei currently found herself staring at the white tiles of her ceiling though she'd been up and ready to start the day for the last ten minutes. It was why she would continue to lay here for another three minutes despite the fact that she'd long ago memorized the tile layout above her. Even when she was only occupied with her own thoughts, she refused to upset those around her unnecessarily. Boredom was not an adequate reason to cause pain.

Additionally, she found that she quite enjoyed the small amount of happiness she could bestow on those around her. If she could provide that small amount of happiness via her actions, or in this case inaction, then she would do so. Especially if she could do so without resorting to actions unbecoming of the Yotsugi. It was the least she could do.

Motionless, Yakei continued to stare at her ceiling. If she knew Captain Tatsuki like she thought she did, then her head retainer would be just a tad bit early to start the day. Yakei listened to the soft, strong beat of her own heart as she waited the last minute before the official start of her day. She would need to modify her morning training schedule if she wanted to use her morning efficiently.

On a normal day, the Ninja Academy started at 0900, but given the nature of today the start time had been pushed back an hour. The theory behind such an action was to give potential graduates the little extra time they might need to prepare for the exam. Whether that was by extra study or simply more rest, it was a nice but misguided notion. In her experience, one extra hour for the average student would make little difference in their overall performance.

The muffled sound of her door sliding open broke Yakei from her thoughts. Captain Tatsuki was indeed a little early this morning.

``Yotsugi-dono, it is time to begin the day,'' Captain Tatsuki spoke as she moved about the room getting Yakei's training garbs out in the process.

``Arigatou Captain Tatsuki. Your assistance is much appreciated,'' Yakei responded as she slid out of bed. It was time to face the day.

\starbreak

``Captain Tatsuki, your presence is not required. I am quite capable of walking to the Ninja Academy on my own,'' Yakei insisted despite the fact that she was positive her retainer would not allow her to make the journey on her own. After all, it would hurt no one to try.

``Hai Yotsugi-dono, you're correct. I have no doubt in your capacity to make the excursion on your own. You are capable of many great things to the honor of our clan. However, as I've reminded you on several occasions, it is my honor to escort you. Given the nature of the day, I would think even Genshirou-sama would grant my small request. Since it's his duty to be an even bigger hard ass than honorable Hiashi-dono, I would hope that you would not deny me this one request,'' Captain Tatsuki replied with a small smile on her lips as she took her customary spot one-step behind and to the right of Yakei.

Captain Tatsuki was Captain Tatsuki, and her assurance that Yakei would allow her request on this issue was clear in her voice and in her stance. Yakei could no more deny Captain Tatsuki the pleasure of waking her up in the morning, let alone a simple request to walk with her as was Captain Tatsuki's right as head retainer. Captain Tatsuki continued alongside her, knowing already the outcome of her request even if Yakei could not vocalize it. And Yakei did not dare answer her request for fear that emotion might escape her.

Captain Tatsuki knew her so well, and Yakei could say that she was perhaps her only friend, if the somewhat distant woman could be called as such. As always she had that innate ability to bring out the very un-Hyuuga like behavior in her. Perhaps it was because Captain Tatsuki had been taking care of her for the entirety of Yakei's life. Yakei mentally shook herself of her thoughts. Now was not the time for her to contemplate that oddity. Instead, she started forward, confident that Captain Tatsuki would follow without a reply.

``Ah, just as I predicted. Today will be a very beautiful day,'' Captain Tatsuki began as they made their way towards the Academy. ``This is a good omen,'' she nodded not expecting her charge to join in the conversation. This was how most of their conversation went, nowadays. ``You shall do spectacularly today greatly honoring the clan,'' she continued, not at all bothered by Yakei's silence. By now, Captain Tatsuki was more than capable of maintaining their one-sided conversation.

``Of course that is to be expected,'' Captain Tatsuki continued, occasionally nodding to a familiar face as they passed. ``You have brought our clan the greatest of honors since the day of your birth. Still, for whatever reason, I feel as if you will experience a different kind of challenge today. Something beyond the mental and physical challenges of the Genin exam.''

``I, of course, will be faced with the challenge of finding something to do with myself. I think I'll practice with Genshirou-sama. He's always badgering me to spar more with him. It's always ‘how do you expect to protect Yotsugi-dono if you do not practice'. I keep telling him that the day you need my assistance is the day that life as we know it will change. Of course, I'll still practice. The physical aspects of training has always been my favorite. And with you beginning your ninja career, I'll have more time to hone my skills. Even so, he keeps forgetting that I have more to do than him. The honorable Hiashi-dono has not needed his direct assistance in years.''

Taking a breath, Yakei paused in front of the Academy building. They were there sooner than she would have imagined, but Yakei was unsurprised. She was positive that Captain Tatsuki had done that on purpose to distract her from the unknown soon to come. The constant chatter, soft and meant for her ears only, was oddly calming. As much as her life was about to change, it seemed that Captain Tatsuki would never change. At least this aspect of her life, the one very permanent fixture would always remain the same.

Captain Tatsuki took one-step forward, bringing her level with Yakei, before turning to her charge. ``Yotsugi-dono, you have always made the clan proud, and you will always continue to do so because that is who you are. Remember to always hold your head high. You are a Hyuuga. No one is above you,'' Captain Tatsuki softly declared, as she looked straight into Yakei's eyes. Yakei could feel the ghost of the gentle touch that would have rested briefly on her shoulders had they been alone in the solitude of her own quarters. With a short nod, Yakei turned to enter the building, the phantom touch still ghosting along her shoulder. She didn't need to ask to know that Captain Tatsuki would be waiting for her when she was done. Some things just didn't need to be said.

\chapter{}
Final chapter... Kanopos nearly destroyed

Aeliana going to her meeting with Sergeant Sang-eo in the red light district near his apartment... He'd made a promise to tell her the results as soon as he knew them.

The Sergeant wanted to tell her right away that she did not make the OCI, and that he'd fought for her.

Aeliana doesn't know what to do about it. It's late, and she couldn't face her parents, so she goes to the warehouse.

At the door to the warehouse, the ship goes into red alert. Haruto's picture up on the emergency Halo screens (except for the commander's screen which was still out of commission).
-wanted for questioning about break-in to the Hokage's tower

Curses Haruto out loud before entering the building. Finds Haruto there.
She tears into him.

Haruto ``First, no one can prove I was there.''

Aeliana gave him a look.

Haruto ``Second, I can explain.''

Haruto tells Aeliana about the deal, Sergeant Y\'{u} gave him to get into OCI.

Aeliana is upset that he believed it.

Haruto tells her that he didn't fully, but if there was a change then he had to take it. If I'd known you didn't make it either, I'd have let you end on it. In fact, I got you a copy, just in case.

Aeliana about to yell at him.

And I didn't give him the real thing. Just this dumby stuff.

``Where are you suppose to meet?'' Aeliana

``Well, technically, we already met. He said, I was in now, but I guess that was a lie too huh.''

Haruto looks in thought, ``Well he won't get far, with that.''

``What did you give him?''

``The old man's porn stash.''

Aeliana knows, that Haruto calls the Sakra the old man, so she puts that together and blushes.

The ship goes down at this moment.

Haruto says he didn't to that!

...Aeliana uses her big brain to figure out what happened...
...we get a look at the SKIMs at full power...

...Haruto builds the chip they need after Aeliana looks at the real data...
...They have everything, but Aeliana realizes that they need top level access, she's talking out loud...

...Haruto says he knows just the person to help...

\chapter{}

This chapter is from Erik's point of view as he follows the trail to find his little sister.

-the ship is in evac mode, his adoptive parents will not go into their hiberative sleep until Aeliana is found...

this first thing Erik does is go to the Helian house, he greets his adoptive parents, but asks why they are not in hibernative sleep

Aeliana is missing, they won't go to sleep until she is found. They tried to reach her at the warehouse, but no one is picking up on the emergency line...

Erik vows to find her, his job to protect the heir... parents say he's more important to them than just that...

He smiles, and turns to go... get into your hibernation, I've got Aeliana

First stop is the warehouse, he uses his comms to call his contacts in the LL... using Guild backup power, as soon as this was over, he was putting his little sister on the Guild grid too... AIMs be damned

She's not at the warehouse... he investigates... looks like they were hear (turns on his heat signature vision), worked on this console... he tries to log on, but is blocked...

going to have to hack in the hard way, goes for the wires, but sees that it's offline... that was a going to be a dead end... their signatures were still fresh, so they couldn't have gotten far...

he get's a reply about movement, say the Helian heir...
Erik as if there was a little red head with her... 
guy pauses to ask around... no one noticed anything like that, 
thanks, over and out

so either H\={e}id\`{o}ng was with her or she was on her own... he hoped the kid was with her, but wouldn't take any chances... this would be the perfect time to kidnap the heir with all the confusion...

Aeliana's been practicing, she's not defenseless... he nodded before heading out to the last known location

ends up in Prayer Alley, patrols are everywhere here, \emph{`Probably securing the K\={o}taishi'} he thinks... moving along, he tries to figure out what they were doing here...

gets no sign of them, pulls a patrol aside and asks... first don't want to work with him, but he shows his Guild badge... the guys eyes widen, before he starts apologizing, sorry sir...

just tell me what you know about H\={e}id\`{o}ng? How does he travel?

Ah, well. Rooftops mostly, but if you're tracking him, you'd have better luck with something else... he knows the skyline better than anyone, and can walk along the catwalk without extra protective gear...

thanks,

he takes to the rooftops, breathing a little heavy after the climb, I've got to work out more

If she's with him, he won't take the catwalk, so where would they go?

Get's a call, a couple of spotting... Erik head in the direction of Tower One...

Aeliana wouldn't be involved in one of the kid's pranks. What is going on?

All this time, the ship is slowly failing, less and less people are here are most have them have evaculated to hibernation chambers...

Erik goes to Tower One, people are working overtime to prepare the ship... it is here where he and the Captain Daisuke experience shockwaves from fighting in the Hokage's Tower
-Erik was escorted to the command hub...

They rush over to the Hokage's Tower, the room not doing well... finally they get to the central command hub

``Aeliana,''  he calls out... surrounding her is the Gento heir in their key fighting stance, hovering over a body...

``You are in my range,''  the heir says darkly...

``No, Princess, it's fine. I know him.''  Aeliana answers, but the K\={o}taishi doesn't loosen her stance, so Erik lets Aeliana come to him...

What's going on...

he sees bodies all around them... blaster damage... but a second later the ship seems to becoming back to life

``Long story, but first Haruto needs medical care.''

should end around there...
