\chapter{SB3-QB9}
``...and the X-dema system support for artificial interactive control had at the time one of the most comprehensive signaling networks, which of course...''

Aeliana's wrist vibrated distracting her from the rest of the Sergeant Cho's lecture on AIM technology. She'd been anticipating this lecture for weeks. Really, had wanted a series on it, but was thankful enough to have the one day devoted to AIM tech. Her arm warmed with the unread message signaling it was from someone in her favorites list. Given she only had her parents and Ilia on the list, she didn't want, or need the distraction.

``Now, given it was FDY 96, AIM tech was still quiet primitive, but for its time definitely the state of the art in interface chips.'' The Sergeant Cho continued. Aeliana's arm buzzed again, growing unconformable warm.

A quick glance confirmed the two awaiting messages were from her friend Ilia sitting just two rows down. Automatically upon view her BISM, the messages opened. 

\textsc{Boriiiiiiiing.} Followed by an old video clip of them dozing to one of Ilia's aunt's lecture. 

Normally the little clips and comments from her friend were welcomed. Always bring a smile to her face. Ilia used to know just when to send them. But now... Aeliana suppressed a frown at the message. Sure the Sergeant Cho was going on about completely useless AIM tech that no one in this room would every see or work with, but at least he was going over \emph{something} about the artificial modules. She knew plenty of Sergeant Chos who wouldn't have bothered, at least not with this class makeup. \emph{Some} of them were going to need to know this for future improvements to their own AIM. \emph{'We can't all be from clans, who just give them their suits and AIMs.'} Aeliana thought darkly.

This wouldn't be the first time Ilia had interrupted her lecture with small notes complaining about information she already knew. The privilege of being from a clan that Aeliana was quickly learning to hate. Her arm buzzed again, but this time, Aeliana focused on the lecture before her.

``The idea of course, was to increase connection time. The faster the response time between pilot and machine the better, which has been demonstrated over and over again via the clans.'' The Sergeant Cho nodded around the room as Aeliana's arm started to burn.

\emph{'Oh, why haven't I taken Ilia off my personal list?'} She thought as she tried to focus on the information being given to her. Eyes turned to her tablet show casing several old formulas used to determine reaction time, but the burn was insistent as it was meant to be.

Looking down, the message opened automatically. \textsc{Like anyone needs to know this shit. Kur-ram's got the right idea for sure.}

Aeliana didn't try to suppress her frown this time, hastily writing a message of her own. \textsc{Some of us aren't just handed this information at birth.} The fury was probably more than the comment deserved, but she couldn't help herself. The clans had everything handed to them. They didn't need this, but she did. She couldn't be a pilot without it. Not like them. Not like Ilia.

Ilia looked up with a questioning rise of her brow over at Aeliana, which Aeliana refused to answer. They'd been having more and more disagreements. Ilia not understanding why Aeliana didn't to study as much as she did, and Aeliana just so upset with the constant unfairness of it all. Four years at KANP had brought how different life was for the clans than for her.

``Cadet Helian,''\ the Sergeant Cho's voice breaking her foul mood with its suddenness. ``Is there something else you'd like to be doing?'' The Sergeant Cho questioned coldly.

Aeliana immediately stood at attention, posture stiff as a board. ``No, sir. Sorry sir. It won't happen again, sir.'' She replied, short and to the point.

He nodded, ``See that it does't, or you can join Cadet H\={e}id\`{o}ng outside.''

Aeliana sat down, a quick look at the blond in question. While he had a broom in hand, he'd been working the same pattern over and over again for the last two hours. She didn't for a second think that was actually him. Only an idiot who didn't know the blond would think that. \emph{'And, I'd not going to be the only one out there cleaning, wasting precious learning time. Not happening.'}

Truthfully, she couldn't afford the waste of time. Or the disciplinary note on her record. \emph{'Not if I'm going to get into OCI, anyway.'} Aeliana thought as she turned her attention to her tablet downloading the next set of videos from her Sergeant Cho's lecture. She had two years, just two years to figure out how she was going to get into the elite officer's pilot school. And she was starting to realize that top of her class academically wasn't going to be enough.

The Sergeant Cho paused briefly to look at Ilia looking something up on her BISM that Aeliana could guarantee was 100\% not related to the class. Sitting only two rows from the front, the Sergeant Cho probably had a good view of whatever it was she was looking at. Old videos of them probably. It didn't matter. He didn't so much as blink in her direction before continuing his lecture.

Her eyes found the back of her best friend's head. Ilia passed notes to just about everyone in class, and Aeliana should have known better than to respond. \emph{'I should have silenced her messages before class today.'} She thought as she carefully jotted down the information about K99 series AIM chips. She'd have to double back on all the information later as the Sergeant Cho often omitted key parts to his lectures. All of them did.

\emph{'And why not? Half the class won't make it to a pilot seat in their life, and a quarter are heirs to their clan.'} She kept her sigh to herself. The Academy wasn't anything like she'd thought it would be. The strict rules they'd gone over on day one had never been meant for everyone. Ilia could message away to her hearts content. Kur-ram could sleep right next to her despite the so called strict no napping policy. But if she messaged back, she could be thrown out of class. By the Goddess, she'd even seen H\={e}id\`{o}ng get kicked out for just \emph{drooping} his head. In her first year at KANP, a boy had been kicked out of class for drinking water, while Kenta currently sat right next to his buddies, Ilia and Kur-ram, chopping away on a bag of chips.

\emph{'Health reasons my backside.'} She thought darkly at the \emph{official} story for why he'd been allowed to eat. In reality, she knew the real reason was because he was an heir to his clan. Just like Kur-ram, and just like Ilia. Every single clan member got treated differently.

Dang, even Seo-Jun got away with blatant cheating, and he wasn't even a heir, just part of the his clan's \emph{head} family. \emph{'Symbiotes should not be allowed to communicate with their host, not during tests!'} The nasty little thing just sat on top of the kid's head, peeking and sweeking back to him.

Aeliana's thoughts darkened as she thought about the unfairness of it all. \emph{'Why did I have to be born in FDY 256? With all of the clan heirs?'} She thought, \emph{'Couldn't my mother have waited a year. Just one.'} Looking around at a class for of clan members, she didn't think that was an unreasonable thing to wish for. Aeliana held back a sign knowing full well that wishes made to the Gods went by unanswered all of the time.

\emph{'For now, I've just got to listen to the Sergeant Cho omit key facts about AIM technology, but go on in detail about obsolete tech.'}

``So, of course you'll never be forced to use the K99 series as they've been discontinued, but it's always important to understand the basis of our current systems.'' The Sergeant Cho took a sip of a hydro pouch before continuing lecture on obsolete AIM tech.

``Now, what came out of the K99 series was meant to be the be all, end-all in AIM technology. Functional artificial intelligence.'' The Sergeant Cho tapped on his BISM uploading the new video files to the class. Aeliana looked down at her tablet to see the specifications the SB3-QB9 AIM chip. ``The SB3 series was the answer. Doctor Fumagawa developed the chip to improve human to machine interactions. And in theory nothing could out preform its interface interaction times.''

Akihiko snorted in the background. If there was any one member of the clans that believed KANP was for civilians only, then it would have been the Zh\`{u}r\'{o}ng. Even now, she could hear him saying how nothing could touch the Zh\`{u}r\'{o}ng AIM. Surprisingly enough the Sergeant Cho called him out on it, ``That's right Cadet Zh\`{u}r\'{o}ng, even better than the clans AIM at the time. Given the chip is more than thirty years old I can't say for sure that it would out preform the clans today, but I'd give it a high probability.''

``If that's true, then why isn't it still in use? Why haven't I heard about it.'' Akihiko challenged.

``Oh? Is there no one who's heard of the SB3 series?'' The Sergeant Cho asked smugly. As AIM tech was considered state secrets, the knowledge was locked away within the Commander's Library. Aeliana wouldn't get access to it until after she finished KANP. She looked around, Kur-ram looked away for once and everyone seemed eager to hear about an AIM that was better than all of the clans.

``We know of this model.'' A voice from the back of the class answered. Aeliana turned around, she'd never heard Cadet Haibeu speak and was a little unnerved to see him do it now. ``We are, however, in debate on whether your statements on the SB3-QB9 model can be considered correct.'' Cadet Haibeu's robotic eyes flickered in thought.

``Don't hurt yourself thinking brick.'' Seo-Jun added derogatorily as his symbiote peeked from his head.

Aeliana didn't know what to think. The boy with the symbiote seemed to have problem with the cyborg, who was currently more human than robot even if it was hard to tell.

``Ahhhh, that's okay Cadet Haibeu. Your clan's difficulty answering my question is understandable. A number of great scholars also are to this very day in debate on whether the SB3 chips should have even been created in the first place.'' The Sergeant Cho interrupted Cadet Haibeu's... well, commune maybe?

``And before I get back to your question, Cadet Zh\`{u}r\'{o}ng, why don't I give a little more background on the chip.'' The Sergeant Cho moved around the front of the class far more energetic than he'd been, well ever.

\emph{Buzz.}

Aeliana looked down on instinct. \textsc{Someone has a hard-on for SB3 class chips.}

Well, Ilia wasn't wrong.

``The SB3 class AIM is to this day the most unique chip ever developed. For one reason.'' The Sergeant Cho paused dramatically, ``There was only ever one model created, the original QB9 model. Which should tell you a lot about it.''

``All that tells me is that it was a faulty chip.'' Akihiko countered.

``Yes, Cadet. It was quiet faulty. In fact, it never made it out of the Guardian beta test, which is why the majority of you have never heard of it.'' The Sergeant Cho nodded to the class as he continued, ``Even so, it could not be denied its strength when it ran optimally. So, while it will never see battle, many scholars use the chip to study artificial intelligence and have made several breakthroughs in robotics because of it. So for now, SB3 will remain in the history books as the closet tech developed for true artificial intelligence. Of course,''\ the Sergeant Cho smiled at his own impeding joke, ``in a battle, no one wants to worry about whether their AIM will obey their commands, so the history books it will remain.'' He chuckled as if lost in a memory and shook his head in amusement.

Kur-ram snored two rows below her, loud enough to wake himself up, but was some how back to sleep in seconds. She wasn't sure when he'd gone back to sleep, but wasn't all that surprised. ``Completely useless, which is why the latest models have all turned away from true AI capabilities despite their improved interface possibilities. So I think it's safe to say the Clans still hold the advantage in AIM tech,''\ the Sergeant Cho finished talking over his snoring student. Akihiko visibly relaxed in his seat.

\emph{'Of course, that's all he was worried about. Being second best.'} Aeliana thought darkly.

``Now class, can anyone tell me the current model used by the common pilots?'' The Sergeant Cho questioned, pausing to wait for hands to rise. Aeliana's was the only one. Even so, he did not immediately call on her, instead choosing to walk up the aisle as if contemplating who to call. \emph{'Oh, come on. I'm the only one who knows. Just pick me!'}

\emph{Bang!}

Kur-ram shot up in his seat at the abrupt sound, ``Cadet Krai, perhaps you could enlighten us?''

Blinking the sleep from his eyes, Kur-ram looked down at his BISM before answering, ``The VX5 series is currently the most popular model among the clanless, but of course that's hardly the newest as there are currently five new version in beta within the Guardians.''

``Ah,''\ the Sergeant Cho paused in surprise. Aeliana quickly jotted a note to cross check that information, if she could anyway. ``That's correct. Although, I'm not sure your father would like you talking about what I'm sure is classified information.''

Kur-ram was already putting his head back down as he replied, ``If it was classified, my dad wouldn't have mentioned it at the dinner table, now would he?''

The Sergeant Cho sputtered before returning back to the front. ``Now, you don't need to know about the current tech, as most of you won't use it, so why don't we...''

Aeliana held back a sigh. Four years of this with two more to go. Why had she picked this for her life again? She blamed Akihiko, he'd complained about learning useless pieces of information only a month into the program four years ago, and now her education suffered. \emph{'I'm starting to hate the clans.'}

\chapter{KANP}

Aeliana wanted this day to be over. She wanted it with a passion, but the artificial light of Solas meant it was barely 1300 in the day. She just wanted to crawl into bed and never get out again. Disappear from the world. It would hardly miss her.

Laughter interrupted her thoughts causing her to look where she was going. Ahead of her were some first or second years by the size of them. She stopped suddenly at the realization that she'd been heading into Solas. Whether she was going home or Tower One, the closest Keeper Tower in the area that could fix her guidance chip, she wasn't sure. What she did know, however, was that all of her classmates would be going there, and she wasn't quite ready for any possibility of running into them. Not yet anyway.

Turning away from Solas, Aeliana picked a path with the least amount of people. Absentmindedly, she looked down at her BISM to check the streets, but only a blank screen stared back at her. Screaming in frustration ``Ah!'' She pulled at the screen with rough fingers. Pain tingled in her nerve-ends. The strange sensation making her feel more alive than seconds before.

An absent thought formed in her mind that she quickly pushed aside as she walked further into the quick streets of what she was beginning to recognize as Prayer Alley. With a slight change in directions, she dove deep into Sanctuary Park. Animals startled at her presence, but Aeliana ignored them.

\emph{'I'm a fool.'} She thought her mind going in circles with different scenarios. Six clan heirs, seven including the K\={o}taishi, born in the same year as she. No matter how she counted, no matter the scores, they were guaranteed entry into OCI. ``Politics.'' She spat the word in hate. It didn't matter that she was the top student. Seven students was already too many for Kanopos to be sending to OCI. Eight?

``I'm a fool.'' She slumped down at the edge of the reflection pool. Her eyes stared unseeing at the thin layer of water at it's surface. For the animals of course, but still an unnecessary waste of water. Or, as her mother could say, a heavy-handed display of wealth from the Gento Clan.

Across from her a white-tailed deer drank from the recycled water. The small population the Gento conservationist kept here looked nothing like their pack relatives that the Krai clan raised as food. Lean and short they had little meat to offer, Aeliana had a hard time imaging people eating them once upon a time. Now, of course, they had little purpose outside of 'conservation'. Why the conservationist could go on for days about why that was important. From a merchants perspective, all she could see what an expensive trophy with little value or purpose.

``No purpose.'' She said aloud a sad smile touching her lips. \emph{'Don't we have that in common now?'}

Her SKIM chose that moment to flicker, but remained brightly colored. A sharp sense of rage bubbled through her at the sight. Useless. Her guidance chip was little more than a babies processors. Was in fact, the very processor she'd received as a baby. It would never be able to computational heavy maneuvers. It's connective lag-time was ridiculously long. But most importantly, it had little defense against viruses. In other words, it was a useless piece of junk.

Popping open her BISM, she rips the chip out with little fanfare. Finally, the bright green and pink of H\={e}id\`{o}ng's prank disappear as her SKIM turns black. She felt a cold shiver at the lose of her link to Kanopos. But she ignored it. Caught up in her frustration, anger, disappointment. She could no more appreciate the lost of heat as her body attempted to regulate its own temperature. Nor could she comprehend her lightheadedness caused by a decrease in oxygen levels. Those and more were lost on her in her single-minded rage.

Pulling herself up, she winds back her arm to hurl it into the recycled water before her. And she held it there. And held it. And held it as her arm trembled. But no matter how much she wanted to, all she could do was hold it at the ready. Not ready to let her childhood processor go. So many memories stored on that small delicate chip. Her arm fell useless down to her side as she collapsed onto her knees. A small sob of frustration leaving her lips.

She didn't know how long she stared at nothing with guidance chip held loosely between her fingers so lost was she in her thoughts. But the ache in her knees grew with each passing moment, and she knew that soon enough she'd have to return to society. Life would go on.

``May I?'' A firm voice spoke from behind Aeliana startling her back into reality.

Turning around she pushed herself back to her feet careful of her guidance chip. Surprise clouded her features at the woman, girl, standing before her was none other than the Gento heiress, the K\={o}taishi. Her hand out stretched, head tilted to Aeliana's guidance chip.

``Um, yes. Yes, of course.'' Aeliana replied as she handed the guidance chip over. The Gento's unique relationship with technology was known throughout the galaxy. Although technically, Aeliana should have gone to one of their Keeper Tower to fix her chip. This, too, would work.

Aeliana watched as the K\={o}taishi focused on the chip. Her nanites in the Gento's eyes gathered together making them look more mechanical in nature than just second before. The K\={o}taishi let out a soft breath as she focused, clearly taking more effort than Aeliana thought a simply virus fix aught to take. But soon enough, the Gento's eyes returned to normal. She handed the chip back, it was warm to the touch.

``It's not safe to be offline.'' Came the K\={o}taishi's reply.

``I...'' Aeliana began, but had nothing to say. ``Thank you.'' She replied instead. As she gently placed her guidance chip back where it belonged. The effect was immediate. Her head cleared, her body warmed.

\textsc{Reboot successful.} The words flashed on Aeliana's BISM. \textsc{Good afternoon, Aeliana.}

``Thank you.'' Aeliana said again. The K\={o}taishi turned away from her looking out at the pond. ``Ah,'' Aeliana struggled with some sort of conversation, ``do you often come here.''

``Yes.'' K\={o}taishi replied shortly.

\emph{'Okay, not much of a talker.'} Aeliana thought, but she soldier on. ``In the middle of the day?'' She continued. ``I'd figure you'd have better things to do.'' \emph{'Like study.'}

``The KANP incident requires the attention of my tutors.'' The Gento answered.

``Oh.'' Aeliana replied, turning to look out at the pond as well. ``Only H\={e}id\`{o}ng could effect you too, huh?'' She added in a low mutter.

``Yes.'' The K\={o}taishi replied. The tone of her voice, however, was not that of anger or frustration causing Aeliana to turn back to her less than talkative intruder. 

Aeliana found herself studying the girl before her. While she was a stoic as any Gento, there was something, calming about her. \emph{'Amusement maybe?'} The thought brought her back to this morning and H\={e}id\`{o}ng's amazing claim. ``You're not really friends with H\={e}id\`{o}ng, are you?'' It was bold and probably over stepping, but Aeliana could hardly \emph{make} the K\={o}taishi answer her.

For several moments, they remain in silence. Turning back to the still water, the silence was not kind to Aeliana. Her thoughts centered around Ilia. Her only friend, now gone, just like her dreams of being a pilot. She blinked as a beautiful black and white fish swam past them, beneath them.

``Yes.''

Looking up Aeliana turned to the K\={o}taishi. ``I'm sorry?''

``Cadet H\={e}id\`{o}ng is my friend. My only friend.'' The K\={o}taishi continued with no emotion to her voice. As far as Aeliana knew, they could have been talking about latest asteroid predictions. ``And you?''

``H\={e}id\`{o}ng?'' Aeliana questioned the ridiculous suggestion. ``Can't stand the guy.'' Realizing how that might sound she continued. ``I mean, his personality can be, abrasive.''

``Yes.''

``He's got all this creativity and energy and he uses it for pranking.''

``Yes.''

``He pretty much just wastes his own potential.''

``Yes.''

Aeliana tightened her lips in frustration, ``I mean, do you know what I'd give to have that kind of raw creativity? I could write my own ticket to OCI.'' She continued not even waiting for the one word reply from the K\={o}taishi. ``And he just, has it.'' She felt the wind blow out of herself. ``I'm not sure you could even understand. You being the K\={o}taishi and all.''

``You work hard, everyday, to achieve your level of competence. Cadet H\={e}id\`{o}ng just is.'' The K\={o}taishi responded. ``I understand.''

Her face didn't so much as twitch as she spoke, but Aeliana could feel a kinship. While she didn't understand how the K\={o}taishi could share her struggle to excel beyond some imaginary goal that seemed to always be out of reach, in that moment Aeliana knew whatever the K\={o}taishi's story was, they were the same in this.

``And you just, keep going. Knowing you'll never be good enough. That the goal is impossible.'' Aeliana asked softly, self-conscious suddenly.

The K\={o}taishi tilted her head slightly before turning around. Aeliana followed her line of sight to see another Gento waiting on the outskirts of the forest. \emph{'A question for another time, then.'} She thought as she turned back to the pond before her.

``If you stand still, you get nowhere.'' The K\={o}taishi spoke before taking her leave. Aeliana watched her go.

A simple statement, but it meant everything to her. A Helian didn't give up. Didn't stop trying. And while she didn't know how she'd manage, she knew one thing for sure. ``I am a cadet of the Kanopos Academy for Novice Pilots,'' she said aloud. ``And I \emph{will} reach OCI.''

\emph{'That eighth spot is mine!'}

\chapter{Mind Games}

\emph{Buzz.}

Aeliana tensed her jaw as a new message popped on her Halo screen. Ilia's smiling face looked back at her from the little profile pic attached. Looking up, she saw her father standing over the star map in the other room. Her mother humming in the background. Both far enough that she couldn't make out what they were saying. Her father's wildly waving arms the only indicator of an intense conversation.

Her mother moved closer, pointing to a different section of the star board. She leaned over to whisper something in his ear with amusement ringing clearly in her eyes. The man in question shook his head wildly before launching into another tirade. Given her parents engagement, Aeliana risked logging off of her Guild connection to look at the messages privately.

\emph{`The last thing I need is for them to find out Ilia's still messaging me. They dislike Ilia enough, they hardly need any more ammunition.'} She thought as she pulled her BISM from the computer system.

Browsing her growing unread messages, \emph{all} video logs from Ilia, she held back a sigh so as not to attract her mother's attention. The woman could hear a pin drop on the other side of a room. And her inbox was hardly a surprise. Really, she'd expected nothing less than five new messages. Only having seven wasn't that bad for the afternoon.

The persistence of her one time friend. Sure that she could make everything right, if only they just talked it out. That had always been one of many things about Ilia that had drawn in Aeliana. A strength of character and confidence in herself that always had a way of convincing Aeliana about something or another. And it would be so easy. Just one click, and Aeliana was sure she'd have a hard time denying her friend at least one meeting. Ilia might even be able to convince her that this break was stupid, silly in that it would change nothing.

Aeliana had enough doubt in herself that it wouldn't be hard to just let Ilia say those sweet words that would fix everything. Fix \emph{this}. Shutting her eyes tightly, she cleared her doubts. What they had was beyond fixing, beyond saving now. Aeliana knew her trust was broken in that moment when she'd needed Ilia to be on her side. Even if it didn't work out. She'd needed her than. Now, well. Now it was all just a little to late. Even if Ilia refused to see it that way.

\emph{`Why must you make this difficult, Ilia? Why?'} She thought as she opened her eyes again. Her finger hovering for a second to long over her unread messages. That second of doubt, taunting her to open the videos. With a deep breath, her finger found the delete button. And a moment later they were all gone.

Her empty inbox was but a moments relief. She knew that within hours, Ilia would try again. Knew the pattern from the past two days. And some how, she would find the strength again to empty her inbox again. It was with a measured sense of relief that she was glad that Ilia could only contact her this way. With KANP closed for the rest of the week, Aeliana didn't have to face her head on. She'd already blocked Ilia's messages.

\emph{`Now, if only there was a way to block video logs too.'} She thought wistfully. She needed time to process. Time to figure everything out in her head. Time she knew that Ilia would not give her. For the more time she had, the easier it would be to let her oldest and closest friend go.

\emph{`Heck, I've gone so far to make sure Tommy, doesn't even tell her if I'm home or not. Not that she could get in even if I were.'} She thought. But knowing Ilia, she'd just camp outside until I left. \emph{`Or do something overly dramatic outside of my window.'} The thought brought a sad smile to her face.

It was times like these, when she was glad her parents never liked Ilia enough to invite her over for dinner. Aeliana snorted at the thought. \emph{`Heck, they wouldn't even let her so much as step into the foyer to wait for me.'} Ilia had always had to wait outside, often with the door shut in her face, which had peeved Aeliana to no end. All in the name of the Helian family practice. An excuse her parents used because Ilia was from the Clans.

As her friend, Ilia \emph{should} have been exempted. They all new that. Aeliana had in fact argued it dozens of times to a deaf audience. And now, she was grateful for it. Her parents unreasonable hatred of the Clans. The irony was not lost on her.

Staring at nothing, Aeliana found herself lost in happier memories. Remembering sneaking Ilia through her bedroom window for their 'secret sleepovers'{}. Or sneaking out that same window to go see a late night movie that neither of their parents had approved of. Closing her eyes she could almost imagine she was there again. Sharing laughs with her friend as Ilia pulled her down the Plaza. Hand in hand like always.

``That Amur girl messaging you again, sweet heart?'' Her mother's voice sounded from over her shoulder causing Aeliana to jump out of her seat in surprise.

Looking up, she found the knowing look from her mother staring down at her. Turning away quickly, Aeliana hastily plugged back into the network, but she knew it was already too late. Where her mother went, her father was not far behind. And now was no different. Her parents had caught her spacing about Ilia, again. And she was sure she'd come to regret it.

``Just taking a small break.'' Aeliana replied, but the sympathetic look her mother gave her in return suggested she'd fool no one today.

``You know I can send some one over. Teach her a lesson about proper courtship.'' Her father spoke his eyes drifting off into another realm before snapping back to attention his fist clinched tightly, ``I told her, swore if she broke my sweet little Stargazer's heart, she'd learn to regret it. Heir or not, we Helian always keep our promises.'' Her father added, joining her mother beside Aeliana's workstation.

``Mom, dad.'' Aeliana pleaded. ``Please, not today.''

``No, sweet heart. Your father's right for a change. No one breaks up with a Helian and lives to tell the tale.'' The glint in her mother's eye was dangerous. And gave her pause. A real cause for concern that her father's words had failed to carry. Mother could be dangerous when she wanted.

``Wow, now! \emph{Breakup}?'' Aeliana held her hands up to stop that line of thought. Again. ``How many times do I have to tell you. We were \emph{friends}.'' She emphasized the friends part for what felt like the hundredth time.  ``\emph{Just} friends. And \emph{I'm},'' she paused her to look at both of them as she pointed to herself. ``\emph{I} am the one who ended it.'' Putting her hands down, she continued. ``So there's no need for violence. Friends grew apart all of the time. That's life.'' Turning away from them, her eyes stared listless through he Halo screen. \emph{`That's life.'}

``Well, I'm sure she gave you a good reason, sweet heart.'' Her mother continued dismissing Aeliana's words with a wave. Turning to her husband she continued, ``Didn't I tell you, just the other day, I was saying how that Amur girl was no good for our little angel?''

Her father nodded in agreement, ``We should have put a stop to it ages ago.'' He added. ``\emph{Clans}.'' The words was surprisingly hateful coming from her father, an easy going man. ``Nothing good comes from them. Always think they're better than everyone else. Doesn't matter how hard we've worked. How much more we have to show for \emph{our} efforts. \emph{Clans}, they're all the same.''

Aeliana sighed in frustration. This argument, or really more of a rant, was all to familiar to her. And while she generally agreed that the Clans had a privilege in Kanopos that did not always measure to their actual wealth that did not make them \emph{all} bad. But they couldn't all be like the Gento clan, and even Ilia had not been able to help taking liberties that were hers by Clan right. Even so, that didn't make the Amur clan, Ilia, the root of all evil within the Clans.

Ilia was just different. \emph{Had} been different, anyway. Or maybe she'd just not been different enough, where it counted. The thought caused moisture to cover her eyes. She blinked away the tears before they could draw the focus of her already steaming parents. Instead, she attempted to focus on the work before her.

A steaming cup of hot cocoa was placed in front of her. ``One Stargazer special. Just the way you like it.'' Tommy's robotic voice replied from behind her. The smell hit her first. Warm and inviting, the specialty hot cocoa had taken Tommy nearly a full year to put together just the way she liked. But that was years ago, and now the autobot managed putting together the ingredients from seven different solar systems with ease. Topped, of course, with fresh hand whipped cream.

Taking a long sip, the flavors danced across her tongue. Tommy always knew how to bring a smile to her face. ``Thank you, Tommy.'' Aeliana replied as she took another sip. Absently whipping a stray bit of whip cream from her nose.

Aeliana returned her focus to the navigation system program she was updating despite the lingering eyes of her worried parents. She understood her parents worry, despite her best efforts she'd not been able to hid the large dark circles under her eyes. And Tommy had no doubt told them about her lack of appetite as well. So she understood. Truly. But that didn't stop her resentment that boiled under her skin every time her parents attempted to 'cheer'{} her up.

What she needed was time and space from everything. She didn't want to talk about it. Didn't want to hear them calling Ilia and her family all sorts of things. Ilia was not a horrible person. She just wasn't what Aeliana needed right now. And how could she explain that to her parents? \emph{`Mom, dad. I still care for Ilia. Only every time I see her, I'm reminded of my impossible struggle to get into OCI.'} She thought, sure that conversation would go over ever poorly.

``Aeliana, sweet heart. Why don't you come here and tell your father why he can't go through Chivanial star space?'' Her mother beckoned with a turn of her head incidentally interrupting Aeliana's darkening mood. 

Pressing her lips tightly, Aeliana disconnected her direct link to her console. Standing up she walked with her parents to review the star space in question.

``Love, I'm telling you. It's the fastest and safest way. And I've got to make up time from that nebula.'' Her father added coming up from behind them.

``Yes dear, so you've said. But I'm telling you that Chivaniallan space isn't the route to take.'' Her mother countered smoothly.

Aeliana felt her mother press her hand lightly onto her shoulder. The warmth from her hand diffusing through Aeliana's SKIM a pleasant reminder of her childhood. It warmed her to her core. Smiling up at her mother, she could tell that had been her mother's intention by the sharp look in her eyes.

With the hand removed, Aeliana felt grounded and ready to derive her father's route. Leaning over the star map, she shrunk the screen to display the full route in detail. She'd done this what must have been more than a hundred times now, but it never seemed to bring her any less tension. The slow movement of Kanopos took center screen. Plugging her own BISM into the map, she linked her archive of galactic weather patterns into the system. Within a blink, she was ready to begin.

``Here, Stargazer. This is my current route.'' Her father spoke as he downloaded in information into her current session. Half a second later, and Aeliana was throwing it on the board as well. The dotted red path outlining her father's current route.

\emph{`Currently marked as a 213.21 day trip. Goddess, father isn't going that far.'} She thought as she traced the current data.

``A perfectly...'' Her father began, but Aeliana cut him off with a wave of her hand tired of her parents bickering.

``A moment, please.'' She spoke softly aloud, as she combined her father's route with additional weather variables. Her parents often went with instinct instead of raw numbers to estimate run routes. Aeliana didn't see the point, when there was plenty of information available in archives from satellite outpost to get an accurate picture. As such, she was often called on by her parents to double-check run routes.

Her mind whiled as she moved her father's ship, SGC Stargazer, slowly down his plotted course while simultaneously manipulating the environment around him. Pushing rogue asteroids and comets through space, changed her father's route minutely, but not enough to suggest a bad path. Forty-two days into the route, however, and she was beginning to see why her mother insistent that the Chivaniallan star space was out of the question.

The increased reports of privacy aside, it was very clear her father was taking into account the rotation of the Tarventor's three moons. Adjusting the moons'{} placement, she enhanced the image for her father to see. ``Dad, by the time you get to Chivaniallan star space, the Tarventor moons will be here.'' Adding her own calculations of their gravitational force, she added the alternative route her father would need to use in orange. ``This pushes you into Nahua territory. And with the civil war going on that could add any number of days to the trip, assuming you can avoid the conflict all together.'' The doubt in her voice was enough for him to get her unspoken words. \emph{`Which is impossible, and both of you know it.'} She thought to herself.

``Yes, my little Stargazer, but at least I miss this asteroid cluster, here.'' Her father adjusted the map to circling the cluster in yellow. ``This'll cut time, overall.'' He gave her a sly smile. ``And I've got a few things up my sleeves for avoiding conflict in Nahua.''

Updating the map by 113 days, the approximate time her father would make it back to Chivaniallan space again. She frowned at the information flashing before her. Moving asteroid clusters around based on her predictive models, the story unfolded before their eyes. ``And then you run right into this much larger asteroid belt on the way back dad.''

``See, dear. This is what I've been trying to tell you.'' Her mother added. ``Take the smaller asteroid cluster, with the SGC Stargazer you'll have no problem maneuvering you and the convoy through it, and you can cut 32,''

``33.45,'' Aeliana interrupted.

``33 days.'' Her mother continued without pause. ``Plus you don't have to adjust for the forty-something odd days it will take to move around this belt.'' Her mother continued.

With her calculations completed, she updated her father's course, ``It's 48.29 days, making your trip 261.5 days if you take that route. But more importantly, if you just avoided the nebula altogether, the run wouldn't even need the SGC Stargazer.'' The updated course on the screen before them, Aeliana her additional route minus nebula that could be completed without her father's ship in light blue. ``It takes the same amount of time as this route, but you don't need to go.''

``Oh, well. Will you look at that.'' Her father replied as he looked at his altered route with the updated data. ``Amazing as always my little Stargazer. Just amazing.'' He smiled as he moved around the star map for a better view. He didn't make mention of the nebula-minus route either.

``Dad, I'm serious. You don't even need to be out there. Just avoid the nebula.'' She continued to argue as she added highlights to the board illuminating the safer path. There was no reason for her father to risk his life out there, and normally her parents always went with the safest route. Looking to her mother, she waited for her to agree with her. But her mother kept her eyes locked on the star map, avoiding Aeliana's own gaze.

Before Aeliana could press their unusual behavior the doorbell rang. ``That will be Erik.'' Her mother spoke.

Tommy brought him out, ``J\o rgensen Erik, here to see you, Master.''

``Thanks, Tommy.'' Erik spoke as he rounded the corner, entering the star room. Staggering to a stop upon seeing her, his hands when to his chest as he gaped dramatically. ``Do my eyes deceive me, or is little Stargazer gracing us with her presence?''

``Ha.'' Aeliana laughed dryly. ``You know very well that KANP's been canceled for the rest of the week.''

``And yet, you're not stuck in some hole, up to your neck in dirty old tomes.'' He continued, dropping the act as he gave her a sideways hug.

``The library in Kanopos is state of the art, and mostly archived.'' She gave him a sideways look as she attempted to push the older boy off her. She'd never known a moment of life without the older boy present. And even now well into his twenties he was still annoying.

``Same diff.'' He replied as he finally let go.

``Dad's going on a run.'' Aeliana looked over at her parents who did not correct her despite her last argument. ``Even i can spare a couple of days to make sure it goes smoothly.'' She finished, resigned to the truth.

\emph{`And it's not like a handful of days of study with changing anything. OCI is an impossible dream.'} She thought darkly. Eventually, the truth would catch up to her brain. Eventually.

``Well, we're glad to have you, kid.'' Erik continued not sensing her change in mood. ``Nice to have my shadow back.'' He added in a playful manner, taking her inattention to mess up her hair like she was still five.

``Stop it Erik. I'm not five.'' Aeliana complained as she fixed her hair. ``I'm not some little kid following you around either.'' She added.

``A guy can dream, yeah.'' Erik replied as he pulled out a bag of what was probably dried fruits from his coveralls. Popping one of the brown things into his mouth and chewing loudly in her face.

She rolled her eyes at his childish antics.

``Children, if you're done.'' Her mother warned in a calm voice, which meant she would take only a little more of their playful batter.

``Oh. Oh. Wait.'' Popping another into his mouth he hastened to put the bag back wiping his hands on his coveralls in the process. ``One more thing.'' Turning to her, he used both hands to look her over as if she'd just come back from a play-date. Nodding to himself, he let go before she even knew what was happening. ``Good, no lasting damage. Keeping the spirits high? Given it the old one-two special.'' He continued nonsensically.

``The what?'' Aeliana exclaimed.

Hopping on his toes he motions two poorly executed punches that were more likely to do more damage to him than his imaginary opponent. ``Ya know.'' Another two bad punches in the air. ``Sticking it out. Not letting that Amur kid win. The old one-two special.''

Aeliana's mouth hang open in surprise. \emph{`Dear Goddess, he can't know too.'} She thought.

``I'd give her a real demonstration if I was ever on the ship long enough. World could do will one less Clan member.'' Erik continued.

``Now Erik. You know, we can't go around killing Clan heirs.'' Mother patted Erik on the shoulder in sympathy.

``At least, we can't go around talking about it.'' Her father muttered under his breath loud enough for them all to hear.

``Goddess help me.'' She preyed loud enough for her family to hear. ``Ilia and I were never \emph{dating}, so there's no reason to kill anyone.'' She took a long look at Erik, but he wouldn't look her in the eyes. \emph{`Ilia will probably be fine.'}\ she thought.

``Anyway.'' Erik continued as he held up a thumbdrive, ``I've got some info for the run.'' His eyes briefly landed on her as he handed the drive over. ``You're going to want to view this before settling on a route.''

Her mother took the drive as she nodded in understanding. Turning to Aeliana, her mother spoke, ``Aeliana dear, why don't you run these dispatches to the message center?''

Aeliana's pressed her lips tightly together in response to avoid frowning at her mother's clear attempt to get her out of the house. \emph{`Running dispatches.'} She thought with disbelief. She could have tried a little harder, seeing as a Guild runner would be by within the hour to do just that task.

Her mother didn't give anything away as her face remained unguarded. Instead she smiled kindly as she continued, ``Some fresh air will do you a world of good.''

Sighing, Aeliana nodded as she picked up the dispatches. Her parents leaning in to talk about something or another as soon as she was no longer in the Star room. It was pointless to argue with her mother. Aeliana had never won, and didn't expect that to change now. So with a nod to Tommy, she was out the door. \emph{`Mother is either intentionally getting my out of the house to hide illegal activity, or she just want me to feel a little better about Ilia.'} Aeliana thought as she turned away from Solas Plaza.

``Of course, she could be doing both.'' She muttered to herself. Dispatches in hand, she began the long trip to the message center just out side of the main docks. Running messages was a relatively new thing. Antiquated in nature, but necessary until the Sakr\'{a} had the air ducts fixed. Just one of a long list of repairs needed to KTS Kanopos. One that was likely at the bottom of the list.

Her parents, being the innovators that they were had developed the runner system just as soon as the first hiccup to the air duct had started some years ago. Now that it was completely down, they, or rather the Guild, was making a steady stream of income from running messages and packages from locations. Aeliana had been extremely proud of her parents when the Sakr\'{a} had officially employed their running system to work throughout Kanopos.

But it was more than that. The Helian clan weren't just Guild Masters, but \emph{the} Guild Masters. Known throughout the intergalactic community with seats on civilian council and much more. \emph{`I come from a long line of tradesmen. We have more money than the Gento Clan. More merchant fleets. More intergalactic influence. We are important!'} She thought bitterly. But the truth was they were civilians. Civilians that weren't even part of the original forming of KTS Kanopos.

Her parents had no real voice, no real power. Paid twice as much for docking space as the Zh\`{u}r\'{o}ng and were allowed only a portion of premium space. None of that had ever registered to her before. While the heir to the Guild, she was also a Pilot-in-Training and unlikely to every touch the Helian business.

Someone bumped into her, pulling Aeliana out of her thoughts. Looking around she was dismayed to find herself across from the Amur flower shop. From here she could just make out... Turning sharply, she jogged away. ``I am not doing this now.'' She whispered to herself hyper focused on her goal.

Without further delay, Aeliana arrived at the message center.

``Cadet Helian, what a surprise.'' The Postman greeted her. ``Helping out your folks while KANP's down?''

She nodded as she passed over the dispatches, ``A new expedition.''

``Always good business for Kanopos, when the Guild goes on big expeditions.''  The Postman responded as he turned to messaging system. ``You know my son is out in Romulus space working with the Guild.'' He replied as he filed the messages away. ``Good honest work.'' He continued. 

``I'm glad to hear it.'' Aeliana replied trying to cut him off. If she listened to every story about the Guild she'd never go anywhere.

As she turned to leave, the Postman stopped her, ``Oh, we've a few things for your father, Cadet. If you don't mind taking them to him.''

``No, I'll take them.'' Going to pick them up her eyes catch on to her BISM. A waiting message, she'd not seen before. Or felt its arrival. For now, she ignored it. ``See you around.'' She tossed over her shoulder on her way out.

``Good luck on the expedition, Cadet Helian.'' The Postman called after her.

Instead, she focused on her trip home. Taking the side street to circumvent the Amur flower shop.

``Welcome back, Mistress.'' Tommy greeted her.

``Here, Tommy. Could you give these to my dad? I'm going to take my lunch break now.'' Replied as she handed over the missives.

``Of course. I'll have lunch ready momentarily.'' He rolled away.

In her room, she looks at her BISM. One waiting message without a profile picture. She was sure her parents had put up blockers for that kind of thing. \emph{`What have I got to loss? Can't be any worse than H\={e}id\`{o}ng's virus.'} She thought before opening the message.

\textsc{For those seeking power of the unique kind, seek us out. 103.14.6677}

``Power?''

Well that wasn't ominous at all.

\chapter{Friends, maybe?}

Aeliana paused just outside of the only flower shop on the KTS Kanopos. After Haruto had rejected another invitation to lunch, she'd found her way here. \emph{`And I've got to stop showing up here.'} She thought as she looked through the long window to several hybrid breeds in different shades of pink. Her hand ran through her hair, perhaps it was time for a change. 

Turning away at the sight of vibrant, long blonde hair that seemed to haunt her nights, Aeliana moved on. Some habits would just take longer to break. \emph{`Like automatically going to Ilia to complain.'} She added in her head. 

Of course, at the heart of the matter was eating alone, again. She never realized how hard it would be to make new friends. Probably didn't help that Ilia was friends with just about everyone in class. And given that this was twelfth time Haruto had turned her down, she was starting to doubt her own likability. \emph{`Too bad Erik isn't here.'} She could always count on him to eat lunch with her.

\emph{`No point in eating alone today.'} She thought with a heavy sigh as she made her way home. And despite all of the difficulties with finding companionship, she'd never eaten alone and didn't plan on starting now. The new barbecue place would have to wait. \emph{`I'll just have to remember to drag Erik to it when he gets back.'} She continued to herself. There was no point in taking her parents. The last thing she wanted was to tank a fledgling restaurant because they couldn't handle her mother's exacting standards. \emph{`I mean, not every restaurant needs to be five stars.'} She thought as she continued into the heart of Solas Plaza. 

As she walked down the street nodding to merchants and Keepers alike, she felt the strange weight of her newest hobby. Illegal as the parts were, she didn't even blink as the Keepers passed her. Unlike Haruto, there wasn't a single Keepers who'd dare to stop and search her without a warrant. \emph{`Mom would probably throw a fit if they did something that outrageous to me.'} She thought with a fond smile. The thought of Haruto, unfortunately, took her smile away.

He was an enigma. As loud and boisterous as he seemed, she always assumed he'd make a ready friend to anyone. In fact, he seemed to strike up easy conversations with everyone even Akihiko, who hated him with a passion. But with her, he was two lengths away. Shaking her head, she paused to let a message run passed her. \emph{`I guess, I've never really seen him interact with anyone outside of class, so maybe it's not personal.'} She thought.

Even so, that didn't change her pressing issue. Ilia had been her only friend. And now, everything just seemed so lonely. Erik could only help with so much. \emph{`I'll give Haruto one more try.'} She thought determinedly. Honestly, anymore and she'd start to look desperate. ``And Helians don't do desperate.'' She muttered under her breath. That and Haruto was a good enough study partner with his unique creativity that she could work with a professional relationship.

Of course, she could do without his lack attention span and volume control, which was probably going to get them kicked out of the library. But in this issue she couldn't be that picky. \emph{`Besides, if I have too, I can eat lunch with Akihiko.'} She shivered at the thought of sitting through a lunch with someone so self-absorbed as him. ``Or I can go home for lunch.'' She continued out loud as she reached her door.

Tommy opened it a second later with a wide smile on his synthetic face. ``Good afternoon, Mistress Aeliana. Will you be having lunch here?'' He greeted her in question as she passed him to enter properly.

``Uh hum.'' She hummed in agreement, ``If you don't mind the extra work.''

``Of course not, Mistress. I'll have something for you momentarily.'' Tommy replied before rolling into a different room.

Walking into the studio, she pokes her head in, ``Hi mom. How's your afternoon going?''

Her mother continues working for a beat more before pushing back to address her. ``Better than yours seeing as you're back so soon.'' She responded. ``I thought you were eating out today?''

``I'm allowed to change my mind.'' Aeliana replied as she entered the room fully, but her mother continued to stare at her. ``Haruto was busy, so I'm eating here today.''

``Again?'' Her mother questioned. Aeliana shrugged and immediately regretted it her mother's lips thinning with disapproval.

``Anyway, do you know when data is getting back?'' Aeliana changed the subject. ``There's this new place down the street that's getting good ratings. I figured we could go to celebrate his return.''

``Down the street?'' Her mother mulled aloud. ``Aeliana, where have you been suggesting to eat lunch with Cadet H\={e}id\`{o}ng?''

``Why does that matter?'' Aeliana replied defensively as she leaned against a wall to help control her body movements.

``Because him turning down lunch with you, my amazing, funny, intelligent daughter, for the tenth time would only make sense if he was an idiot.'' Her mother continued. Aeliana choosing to stay quiet on the actual number. ``From all of my resources, Cadet H\={e}id\`{o}ng is no idiot.'' Her mother added with a piercing look.

Aeliana was the first to look away with a sigh, ``Just the new places popping up.''

``In Solas?'' Her mother questioned.

``Yes, in Solas.'' Aeliana answered trying to suppress an eye roll. ``As if I'd step into a place in the Lower Level or the Zh\`{u}r\'{o}ng district.''

Her mother sighed heavily in response. Running a head through her brown hair, she responded, ``This is our fault. We spoil you so.''

``Excuse me?''

``Aeliana,'' her mother began instead. ``Cadet H\={e}id\`{o}ng is an orphan.''

``Yes,'' Aeliana began, but stopped mid-sentence. ``Oh.'' The orphan stipend wouldn't come close to allowing him to afford anything she was interested in. \emph{`No wonder he keeps turning me down.'}

``Yes, oh.'' Her mother mimicked. ``Why don't you invite him over for lunch when your father returns? That way he doesn't need to worry about money at all.'' Her mother replied easily. Clearly done with the conversation as she turned back to her work.

The off-handed invite; however, pulled Aeliana up short. Her jaw tightened at how \emph{easily} her mother had extended the invitation. ``That's it.'' She replied shortly. Her mother looked up in confusion at the tone. ``Just like that, a guy I'm maybe friends with get's an invite?'' Her voice raised a touch higher.

Her mother gave a heavy sigh, ``This is about Amur isn't it?''

``She was my friend for \emph{eight} years. Eight!'' Aeliana continued her whole body tightening as she stood ramrod straight. ``And she couldn't get invited past the forger!'' She continued taking a step forward in her anger. ``And this \emph{boy}, get's an invite to dinner?''

``One, it's only lunch. Two, as you very well know this isn't about gender.'' Her mother countered giving Aeliana her full attention. ``No one from the Clan enters the Helian household. \emph{No} one.'' Her mother emphasized. ``Not an Amur, not an Zh\`{u}r\'{o}ng, or even the K\={o}taishi, because that is our way.''

``Our way is about trust!'' Aeliana countered. ``And I trusted Ilia. I knew her!''

``And see how well that turned out.'' Her mother replied swiftly like a physical slap. Aeliana took a step back, betrayal in her eyes. ``Aeliana, sweetheart, I'm sorry. I didn't mean...''

But Aeliana shook her head to stop her mother's pointless apology. ``No, you meant exactly what you said.'' Her voice was hard as a composite alloyed. 

``Aeliana.'' Her mother sighs her name. ``I know you think Ilia's loyalty were unquestionable, but we couldn't take that chance. Now Cadet H\={e}id\`{o}ng is just an orphan like Erik. No Clan claims his loyalty and likely never will.'' She continued. ``Surely you can see the difference.''

Aeliana shook her head. ``No mother,'' she responded. ``The problem isn't the Clan, not this time. You just didn't trust me, trust my judgment.''

``If Amur truly cared about you, do you think she'd stop messaging you after only two weeks.'' Aeliana looked up in surprise. 

``But...'' Aeliana questioned. \emph{`My BISM is supposed to be private.'}

As if answering her unasked question, her mother continued, ``You're still my child, Aeliana. A mother knows.''

At her mother's sad eyes, Aeliana turned away and headed for her room upstairs. Her mother didn't call out or try to stop her, for which Aeliana was glad. She didn't need this, not now.

The smell of something delicious greets her when she enters her room. \emph{`Seafood broil, Tommy always knows how to make me feel better.'} She thought as she took a seat at her desk. Her BISM automatically linked with her console, booting up the Halo screen before her.

Taking a sip of cold water, she paused. Her mother could be cold some times, but she had been right about Haruto. \emph{`He's probably never even tasted real water.'} She thought as she continued to drink. Ilia had never mentioned price when they went out to eat. More often than not, she didn't think of it either. She didn't know what it was like to be poor, and couldn't really imagine it. \emph{`Maybe I'm just a horrible, shallow person.'} It would explain why Ilia had given up so quickly, why she struggled to make new friends.

A sad smile graced her lips for a moment as she eat a dish that was probably more than Haruto's yearly stipend. She eat in silences as she scrolled through files on Azca relics. Her father was traveling through the Nahua territory, and given the hate for the old Azca Empire she imagined he'd find a relic or two for cheap there.

It wasn't until her lunch was completed that she moved on to something more pressing. All thoughts of friends gone to haunt her in her dreams. Pulling out the rusty box Haruto had given her, she carefully took out the trigger. \emph{`Good, nothing's broken.'} While she was sure she could have fixed it, she was also sure the black-link she used to download blaster schematics would get picked up by her parents if she used it too many more times.

Looking at the schematics now, she pulled out the rest of the almost fully assembled short range blaster. After her unfortunate altercation in the Lower Level, she never wanted to feel helpless again. \emph{`And my own blaster will be perfect protection.'} She thought, ``As long as it works.'' She muttered under her breath.

With the trigger in place, she re-assembled the blaster before hooking it up to her BISM for calibration and diagnostic. The plastic felt heavy in her hands, as the run completed. \emph{`I guess, all that's left it to try it.'}

With a click of a button, energy targets appeared in the corners of her room. The special ordered material had gone through Tommy and wasn't likely to raise any eyebrows with her parents. Better yet, it would allow her to fire the weapon in her room without making a noise. \emph{`Well, as long as I don't miss.'}

Carefully aiming the blaster, she shot off a single shot. 

\textsc{3 cm, 13 degrees off from target.} Appeared before her eyes.

``Adjust calibration.'' Aeliana commanded watching as a stream of code flowed past her left eye. Leveling the blaster at the center of the target, she shot again.

\textsc{2.5 mm, -2 degrees off from target.}

``Adjust calibration.'' She replied for a second time and was rewarded with her third shot 100\% on target. Shooting off at the targets around the room, she fired until the plastic warms uncomfortable in her hands.

\textsc{100\% on target.} Her BISM replied as Aeliana set the blaster down. Placing the weapon back in it's hidden compartment, she cleared the room of the targets. While her parents never entered her room, there was always a first for everything and she didn't want them to know about her blaster, or really why she thought she needed one.

Sitting back down, she looked around the room, before putting on one of her favorite dramas. Today Kagome needed to pick between waiting for her true love to wake from his year long coma or his handsome, but evil brother, who had masterminded the accident behind his brother's coma. It really should have been an easy choice, but poor Kagome didn't know the brother was seducing her for her power. \emph{`If only Kenshin wasn't so cute he wouldn't stand a chance with her love!'} Aeliana thought as she lost herself in the drama.

``Don't sleep with him Kagome!'' Aeliana whispered fiercely, ``You're better than him.''

\emph{Buzz, Buzz.} Her show paused briefly at the incoming message. 

Aeliana's brow furrowed at the unfamiliar IP address. \emph{`Is this even from Kanopos?'} She thought. But before she could delete the likely virus, it opened own it's own.

``Oh no!'' Aeliana shut her eyes waiting for the virus to take hold. Anything that could get through the Guild firewall was likely to be nasty. After a few seconds, nothing happened exact her show continuing. ``Pause.'' She commanded as she looked at the open message.

\textsc{888HeY! sORRy loOKS LiKE i GOT kICk oUt of LibRArY.131313}

\emph{`Haruto?'} She thought as another message appeared in her inbox and immediately opened itself.

\textsc{wElL, nOt eVEryDaY.67676. juST liKe i cAN't gO MOre tHaN ONce a wEEk.00922?>777\&}

``Yup,'' Aeliana thought with mild irritation. ``Trust Haruto to get us kicked out of the library.'' Another message opened up.

\textsc{45454\#\#HopE yOu GoT aNOthEr PLaCe wE cAN gO Too.:):)*8*8*}

\emph{`Well at least he added a smiley face.'} Aeliana thought with a sigh. Her eyes drop down finding the concealed box with her new blaster. ``Well, I guess it couldn't hurt to get a bigger place.'' She said aloud. She'd definitely need something to house a relic.

Messaging back, she wrote. \textsc{I'll think of something.}

