\chapter{}
Haruto looked out the window to the KANP park outside. Further down would be Prayer Alley, not that he'd gotten to visit it much. Every since the turn of the Founder's year, the Keepers had been riding him everywhere he went.

While it wasn't unheard of for them to do that, as he regularly got stopped anywhere within central Solas. 'Cadet H\={e}id\`{o}ng, why don't we escort you to class. We wouldn't want you to be late for your lessons.'{} 

Or 'We've had a few complaints in the area. Just checking to see if you're alright.'{}

As if he'd believe any of that, although QB9 was getting a kick out it. To the Gods, they were even harassing him in the LL.

'This is a dangerous area, Cadet H\={e}id\`{o}ng, let us escort you through.'{} The nonsense. And for the life of him, he couldn't figure out why.

\textbf{\sffamily{Don't ask me. I've already searched your database.}} QB9 answered his unasked question for once. 

\emph{`Well, it happens every year. Just not nearly this bad.'}

\textbf{\sffamily{Probably a response to the KANP incident.}}

Haruto rolled his eyes. He'd figured that much out already. \emph{`Figures. What I don't get it what's so special about this time of year?'} Haruto thought as Sergeant Sang-eo continued about some history lesson or another. QB was recording the lecture and would cut to the points that mattered for him.

Aeliana was busy typing away at her tablet, probably adding another year of text she'd only expand upon once class was done. If he had to listen to her rant, or rave whatever, about Sergeant Sang-eo's lecture style for one more hour, he was going to seriously rethink the breathing day gift. 

\textbf{\sffamily{Don't blaster your foot off with that one, kid.}} QB9 replied at the thought.

\emph{`It's thirteen weeks away, more MINOS might change my mind again.'} But Haruto could still feel QB's disapproval. The long rifle was looking to take eight maybe nine weeks of built time. Not including calibration tests, so he could still change his mind about it. \emph{`Or get some noise cancellations implants.'} He thought.

\textbf{\sffamily{As if we could afford it.}} QB replied.

\emph{`Can't be that hard to make.'} He thought bitterly.

Sergeant Sang-eo droned on at the front of the lecture, stopping on briefly to wake Kur-ram up. At least he was an equal opportunist when it came to being annoyingly present. Haruto blinked in concentration. \emph{`I'd rather watch an alloyed coat dry.'} Which was saying something because the gassy fumes always gave him a headache.

\textbf{\sffamily{Stay in there, kid. Or at least think of your next training prank.}} QB9 commented. \textbf{\sffamily{That should keep you looking attentive for the handful more minutes before lunch.}}

\emph{`Duly noted.'} Haruto replied with a mental salute, but he found it hard to concentration on even things he enjoyed with the soft swaking of Seo-Jun's symbiote. \emph{`I wonder if the holidays with the Empire?'} He thought absentmindedly pushing pasty old looking Generals, or Commanders, or whatever around his tablet screen. Images were surprisingly distracting when they weren't moving and talking.

\textbf{\sffamily{I've double-checked the list of holidays and festivals on the Ship and in the Jade Empire.}} \textbf{\sffamily{Still nothing on the official record, kid.}} QB9 interrupt his thoughts.

\emph{`Oh? Well thanks anyway.'} Haruto thought as his eyes landed on the observatory outside. He really did hate this time of year. And if he knew what fancy party or whatever the Keepers were trying to keep him away from, he'd have pranked ten times over in retribution. As it was, he had to settle for his yearly mega prank. The prank that set the standards for all future pranks to come by. The prank everyone on-board and off it would be talk about for the year to come until he out did himself. The most awesomest, most...

\textbf{\sffamily{Yeah, yeah. I get it. The prank to end all pranks.}} QB9 interrupted. \textbf{\sffamily{I change}} \textbf{\sffamily{my mind, think of something else.}} He continued sourly.

\emph{`It's not just any prank, QB.'} Haruto began, \emph{`It's the biggest prank of the year, which is supposed to only be topped by the next New Year prank.'} He continued. \emph{`And seeing as you made the KANP prank into this big thing, now I've had to really work on it.'}

\textbf{\sffamily{I don't get it.}} QB9 questioned. \textbf{\sffamily{If you do it every year, surly the Keepers know}} \textbf{\sffamily{somethings coming.}} Haruto nodded in response. \textbf{\sffamily{So, why not vary it? Seems like}} \textbf{\sffamily{you're making it harder than it needs to be on purpose.}}

Haruto tilted his head in response. \emph{`I've always kind of thought of it as a game.'} He replied. \emph{`They know I'm coming, so every year they add more and more protection around the ship. But they don't know what I'm going to hit, or when I plan on hitting it.'}

\textbf{\sffamily{Still seems silly to me. Making it harder than it needs to be.}} QB grumbled in response.

\emph{`It's all about the chance.'} Haruto replied easily. \emph{`They have to have a chance. That way, when I still win despite their best efforts their embarrassment is nearly as high as the inconvenience they give my for the past five weeks.'} Although privately, he didn't think it quite covered his productivity time lost with their street harassment, legal as it was.

All of those factors and more was why he was hitting a target they'd never see coming. The Commander's Halo. \emph{`Which lies in the previously untouchable observatory deck.'} Haruto added mentally. The old man would get a kick out of it, even if that wasn't the outcome he might have wanted after showing the big screen to Haruto during they monthly meeting. 

\textbf{\sffamily{I still think this is an unnecessary risk.}}

\emph{`Of shove it, QB.'} Haruto thought. \emph{`You should be glad I'm giving you a job to do this time. So don't mess it up.'}

Today was going to be one to remember. And it would be a chance to test QB9's controlled hack. They'd need it if this was going to work. \emph{`And who would even want to be the Sakr\'{a} anyway?'} He questioned himself out of nowhere. His memory of the old man surrounded by more than a dozen of secured tablets. Paperwork should have been labeled as a dirty word.

\textbf{\sffamily{Kid, focus!}} QB9 growled out. 

\emph{`Yeah, yeah. The prank.'} Haruto waved the thought away. He'd been running pranks since he could walk. And this would be no different. \emph{`You know, if they'd just leave me alone, I wouldn't have to embarrass them so badly.'} His mind jumping to another thought.

He could feel QB9 sigh, but seeing as Haruto was on topic at least the AIM didn't see a reason to nag at him. \textbf{\sffamily{If this works, let's hope they learn their lesson.}} QB9 commented. \textbf{\sffamily{If it works.}}

Haruto snorted causing Sergeant Sang-eo to give him a dirty look, but continued with his lecture as if uninterrupted. \emph{`The question isn't if. You've read my program, even you can't find anything wrong with it. No, it's whether the Keepers will take a hint. But every year they just seem to escalate.'}

\textbf{\sffamily{It's not the program I'm worried about. You still have to get in there.}} QB9 answered. \textbf{\sffamily{And you never know, this could be the year.}}

\emph{`Now that's the easy part, just watch and learn.'}

His BISM buzzed for the noon hour. Kenta was already halfway out of his seat before the Sergeant officially dismissed them for lunch. ``Alright, alright. I get it. You're all hunger. Get out of here and come back refreshed and ready to learn.'' Sergeant Sang-eo spoke.

Aeliana was already out the door mid-sentence, but he didn't take offense. She'd already told him, she was avoiding Akihiko, and thus, couldn't eat lunch with him anymore. Honestly, that worked perfectly for his plan.

``Hey Seo-Jun, wait up.'' Haruto called out.

\chapter{}

Haruto washed his hands in the bathroom on third floor of KANP, his classroom just across the hall. He'd made sure that at least five of his Clan classmates had seen him enter. They were, after all, his alibi for the lunch break. A wide smile spread on his face as he shook out his wet hands.

\textbf{\sffamily{This better be worth it.}} QB9 growled out. Haruto ignored him, he was still upset about the cost of lunch. Haruto had warned him it would be expensive. It was one of the reasons he'd been saving up for the prank. The Clan's all had rather expensive tastes and Seo-Jun wasn't any different with his love of Gongsaeng barbecue only rivaled by Kenta's love for Sakhalin barbecue. 

Nodding to a sixth year that looked like he cut his own hair, Haruto entered the stall closest to the window. Sitting down in the stall he linked his BISM into the bathroom terminal. While security had increased overall, SKIM connections in the bathroom still had a backdoor, one he planned to exploit. 

\textbf{\textsc{Access confirmed. Welcome Headmaster Aiko.}}

\emph{`Why thank you.'} Haruto replied smartly.

\textbf{\sffamily{Stop playing around kid. We're alone. Get moving.}} QB9 commanded.

\emph{`Yeah, yeah.'} Haruto replied as he unlinked from the bathroom and climbed out of the window. \emph{`You know,'} he paused in thought. \emph{`If you don't have any fun, than you're missing the point of the prank.'}

\textbf{\sffamily{I'll have fun, when this is over.}} QB9 replied. \textbf{\sffamily{Now move it.}} He continued. Haruto didn't take his tone very seriously. He could feel QB's excitement just under the surface. 

Climbing up, he made his way to the roof central terminal. The cameras were currently looping, and would be doing so for the next five minutes. A tight window, but nothing he couldn't manage. Pulling into the terminal, he logged in. \emph{`Alright QB, you're up.'}

\textbf{\sffamily{It's QB9, kid.}} QB9 growled out, but the terminal opened within seconds. \textbf{\sffamily{What are you waiting for, an invitation?}}

Haruto waited a moment more, \emph{Bang!}

A second later his BISM buzzed. \textbf{\textsc{Sorry class, give me five more minutes. Sang-eo out.}}

Hopping into the terminal it shut behind him. \emph{`Now, we're...'} Haruto began, but the sudden change in gravitational force interrupted his train of thought. ``Woo hoo!'' He yelled out as the breath was sucked from his lungs.

It was the first time, he'd used the terminal system without a random pattern, but it was the most risky way to use it. Given his time limit, though, he knew they didn't have time for misdirection. No, he just had to trust that QB9 had done his job correctly so that no record of this KANP terminal would be recorded.

\textbf{\sffamily{Hey, don't worry about me, kid. I've got my end.}} QB9 complained. \textbf{\sffamily{And now}} \textbf{\sffamily{it's your turn.}}

Haruto was up ended into the trash compost heap of the observatory deck a millisecond later. While he'd made sure to timed it \emph{between} burn cycles, the garbage still ran hotter than he'd been expecting. Ignoring the sting of pain, he pulled himself up and out of the trash shoot. 

\textbf{\sffamily{Incoming.}} QB9 warned.

Haruto pushed himself back along the wall, holding still as several Pilots passed his position. Dropping down, he made his way swiftly down the hall and up into the air vents in the next section. Here, the metal's heat made him miss the trash heap. But soon enough QB9 was soothing his pressure areas so that he could crawl the last meter to his final destination. 

Popping the air vent open, he dropped down swing it shut as he went. \emph{`Time?'}

\textbf{\sffamily{T minus 3 minutes and 13 seconds, kid.}}

Good, he had a bit more than a minute to work with. Making his way to the center. Haruto moved to the back of the terminal. He wasn't stupid enough to try and hack this directly. That and he didn't have the time. Instead, he opened the service hatch of the terminal. Moving the wires out of the way, he searched for the correct spot. 

\emph{`Let's see, a little north of... Yeah, this will do.'} Opening his BISM, Haruto took out a small chip housed protectively next to QB9. Completely sealed off as it was, he wasn't worried about cross contamination. Closing his BISM, he gently placed the new little bug right behind where he knew the CPU for this terminal would be. 

The little chip sizzled as he dig into the synthetic material finding it's way to the CPU beneath. \emph{`That should teach 'em to use composite alloys in critical central terminals.'} Haruto thought with a smile as he pushed the wires back in place. By the time, they figured it out, his little chip should have degraded. Theoretically anyway.

\textbf{\sffamily{Let's go kid. We're on the clock.}}

\emph{`Yeah, yeah.'} Haruto replied as he pulled himself back into the crawl space. \emph{`Let's get out of here.'}

\chapter{}
Haruto running along rooftops from LL, running late as always. \emph{`I don't see why you couldn't have warn me about the time.'}

\textbf{\sffamily{I did.}} QB9 replied in bore tone. \textbf{\sffamily{Cut through this alley.}}

Jumping down, Haruto broke his fall with a roll, popping up he used the side of the building to change direction. Cutting through the nearby alley. The fabric of his coveralls waving over his shoulder. \emph{`Saying 'your going to be late' is not warning me. I was already running behind when you said something!'}

\textbf{\sffamily{Not my problem. No take the left.}} QB9 replied.

\emph{`I think you just like telling me where to go.'} But Haruto took the path anyway. QB9 didn't respond to the accusation, so Haruto took that as the informative. Reaching the end of the alley, he paused to throw on his coveralls, before stepping out into the crowd.

``I don't even see why I need to waste my two week vacation on this.'' Haruto muttered sure no one would look at him twice.

Here, QB responded. \textbf{\sffamily{We agreed. If you couldn't pick up your grades, I would get involved.}} He paused for dramatic effect. Haruto was regretting teaching him the technique. \textbf{\sffamily{Now, I'm involved.}}

Sighing, he pushed his way forward. While he'd averaged a 87.4\% on his last three exams, the score was several points lower than the 92\% he'd needed to get that allusive 70\% average. Now he needed an impossible 97\%, while technically 96.6\%, on his last three exams. If not for the impossible situation he'd found himself in, he would have protested more, but... well he wasn't going to admit QB9 was right. Never.

Instead, he changed the topic to just finding the place. ``Fine, but if I miss this place, I'm going back to the warehouse.''

\textbf{\sffamily{Impossible.}} QB9 countered. \textbf{\sffamily{It's supposed to be the biggest building in this}} \textbf{\sffamily{sector. You can't miss it.}}

Looking around, Haruto still wasn't sure what he was looking for. ``What's the name of...'' Haruto cut himself off as he came to a slow.

More than twice the size of KANP, stood the fanciest arches he'd ever seen. \emph{`Is that jade?'}

Haruto could feel QB9's amusement. \textbf{\sffamily{Welcome to the DOMAINE, kid.}}

Walking into the building, Haruto was a little lost. \emph{`You wouldn't happen to know where I need to go, would you?'}

\textbf{\sffamily{I can't do everything for you kid.}} QB9 growled out.

Haruto snorted. \emph{`So, they don't have the building schematics online. Interesting.'} He thought.

A group of uniformed people, students maybe, passed him. ``Hey,'' he called out weakly.

A girl paused looking back at him with a warm smile. Turning to her companions she motioned them to continue. ``Hi, you looking for the cram school, right?''

``Ah, how'd you know.'' Haruto replied sheepishly.

She smiled back, ``Well it is that time of year again. And well,'' she pointed to his coveralls. ``Students here wear standard issued.''

Haruto blushed in embarrassment. \emph{`I thought you said this was standard issue coverall, QB'}

\textbf{\sffamily{I never said that.}} QB9 replied defensively. \textbf{\sffamily{I said, you'd need it. And you}} \textbf{\sffamily{do. You're cover is from the Sanctuary Academy. Orphan with average grades not cut out for}} \textbf{\sffamily{Keeper Academy.}} QB9 continued. \textbf{\sffamily{All of which, I sent to you in the briefing folder.}} 

Haruto tried to remember which one that was, but was coming up blank. ``Well, you caught me.'' He replied aloud, half to the nice girl and half to the increasingly annoyed AIM. ``You wouldn't happen to know where it is. I'm already running a little behind.''

\textbf{\sffamily{Which you didn't read. Just great.}} QB9 growled in frustration. \textbf{\sffamily{I}} \textbf{\sffamily{worked on that cover for days. I even got a guidance chip assigned to it.}}

``Sure.'' She replied perkily. ``Why don't you just follow me?''

\emph{`Is that what that chip was for? You should be glad I even put it in my SKIM.'} Haruto replied to QB. ``Thanks so much.'' He replied to the girl. ``You're a real life saver. I'd hate to start class on the wrong foot.''

The girl nodded. ``I'm Naomi, just Naomi.'' She looks over at him, ``I was a Keeper brat too, so I'm always trying to help others like me.''

\textbf{\sffamily{Solid.}} QB9 replied. \textbf{\sffamily{At least someone appreciates the work I do.}}

``Do you like it here?'' Haruto asked. QB9 might have put what this place was in his dossier, but well he wasn't going to push his luck with the moody AIM.

\textbf{\sffamily{I am not MOODY.}} QB9 growled out. 

The girl nodded brightly, ``Oh yes. I know everyone looks down on Techies, but we do the most important stuff.'' She answered.

\emph{`You enrolled me in a TECHIE class!'} Haruto thought in outrage, but hoped he'd managed to keep it off his face.

``Really?''

Her giggled response showed he'd probably been less than successful. ``I know what you're thinking. But no Pilot can run a ship, or do the complicated calculations necessary to fight in combat without a Tech crew. Not anymore anyway.'' She replied.

``What?'' Haruto replied in disbelief, ``no way that's true.''

The girl nodded, ``No, it's true. High Commanders Lee and Stone are teaching you cram this year, and will no doubt give you hints about the full capacity of the Head Technician. It's really just a sad common misnomer that pilots fly their ZenKZ sole. The Head Tech is there too, fighting side-by-side. Just without all of the glory.'' She answered as she paused outside of a door. ``Anyway this is you.''

Haruto couldn't argue with her here. He honestly knew next to nothing about what Techs did. The old man always like to talk about Pilots and OCI. He'd never even mentioned this DOMAINE place. ``Thanks.'' He replied as the door slid open.

``Good luck,'' she replied before taking off at a run down the corridor.

\emph{`I hope she not late.'} He thought as he entered the room. \emph{`Hey, QB? What do you know about the DOMAINE.'}

There was a long pause as Haruto found a seat near the back as he waited for the AIM to answer. \textbf{\sffamily{Mostly what you know, kid. KANP only}} \textbf{\sffamily{keeps records of the Cadets it send here, not about the program.}} QB9 answered. \textbf{\sffamily{If you}} \textbf{\sffamily{want to know more, we'll have to hack into their system.}}

Haruto rolled his eyes. \emph{`Or we could just ask the right questions.'} He replied. \emph{`I'm not ready to let you loose everywhere, QB.'} Sitting down, he rested his head on his hands as he listened to the chatter of his classmates. \emph{`Besides, there are two ways to get information. And it's time you learned strategy number two. Listen.'}

\textbf{\sffamily{Listen!?}} QB9 raged back, but Haruto was only half listening to him. \textbf{\sffamily{Who takes your notes? Me! I listen just fine.}}

Haruto waited a beat longer as he continued to listen to his new classmates.

\textbf{\sffamily{YOU are the one with the LISTENING problem!}} QB9 continued, getting angrier by the second.

\emph{`Did you know that those six students all know each other probably from KANP?'} Haruto replied.

\textbf{\sffamily{What?}} QB9 spoke, his rage settling.

\emph{`And those three are from the same Gento orphanage program.'} Haruto nodded his head in the direction of three student, two boys and a girl huddled together.

QB9 paused briefly, \textbf{\sffamily{So it's okay for you to hack into the DOMAINE, but}} \textbf{\sffamily{I can't?}} He questioned darkly.

\emph{`I didn't hack the system. Just their body language.'} Haruto could tell he had QB's attention so he continued. \emph{`See that group over there, four girls all with the same badge on their coveralls?'} Knowing he had QB9 attention he continued. \emph{`They're orphans, but live together in one of the apartments at the end of Solas. Closer to the Sakhalin sector than the Gento sector.'}

\textbf{\sffamily{How could you possible know that without hacking their BISM, or the class register?}} QB9 questioned.

\emph{`Easy. That badge is for orphanage 5A in the Sakhalin sector, which can only hold a small number of kids. All orphanages prioritize the young children, which means they girls live in group.'} Haruto replied. \emph{`And before you ask. I know they live together because of their proximity to each other.'} He paused as he continued to observe the class. \emph{`They're comfortable with each other, because they know each other.'}

He could feel QB9 thinking, so he let him as he got the measure of the rest of class. \emph{`Just twelve of us, and no one seems to really want to be here. Interesting.'}

\textbf{\sffamily{Can I learn to do this... Observe thing?}} QB9 questioned. \textbf{\sffamily{Or is it a human}} \textbf{\sffamily{thing.}}

\emph{`You can see them, just as I can. Hear them too.'} Haruto replied. \emph{`Don't worry so much QB9, humanity has nothing to do with this.'}

At that moment, the classroom door slid open reveal too sharp looking women. \textbf{\sffamily{The High Commanders? I don't know why they'd be teaching}} \textbf{\sffamily{a cram class.}}

\emph{`Me neither. Maybe High Commander titles aren't that big a deal at the DOMAINE.'} Haruto replied.

``Good, it looks like you're all here.'' The High Commander with streaks of gray in her hair spoke with a hard commanding tone. ``We expect you all on time for the forcible future. Is that understood?''

``Yes, ma'am.'' Haruto replied standing in salute to the woman.

``Good morning, Cadets.'' The woman next to replied in a softer voice. ``My name is High Commander Stone, I have the current pleasure of leading the Department of Neurological Engineering and advanced technological development.'' She smiled brightly at the class. ``My companion is High Commander Lee, who leads the Department of Mechanical Engineering and military readiness. And while normally we are both very busy women, for these next two weeks we are you esteemed professors.'' Her eyes turned sharp as she looked around the room, ``I hope you all work very hard for us.''

``Yes, ma'am,'' Haruto chanted with the class, ``Thank you for teaching us.'' They continued as Haruto kneeled in a shaky bow. He'd had to do this once before with a guest lecture, but he was a little worried QB9 had gotten them into a high profile class.

\textbf{\sffamily{I swear kid, this is a required class for all KANP students that don't make the academic cut}} \textbf{\sffamily{off. Not to mention all of the non-KANP students.}} QB9 replied.

\emph{`Alright, we'll just have to stick to the middle of the pack.'} Haruto thought as they took a seat.

``Now before we get started,'' the cold voice of High Commander Lee sounded. ``You probably have no idea what you're in for.'' 

Haruto nodded along with several others.

``Twelve hours seven days a week. This isn't KANP,'' she looked over at the group of six students Haruto had labeled as KANP Cadets. ``We don't have time for days off, if we're to get you DOMAINE ready.'' She looked around the class, pausing at each student as if memorizing faces. ``Some of you will fail that's fine. The DOMAINE isn't for everyone.''

``But as long as you try as hard as you can, we'll make sure we get you in the right place for you with stellar recommendations.'' High Commander Stone took over her voice soft compared to her companion's. ``This is the DOMAINE, where we train the future Technicians to surpass tomorrow. Everyone is important, no matter your physical capabilities.'' She finished.

Haruto half thought she's start hugging everyone. High Commander Lee rolled her eyes a small smile on her lips that made her less intimidating. \emph{`We need to be really, really average here, QB.'} He warned.

\textbf{\sffamily{Noted.}} QB9 replied softly.

``Now some of you might still have hope of becoming a Pilot.'' High Commander Lee continued. ``And maybe you make it, I can't tell you the future. This class, however, is not for that.'' She looked around the room hard stopping at a face or two but never for long. ``You are all potential Techies, maybe even Head Tech material.'' She continued. ``And we will treat you as such.''

Silence reign on the room before High Commander Stone clapped her hands together cutting the tension. ``Now let's get down to business. I just know that if we can get through the boring stuff, we'll be able to try some TARGET assisted simulations.'' She replied with a smile.

Haruto couldn't quite shake the feeling that this could go very badly for him. This was the last time he let QB9 schedule \emph{anything}.

\chapter{}
Running swiftly along the rooftops, Haruto slipped down between two residential buildings as the coordinates filtered into his consciousness. A handful of seconds later, a Keeper patrol walked overhead. It was that time of year again, during the long vacation from KANP where the Keeper's had tripled their patrols in this region. The time of year, where he could go nowhere in public without being accosted. As such, he and QB had taken some precautions. Namely, keeping track of the patrols movements.

\textbf{\sffamily{If they're stupid enough to leave that kind of back door in their system, then they deserve}} \textbf{\sffamily{to be tracked.}} QB9 growled in his head.

Haruto counted six more seconds in his head before returning to the rooftops. \emph{`You're making light of a very difficult hack.'} Haruto replied as he continued on his way.

\textbf{\sffamily{I could have done it in half the time.}} QB replied.

\emph{`You'd still have had to get into the building.'} Haruto replied as he took a left. He'd have to go the long way, but he already knew that. 

\textbf{\sffamily{That's what you're for, kid. The legs.}} QB9 answered. Haruto could feel his smugness. Another patrol forced him down again. This time, he turned down the alleyway, avoiding a secondary street patrol.

New coordinates made him retrace his steps to avoid a third patrol.

\textbf{\sffamily{What's the point of doing this anyway?}} QB9 questioned as they waited a second longer before returning to the rooftops. \textbf{\sffamily{Day of birth? I just}} \textbf{\sffamily{don't get it.}}

\emph{`She got me the whole season of Devil Cop,'} Haruto thought back as he speed up, \emph{`There isn't a single copy of that within Kanopos.'} He continued as he took to the curved catwalk that circled the area. His eyes were sharp on the look out for anything QB didn'or couldn't warn him about.

\textbf{\sffamily{So?}} QB9 replied. \textbf{\sffamily{That show is inaccurate on so many counts. It spits in the}} \textbf{\sffamily{face of physics.}}

Jumping down lightly, he slipped off the side of the nearby roof to avoid the two patrols in the area. He had a few seconds before the next staggered group would be around. Ignoring QB as he concentrated was difficult. Especially since they'd had this exact conversation before. 

Slipping into the rock garden below, he was careful not to step on the small pebbled design. \textbf{\sffamily{I'm just saying that this is a waste of}} \textbf{\sffamily{energy.}} QB9 continued. 

Climbing up the side of the housing unit, Haruto ducked his head down as a patrol ran across the roof. Tension released from his shoulders as he lifted himself up and to the viewing hack of the housing unit. \emph{`It's her birthday, QB. And it's important to me. So,'} Haruto pulled out his BISM setting it close to the hack. \emph{`Are you going to help? Or should I do it?'}

In response the hack popped open. Haruto nodded his head in thanks as he dropped down into the room below. QB9 was getting better at hacking, soon it would be time to bring him in on the big pranks.

For once, Haruto arrived alone in his friend's room. Looking around, he couldn't help the negative thought at how bare it was. A desk, a single dresser, and room for a futon. Nothing on the walls, nothing personal. If not for the fact that he knew this was a lived in room, he'd have swear this was some kind of weird waiting room. An of course there was no color, but seeing as his friend was colorblind, he supposed that one he could give her a pass on.

\textbf{\sffamily{What now?}} QB9 questioned as Haruto walked over to the desk. He checked his BISM, pulling up his location monitor.

\emph{`Well she's here, somewhere.'} Haruto replied in thought. He was going to have to update his program to give something more than an general location, but that was for a later date.

\textbf{\sffamily{We can't wait here forever, kid.}} QB9 warned. Haruto could see the movement of the Keeper patrols, and for whatever reason there seemed to be increased activity within the area.

\emph{`That's not patrol movement.'} Haruto thought.

\textbf{\sffamily{No it isn't. And I don't want to be here and find out what it is.}} QB9 replied in a low growl. \textbf{\sffamily{Just leave it on the desk, so we can get out of here.}} QB9 suggested.

Haruto tapped his left arm, revealing a small storage pouch in his SKIM. No sooner was he pulling out the chip-set he'd programmed for his best friend's birthday, did one of the walls move.

``Star dust!'' Haruto cursed softly as he turned to leave, but he was good and caught, and he knew it.

``Cadet H\={e}id\`{o}ng?'' The light voice of his friend caused him to relax.

``Hey Princess.'' He responded as he dropped back down from the roof window he'd been hanging from. ``Man, I was starting to worry, I'd miss you.'' Handing the chip over, he gave a large smile, ``Happy birthday!''

She fingered the device slowly. Her eyes darkening and whirling in an all to familiar pattern as she investigated the chip. Finally, placing it in her BISM she turned her attention over to him. ``Thank you.''

Her voice lifted in a way that told Haruto she enjoyed the gift. ``Hey now, it was nothing.''

\textbf{\sffamily{Nothing...}} QB9 replied harshly. \textbf{\sffamily{If you call breaking into a Keeper}} \textbf{\sffamily{academy nothing, than I'd hate to see what is actually something.}}

\emph{`That was to figure out her b-day, QB. Honestly the gift part was simple.'} Haruto thought.

She shifted in her place even as her smile waned. Bring Haruto's attention to her fancy coveralls. Normally, they hanged out for a couple of hours, but it was clear now that she was busy. \emph{`Of course she is. She's got a family and stuff.'} Haruto thought. He felt stupid for thinking they'd get to hang now. ``And you don't had time to hand.''

\textbf{\sffamily{You couldn't hang even if she had the time.}} QB9 replied. \textbf{\sffamily{Or are you already}} \textbf{\sffamily{forgetting the massive force of Keepers congregating on us now.}} QB9 growled out. \textbf{\sffamily{Say your goodbyes, we got to go, kid.}}

``Anyway, I guess I should go, huh?''

She tilted her head in apology, ``Perhaps next week?'' She asked.

He shrugged in reply. ``Sure, I guess.'' Lifting himself back up, he turned back for a second, ``Hey, you won'd happen to know why there's a mac(more than a shit, compressive) ton of Keepers surrounding the area?''

``Yes, for my birthday.''

``Huh?''

``It is a celebration, festival, for the Clan.'' She replied softly her hands disappearing into her coveralls. He'd noticed she did that when she was nervous.

``A festival? Like everyone celebrating it?''

Her eyes shift to black, before turning to normal. ``The heir is a symbol to many, including the Y\`{u} Hu\'{a}ng Sh\`{a}ngd\`{i}. So it is widely celebrated here.''

``The what now?''

Her lips pressed together in her sorta smile, ``The Sh\`{a}ngd\`{i}.''

``Ah, that sounds boring.''

``Very much so.'' She replied easily. ``Now, you must go, if you hope to leave unseen.''

``Alright, alright.'' Haruto replied as he pulled himself out. Dropping his waist back down, upside down in the room. ``Oh, and you should consider increasing the firewalls for the Keeper's Academy. Someone of dubious intent might get in, and it's got a large backdoor into the Keeper's network.''

Pulling himself back up, he left with the soft words of thanks following him.

The trip back to the warehouse was much faster as the farther he got away from Prayer Alley and his best friend the fewer patrols he ran by. Landing on his rooftop access to the warehouse he paused. He could hear the soft pinging from the gun range targets meaning Aeliana was practicing again. His sensitive ears picking up the whinding of the gears that made her range mobile. Given the time between shots, he was sure she was using the new rifle he'built for her.

While he knew she would greet him warmly, or as warmly as Aeliana greeted anyone these days. But for whatever reason he didn'go in. There were no rooftop patrols in the LL. Never had been, and probably never would. The noise from the street was limited as few traveled the warehouse district of LL. Normally, Haruto detested quiet, but now...

\textbf{\sffamily{We'll see her next week.}} QB9 replied softly.

\emph{`Yeah, I know.'} He replied, but still he felt. He wasn't sure what he felt. Lonely maybe.

\textbf{\sffamily{What am I? Space junk?}} QB9 growled harshly, but Haruto could feel his concern.

\emph{`Space junk would be more useful.'} Haruto replied automatically. The low snorted he got in return lifted his spirits a little. \emph{`Some times I forget that most people have families.'} Haruto added after a moment. \emph{`Aeliana, everyone at KANP.'}

\textbf{\sffamily{And your Princess.}} QB9 added. \textbf{\sffamily{Although, I hardly think hers count.}}

\emph{`It's still a family. A whole clan that celebrates her birthday.'}

\textbf{\sffamily{You've got a festival for your day of birth as well.}} QB9 reminded him.

\emph{`It's not the same.'} Haruto replied as he lay down on his back. A twisted mess of wires greeted him. Now that he thought about it, his friends rooftop window opened up in the direction of the observatory. He tried to image what that would be like when the old man opened it up. His vision went dark in response.

\textbf{\sffamily{Give me a second, kid.}} QB9 replied and a handful of seconds later, Haruto was looking out at the Satrian star space. \textbf{\sffamily{That's}} \textbf{\sffamily{where we are now.}} 

For a long while, they both looked up at the stars. New coordinates appeared in his visual as a Keeper patrol walked by interrupting his view. Sighing heavily as his vision returned to normal, Haruto rested his hands behind his head. \emph{`Her birthday, huh.'} Lays on his back. \emph{`Who'd have thought that.'}

\textbf{\sffamily{Obvious now that we know the date.}} QB9 responded already following Haruto's line of thought. The increase in patrols this time of year made so much sense now. \textbf{\sffamily{I still find it hard to believe that the Sh\`{a}ngd\`{i} would}} \textbf{\sffamily{come here.}}

\emph{`She didn't say that.'} Haruto responded. \emph{`Only that important people paid noticed. That could mean a number of things.'}

\textbf{\sffamily{Kid, given how humble she is. The Sh\`{a}ngd\`{i} himself could very well show up to this thing.}} QB9 countered.

Haruto shook his head. \emph{`The old man would make a big deal about it. There'd be Guardian flights and stuff, but,'} Haruto guested in the direction of Solas Plaza, \emph{`the skies are clear.'}

QB9 huffed in response. \textbf{\sffamily{Still it's impressive.}}

``Yup.'' Haruto spoke aloud as he pushed himself off his back and on his feet in one smooth motion. \emph{`And that calls for something extra special for the new year.'} He continued in his head as he unlocked the rooftop hack to let himself in.

\textbf{\sffamily{Brat, what you need to do is focus on your studies. Lay low for a change.}}

\emph{`And who says I can't do both?'} Haruto replied as he made his way down the stairs to what was becoming his console. 

\textbf{\sffamily{Both? With your attention span!}} QB9 growled in disbelief.

Aeliana didn't even pause at his arrive. A new set of targets flying through the danger zone of her range having her full attention.

Sitting down at the console, he fired the wonder of a machine up. \emph{`I'd have thought you'd be begging to give your hacking skills a real test.'}

There was no response as Haruto connected his BISM to the system. This console, and this one alone was the only one not connected to Kanopos directly. The offline computer didn't really need it as Haruto never did anything that required a Kanopos connection, a.k.a. hacking, at the warehouse. Well, expect for hacking the warehouse its, but that was a different matter all together.

Throwing up his schematics for his biodegradable polymers that had worked so well nearly a year ago to this day in the infamous ghost rider prank, Haruto let the silence from QB to stretch a little longer. \emph{`But, if you don't wan...'}

\textbf{\sffamily{Now, I didn't say that, brat.}} QB9 interrupted causing Haruto to smile. \textbf{\sffamily{If it's me doing the real work, then of course we can manage both.}} QB9 replied smugly. \textbf{\sffamily{That is, if you're serious, kid.}}

Running his latest algorithm on the polymer, Haruto sat back and let the machine work its magic. \emph{`When it comes to pranking, I'm always serious, QB.'} The sound of targets moving stopped in the background. \emph{`Besides, I owe the Keepers something really special this year. After how long they kept me locked up last year, yeah. I owe them something real personal.'} Haruto thought as his smile grew.

``Do I even want to know?'' Aeliana's voice sounded from behind him. 

Haruto tilted his head up at her, ``You're going to want plausible denibility on this one.'' He replied.

She shrugged as her Tom-Tom bot.

\textbf{\sffamily{Charlie. He's got a name, brat.}}

As \emph{Charlie}, brought her a pouched water. \emph{`You're too sensitive.'} Haruto thought.

``Thanks, Charlie.'' Aeliana said softly before turning her attention his screen. Given her intelligence, Haruto was sure she was getting an idea of what it was. ``You're back early.'' She continued eyes never leaving the screen.

``Plans changed.'' Haruto replied. He'd not told her what he was planning on doing and didn't want to bring it up now.

Aeliana raised an eyebrow in question, but didn't ask anything further. ``Look, my parents want me to invite you to our winter solstice party. The Guild throws one every year and their generally entertaining. Plus plenty of free food.''

``Ah?'' Haruto blinked in surprise. QB9 was oddly quiet.

``If you've got other plans with your AI, you don't have to come.'' Aeliana finished.

\textbf{\sffamily{Brat, I want to go.}} QB9 growled out. \textbf{\sffamily{I've been tracking a Guild member}} \textbf{\sffamily{who's can get us some parts, so I can finally have my own body.}}

\emph{`We don't have the money, QB, which is why I haven't bothered finding this guy.'} Haruto replied in thought. Aeliana waited as he talked it over.

\textbf{\sffamily{I. Want. To. Go!}} QB9 replied. \textbf{\sffamily{I want a day for me. You owe me.}}

\emph{`I owe you?'} Haruto was about to begin a rant.

\textbf{\sffamily{Yes! You can fool yourself just find, but I don't want to go through another depressing}} \textbf{\sffamily{solstice.}}

Haruto took a sharp breath in surprise. \emph{`It wasn't that bad.'} He thought hesitantly. QB9 didn't have to reply for Haruto feel his answer.

``I'm going to put you down as a yes.'' Aeliana replied as he moved away. ``And please try not to get into trouble during the party.'' She continued without turning around.

``What? I would never.'' Haruto began, but she was quickly moving out of earshot. \emph{`Well, I guess you win this one.'}

QB9 pleasure was unmistakable as his script finished. Haruto zoomed in at the new modification to the polymer. The statistics for strength, elasticity, degradation, and most importantly conductivity summarized neatly on his screen. A wide smile spread across his face as Haruto let QB9's pleasure become his own.

This was going to work out just fine.

\chapter{}
Haruto fidgeted in his seat as he struggled to pay attention to Sergeant Sang-eo. While the Sergeant had started to add little flares to his voice and bits of dramatics - in Haruto's opinion improving the quality of his teaching ten times, today was just the day that even fireworks would have kept his attention.

\textbf{\sffamily{Will you sit still!}} QB9 growled. Momentarily causing his fidgeting leg to settle down. But the pause in his activities lasted only a handful of seconds before his fidgeting returned with a vengeance. If not for the empty seats surround him, Haruto was sure he'd be getting dirty looks. As it was, only QB9's disapproval reverberated through him. \textbf{\sffamily{Why do I even bother?}} QB9 continued in a low mutter.

\emph{`Sorry QB, I just can't help it.'} Haruto replied as he forced his leg to settle if only for a handful of seconds more. \emph{`It's just, today's the day.'}

\textbf{\sffamily{Yes, yes. But if you get kicked out of class now, we'll have the whole Keeper force tracking}} \textbf{\sffamily{our movements.}} QB9 replied. \textbf{\sffamily{And don't think Sang-eo won't do it, if you start}} \textbf{\sffamily{disrupting class.}} He continued. \textbf{\sffamily{Even he knows, when you're a lost cause.}}

With a deep breath, Haruto attempted once more to refocus on Sergeant Sang-eo's lesson. His mouth moved as if in slow motion, but nothing appeared to be coming out. At least nothing coherent.

\textbf{\sffamily{Oh, just give it up.}} QB9 replied. \textbf{\sffamily{I'm taking notes. We'll go over the lecture}} \textbf{\sffamily{later.}}

With a deeper sigh of relief, Haruto leaned back a small smile forming on his lips as he let his mind wonder properly his last and final, super epic, prank. \emph{`Well at least on Kanopos.'}

\textbf{\sffamily{Assuming you get into OCI.}}

\emph{`Hey, I've got a 100 on my last exam.'}

\textbf{\sffamily{Thanks to me and getting you into that cram school.}}

\emph{`Which I'm still dodging calls from.'} Haruto thought darkly. Trust QB9 to get them in a course where the teachers take note of every student. Fail to badly, and they try to get him placed into an alternative program. To well, and they start asking him questions about the future. Even smack dab in the middle had the eyes of High Commander Lee on him.

\textbf{\sffamily{I told you not to get the exact average of the class. It was bound to cause concern.}}

\emph{`Blab, blab, blab, blab.'} Haruto mentally mocked the AIM. \emph{`You're the one who got me into that mess. Don't think I won't forget it!'}

\textbf{\sffamily{And now you're scoring 100's.}} QB9 growled back in answer. \textbf{\sffamily{You should}} \textbf{\sffamily{be thanking me.}}

Haruto ignored him. Instead he let his mind focus solely on successfully executing his most complex and expansive prank to date. His leg bounced up and down excitedly, knocking into his desk. Sergeant Sang-eo gave him a warning look, which Haruto returned sheepishly. \emph{`Okay, so maybe my fidgeting is getting a little out of hand.'}

\textbf{\sffamily{A little?}}

Taking a slow deep breath, like Aeliana's mediation exercise instructed supposedly to improve his attention span and information retention. \emph{`Like I need memory retention. I remember everything.'} Haruto thought as he lost his meditative calm. \emph{`How much longer, QB?'} Haruto asked anxiously.

\textbf{\sffamily{I'm not your clock.'}} He growled back.

Looking down at his tablet, \textbf{\textsc{1150}}. Suppressing a groan, Haruto slumped into his seat. How was he ever going to survive the wait!?

\textbf{\sffamily{We're not going to die in ten minutes, kid.}} QB responded.

\emph{`Says you.'} Haruto countered harshly. The wait was more than three times as long as it took his MINOS to cook. \emph{Three times!} Eyeing the door, he seriously contemplated just getting himself kicked out of class. Sure he'd have to dodge patrols, but he'd been doing that for most of his life.

\textbf{\sffamily{And now I've got to baby you.}} QB growled back in anger. \textbf{\sffamily{Just sit}} \textbf{\sffamily{tight and talk to me.}} He continued. \textbf{\sffamily{We'll go over the plan, or something. Just}} \textbf{\sffamily{don't get us kicked out.}} There was a brief pause as Haruto felt QB9's growing disapproval. \textbf{\sffamily{I've done too much work, for you to wreck it all because}} \textbf{\sffamily{you can't wait ten minutes.}}

\emph{`Oh, don't be so dramatic, QB.'} Haruto complained, but he settled down in his seat. The AIM had a point, a small one, but a point none-the-less. They'd finished eleven Keeper Towers. Eleven over the last 17 weeks. And today was supposed to be the last, and hardest, and probably the most important target, Eastern Tower.

At that point, their makeshift blueprints and patrol routes for the Eastern Tower appeared in his vision. Blueprints and routes he'd reviewed countless times for the past week in preparation for today. And Eastern Tower, of all the five Solas Towers, had the second highest security. The highest, of course, reserved for Tower One.

\textbf{\sffamily{Which we are NOT touching.}} QB9 commented.

\emph{`Yeah, yeah.'} Haruto thought as he waved away QB9's concerns. \emph{`You act as if that was YOUR idea to begin with.'} He added offhandedly. It had taken a while to convince QB that they weren't good enough to infiltrate Tower One. Well at least without being caught on the way out, which was bound to raise red flags that they just didn't need.

And if not for the stumbles they'd had with the Port Tower, which had the weakest security of all thirteen Keeper Towers, he was sure he'd still be going back and forth with the AIM on why it was a bad idea only 8 weeks out from the Jade Festival.

\textbf{\sffamily{But the Market Tower and the six Sector Towers were like a walk in that silly park you like}} \textbf{\sffamily{to go to.}} QB9 commented.

\emph{`Yeah, and the Northern, Southern, and Western Towers took three weeks a piece.'} Haruto commended as he brought up the schematics for the other three Solas centered Towers. \emph{`And that's with decent intel.'} Haruto shook his head at the thought of going after Tower One, \emph{`No, if we want this to work, will need the full 8 weeks for the Keepers to get comfortable again.'}

\textbf{\sffamily{I never said we should try it now, kid.}} QB9 grumbled back.

\emph{`Yeah, but I can tell you're still thinking about it. So stop.'} Haruto replied. The amount of work they'd put end, would go down the compactor even more surly than a little added attention if he'd gotten himself kicked out of class early. But if everything went work, this past 17 weeks was going to be worth it. \emph{`Oh so worth it.'}

\textbf{\sffamily{What ever you say kid.}} QB9 commented disbelievingly.

\emph{`Oh, but QB. This year the Jade Festival is going to be a night to remember.'} He replied a grin spreading across his features just thinking about it.

\textbf{\sffamily{As if you'd even be allowed to attend.}} QB added.

Haruto's eyes traced the Eastern Tower's bare schematics. Just thinking about this prank, and he knew he didn't want to miss it. No, this year, he might just have to make an exception.

\textbf{\sffamily{Don't do anything stupid, kid.}} QB9 warned.

\emph{`I wouldn't dream of it, QB.'} Haruto replied easily, but QB9 was still uneasy. \emph{`Don't worry, it's not stupid if I don't get caught.'} He added as he leaned back in his seat finding himself lost in the Eastern Tower patrol routes.

\emph{Buzz. Buzz.}

Looking down at his BISM and the time read, \textbf{\textsc{1200}}.

``Lunchtime!'' Haruto shouted as he short out of his seat. 

\textbf{\sffamily{Subtle much.}} QB9 commented dryly.

Haruto looked around the room to find everyone staring at him. Aeliana giving him a particular evil look because of his disruption of class. He smiled sheepishly as he started to sit back down. Sergeant Sang-eo frowning at him as he addressed Haruto, ``Cadet H\={e}id\`{o}ng, while I know your excited about lunch, I must remind you that the clock doesn't dismiss you. I do.''

Seeing his chance to get out of here now, Haruto reversed his movement to hop onto his desk dramatically eliciting QB9's disapproval in the process. \emph{`Oh, just watch and learn.'} He thought as he took a large lunch to argue with the Sergeant. 

``It's lunchtime,'' he argued, pointing an accusing finger at his favorite Sergeant. ``You can't starve us by keeping us chained in here.'' Shifting in his spot, Haruto gazed out at his fellow classmates before continuing with a rallying cry, ``Come on, who's with me!''

As if by some amazing stroke of luck, Kenta's stomach chose that exact moment to growl loudly, the sound filling the classroom causing the entire room to break out into light laughter as they chattered amongst each other.

``Alright! Alright.'' Sergeant Sang-eo tried to calm the class down with only mild success. ``Go eat,'' he yielded with an exasperated sigh giving up any further attempts to gain control of the situation.

Hopping off his desk, Haruto headed for the door ever aware of his rather strict timetable. Only moments before had he traced his route to Eastern Tower. As if on cue, the route appeared in his field of vision.

\textbf{\sffamily{I suppose it worked.}} QB9 commented with a small amount of approval leaking through.

``Yo, Haruto. Want to grab lunch?'' Seo-Jun called after him.

Haruto waved him off. ``Another time man,'' he called over his shoulder before high tailing it out of there. 

The seconds ticked down in his field of vision as Haruto scaled the nearby building. For all of the Tower outside of Solas, Haruto had used his special terminal transport. Unfortunately for him, the Keepers kept a close eye on terminal traffic within Solas. Even the hint of movement within one, would send them in to high alert. As such, he was going to have to use less than conventional methods.

\textbf{\sffamily{They've worked so far.}} QB9 commented. \textbf{\sffamily{I don't see why you're worried.}}

Climbing up to the catwalk, the heat blasted at him as he responded. \emph{`It just takes one time, getting caught for this to all fall apart.'}

QB9 grumbled in discontented but didn't argue further. The next apart was the trick bit. Running swiftly along the catwalk, his BISM counting down before his eyes.

\textbf{\textsc{9..8..7..}}

\emph{`This is going to be tight.'} Haruto thought as he arrived at an open air-vent. 

\textbf{\sffamily{Wait a second, kid.}} QB9 warned.

The clinking of Keeper footsteps was growing closer. \emph{`QB...'}

\textbf{\sffamily{Now.}} QB9 called out, just as the air shifted. Pulling himself into the air-vent, he pushed himself down and out of side. The hot metal just this side of burning.

Seconds later and the patrol strolled passed him. \textbf{\sffamily{Don't stop}} \textbf{\sffamily{now, kid. Times running.}}

To emphasize his point, the next minute started ticking down. \textbf{\textsc{60..59..}}

Crawling down the air-vent section, ``Easy for you to say, your not the one crawling on overheated metal.'' Haruto muttered under his breath.

\textbf{\sffamily{No, but I'm the one who's got to hear about it.}} QB9 countered.

Reaching the end of the air-vent, he dropped down landing on another catwalk. Two more of these, and he'd make it to Eastern Tower's sector. With the practiced ease of having done this successfully three times, Haruto made his way silently along catwalks and through air-vents. Dodging increasingly dense patrols. The final air-vent dropped him out in the Eastern Tower's largest trash heap.

Landing in a pile of trash, he smiled. ``Got to love trash day.'' He spoke aloud softly as he climbed back to the top. \emph{`Which section, which section.'} He thought to himself as he moved around the walls tapping it quietly periodically.

\textbf{\sffamily{Kid, you're pushing the time.}} QB9 warned as if the timer constantly counting down wasn't warning enough.

\textbf{\textsc{15..14..13..}}

A hallow thump sounded, ``There you are.'' He whispered as he pried the hidden door open. Entering the trash shoot. He waited the final seconds of his timer.

\textbf{\textsc{3..2..1..}}

Behind him the trash heap groaned as the composter got to work. The loud noise the perfect cover for climbing up this particular shoot.

\textbf{\sffamily{Got to love trash day, indeed.}} QB9 echoed Haruto's earlier statement as Haruto worked his way up.

The shoot opened up a meter up from the trash heap. Splitting at a 90 degree angle just as the original shoot changed to an impossible climb at 180 degrees. But Haruto was expecting it, planning for it. Taking the new metal vent. Haruto gently pushed open the air-vent.

\textbf{\sffamily{Wait a second.}} QB9 warned just as Haruto heard the soft footsteps of a Keeper.

Pulling the grate back in place he waited.

``So did you hear? The Honorable K\={o}taishi's supposed to be visiting the Keeper Academy tomorrow.''

``Yeah, I heard some of our top Cadets are going to get a chance to face her.''

``Really?''

``Yup.''

``Well, do you think I could get one of the rookie units to cover for me? Ive never seen the Honorable K\={o}taishi in action.''

``I don't know man. It's just a couple of simulations. I don't think the lieutenant going to approve something like that. You know how she gets about duty and honor.''

There was a pause, where Haruto assumed the other man was nodding in agreement. 

``You know what I should have done.'' The other man paused as well. ``Put in that transfer to Market Tower or even Port Tower. Now their lieutenant's a pushover.''

``Yeah, I hear you, but I just can't do Port. My family's been at Eastern Tower for centries...'' 

There was another pause, but luckily they voices were getting farther away.

\emph{`Gossip,'} Haruto sighed as he pushed the grate off, stepping into Eastern Tower proper. \emph{`Man, I hate the stuff.'}

\textbf{\sffamily{I don't see why.}} QB9 countered. \textbf{\sffamily{Now you know where your girlfriend's going}} \textbf{\sffamily{to be tomorrow.}}

Pushing the grate back in place, Haruto paused to reply to the AIM, \emph{`First off, she not my girlfriend. I don't know how many times I've got to tell you that.'} Pushing off the floor, Haruto turned to the nearby terminal. \emph{`And secondly, you know I have class. Sergeant Sang-eo will chase me half across LL before he lets me skip a full day.'}

Hacking into the system was simply enough. He was, after all, in the equivalent of a laundry facility. And for whatever reason, the Keepers didn't seem to keep tight security on their system. Despite the fact that every piece of high powered and low powered equip went through these facilities.

\emph{`But most importantly,'} Haruto started as he let QB take over for his part of the prank. \emph{`There's no way, I could get in there without someone noticing.'} He continued. ``Tried it once, didn't end well.'' He muttered under his breath.

\textbf{\sffamily{If you're done whining, I'm finished.}}

\emph{`You sure? Because this is the most important one. If you miss an armor it will ruin the prank.'} 

There was a low snorted. \textbf{\sffamily{I am a master at my craft.}}

Haruto snorted, before heading for the hallway. Now, it was his time to shine. Tip-toeing through the hallway, he made his way up a flight of stairs between patrols. The laundry room being the only stairway without several camera angles, it was easy enough for him to move around them. 

\textbf{\sffamily{This should be it, kid.}} 

Haruto nodded as he opened the terminal with a gentle pull of the handle. Haruto sighed at the sight of an elevator control panel. Seconds later and he had the thing wired to take him to the third floor. Opening the nearby vent, Haruto climbed through and into the elevator shaft just as the elevator speed toward him. Bending his knees, he jumped down with a soft thump. Pausing, he was pleased when no shouting went off.

This next bit was the easy part. Climbing out of the elevator shaft he landed next to a camera. The angle just missing him in its sweep. By passing the terminal, Haruto opened the service panel next to it. Pulling out his latest little biodegradable chip. He placed it right behind the terminal motherboard, right over the CPU if his schematics were correct. Given that he'd spent the better part of ten minutes in the Port Tower making sure he had the spot right, he wasn't worried now.

Sitting back on his heels he smiled at his work.

\textbf{\sffamily{Honestly, if they're going to link their central power like this, they deserve to have the}} \textbf{\sffamily{weakness in their system exploited.}} QB9 commented his own pleasure mixing with Haruto's.

\emph{`Well maybe they'll thanks us later for pointing out the weakness.'} Haruto replied.

\textbf{\sffamily{Sure kid, and the heavens will open up and swallow you.}} QB9 replied dryly.

Turning to go, Haruto hopped back into the elevator shaft and waited for a ride up. \emph{`Oh, QB. I didn't know you were religious.'} Haruto teased back.

\textbf{\sffamily{Smart mouth kid...}} QB grumbled just as their ride arrived. Waiting for the last second, Haruto stepped out to avoid making a sound. Dangerous, but the only way to get out of this place unseen.

Climbing out onto the rooftop of Eastern Tower, Haruto took a second to admire the view. \emph{`How long do you think it will take us to set up the fireworks?'}

\textbf{\sffamily{Not too long now that I have all, well almost all of the Keeper patrol data.}} QB9 commented. \textbf{\sffamily{They really should consider better security protocols.}}

Haruto snorted as he picked himself up. \emph{`Really? Somehow I don't think they thought they'd get hit from the inside.'}

\textbf{\textsc{5..4..3..}} Taking off at a run, Haruto jumped off and landed softly on the finished composted trash heap.

``Got to love trash day, QB.'' Haruto spoke aloud.

\textbf{\sffamily{Yeah, and now you just need to get back to class before lunch ends.}} QB9 growled in response, but Haruto could feel his pleasure.

Today was a great day.

\chapter{}

Haruto dodges into an alley way. He pulls his messenger hat down more over his ears as Keeper patrol pass by.

He was in a part of LL that under normal circumstances he'd never be caught in. Dangerous.

Some banter with QB.

Small blackout should happen.

QB and Haruto, but red light was already ready for it. some glow lights go on and the music doesn't stop. Haruto in the red light sector.

Note about life-support working well.

A little worried about the blackouts. He'd never planned or meant for anything like this top happen. QB blames the Keepers for shotty circurity... shows Haruto a skeptic he'd been keeping to himself.

Haruto pause in outrage. Asks if QB knew something like this could happen. He's silent for a moment, but Haruto knows he must reply. It was always a possibility, low but possible. More damage to the ship, not their doing. (allude to something nefirous going on)

They keep going, pretending to be a runner, because that was the only safe, relatively safe, position to be down here. He sure couldn't be himself. His face didn't get too many likes.

...QB still thinks they did them a favor... shouldn't have had their towers that intridend with the ships power supply

...Still Haruto a little worried.

...They can't prove anything... -QB

Yeah, but when things get this bad, someone has to take the fall for it. Old man wouldn't be able to help them here.

So we laylow, no problem. -QB

Easy for you to say. They'd been bouncing from place to place, had to keep moving. The Keepers were closing on him by shear numbers. He was getting a laugh at their body armor, no one had bothered to change out of it as if a couple of extra minutes would be the difference between capturing him and not.

The red was also easy to spot. QB already had a recogniztion program running on top of their Keeper tracker protocol. 

But numbers would get him eventually.

At this point he sees someone who looks like Iruka entering a run down building...

Finds it odd, and goes to investigate. He didn't have anything better to do with his time.

...follows him... but gets picked up by the back of his messenger coveralls by what looks like a hooker, very strong hooker. 

The ladies of the night had different colored SKIMs... 

meets the crazy lady... (who doesn't turn him in)

...Anko, Iruka, and Haruto at Anko's apartment...

Iruka not sure about harborring a fugitive, but Anko wants too, so they do...

...insert some banter before another blackout happens.

...another blackout... Anko has backup generate that kicks in

\chapter{}
Haruto rushed from his apartment like his life depended on it. Running across rooftops like a ghost on the wind.

\textbf{\sffamily{I told you not to watch that last episode.}} QB9 gave a smug response as Haruto slipped off the rooftops to avoid a Keeper patrol. After the Jade Festival Incident, they seemed extra alert to his presence (i.e. we just have some questions for you Cadet H\={e}id\`{o}ng). 

\emph{`Well you could have woke me up,'} he responded as he slipped through the crowd and into another back alley. A couple of leaping jumps and he was back onto the rooftops at break neck speed. \emph{`This is both of our livelihoods!'} He continued.

\textbf{\sffamily{Tried. But someone has gotten really good at ignoring me.}} QB9 complained. \textbf{\sffamily{Next left.}} He added, causing Haruto to use the satellite pole to swing himself in the correct direction. \textbf{\sffamily{And I told you last night this}} \textbf{\sffamily{would happen. Now you're just going to need to use the H\={e}id\`{o}ng 'charm to get us into the exam.}}

Hopping down, Haruto's stomach growled in hunger. \textbf{\sffamily{No, we don't}} \textbf{\sffamily{have time to take Main, I don't care how hungry you think we are.}}

\emph{`It'll only add one, two minutes tops. I'm already late, because of someone.'} Haruto thought.

\textbf{\sffamily{I'm not your personal alarm clock, kid.}} QB9 replied. \textbf{\sffamily{This building's vacate.}} \textbf{\sffamily{Use the right window.}}

Taking QB's advice, he swung himself feet first into the closest building. \emph{`Renovations?'} He thought as he passed plastic covered furniture. \emph{`Good for them.'}

\textbf{\sffamily{Good for us, this cuts half a minute from our ETA.}} QB9 corrected. \textbf{\sffamily{You should}} \textbf{\sffamily{be glad, you have me at all. Really, I don't see how you functioned without me.}} QB continued. Ever since he'd started talking to Aeliana and Charlie, he seemed to be getting a inflated perception of himself. \textbf{\sffamily{Inflated?}} He questioned a hint of anger in his thoughts. \textbf{\sffamily{Who catalogs you notes? Changes your SKIM waste? Suppresses your hunger so you can}} \textbf{\sffamily{concentrate?}}

Haruto used the stairs and jumped out the window all indication QB could give him while he ranted.

\textbf{\sffamily{This is hardly a RANT.}} QB9 responded as Haruto rolled to keep his forward momentum.

``If,'' breath, ``I'' puff, ``wasn't running.'' Haruto spoke aloud as he jumped to the next rooftop.

\textbf{\sffamily{You'd think all of your thoughts slowly.}} QB9 countered. \textbf{\sffamily{No keep going.}} He continued as Haruto prepared to take the left.

\emph{`All run right off...'} He closed his eyes as the rooftop ended, but luckily he kept going. Peeking out, \emph{`More construction?'}

\textbf{\sffamily{Technically, you can thank yourself for that one.}} QB9 responded.

``Oh,'' he spoke aloud. That would explain the increased construction happening all around Solas. While, he didn't really blame himself for the blackouts. Who connected the Keeper Towers to the main power grid like that anyway? It seemed he was, even a little bit responsible for the current technical difficulties of KTS Kanopos.

\textbf{\sffamily{Come on kid, focus.}} QB9 replied. Haruto was sure he was counting the clock hiding his own worry behind layers of sarcasm. Haruto was already preparing a long speak that might appeal to Sergeant Sang-eo's good-nature, but it wasn't likely to work on Sergeant Y\'{u}. 

\emph{`Five minute window. How close are we?'} He asked, but received no answer, which was answer enough. He might be able to get a deduction, but if they took it out of his written, well he might as well not show up.

\textbf{\sffamily{Just focus, kid.}} QB9 spoke up. \textbf{\sffamily{We'll either get there or we won't.}} He continued. \textbf{\sffamily{OCI won't define our future.}}

\emph{`That's not what you said last week, or last night.'} Haruto countered as he jumped down from the rooftop and skidded through the KANP arches. The hallway was unusually quiet, but he couldn't think of why that might be. Instead he sped through the empty halls and sprinted up the stairs. What he wouldn't have given for roof access to this place.

Bursting through his classroom doors, he huffed, half bent over to catch his breath. \textbf{\sffamily{Good timing, kid. 0905.32. Even Y\'{u} will have to let}} \textbf{\sffamily{us take the written.}}

Haruto smiled between breaths before straightening out, ``Cadet H\={e}id\`{o}ng, reporting.'' He answered in the KANP salute.

``Good morning, Haruto.'' Sergeant Sang-eo greeted him from his desk a large smile, laced with mild confusion on his face. ``Anko will never believe you showed up early for the exam today.''

\textbf{\sffamily{Early?}} QB9 growled in anger at the same time Haruto answered aloud. ``What do you mean \emph{early}?''

\textbf{\sffamily{I'm going to kill that man, just as soon as I get my own body.}} QB9 continued in a low growl.

``Didn't you get the memo?'' Sergeant Sang-eo asked. ``The exam starts at 1000.'' He continued as he flipped through his tablet screen. ``Yes, Sergeant Y\'{u} messaged the class with the time yesterday.'' Looking up he continued, ``Haruto, I know you don't always get along with the man, but you have to read his messages. I don't know how many times I have to tell you that.''

``Yeah, yeah.'' Haruto waved the concern away. QB9 already pulling up the message received marking the exam at 0900. \emph{`There's nothing we can do, QB.'} Haruto thought to his AIM, trying to calm him down. \emph{`Y\'{u} can just claim I doctored it to get brownie points or something, just let it go.'} Haruto had worked with other Sergeants who'd done something similar when he'd gone to the Dean. Nothing he said would be taken seriously and it would only end up in him being punished not the other way around.

\textbf{\sffamily{Sang-eo is different.}} QB9 complained. \textbf{\sffamily{He could...}}

But Haruto cut him off, \emph{`And what do you expect him to do, now?'} Haruto waited a beat, but QB9 was at a loss. \emph{`Like I said. Let. It. Go.'}

``Sorry, Sergeant Sang-eo.'' Haruto replied instead. ``I'll do better next time.''

The Sergeant's eyes shined with pride before he looked around, ``You know, when it's just the two of us, you can call me Ken. Besides, soon you won't be my Cadet anymore, but a Cadet going to OCI.'' He replied with pride filling his voice.

``Yeah, just got to Ace this test, right.'' He responded. ``No problem.'' He muttered under his breath.

``I'm sure you'll do fine.'' Ken replied. ``Why don't you pull up a chair, while you review your notes. You can ask me any question.'' He continued as he moved his things over to make room for Haruto at his desk.

``Thanks.'' Haruto replied. QB9 booted his borrowed XP3 tablet, and soon enough Haruto was buried in simulated memories. Unfortunately, he didn't get very far, a tantalizing smell breaking him out of his lecture notes every couple of minutes.

\textbf{\sffamily{More like seconds.}} QB9 muttered. \textbf{\sffamily{Sang-eo's got some kind of food, and I can}} \textbf{\sffamily{only do so much.}}

At that point, QB seemed to give up on his hunger suppression causing his stomach to roar in protest. ``Hehehe,'' he laughed while rubbing the back of his head in practiced innocent. ``Sergeant Ken, you wouldn't happen to have anything to eat would you? I kinda forgot to eat breakfast.'' He asked sweetly. 
``Well, I was saving this for Anko, but since I'm sure your stomach can be heard from across the building, I think I can give it to you,'' he replied, digging into his desk to grab the requested items.

``Wow now. I don't want to take anything meant for Anko.'' An imagine of her blood thirsty smile came to mind, aided by QB9's own imagination. ``I'm good.''

``Don't be silly, Haruto. I think people can hear your stomach for miles.'' He replied as he pushed over the food. ``I'll buy her some more later.'' Still Haruto hesitated. ``Tell you what, why don't you make her dinner tomorrow to celebrate you \emph{Acing} this exam in exchange.''

Haruto nodded at the agreement, putting out his hand in a gesture he'd always wanted to try. The Sergeant blinked in confusion before taking it weakly. ``It's a deal.'' He replied voice low as he mimicked Galaxy Man's alter ego.

\textbf{\sffamily{I demand you never do that again!}} QB9 complained.

\emph{`I demand you stop being so lame, but here we are.'} Haruto replied as he dug into the food.

Studying became significantly easier after that with Sergeant Ken asking him questioned between sections. He even managed to not sound condescending like some AIM Haruto knew. Said AIM decided that now was a great time to conserve energy and remained quiet as he studied. So much so, that time passed in a blur, soon enough the classroom door was sliding open signaling the arrival of the first student. 

Haruto didn't bother to look up, sure that the early bird was unlike going to want to talk to him. His friends included all of the laze ones, except for Aeliana, but she rarely associated with him during class so she didn't count. Seo-Jun would wait until the last minute like Haruto normally did. Kur-ram would probably revolt at the idea of waking up any earlier than necessary, and Kenta went where Kur-ram went, so they'd get in five minutes til. And as he wasn't about to talk with anyone else this early in the morning, he could relax as he continued to study.

Of course that sentiment lasted all of the two seconds it took for Sergeant Ken to glance up at the newcomer. Instantly, the startled man jumped from his seat, hastily making his way to the door, which was a completely unprecedented move.

\textbf{\sffamily{Maybe it's the Dean again?}} QB9 questioned as Haruto followed the Sergeant's movement to the door.

``Princess?'' Haruto replied in shock at the cold stare of his best friend, who for the first time had entered KANP.

\textbf{\sffamily{Of course. Even she must take the exam.}} QB9 responded. \textbf{\sffamily{But how will they}} \textbf{\sffamily{grade her written?}} He muttered softly to himself.

But Haruto could care less, because decked out in what he assumed was some kind of ceremonial coveralls, was his best friend. And he hadn't seen her in ages.

\textbf{\sffamily{We talked to her just last week.}} QB9 commented.

\emph{`But we didn't, SEE her.'} Haruto countered.

``A blessed morning to you Honorable K\={o}taishi.'' Sergeant Ken greeted with a low bow. ``I am Sergeant Sang-eo Ken. Welcome to class 6A. We are all pleased to have you joining us today,'' he continued. 

``The pleasure is mine, Sergeant Sang-eo.'' His friend answered.

``Please have a seat in 2C.'' The Sergeant continued.

\emph{`2C, 2C. Why does that sound familiar.'} Haruto thought as Sergeant Ken continued.

``Sergeant Y\'{u} handles the roster and attendance. Once he arrives, he will be able to tell you the order the simulation and skill demonstration showcase will be given.'' He pointed in the general direction of said seat, ``Please, don't hesitate to call upon me with anything. I will be happy to assist in any way I can,'' Sergeant Ken finished with another short bow.

\emph{`2C, 2C,'} Haruto continued to ponder on the seat. \emph{`Why so familiar?'}

\textbf{\sffamily{Oh, I can't take this anymore.}} QB9 interrupted. \textbf{\sffamily{It's the empty seat next to}} \textbf{\sffamily{yours. Just go over there now, so we can get this pointless greeting and complete derail of your}} \textbf{\sffamily{review over with.}} 

``Yosh!'' Haruto replied as he jumped up out of his seat next to Sergeant Ken's desk.

\textbf{\sffamily{Way to show constrain.}} QB9 replied as the pair turned to look at him.

``I can show you too your seat, Princess.'' Haruto nearly skipped over to them. Sergeant Ken gave his BISM a quick look through in horror as if just realizing the seating arrangement.

``Actually, Honorable K\={o}taishi. You can pick any seat you'd like.'' The Sergeant interrupted. ``We can move students around once everything is settled.''

``That will not be necessary.'' His best friend replied as she turned to him. Haruto happy to show her to their seats.

``If anyone, anyone at all bothers you, Honorable K\={o}taishi, please don't hesitate to inform me.'' Sergeant Ken replied eyes pleading with Haruto not to go overboard. Haruto rolled his eyes at him. 

``We'll be fine, Sergeant.'' Haruto answered for his friend as they found their seats. ``Man, this is so cool. Like fate or something.'' His friend's eyes shone with amusement.

``Is it?''

``Oh yeah. I mean, like the God of Luck must really like me today.'' He replied with a wide smile. ``Because I sit right here.'' He emphasized the \emph{here} by sitting down.

-Haruto has a short conversation with Hinata, which goes into the latest episode he'd just watched. He downloads the contents into her BISM without asking (it's what they do).

-Hinata makes a comment about how pranking seems to have gone down in the last few months

-They have a small back and forth about why that might be with Haruto denying complete involvement

-Haruto takes a bold step and asks if she wants to join his and Aeliana's study group, because they work on relic ZenKZ like the Moon Princess (he has a well thought out argument)

-There conversation is interrupted by Y\'{u}

Before his friend could answer to his bold question, Sergeant Y\'{u} appeared in front of them partially out of breath.

``Honorable K\={o}taishi please forgive my tardiness,'' Sergeant Y\'{u} apologized with a half bow. ``Had I known that you would arrive so promptly, I would have striven to get here sooner. I am Sergeant Y\'{u}, the assistant instructor for class 6A.''

``No apology is necessary Sergeant Y\'{u},'' his friend replied with a tilt to her head as her entire focus shifted to the nervous man in front of them. Haruto had never seen Sergeant Y\'{u} act like this. He was always so confident and self-assured even when brown-nosing. Now, well now, he looked like he was about to be punished for failing some social norm Haruto know nothing about.

\textbf{\sffamily{It seems you're Princess pulls a great deal of weight.}} QB9 replied in a distracted voice.

\emph{`I guess.'} Haruto thought as he looked between the two.

``No I insist,'' Sergeant Y\'{u} protested as he finally rose from his bent position. ``You see my tardiness is not my only failure this morning,'' he continued, his eyes firmly on the ground. ``Please forgive me, but I may have forgotten to add you to the roster. ``However, I shall spend the next several minutes before class to rectify this failing.'' Clearly ashamed of his blunder, although Haruto couldn't see why as Sergeant Y\'{u} routinely forgot to add \emph{him} to the roster, and he never rectified those situations, making Haruto go last or fail the exercise. 

\emph{`But more importantly, I always have to listen to Akihiko go on and on about my Clan this or my Clan that.'} He thought. \emph{`I'm glad the Princess doesn't have to go through that torture.'}

``Thank you Sergeant Y\'{u} for informing me of the situation; however, I see no harm done,'' His friend answered reasonable, like he knew she would.

``Thanks and praises to the Goddess, Honorable K\={o}taishi. You are as fair and benevolent as the Honorable Yozora,'' Sergeant Y\'{u} added before backing away bowing one more time looking relieved.

``Hey,'' Haruto spoke abruptly, ``how come it's always just the Goddess with the Gento Clan.'' He continued. ``I mean, Aeliana does the same thing, but her families not really from the Empire, ah Jade Empire,'' Haruto self-corrected remembering that there were five big Empires the controlled known space. QB ought to be proud.

\chapter{}
After finishing his simulation, he settles down...

\emph{`Woo, that was fun.'} Haruto thinks.

\textbf{\sffamily{Focus kid, we're not done yet.}} QB9

``Great job, Cadet.'' Sergeant Sang-eo smiles as he looks down at his tablet. ``Why don't you move right into your demonstration?''

\emph{`You ready QB?'} Haruto questions.

\textbf{\sffamily{Ready?}} QB9 confused, not able to follow Haruto's thoughts.

\emph{`I'm not the only one who worked hard to get us to OCI.'} He replied. \emph{`Why don't you take it from here?'} A wide smile crosses his face as he can feel QB9 comperhension.

QB9 runs a hack that takes a hundredth of the time it would have taken Haruto to run.

Y\'{u} protective armor has been hacked

It takes the Sergeants a moment to figure out what just happened, but they do.

Sang-eo smiles, ``Creative as ever, Cadet H\={e}id\`{o}ng. I'm sure Sergeant Y\'{u} would agree that was a unique skill.''

Y\'{u} still can't get his armor under control doing a good job as a background dancer for the latest j-pop star.

\emph{`Tame for you, QB?'}

\textbf{\sffamily{He's not worth the effort.}} QB9 replied smuggly.

``We've got to finish with the rest of the student.'' Sergeant Sang-eo replied. He hesitates as Sergeant Y\'{u} excuses himself. ``Anyway, I graded your exam, 100. If everything goes well, I believe I'm looking at a OCI Cadet.''

``Yatta!''

``Hey, don't celebrate just yet. We have to get all the scores in, then the Sakr\'{a} will draw cut offs.'' Sergeant Sang-eo continued.

``The old man loves me,'' Haruto replied.

Sergeant Sang-eo smiled as Sergeant Y\'{u} returned. ``Go on now.''

\emph{`We should wait here,'} Haruto thought.

\textbf{\sffamily{For what? The results could take hours.}}

\emph{`Yeah, but I want to know as soon as possible.'} Haruto continues. They walk off to Santuary Park. \emph{`Can you believe it? We're going to be OCI Cadets. Oh do you think Aeliana made it too.'}

\textbf{\sffamily{Aeliana's fine. I helped with her demonstration, it's perfect.}} QB9 bragged. Haruto choose not to remind him that they all helped with her demonstration. Small wins all around.

Haruto wasn't sure how long he played in the Park, before a figure moved toward him. On instinct he dodged away from the intruder, not recognizing the figure.

``Hey, Haruto it's me,'' the voice of his Sergeant called out as Sergeant Y\'{u} appeared from the shadows of a cropus of trees. ``I thought you might be here.''

``Uh,'' Haruto looked for an escape route and found about a dozen, so he turned back to the Sergeant, ``What can I help you with?''

``I wanted to be the first to tell you.'' He looked down face transformed in sadness. ``The Sakr\'{a} had to increase the exam curve. Too many Cadets.''

\emph{`Oh no.'} Haruto thought, face transforming.

\textbf{\sffamily{He could be lying.}}

``Sergeant Sang-eo, should be calling you soon. He'll want to ask you over to dinner.'' Sergeant Y\'{u} looked on synpathetically. ``But it won't be to celebrate.''

``I,'' Haruto came up short. ``Why are you telling me this?''

``Because what Sang-eo won't tell you, is that there's another way. A second chance for students like you.'' Sergeant Y\'{u} looked him over, ``Students personally sabetaged by their Sergeants.''
\emph{Buzz. Buzz. Buzz.}

Haruto looked down at his BISM.

\textbf{\sffamily{It's Sang-eo.}} QB9 replied as he patched him in.

``Haruto,'' Sang-eo voice was sad. ``Do you think you can make it for dinner tonight?''

``Ah,'' Haruto paused.

``Don't worry, I'm cooking.'' Sang-eo continued. ``I just thought, we could talk.''

Haruto looked up at Sergeant Y\'{u} who was holding his gaze. ``I'm a little busy tonight, Sergeant.''

``Oh,'' Sang-eo continued. ``Maybe we can do lunch?''

``Yeah, sure. Lunch.'' Haruto replied as QB9 hung up. Turning to Sergeant Y\'{u} he continued. ``What do I have to do?''
