\chapter{}
The KTS Kanopos' artificial light slowly brighten the ship.
This close to the observatory, Haruto could just make out the Nebula star system.
A handful of small droids littered the air, but not nearly as many as a couple of years ago.
Small things like that worried him.
Things were starting to break faster than they could be fixed. \emph{`Still, if the old man wasn't worried, then I shouldn't either.'}

Turning his attention away from the observatory, Haruto let his eyes fall on the nearby park.
Although technically it was the KANP training grounds, it still had real trees and a small pond made of recycled water, which were all things that made up the parks of Kanopos. 
So, Haruto didn't see why the old man differentiated it from any other park.

\emph{`Not as pretty as Sanctuary Park, but really nothing else is.'} He thought as he closed his eyes to imagine the small birds and other extincted species that called Sanctuary Park home. The center piece of Pray Alley and his best friend's Clan sector, there wasn't another park that could compare. All in all, it wasn't all that surprising as the Gento Clan was known for it's patronism of the arts and conservation efforts. The Princess could go on for days about that stuff.

The thought brought a small smile to his face. He quickly wiped it off, and waited, but his new AIM was strangely silent. Haruto relaxed at having his own thoughts to himself for as short as he knew it would be. QB would go out like this periodically as the AIM seemed to still by calibrating itself. It was only during times like these when he needed worry about QB using anything Haruto thought about against him. And it wasn't like he was hiding the Princess or anything like that.

It was just that for the four years they'd been friends, it had always been just them. And Haruto wasn't sure he was ready to share. That and the AIM was proving to be less than useless.
The Princess had warned him that the SB3 series was the closest AIM every developed to having functional artificial intelligence. At the time, Haruto had only cared about the theorical performance. How else was he going to get an AIM that preformed on the same level as the Zh\`{u}r\'{o}ng Clan's AIM or even the Princess' AIM?
But so far all SB3-QB9 wanted to do was get its own body, and the thing didn't talking about getting one in a nice way. Somehow he was going to have to make this work.

Turning his attention to the world outside, he couldn't help but picture himself in Sanctuary Park, minutes away from the Princess. There, life just seemed to be better. Little birds would play within the tallest trees of KTS Kanopos. Blues, blacks, oranges, pinks, every color of the spectrum. He'd seen a vivid purple bird once, fluttering amongst the leaves. Singing sweet songs to each other. The thought taunted Haruto with endless possibilities just out of his reach. 

\emph{`Why am I even here, again?'} He questioned himself. Nothing the Lieutenants taught in class would be on the test. Half the time, Haruto was sure the Lieutenants were purposely skipping material that the students from the Clan's already seemed to know. While he couldn't prove it enough to go to the old man, every time Akihiko so much as turned his head to the window, the Lieutenant in charge would change topics.

And the Gods forbid if he asked a question. That never ended well for him or any of the other non-clan members. \emph{`Well mostly,'} His eyes fell onto the silver haired girl one row in front of him. Tomorrow it would probably be light pink again as the Helian heir seemed to change hair colors faster than her mood swings. Cadet Helian Aeliana was the only exception to the non-clan members no asking questions rule. When he'd told the Princess about it, she'd mentioned something to do with politics after which he'd toned the rest of her explaination out.

Haruto looked down at his tablet. He knew better than to look over at someone else's knowing it was a quick way to detention. Still, out of the corner of his eyes he saw halograms playing. On his was just a dense set of words, all in the ancient tongue.

He tried not to let the bitterness seap through. He should be lucky enough to have this tablet even if it was ancient. The loaner tablet, while several decades old was free and it worked. Sure, all it showed was the dense text, which he \emph{was} supposed to know by now.

All of the ZenKZ created by the great Jade Empire used the ancestors' language. So of course all of KTS Kanopos' Pilots used it too. But despite the nearly four years he'd spent at KANP, Haruto still struggled with it. The Princess had tried to help, but her method of learning the language had been to spend hours upon hours for years studying it. He didn't have that kind of time or patiences.

\textbf{\sffamily{Oh stop feeling sorry for yourself, brat.}}  QB9 answered causing Haruto to nearly jump out of his SKIM. \textbf{\sffamily{At least you have a body.}}

\emph{`Dang it, QB stop doing that. Give a guy a warning or something.'} Haruto replied startled.

\textbf{\sffamily{My name is SB3-QB9, you may call my that or QB9, nothing else you ungrateful brat!}} QB9 answered back. \textbf{\sffamily{You seem to forget I am in control of your bodily functions.}}

Haruto snorted. \emph{`Yeah, and if I die you die.'}

\textbf{\sffamily{I never said anything about dying...}}

His wrist buzzed and an image of stained pants flashed quickly. Haruto flushed at the thought, \emph{`You won't dare.'}

\textbf{\sffamily{Try me, brat.}} QB9 answered. Haruto was really going to need to figure out some kind of compromise with the AIM.

\emph{`Stupid program doing whatever it freaking feels like.'} He thought darkly, luckily QB9 didn't bother to respond. He'd probably get what he wanted, if Haruto couldn't figure out an alternative. \emph{`What kind of name was QB9 anyway?'}

\textbf{\sffamily{Doctor Fumagawa had a mind far more brilliant than yours.}} QB9 challenged. \textbf{\sffamily{H\={e}id\`{o}ng, however. Trying hard aren't we?}}

\emph{`The Princess says the H\={e}id\`{o}ng's were an elite Clan that once mastered time and space.'} Haruto countered.

\textbf{\sffamily{Clan?}} QB9 replied in disbelief.

Haruto flushed, \emph{`Well I didn't say they were a Kanopos Clan.'} He added quickly. Haruto felt an amusement not his own settle.

\textbf{\sffamily{And who in the Gods' name is Princess?}} QB9 questioned. \textbf{\sffamily{You've been thinking about her constantly since I was activated.}}

Haruto ignored the jab at the end focusing on the new information, \emph{`So he doesn't just know everything I know.'}

\textbf{\sffamily{Answer the question, brat.}} QB9 growled out.

\emph{`I don't know, QB9. You haven't been all that nice to me.'} Haruto feels a built up of anger. \emph{`How about we make it a game?'}

\textbf{\sffamily{A game boy? I don't play games.}} QB9 responsed in a low growl of frustration.

\emph{`I'm bored and you want an answer that only I can give you,'} Haruto taunted. \emph{`Seems to me like you don't have a choice.'} Haruto felt resignation and smiled as he continued. \emph{`I'll give you one hint, and only one hint to the Princess' identity. And if you can't guess her name with that one hint, then I get to call you QB.'}

\textbf{\sffamily{And if I win?}} QB9 questioned. Haruto paused in thought, not entirely sure what an AI would even want. \textbf{\sffamily{My freedom.}} QB9 answered for him. \textbf{\sffamily{I want my freedom.}}

Haruto rolled his eyes at the dramatics. It wasn't as if he was holding the AIM captive or anything. The thing \emph{was} an AIM after all. \emph{`Sure, why not.'} Haruto replied. \emph{'If you win, I'll get you a body of your own as soon as I can. Build it if I have to.'}

Satisfaction bubbled up from within him. \textbf{\sffamily{The hint, brat.}} QB9 demanded.

\emph{`She's from a Clan.'} Haruto smiled. \emph{`Hey, I never said it would be a good hint.'}

\textbf{\sffamily{Brat, you underestimate my skill}} QB9 challenged.

\emph{`Prove it.'} Haruto replied. As far as he was concerned this was a win-win-win. He got to entertain himself, and he wasn't going to have to do anything he wouldn't have already agreed to do if the AIM had given him half a chance.

\textbf{\sffamily{Well you've got a pretty smug feeling about you, so the nickname isn't for just shits and giggles. If she's in a Clan that rules out a great many girls, including that Helian girl. Really kid, you shouldn't have given my the gender.}}

\emph{`I'm hearing a lot of talk.'} Haruto replied. There was a long pause as Haruto could feel QB9 processing. \emph{`You give up?'} Haruto questioned as he kept his mind thinking of the trees outside and imaginary birds.

\textbf{\sffamily{Impossible}} QB9 responsed.

\emph{`So is that your way of saying you failed?'} Haruto questioned.

\textbf{\sffamily{Of course not, brat!}} QB9 responsed. \textbf{\sffamily{My conclusion is simply impossible, even for you.}}

\emph{`Either you give a guess or you give up QB9. Those are the rules of the game.'}

\textbf{\sffamily{I believe this is her.}}

Haruto looked at his BISM screen, to find his Princess staring back at him in her formal Moon Princess coveralls. He smiled disappointedly, \emph{`Yeah, that's my best friend.'}

\textbf{\sffamily{Then I win.}} QB9 gloated.

\emph{`Hey now, that wasn't part of the game.'} Confusion but continued before QB9 could interrupt him, \emph{`Her name, QB9.'} He smiled at the blank response. \emph{`You're supposed to guess her name.'}

\textbf{\sffamily{She's the Gento heir, the K\={o}taishi,}} QB9 huffs in frustration. \textbf{\sffamily{You don't have access to the kind of information that would allow me to know more.}}

\emph{`That's only because I have to clear our chat history weekly.'} Haruto replied cheekily. \emph{`Well QB9?'}

\textbf{\sffamily{You already knew I wouldn't be able to get her name didn't you.}} QB9 growled out. \textbf{\sffamily{You played me.}}

\emph{`Hey now, don't get mad. You actually got more than I thought you would.'} Haruto paused in thought seeing how this could go badly for him. \emph{`Look, why don't we call it a draw. I'll still help you out.'}

\textbf{\sffamily{You're not calling me, QB.}} QB9 responsed. 

Haruto shrugged. \emph{`No big deal.'} QB9 settled down.

Haruto leaned back in his chair as the Lieutenant continued to drone on at the front of the classroom. He wasn't entirely sure what they were supposed to be learning and frankly he didn't really care. Heck, he hadn't even bothered to remember his Lieutenant's name, and he'd had the man for months now.

\textbf{\sffamily{The Clans.}}

``Huh?'' Haruto questioned under his breath.

\textbf{\sffamily{Lieutenant \emph{Cho} is discussing the Clans.}} The sass was real.

Haruto forces himself not to bang his head on his desk. \emph{`Why am I even here?'}

\textbf{\sffamily{Don't be overly dramatic brat. This is important information.}}

\emph{`For you maybe, but nearly a quarter of this class is in the Clan. I've known all about them for ages.'} Feels QB9's disbelief. Looking to the front row Haruto continued. \emph{`The blond up front is Ilia the Amur Clan heir. I think they do mind control or something. Involved in a lot of enhanced interrogations and the like too.'} Haruto looked over to Helian. \emph{`Side note, I'm pretty sure there dating.'}

\textbf{\sffamily{How do you know any of that?}} QB9 questioned. \textbf{\sffamily{You don't have access to that kind of information.}} Accused tone.

\emph{`Best friends with the Gento heir remember.'} Haruto replied cheekily. Although he was sure the Princess had said significantly more on the top, he'd remembered the important bits. \emph{`Anyway, sitting next to her napping is Kur-ram. Cool guy and killer at Komi.'}

\textbf{\sffamily{Kur-ram is not a Clan.}} QB9 replied.

\emph{`Oh, yeah. He's the Krai heir. And the big guy next to him is Kenta the Sakhalin heir. They have the best food anywhere on the ship.'}

\textbf{\sffamily{How is that relavent?}}

\emph{`How is it not relative?'} Haruto countered. Before QB9 could answered he continued. \emph{`Anyway, the Princess says the three of them are like really old family friends and will be a Pilot unit together after OCI.'} Turning slightly in his seat his eyes landed on Akihiko. \emph{`That brooding stick in the mud, is the second son to the Zh\`{u}r\'{o}ng head family. Which appearntly makes him as useful as a eleventh finger.'}

QB9 snorted in amusement. \emph{`The kid with the symbiote on his head is Seo-Jun from the Gonsaeng head family. Solid guy to have at your back during a prank. Also cheats on every test.'}

Haruto seatback as he found himself lost in some of his favorite pranks with Seo-Jun.

\textbf{\sffamily{And the kid in the back? With the goggles?}} QB9 questioned as a buzz came from his BISM. \textbf{\sffamily{He must be from the Haibeu Clan.}}

\emph{`Who?'} Haruto questioned as he looked at the stock picture on his BISM. Not reconising the Cadet.

\textbf{\sffamily{He is literaturely sitting in the back right now.}} Some anger.

Turning his head quick he looked and sure enough they were there. \emph{`Well what do you know.'} Haruto commented as he sat back to face the front. \emph{`I guess that must be Ji-Min the Haibeu heir. The Princess mentioned they were in the class. Must have blocked them out again.'} Haruto added. \emph{`Those guys give me the creeps.'}

QB9 was not amused. \textbf{\sffamily{There's only one of \emph{him}.}}

\emph{`Yeah, but since they're somekind of hivemind, the correct pronoun is they/them.'} Haruto replied smartly.

\textbf{\sffamily{I suppose your \emph{Princess} told you all of that too.}}

\emph{`More or less.'} Haruto replied. \emph{`Honestly though, if you get in a game of Komi with Kur-ram he's an open book. The Sakhalin Clan are really nice and will feed just about anyone who shows up at their family get togethers no questions asked.'} He continued for QB9's benefit.

He'd followed Seo-Jun to the Gongsaeng sector too many times to count. Haruto still remembered his failed attempts to get Seo-Jun's sister to give him one of her symbiotes. And if wanted to hear a biased opinion on the Zh`{u}r\'{o}ng Clan, then all he had to do was insult Akihiko.

\textbf{\sffamily{Is that is? Just the seven Clans if you could your Princess?}} QB9 questioned skeptically pulling Haruto from his thoughts.

\emph{`Oh, well no. There's twelve in total, and...'} Haruto sighed. He really didn't want to have to explain them all. \emph{`Give me a second, would you?'}

Picking up his tablet, he tuned out Aeliana as she answered \emph{another} question like her life depended on it. Personally, he thought she needed to learn a lesson in fun, but that was just him. Angling it just right so the Lieutenant wouldn't see him accessing his BISM, he began to hack into his neighbor's tablet.

A moment later and he had the direct feeds from his Lieutenant's notes.

\textbf{\sffamily{Oh, nice...}} QB9 murmured as he download and sorted though the data on the Clans. From the flashes coming across his BISM screen, he could tell QB9 was also following secure links to even more data.

Haruto turned his attention back to a window as he waited.

``...the Gento...''

Haruto's attention was drawn to the Lieutenant at the front of the class at the sound of his best friend's Clan name. While he liked to think of himself as an expert on the Clan, partly due to being best friend's with the Princess and partly due to his continuous run-in with the Keepers, it never hurt to see if there was more to learn.

``As you all should have read last night, the Gento are one of the big four, and the one of the two original founders of our mighty KTS class ship,'' the Lieutenant spoke.

\emph{`There was homework?'} Haruto thought as the Lieutenant plowed on.

``What was not included in that reading; however, was the difficult in getting the Gento to join. The Sakhalin were all too happy to join in the cause. And the Zh\`{u}r\'{o}ng instantly saw the benefits of helping the shaping of a KTS class ship, which would be the first such ship within the Jade Empire.'' The Lieutenant chuckled at the comment. ``It would seem that Empire, great as it is, always seems to be last to the party.'' He chuckled again at some random inside joke.

\emph{`Tell me something I don't know.'} Haruto thought as his mind began to wonder. The Princess used to tell him bedtime stories about her Clan when he'd had trouble sleeping. The time of the Honorable Hanza, her great, great, great, great, grandfather, was one of her favorites.

``But the Gento, a powerhouse in their own right were reluctant to join their enemy.'' The Lieutenant tapped his own tablet sending information to the class. Haruto looked down at his only to see another block of dense text.

\emph{`Hard pass.'} He thought, \emph{`Besides, I've heard the story a dozen times now.'}

QB9 was quiet as he processed the new data.

``Their blood feud with the Fujimi, as you can see, is something out of the history books. Some of the greatest battles of that were recorded were between the honorable Fujimi Hoshizora and Gento Hanza.''

Haruto let his eyes drift back to the world outside the clasroom as murmurs errupted fromt he class.

``Lucky for us, a fabled friendship between the first Sakr\'{a} and the Honorable Hanza greatly aided the alliance process.''

``What was the feud about?'' Seo-Jun asked Lieutenant. 

Haruto answered for the Lieutenant, ``Really Seo-Jun?'' he commented. ``Everyone knows that the Fujimi and Genot Clans were Pilots for hire and normally on opposite sides of battles during the Warring Stations period.'' He continued. ``There was so much bloodshed, so much death...'' he trailed off as he remembered the Princess' words. The pain heavy underneath them.

``A time where children younger than us fought and died.'' He added lowly. ``That's why KTS Kanopos is so important. We're here,'' haruto nodded to the classroom, ``Until we're ready to be out there.'' He tilted his head to the windo in the general direction of the observatory deck.

There was silence before Helian interrupted, ``How do you know any of that?'' Her words were accusatory. ``It wasn't in the reading, or in open records.'' She continued.

Akihiko interrupted before the Lieutenant or Haruto could reply. ``With the power of the Zh\`{u}r\'{o}ng Clan, there should have been no problem in defending and building the KTS ship. No reason to team up with the \emph{Gento}.''

Haruto leaned forward anger at the disrespect to the Gento Clan on his friend's behalf. ``Like the Zh\`{u}r\'{o}ng could afford the expense or the man power?'' Haruto already knew the answer. ``The Gento put up half. \emph{Half}. The construction cost of the KTS Kanopos. Gave up half their own ships, brothern, may who died in the defense of this ship during construction. No profit, nothing gained but the honor of their Clan.'' Haruto paused as he looked around at the stunned faces. ``And we all know the Zh\`{u}r\'{o}ng aren't well know for their \emph{honor}.''

Akihiko's nose flared, ``How dare you...''

Haruto cut him off, ``Without the Gento Clan, stick in the mud that they are, KTS Kanopos would still be a dream of two young friends.''

``That's enough, Cadet H\={e}id\`{o}ng.'' The Lieutenant interrupted. ``While you have some facts amazoningly correct, you're wrong on several counts. Most glaringly your claims on the Gento Clan's investment, which was not half of the funds and man power, but initially only half the funds. If not for the constant respect and fair treatment that the First Sakr\'{a} showed the Honorable Hanza, it's very possible that the Gento Clan may have never joined.''

Haruto opened his mouth to correct him, but the glare of the Lieutenant caused him to shut it. He didn't often get warning before being kicked out of class, but even Haruto knew one when he saw it.

``Now, if I may teach my class without further interruption.'' The Lieutenant snapped as he looked around the room. ``Can anyone tell me about the terms of the treaty that the Gento Clan signed?''


Haruto watched as Aeliana shot her hand up into the air.

``Cadet Helian,'' Lieutenant acknowledged her with a nod, which was a rare occurrence. Haruto half thought the Lieutenant wished Aeliana would answer significantly less questions.

``The Gento Clan were given the protection of the Kanopos forming the Keepers in exchange for never having one of their Clan members become the Sakr\'{a},'' she answered swiftly. ``They have since grown to be the most prominent Clan within Kanopos,'' Akihiko snorted at the answer, but it would seem that Aeliana wasn't done, ``For example, the K\={o}taishi is already considered a ranking officer despite being our age.''

\emph{`Wow now, the Princess never mentioned that.'} Haruto thought. He'd have to ask her about it later. \emph{`Did she even need to go to OCI?'} Because if she didn't, that changed everything.

``I see someone has done extra reading.'' The Lieutenant replied grapping Haruto attention. ``Cadet Helian is correct. When the Gento Clan joined KTS Kanopos, their treaty gave them the exclusive right to maintain and control the Keepers of the Peace that keeps watch over our great ship, in exchange for never having the ultimate power of the Sakr\'{a}.''

``Wait a second.'' Haruto interrupted accidently. ``In the initial treaty?''

Lieutenant tightened his lips. ``Are you hard of earing too? Hard to believe with those ears.''

Haruto flushed in embrassment. ``No, it just the Keepers weren't even mentioned in the initial Gento-Kanopos Treaty. That was added like fifty years after the completion of the ship.'' Haruto leanted forward as he continued. ``\emph{And} the Gento didn't join the Kanopos because of fairness and respect.'' Haruto added not seeing how anyone could believe that. ``Honorable Hanza had already made a deal with...''

``Enough H\={e}id\`{o}ng!'' The Lieutenant yelled. ``I don't know where you think you're getting this information, but it's all wrong. The official record states...''

``\emph{I'm} getting this information from the Princess, eh Moon Princess, herself. And some how I think the heir of the Gento Clan would know her own history.'' Haruto countered angerily.

The Lieutenant looked pissed for a second before his face returned to a blank mask. Haruto was sure he was about to get kicked out, but before the Lieutenant could speak Aeliana did.

``The Gento heir?'' She questioned. ``Moon Princess? You call the K\={o}taishi by her ZenKZ's name?''

``Well it's a nickname actually. She's got one for me too...''

``One for you?'' Seo-Jun questioned his symbiote sweaked on his head. ``What are you on man, because there's no way your friends with the K\={o}taishi.''

Haruto crossed his arms in defense. ``We're best friends. We talk all the time.''

``Sure you do, idiot.'' Akihiko answered with sarcasm. ``Because the K\={o}taishi is friends with the dead last, Clanless orphan.''

``The H\={e}id\`{o}ng was a powerful Clan...'' Haruto started to counter, but was interrupted as the entire room bursted into a fit of laughter.

``But not a Kanopos Clan, which is why their all but dead.'' The Lieutenant interrupted calmly as the laughter died down. ``And Cadet,'' he continued looking at Haruto, ``if you're going to lie make it a better one next time.'' The Lieutenant shook his head in disappointment. ``Best friends witht he K\={o}taishi.''

``I'm not lying.'' Haruto tried to defend.

``The door, Cadet.'' The Lieutenant pointed to the door. Staring Haruto down as he gathered his things.

With a huff Haruto slowly rose from his seat before walking out of the classroom. \emph{`See if I care if they get the shole story worng anyway.'} He thought as he closed the door behind him.

Still, this went a little further than normal. And the Ghost Hacker of Kanopos didn't let anyone get away with laughing at him.

*****

It never was. What was the point in being stuck in this stuffy classroom trying to get through another mind-numbing lecture? Out there he could explore the parks or even take a trip to the Lower Level if he wanted an easy day. \emph{`I could sneak onto the Sakhalin ships if I really got board. They have the best eats.'}

Haruto held back a sigh. As if he needed another reason not to be here. What was so interesting about history anyway? How was the \emph{Battle of the Tlacopan Station} supposed to make him a better pilot? To the Gods! He wasn't even sure how to \emph{say} it!

****

All his curiosity would earn him was embarrassment as he'd be reduced to the butt of some joke by the Lieutenant. Not that the laughter had hurt him or anything. He was going to be a \emph{great} pilot. No, not \emph{just} great, he was going to be one of the \emph{best}! Little things like that didn't even faze him. So what if he didn't understand everything right away. He was still going to be the most \emph{kickass} pilot KTS had every seen! They'd be writing stories about him for years!

****

Why they had to use it exclusively was beyond him. Surely, the common tongue was just as important, wasn't it?

****

\emph{`You don't have to answer everything that pops into my head.'} Haruto replied.

\textbf{\sffamily{You were asking a question, I'm required to give you something.}} QB9 paused before continuing, \textbf{\sffamily{At least until I figure a way out of here.}}

\emph{`Well, than answer the question.'}

****

\emph{`Yeah, yeah, yeah.'} If he had to hear another monologue about how the AIM was going to get his own body and strike out in the world, then he'd drown in his on MINOS.
