*Park, passes a Tech. He's working with this Tech as part of a punishment for the prank. Unofficial punishment.

Haruto walking in Prayer Alley, slacking. It was his day off, he'd get to the archives when he got there.
Passes Sanctuary Academy, he'd have gone there if he'd not met the Princess and decided he'd take the old man up on being a Pilot after all.

A group of uniformed students, passed him. A girl older than the rest caught his eye. ``Hey Naomi!'' He called out. ``So you really were a Keeper brat.''

Girl smiles at the group before moving to him. ``What brings you to this part of Prayer Alley, Haruto? I'd figured you'd be in the Park by now.''

``Got to study...''

-needs to find the place first... Never been...

should have some banter back and forth between QB9 and Haruto... QB9 talking about something he spoke with the Princess about... Haruto not a fan that they're buddy-buddy...

Naomi sends him the location via cooridinates (drop a pin). QB9 leads the way... the moves into arriving at KOAL (Kanopos Open Access Library).
...Naomi should mention spending a lot of time during her SA days. Lots of Keeper brats go there to rent equipment too, but Haruto was unlikily to get to do that due to his repretation.

********************

Naruto approached KOAL with trepidation. Official buildings weren't really his thing. Too many people, and lately he'd been banded from a number of consol farms. But the Archival of Kanopos supposedly housed both tomes and state of the art consols. Still this was only place a KANP cadet could go to suppliment his education. 

Walking into the large building with as much confidence as he could muster, Haruto walked right past the old woman guarding the entrance.

``And just where do you think you’re going, Cadet Heidong?'' the old woman crowed at him. A crooked, wrinkled finger pointed in his direction stopping him in his tracks. ``We don't have anything for you to steal and all terminals and consols are under constant serveylance.''

``Then it's a good thing I'm here to learn.'' Haruto replied as he continued on his way.

``Not so fast.'' She continued directing him to her desk at the front. ``If you're really here to \emph{study} then you'll have register your BISM for access.''

``Ah... okay.'' Haruto walked hesitately to her desk her eyes gleaming like a pretatory.

``And you'll need to sign, these, read these, and complete several tests about proper KOAL use.'' Her eyes glanced at him. ``And that's assuming you only want archival access.'' Batter her eyes challenging.

``Ah...'' \emph{`You've got to be kidding me.'} Haruto reads one of them, dense text.

QB9 - Just do it kid.

Haruto argues that he doesn't need all this to learn, plans to walk away when old lady speaks again.

``Of course, if that's too much work for you. You know the way to the door.''

Haruto pissed, and pulls the documents to him. `QB9 reads these, and makes sure everythings on the up and up.'

Two hours later and Haruto was done with the ridiculous tests and paperwork. Signs his BISM him and moves on, her gaze never leaving his. ``And remember Cadet, if you don't follow the rules, I'll have you out of here so the serious students can learn in piece.''

\emph{`Remind me to prank her later, QB.'}

QB9 - With pleasure.

Haruto's eyes feel onto the room at large. There were more people here than he'd thought would bother on an off day.

QB9 - give me access to KOAL and I'll have all their information in a heart beat

\emph{`I'm not hacking into the system. I don't know any of their weak points and we just spent hours getting access to the place.'}

* In KOAL, Haruto observes people...

Haruto rolled his eyes. \emph{`Look, QB. There are two ways a master hacker like myself gets information.'} He replied. \emph{`The first of course is to hack into the system, but that needs days of prep to do successfully.'} Sitting down at a empty table, Haruto pulled out his KANP tablet and logged onto the KOAL network. \emph{`Strategy number two, while it sounds easy is just as hard. Listen.'}

\textbf{\sffamily{Listen!?}} QB9 raged back, but Haruto was only half listening to him. \textbf{\sffamily{I listen \emph{just} fine.}}

Haruto waited a beat longer as he continued to listen to the students around him.

\textbf{\sffamily{\emph{You} are the one with the \emph{listening} problem!}} QB9 continued, getting angrier by the second.

\emph{`Did you know that those six students are sixth years KANP cadets?'} Haruto replied.

\textbf{\sffamily{What?}} QB9 spoke, his rage settling.

\emph{`And those three are from the same Gento orphanage program.'} Haruto nodded his head in the direction of three student, two boys and a girl huddled together over one Haloscreen.

QB9 paused briefly, \textbf{\sffamily{How can you possible know that?}} He questioned darkly.

\emph{`Body language, coveralls, size and height.'} Haruto could tell he had QB's attention so he continued. \emph{`See that group over there, four girls all with the same badge on their coveralls?'} Knowing he had QB9 attention he continued. \emph{`They're orphans, but live together in one of the apartments at the end of Solas. Closer to the Sakhalin sector than the Gento sector.'}

\textbf{\sffamily{How could you possible know that without hacking their BISM, or the KOAL register?}} QB9 questioned.

\emph{`Easy. That badge is for orphanage 5A in the Sakhalin sector, which can only hold a small number of kids. All orphanages prioritize the younger children, which means those girls live in group.'} Haruto replied. \emph{`And before you ask. I know they live together because of their familiarity with each other. They laugh ease, brush each other SKIMs without thinking about it. That's group life.'} 

There was a long pause. \textbf{\sffamily{Why don't you live in a group home?}} QB9 questioned. 

\emph{`I was born in Kanopos, or so the old man tells me, but my mom, she was a Heidong. Our clan, just like that Haibeu and the Gento took genetic modification to for space travel to the extreme.'} Haruto pulled up a picture of a smiling blue-eyed red haired woman. Her ears pointed, eyes slanted, and nose just a little sharp, animalistic markings on her face. \emph{`I look different, scare to some. And without a Clan to share in my oddity, well...'}

\textbf{\sffamily{She was a very beautiful woman.}}

Haruto's hand traced her face, \emph{`Yeah, she was.'}

\starbreak

Giving up using the tablet as a bad job, Haruto moves over to the consols.
-not enough connection speed.

-having a hard time concentrating. Bored out of his mind studying... Wants to be playing...

this mixes with thoughts of wrongful punishment, and the Princess not having any time because she was preparing for a long trip through the Empire. Haruto not exactly happy, thinks this is her dad getting back at them... He'd be stuck sending official transmissions, which meant he'd have to be careful what he wrote and so would she.

Aftermath of the KANP prank (class is cancelled) Haruto doing manual labor because no one trusts him with the software.

Haruto thinks about how he could do so much more with the stuff then they could.

-brief mention of High Commanders (DOMAINE, Department of Mechanical, Artificial Intelligence, and Neurological Engineering).

-Not everyday, that all three DOMAINE High Commanders gets called in to assist with KANP security.

``Good morning, Cadets.'' The woman next to replied in a softer voice. ``My name is High Commander Stone, I have the current pleasure of leading the Department of Neurological Engineering and advanced technological development.'' She smiled brightly at the class. ``My companion is High Commander Lee, who leads the Department of Mechanical Engineering and military readiness. And while normally we are both very busy women, for these next two weeks we are you esteemed professors.'' Her eyes turned sharp as she looked around the room, ``I hope you all work very hard for us.''

High Commander Chin\={o}, ``Impressive Woong. Your skill at the helm is always something to admire.'' The old man spoke. ``Testing a new targeting patch? Or will it be in the next model of your amazing m-TARGETS technology?'' He continued. AI Department

Tries to focus again, and starts at number one on the list the Princess had made for him to help him study. Official history, which turned out not to be the correct one, for Kanopos and the construction of KANP.

***************

(this should come out of no where). ``H\={e}id\`{o}ng.'' Her voice harsh as she spoke. The redhead in question blinked up at her in confusion.

``Helian? You want something?'' He asked.

``You're sitting at my console.'' She replied tensely arms crossed. ``Surely you wondered why no one was sitting at it?''

The redhead looked around at the many empty nearby seats in confusion, ``Ah...'' He started to reply, but cut himself off. His face drifted off to the side, scrunching in displeasure as if arguing with some invisible enemy. Aeliana herself was a little lost for words. While technically consoles were first come first serve, she'd had an understanding with all of the regulars about this console. And while she knew it was petty, right now she wanted the comfort of her normal seat.

After a moment, his face settled. But instead of talking to her, he turned back to her console. Aeliana saw red for a moment. It was H\={e}id\`{o}ng's fault that she was even here at this time of day. \emph{His} prank that had caused her relationship with Ilia to come to a boil. No matter how unreasonable that thought was, she couldn't help the bitterness she felt towards him. As such, her mind quickly reviewed the number of ways she could get him kicked out of here. But before she could put any one plan into action, the redhead logged off and hopped over to the empty seat next to it.

``All yours.'' He replied as he logged-in to the new console.

Aeliana hesitated for a second longer, before seating down in the warmed seat. Linking her BISM to the console, a new archive search popped open automatically. Staring at the window with H\={e}id\`{o}ng tapping away beside her, she was struck with the realization that she had no idea what to type.

``You just going to stare at the screen all day?'' H\={e}id\`{o}ng questioned as his fingers flew across his keyboard at a surprising rate. ``'Cause that would make me moving kinda pointless.''

``I'm just thinking.'' Aeliana answered.

H\={e}id\`{o}ng snorted in reply, ``What do you even need to study for anyway?'' He continued. ``Don't you already know it all?''

``I've never claimed to know everything.'' She snapped in frustration. ``\emph{Some} of us have to study and review to even have a chance at getting into OCI.'' She continued her mind thinking of Ilia despite herself, ``We can't all be born into a \emph{Clan}.''

H\={e}id\`{o}ng shrugged in response. ``You all seem the same to me.'' In an easy going tone, he continued, ``Well, except for the Moon Princess. At least she's not stuck up.''

There was an odd note to his voice as he talked about the K\={o}taishi. Aeliana wasn't sure how to take it or how to answer him. So she didn't. Even so, his words brought memories of watching arguable the most beautiful ZenKZ of all time. One of two ZenKZ-D completely untouched by time. Now they were truly unique.

\emph{`Unique?'} The word struck her with an idea. Her own hands flying across her keyboard joining H\={e}id\`{o}ng's. The Moon Princess ZenKZ was a relic and possibly the answer to her problems. Minutes later and Aeliana had a list of sources that reviewed relics. Opening the first one, she paused. ``Thanks.'' She called out.

``No problem.'' He answered not questioning what she was thanking him for, for which she was grateful. ``Besides, I could tell you were having a bad day.'' He continued.

Aeliana's brows furred in response. H\={e}id\`{o}ng was... different, surprising maybe. She wasn't sure what descriptor to use with him. Either way, he wasn't nearly as bad as she'd thought he'd be. \emph{`Tolerable.'} She concluded.

``Can I ask why you're even here?'' She questioned. ``I mean, not to sound rude, but you've never taken your studies seriously before, so...'' She trailed off.

H\={e}id\`{o}ng turned to her, large grin in place as he held up a finger, ``First off, if you've got say not to be rude, then you're definitely about to be rude.'' If possible his smile got wider as he held up another finger. ``And second,'' he paused for dramatic effect as if sharing a secret. ``I've decided I'm going to OCI.''

His confidence was both infuriating and intrigue at once. ``You? OCI?'' She questioned. His smile turned mischievous. 

``Yup!'' Turning back around he started typing once again, ``No matter what it take!''

Given their last ranking test scores, she knew for a fact he wasn't just below average, but dead last. ``You'd need a 92\% on the next six ranking exams to break even. And that's assuming they don't raise the test score average from 70\% to 75\%.'' She replied automatically doing the math in her head.

H\={e}id\`{o}ng only grinned back at her, ``Whatever it takes.''

Aeliana shook her head in disbelief. Her eyes finding her first review article on relics. \emph{She} was banking on ancient history to get her to OCI. In this, she wasn't any better than H\={e}id\`{o}ng. ``Whatever it takes,'' she parroted, \emph{`within reason.'} she privately added. Because a Helian didn't do desperate.
