\chapter{Hyuuga Police - Pranking session 0}

``First attempt to seal operation supplies… Success!''

``Release of seal, super successful,'' he recounted in joy. This was a major accomplishment. After he completed his prank of the century, he was definitely going to treat himself to Ramen Ichiraku. Briefly inspecting his supplies to make sure there was nothing missing or broken, Naruto was excited to note that everything looked great. Now was the time to begin.

Naruto quickly resealed his supplies and continued with the mission. ``Operation Honey and Feathers is a go.'' It was finally time to get that no good Sensei back. No one kicked him out of class for no good reason without suffering the consequences.

With his supplies resealed, Naruto placed the scroll in his pants before making his way to his target location.  As master pranking rule numberforty stated, always know your target’s typical patterns and usual mannerisms before pranking. As a result, Naruto had spent that last week studying his Sensei’s movements inside and outside of the classroom.

Before he’d gone on his week-long surveillance venture, Naruto’s initial reaction had been to prank the man at his home. Theoretically, the location was perfect as firstly, it was the easiest place to excess which would, secondly, require next to no research before he could execute his prank. Sure Sensei would likely have several low key traps on the place, but those wouldn’t be all that difficult to bypass. After all, nothing was harder to get around then the traps at the Uchiha Compound or the Hyuuga Police buildings, and he’d still managed to make it past those. Of course that was before they’d improved their security, little details that really didn’t matter much as he was sure that with enough time he’d get around those new ones too.

So, yeah, Naruto was fairly confident that he could have done it, broken into, I mean infiltrate his Sensei’s apartment, but with no witnesses where was the fun in that? After all, a prank was only truly great if it had someone to witness it. That level of embarrassment couldn’t go without an audience. That was the whole point of master pranking rule number fifty-six point five.

So Sensei’s apartment was out, and of course it went without saying that the classroom was out too since Sensei would be expecting something from there. Although that didn’t mean that Naruto couldn’t have hit him there. In fact targeting the classroom would have added a level of difficulty that would have made the prank all the more fun with the end result even sweeter.

However, that type of prank would have tacked on another week of preparation. There was just no way he was going to wait that long. Especially not when it was still possible for Sensei to catch on and notice it before the prank went off. There was just no way he could guarantee a successful prank with Sensei this alert. Even he was willing to admit that his trap making and setting skills were only so good.

Hopefully, with the new seals he was learning, that would no longer be the case, but that was neither here nor now. Improving his pranking skills would come with time. He could wait on something like that. It wasn’t like he really wanted to pull another classroom prank so close to the last one anyway. That type of decision would probably not sit so well with Jiji and he was already going to be on thin ice when he finished this prank. No need to make it worse.

Which left him with only one more real option, follow Sensei around to find his favorite hangout. In all honesty, it hadn’t actually taken the full week to figure out Sensei’s favorite after class hangout. The man was like clockwork with his habits and the Shitaki Bar \& Grill was just a big part of it. Personally, Naruto thought the man spent a little too much time at the mostly ninja bar, but hey what did he know? He didn’t usually make a habit of clocking how much time the average ninja spent at bars so he didn’t really have that much to compare it to.

Of course it didn’t particularly matter if Sensei had a drinking problem or not, that really hadn’t been what Naruto had truly been paying attention to over the last week of following the man. No, in the hours of study he’d done he’d figured out a number of things. Firstly, the owners were civilians. A rather average couple that had three kids of which none particularly looked like they wanted to join the ninja ranks and only one, the youngest, that looked even remotely interested in taking over the family’s legacy.

Naruto shrugged at that thought. He really couldn’t understand why anyone would want a boring old civilian life. Even at the orphanage, most of the kids there had either wanted to join the ranks of the Hyuuga Police force or that of the Konoha Ninja force. Of course maybe that was because none of the orphans he knew ever thought they had a chance at apprenticing with a merchant, but he was pretty sure it had more to do with the fact that being a regular old civilian was just capital b, Boring.

Of course all that meant was he wouldn’t have to worry about the owners getting in his way. They were in no way equipped to even try to stop him. However, that did leave the second piece of information he’d gained from his week of observation, the patrons. From what he could see, the patrons were comprised of mostly Chuunin and older Genin. They made for a loud, boisterous crowd, but other than that didn’t really pose much of a threat to his mission.

So in a nutshell, he’d learned that it wouldn’t take much to infiltrate the place. Which was a good thing, because that meant he wouldn’t have much to worry about on his way out either. While escape was always the more difficult of tasks that difficulty was limited to how skilled the shinobi were who would be chasing him. Luckily for him, he’d been out running Genin since he was six and Chuunin since he was nine. He wouldn’t have a problem escaping from the patrons from this bar.

Of course that didn’t mean he wasn’t limited because no matter the rank of the shinobi they were still shinobi. Which meant they would likely be able to spot a rig if it was on the front door no matter how well he hid it. So that spot was simply out of the question. Another option was to target a chair, but that wasn’t really a good idea either. Mostly because in the several days that he’d been following Sensei, the older man hadn’t sat in the same seat twice.

Sure, he typically sat in the same area, and Naruto could target all the chairs in that area, but that really wasn’t the point. He wanted to prank Sensei not Sensei and a bunch of random shinobi. And though it might have been easier, he wasn’t about to go back on his master pranking rules now. No, he was going to follow rule number fifty-one and only prank Sensei, his intended target.

Which left him with one more option, the bathroom door. Though it was a high traffic area, the bathroom door had the added advantage to be tucked fairly far back into the bar. Which in the end was for the best because it meant that the darkened bar interior would help hide his trap as opposed to the neatly lit front entrance. Now all Naruto had to do was peg how long it took his Sensei before the man needed to relieve himself.

Surprisingly, Naruto was able to uncover a pattern fairly quickly. Taking only two days before he realized that Sensei must have had a bladder the size of a walnut because the older man was up and running after every two drinks laughing off his inability to house more fluids in his body the whole way to the door. Naruto had frowned at that knowledge as it put a rather large damper on his timetable.

While Sensei always managed to stay for at least two drinks, he didn’t always have the same number each day. Sometimes it was just the two, while others he had upwards of five. Though Naruto had been unable to figure it out while he was following the older man, he had discovered a rather useful pattern after he’d reviewed all his notes. Sensei stayed the longest right after he assigned the class some lengthy homework assignment and he stayed the shortest amount of time on quiz days.

That of course had been the primary reason, Naruto had chosen today of all days to prank Sensei. Though Naruto had skipped the second half of class to prep for this prank, he’d been there long enough to receive the night’s homework assignment from Sensei. Given the length of the assignment they’d received earlier that day, Sensei was bound to spend hours at his favorite bar. Naruto would have at least two tries at it. Which was altogether a good thing considering the rather large time variant it took Sensei to finish each drink.

Unfortunately after only a week’s worth of study, Naruto couldn’t narrow down the rate of consumption any further than a fifteen minute interval. It was a time frame that he’d already tested out, having already done two dry runs with varying degrees of success, but he was unworried. He’d picked today of all days to compensate for that flaw in his plan. All he needed to do now was get there, work his magic using the ample shadows in the already darkened space and watch Sensei to figure out just how drunk the man was to estimate how many drinks he’d had.

That last part would be the easiest because all he had to do was listen in on the man’s conversation. As it turned out, Sensei was a loud, boastful drunk. As such, the number of drinks he’d consumed was directly proportional to how loud he was as well as the frequency of the phrase ‘when I was a Genin’. Easy enough to follow.

Of course he’d have to be careful when activating the trap. This was a public bathroom after all, and it would do him no good to hit the wrong person just because he wasn’t paying enough attention. Naruto sighed. It certainly would have been nice if he had a seal that could do if for him. Something that could sync to a specific person taking out that variable so he wouldn’t need to worry so much. Yeah, he would definitely need to make something like that, but that type of thinking was for another time. Right now he needed to take it one step at a time. And that first step happened to be this, Operation Honey \& Feather.

Naruto paused outside of the Shitaki Bar \& Grill, glancing up at the sun in an attempt to get a rough estimate of the time. Man, he really needed to get a watch. Shaking that thought aside, Naruto finished his estimation. If he had this right, then Sensei had another two hours of class left before the rest of his classmates were dismissed. That gave him two hours plus the hour and a half of extra time that Sensei spent going over notes and helping anyone, well almost anyone, who wanted the help after his lesson. Nodding to himself, Naruto clicked the tiny red button on his recorder as a thought struck him. “Note to self, design a timing and activation seal… Also, think about adding some type of personal recognition thingy later.”

With one quick click, Naruto stopped recording. Melting into the shadows as he entered the bar. Now was time for setup.

\newscene

Less than an hour later found Naruto back outside of the bar attempting to find something else to do to fill his time. \thought{Well, I can’t just sit here twiddling my thumbs,} he thought as he pushed off the side of the building. \thought{You know, I am kind of hungry,} he continued as he headed towards he’s favorite food stand, slinking through the crowds in an attempt not to be seen. Pranking was fun and all, but it often didn’t leave time for much else, like lunch. A low rumble filled the air causing Naruto’s ears to burn red. ``Yeah, food sounds like a great idea,'' he mumbled softly to himself with an embarrassed pat to his stomach.

Digging into his pockets, Naruto checked to make sure he had enough for at least one bowl. After a few moments of fruitless searching, he managed to come up with a couple of crumpled up ryo, not nearly enough for even the cheapest bowl. \thought{Dang, looks like I left Gama-chan at home,} he thought before swiftly changing directions while he could sometimes talk the old man out of a free bowl of ramen, it wasn’t always a sure thing. Plus, he was supposed to still be in class. The old man might chase him away on principle and where would that get him? Just a half hour wasted when he had a perfectly good supply back at his apartment.

\thought{Actually, on that thought, I should probably be more careful,} Naruto thought as he moved closer to the surrounding buildings, blending into the shadows. As had become a rather annoying occurrence, if he got spotted by the Hyuuga Police, especially during Academy hours, they would often apprehend him. He didn’t even have to be doing anything wrong anymore! What was the world coming to when a boy couldn’t walk the streets of his ninja village without being molested!

Naruto shook his head at the notion as his eyes landed on three of that horribly familiar gainsboro  colored uniform. \thought{It just wasn’t right,} he thought as he easily circumnavigated the trio, their light gray uniforms a dead giveaway that they weren’t too high up on the food chain. Continuing towards his apartment, Naruto sped up the pace. He may have avoided a completely unwarranted capture, but as long as he was out in the open he couldn’t really relax.

\newscene

Two hours later and Naruto’s hopping from his apartment, having eaten, restocked his supplies as well as inventoried everything he would need to buy or make to replenish his supplies. While he was fairly certain he’d be able to afford everything he needed if he shopped correctly, he was definitely looking forward to his birthday when Jiji managed to get him a little more for his stipend. From what he could tell, he was going to need the extra money to pay for the sealing supplies he’d need.

Of course none of that really matter right now, not when he had a prank to finish. Sticking to the shadows, Naruto made his way back to Sensei’s favorite hangout. As long as he didn’t look too suspicious the Hyuuga Police really couldn’t stop him. It wasn’t Academy hours after all, he was allowed to walk the streets of Konoha.

Stepping out of the shadows, Naruto fell into step with the late afternoon crowds. Blending in as he followed the rather rowdy group to the street he needed to be on. \thought{Looks like everything’s going according to…}

Startled out of his thoughts at the rather hard pull to the back of his jacket, Naruto stared up into pale white eyes and a blank face. \thought{Nan da?} he questioned as confused eyes met the stern stare glaring back at him. ``Uzumaki-san what are you doing in this part of the village?''

Mouth open, an easy excuse ready and waiting to fall from his lips, Naruto was interrupted by Hyuuga-san’s blue eyed partner. ``Only bar ‘n grills are on this street, Uzumaki-san. All of which require adult status to enter. Last time I check that didn’t include you,'' he stated, finger poking Naruto in the chest.

Naruto glared at him. The man wasn’t a Hyuuga, but he sure was mean enough to get along with them just fine.

Focusing back on Hyuuga-san, Naruto attempted to wiggle out of his grip. He really couldn’t afford to get taken to the Hyuuga Police Headquarters. He had a hard enough time escaping the regular Police Towers as it was. And if he still planned to prank Sensei tonight then he wouldn’t have the time to work around the added security of HQ. \thought{Shimatta!} Naruto internally cursed as Hyuuga-san’s grip tightened. It looked like he was going to have to talk his way out of this one.

``Oh come on Nii-san, Hyuuga-san, there’s nothing wrong with me taking a little walk. No need to get so handsy,'' he complained, attempting to keep his tone light and sweet. By the look on Nii-san’s face, he didn’t think he was fooling either one of them.

``Is that so,'' Nii-san began a frown pulled firmly on his face. ``Then perhaps we can help you get there. Where did you say you were going again, Uzumaki-san?''

``I, ah, I didn’t. I’m not really walking towards anything per se, just…talking a stroll. I’m allowed to do that you know.''

The Hyuuga and his partner exchanged looks. ``A stroll huh?''

``Yeah, it’s not a crime,'' Naruto nodded confidently. There was no way they could take him in for just walking around Konoha, not outside of Academy hours.

``Well, I do believe that’s probable cause, Keigo-san,'' Nii-san stated, looking straight over Naruto’s head.

``Hey wait! What ya mean probable cause!? I’m just walking! I’m just out to go to the park,'' he yelled, flailing his hands about as Hyuuga-san lifted him higher off the ground.

``Try again Uzumaki-san, the park isn’t anywhere near here,'' Nii-san replied, signaling his partner with a nod. ``We’re taking you in before you can get into any more trouble.''

Dangling in the air as they moved, thankfully not in the direction of HQ, Naruto glared up at his capturer. ``Is this really necessary?'' he complained, a hand pointed accusatorily at the offending fist still holding him above the ground.

``Simply protocol, Uzumaki-san,'' Hyuuga-san stated as they approached the nearest Hyuuga Tower, the glaring number three staring down at him.

\thought{Shimatta!} Naruto cursed, a pout slowly forming on his face. \thought{This is all I need, and on the cusp of such a great prank! Absolutely wonderful,} he thought as they crossed the threshold, not bothering to glance around the place. It wasn’t like this was anything he hadn’t seen before. He wasn’t exactly a stranger to any of the Towers, not by any stretch of the word.

And honestly, the Hyuuga’s were just really poor designers at least that was his expert opinion. Basically, if you’ve seen one boring Tower, you’ve seen them all. And he would know. Naruto was pretty sure he was the only person to ever be taken to every tower in Konoha. That was an accomplishment he was pretty proud of for obvious reasons.

Naruto didn’t bother to look up until he was dropped, rather rudely, on to a familiar hard metal chair. \thought{Ah, interrogation room nine,} he thought with a quick glance around. \thought{Looks like it’s my lucky day,} he finished with a grin on his face. Nine was his lucky number after all.

Nii-san plopped down into the seat across from him, his light blue eyes attempting to borrow holes into Naruto’s head. Naruto was wholly unfazed by his attempt, amateur.

``So, what’s the charge?'' Naruto grinned. He hadn’t actually done anything yet and he hadn’t prank anyone in over a week. They had nothing on him and he had absolutely nothing to worry about. He had this in the bag.

``Oh, don’t worry. We don’t need you to confess to your crimes. I’m sure some civilian’s already reported you. Just sit back while Keigo-san checks to see what trouble you’ve managed to do today. At this rate, we’ll have you sitting in front of Hokage-sama in less than an hour.''

``I shall be but a moment, Kouga-san,'' Hyuuga-san announced before exiting the room.

Naruto’s grin only widened as he leant back in the hard seat, kicking up his feet to rest them on the table between them. Luck was definitely on his side today.

``Go head, I’ve got all day,'' Naruto lied easily, he’d learned early on that cocky was the best way to deal with the non-Hyuuga members of the Police Force. ``But, you’ll be letting me go in half an hour, tops. Do they still make you issue the apology or does your Sergeant have to do it? Funny, but I can’t seem to remember,'' he finished with a smirk, happy to see the red coloring his cheeks.

``Laugh all you want, Uzumaki-san, but it won’t get you out of this room any faster. We both know you’re up to no good,'' Nii-san replied, his tone even despite the fury Naruto could see burning in his eyes. Naruto nodded once. Nii-san certainly managed to keep his cool. All things considered, that was pretty impressive. He might actually go pretty far within the Hyuuga Police.

``Maybe, but that doesn’t change the fact that I haven’t done anything today. You’ll see,'' Naruto finished, glancing around the room until his eyes landed on the surveillance camera in the corner. Grinning at the camera, Naruto retreated to his thoughts. This was taking up a lot of time, but not too much. If he was careful, he should still be able to make it to the bar before his missed both of his chances to get back at Sensei.

Soon enough, Hyuuga-san was poking his head back into the room. ``Kouga-san if you would,'' the man stated quickly, cutting off his partner before Nii-san could get a word in. With a nod, Nii-san left, but not before threatening Naruto against escape which was of course entirely unnecessary. He only ever tried to escape when he was actually guilty of something after all it wasn’t really a loss until he was standing in Jiji’s Tower.

Minutes later the door reopened and Naruto’s smirk grew wider. While Hyuuga-san wasn’t giving much away, Nii-san was an open book. And right now, he didn’t look all too pleased.

``So, what’s the damage?''

``Uzumaki-san, if you will,'' Hyuuga-san stated, pointing towards the open door.

``Of course I will, Hyuuga-san,'' Naruto replied, grin still lighting up his face as he hopped from his chair, hands stuffed firmly into his pocket.

The walk back to the entrance was silent and awkward and Naruto loved every moment of it. Pausing at the door, he waited. This was the Hyuuga Police. An apology was expect. After all, it was the polite thing to do.

``Gomen, Uzumaki-san,'' Nii-san ground out, anger clear in his stance as he forced the apology from his lips.

``Why thank you ever so much,'' Naruto laughed before starting in the opposite direction of where he really needed to go. ``Told you, you’d be giving me that apology, Nii-san,'' he called over his shoulder as he sped up his pace. He needed to get out of sight before Nii-san actually lost his cool.

Sticking to the shadows, Naruto spent another ten minutes heading in random directions before finally making his way back to the bar. He may have gotten away from the Hyuuga Police once today, but he wasn’t naïve enough to think they wouldn’t have someone following him. Like master pranking rule number forty-seven stated: don’t make risks you don’t have to take. So even if no one was on his tail, which he highly doubted, his pranking skills were legendary and they would be fools to not track him, he wasn’t about to risk it.

Finally, Naruto made it back to the Shitaki Bar \& Grill. Operation Honey \& Feather was a go. Creeping into the dark confines of the bar, Naruto made his way towards his rehearsed spot. He may have been late, but that didn’t mean he was out of the game yet.

Listening in to Sensei’s conversation, Naruto smirked. The man was loud, far louder than his two drink minimum. And even better, it seemed Sensei couldn’t go two sentences without mentioning his time as a Genin. If he had this right, then that drink Sensei was knocking back was likely the fourth one of the night.

As it so happened, luck was on his side because no sooner had Naruto made his calculation, his Sensei was getting up from his table, laughing loudly as his friends teased him as he made his way to the restroom. Waiting on the tips of his toes, Naruto watched as his Sensei makes his way to the door. Finally, after what felt like an eternity, Sensei was in place, right next to the restroom door. With no one else near enough to get caught in the blast, Naruto released his trap.

Bang, the sound was soft yet effective, stopping Sensei in his tracks as honey shot out, covering the man in the process. Acting with the reflexes of a Chuunin, Sensei ducked out of the way, stepping to the, conveniently, only available side. Just as expected, the last half of his trap released, goose feathers falling like rain as they stuck to the honey like glue. Naruto grinned wide, admiring the new look his Sensei was sporting. It had all happened in a split second, but it was one of the most satisfying seconds of his short life.

Glancing around at the residue of the trap, honey and feathers littering the already dank floor of the bar, Naruto almost felt sorry for the mess, almost. Unfortunately, it was just the sad fact of life. In the pursuit of justice, sometimes there was collateral damage. Of course from the volume of the laughter booming throughout the bar, Naruto didn’t think too many people would care. Many the owner’s kids when they had to clean up the mess, but hey, they’d get over it.

``Looks like Uzumaki got you good!'' Naruto heard as he headed for the door. It was always good having his work recognized.

Slinking through the shadows, Naruto couldn’t help the little laugh that escaped him. He’d gotten Sensei pretty good. That was a job well done in his book.

Plus, it had been really fun. Sure he’d have to be more careful about the Hyuuga Police, but he’d gotten to do an awesome prank. Better yet, the pranks would only get better with each new seal he learned. He only wished he could do more than just the one per new seal. Still, he’d promised Jiji he wouldn’t go overboard so he wouldn’t. He was Uzumaki Naruto and he never went back on a promise. Plus, there were always ways around it. After all, he never said anything about going overboard on one prank.

Grinning widely, Naruto took out his recorder. ``Note to self, go all out on the next prank, uh I mean training session.''
