\chapter{The Moon Festival}

``Ha ha ha haaaaa!'' laughter bounced off the alloy walls as Haruto cut around another corner, flickering fluorescent lights casting odd shadows around him as he skirted passed. Tightening his hold on the tattered remains of his synthetic jacket, his five finger discounted feast pressed against his chest securely. His light footsteps easily navigating through the narrow trash-filled corridor as heavier, louder footsteps followed in his wake.

{\em Bang!}

``Star d...''\ the curse was lost as the violent flames of a nearby furnace blasted across the young boy's path. Haruto danced around the hot blast as he dashed down a side corridor. Swallowing heavily, his pursuers a little closer than he cared for, Haruto turned down the last corridor to what appeared to be a dead end.

Pulling his sleeve down, revealed his BISM flashing between orange and red as his pursuers tried to lock on to his location. Ignoring the warning signs, Haruto easily bypassed the admin system lock. \emph{'Honestly, if they didn't want anyone accessing it, they ought to make it harder to hack.'} He thought as his fingers flashed across the screen.

Skidding to a halt in front of a central Delta terminal. Haruto flipped open the control panel, and pulled the coaxial cable down and into his own BISM. His fingers danced along the screen as he ran his portal jumping program on the system. ``Come on, come on, come on.'' Haruto chanted to himself as he watched lines and lines of code pass long his BISM screen.

The Delta terminal flashed an angry red as he program worked its magic. ``Code Yellow, Terminal 01-alpha-omega-2 under cyber attack.'' A light female modulated voice boomed from the aerial speakers above. Big black letters flashing on the terminal's screen. \textbf{\textsc{ACCESS DENIED.}} Blinking over and over again.

\emph{'Not for long.'} Haruto thought just as the screen turned green, and the alarms quieted. Jamming his finger down on the terminal screen. Haruto navigated to his get-a-way strategy. \emph{'Open sesame bun.'}

{\em Whoosh!}

The black glossy service tube next to the terminal opened releasing white hot steam. His BISM flashed yellow in warning as he hurried into the waiting tube. The Keepers heavy footsteps picked up to a sprint, but Haruto was already locking the terminal out.

``Halt H\={e}id\`{o}ng!'' One of the Keepers bellowed. He was too far, and he knew it. And by the time they did catch up to him, he'd have long finished devouring his score. With that knowledge Haruto grinned as he gave his best impression of a Keeper salute. The tube closing on his face as he was violently slung into the air.

Shutting his eyes, Haruto braced himself for the impact of the first sharp turn.

{\em Bang!}

Haruto grunted as his BISM went from yellow to orange in warning. \emph{'Yeah, yeah, yeah.'} Haruto thought as sweat poured down his face. Tucking his elbows in, another sharp turn slammed him into a boiling wall. He'd be okay. A day or so and his bruises will have cleared up.

His BISM flashed a darker orange, forcing Haruto to open his eyes to see into the darkness. A deep notch in silicon was enough warning for him to start typing away on his BISM. A second later a wall opened up to his left. A heavy fan forcing him through it and away from an open exhaust that would have done more than leave a handful of bumps and bruises.

Counting silently in his head to ten, Haruto closed the emergency release causing him to drop like a sack of rusted bolts. The tube widen not a second later as cooler air rushed around him. Bending at the knees, Haruto readied for a hard landing.

{\em Slam!}

``Whoa!'' he let out as he landed with a roll on a pile of trash. Keeping his head tucked in, he continued his roll. Landing at the bottom in a small heap.

``And the crowd goes wild. H\={e}id\`{o}ng with a clear 10 out of 10 for excellent landing.'' Haruto spoke low and excited to himself, adding light cheering noises to the mix. At that point, his stomach growled loudly.

He rubbed it lovingly, ``Don't worry. I gotcha buddy. Just a little bit longer.''

Something sharp poked his spleen. Reaching around, he pulled out a broken antenna to an antique radio head. Shrugging he pocketed the find before picking himself up. At least he'd not landed in the compost dump.

Stretching out, Haruto rubbed the feeling back into his legs, before taking off down the dimly lit corridor at a light jog. While delta section had been dark, here in the underbellies, the light fixtures were more ornamental than functional. Even so, his eyes could pick up even the littlest cockroach. The little things got in everything if you weren't careful.

A wide smile crossed his face, this was his element. Heat blasted from the furnaces on high gear. Really, it was just the hot air form the electronics in Solas, but hot air was hot air. Turning one last corner to Delta Lower Level Terminal, he could hear the beginnings of movement. The Keepers were good at their jobs, he'd give them that. Even so, tracking him to the underbellies was the first step. Catching him, on the other hand wouldn't be so easy. \emph{'Especially seeing as all roads lead to LL'}

They'd need more than common sense to find him. Hours and man power, both of which they didn't have. \emph{'At least not today.'} Haruto thought as he turned his focus on the LL terminal before him.

Running a modified version of his portal jumper program, the \emph{Skipper}, Haruto waited the three long agonizing minutes it would take to hack. The \emph{Skipper} was significantly harder to track or detect, but it was also slower. \emph{'But at least I get to pick where I want to end up at.'} Haruto thought as the screen finally turned green. No red warning or angry voices. The \emph{Skipper} was virtually undetectable. With a destination and route in place, he slipped into the tube and shot off at speeds that would have a lesser boy vomiting.

The thought brought about memories he'd rather forget. \emph{'One time, and never again!'} If he could shiver in the tight space he would have.

A second transfer later, and he was safely walking above the Beta section of KTS Kanopos. Haruto's stomach protested again, but he ignored it. Tightening his grip on his jacket as he continued on his way. He'd made the mistake of trying to eat on a catwalk once, and had lost his meal in one of the random flushes. His stomach was going to have to wait this time.

Neon lights flashed from Solas, their intensity diluted this far out in Prayer Alley. Still, if he squinted \emph{just} right, he could catch a glimpse of something large and colorful off the giant Halo screen. \emph{'Festivals.'} He thought darkly, \emph{'Surely, put on this ship to test me!'}

He ought to be thankful for it. For this wasn't just any festival, but the \emph{Moon Festival}, the celebration of the Heavens or something like that. He did really care one way or another about the details, but over the years he'd picked up pieces of information. Like the best routes to take around Solas, and the exact time-line for the Gento Keepers to go off duty. The important things. Did it matter that he had no idea which moon the ship was celebrating? What did that information do for him if he got caught liberating his festival dinner?

\emph{'Nothing!'} Haruto thought darkly. Memories of the other orphans picking on him for his lack of knowledge coming to the surface of his mind. None of that mattered now. What mattered was that he knew all of the Gento Keepers were off duty, which meant \emph{they} weren't chasing after him. 

So, yeah that made him lucky, 'cause when \emph{they} were on his tail, some how they always seemed to know where his program was taking him. \emph{'Even I don't know where Portal Jumper is taking me.'} Haruto thought as he jumped down from the catwalk onto the rooftops of the housing units of Prayer Alley. \emph{'It is supposed to be random, after all...'}

Pausing in a shadow as a patrol of Keepers walked by, Haruto continued on his way, \emph{'Oh well, I'll figure it out eventual.'} Taking a leaping jump into the air, he gave a one-two punch to an invisible opponent, \emph{I'm not the number one hacker of Kanopos for nothing! Yosh!'}

Nodding to himself, he jumped across another house, not to worried about the noise. Anyone who was anyone would be in Solas at the heart of the biggest festival of the year. And Prayer Alley was the closest to the Gento docking bay. Haruto grinned widened as he started to look around for a good place to eat dinner. There were very few souls within KTS Kanopos that wouldn'd be at the \emph{Moon Festival}, and even less in Beta section, which hosted the majority of on board Gento Clan and Gento affiliated organizations. It was after all the biggest and grandest of festivals that the KTS Kanopos would host. Including more ZenKZ in one parade then the rest of them combined. Not to mention the fireworks. It wasn't everyday that fireworks went off {\em inside} the KTS.

And who would be leading it all? None other than the Gento Clan, the biggest clan on KTS Kanopos. He'd seen their flotilla for the first time a month ago, and still couldn't imagine that many ships just floating alongside Kanopos. Closing his eyes, he was back at Solas Beta port looking out at the fleet of ships that made up the Gento flotilla. Sure his classmates had made fun of him, but he didn't care. That, and only that had made going to class worth it.

A light whistle of steam blowing overhead pulled Haruto from his day dream. A loud noise from Solas grabbed his attention to the celebration happening so close to him. The celebration of celebration. He'd heard that the Gento ZenKZ-D would be reenacting some epic battle or another. Something to do with Gods fighting, which couldn't be all that special. Based on his history books, the Gods fought each other and people \emph{all} the time. Some day, he'd see what all the fuss was about himself, but just not today. \emph{'I'm going to need to be a heck of a lot sneaker for that.'} He thought.

Haruto's eyes glanced to the center of the ship once more. Eyeing the colorful neon lights from Solas Plaza. Today marked the six hundred and third annual celebration of the Heavens. It also happened to be his tenth breathing day. Despite the fact that this celebration had been happening for well before he was born or even the KTS Kanopos'{} founding day, Haruto had never before been allowed to participate. Well, technically he wasn't allowed to participate in {\em any} festival. Something about scaring the \emph{regular} folks, or whatever that meant. It wasn't like he cared or anything.

Still, since it was something like his breathing day party, he'd figured he'd at least try to take a peek at all of the excitement. Now that he was ten, he was one step closer to becoming a Kanopos pilot, which was far to old and responsible to be living in an orphanage. Orphanages were for babies.

Haruto's thoughts were interrupted by the sound of another Keeper patrol above him. \emph{'On the catwalk?'} His eyes turned up spotting them in the distance. Even he would have trouble hiding in plain view in the empty streets of Beta section.

Finding the access panel for the house he was on top of, Haruto hacked into it's surprisingly good security with his tunnel worm program, \emph{Worm Hole}. The hard hack would be unlikely to draw immediate attention. In fact, he'd have a couple of hours before anyone came home giving him plenty of time to clean up his security breech. Just as the footstep drew closer, the solar panel viewing window opened up allowing him to slip though before closing back up.

Haruto waited a moment, but nothing turned red and the room remained silent so he plopped down on the floor letting his feast spill out on the ground before him. Two large sticks of yakitori, three baozi, three onigiri, and a bag of jian dui. All of it long gone cold.

``Ahem.'' The sound of someone clearing their throat played in the background of Haruto's mind as he surveyed his haul. The onigiri were slightly disfigured, but the jian dui was still a little warm. Haruto popped one of the sesame covered red bean paste balls of deliciousness in his mouth.

Sure the chicken was falling off the metal skewer and the buns to his baozi had seen better days, but the meal was fresh and hadn't seen the insides of a compost bin yet. All in all, it was the best meal he'd ever had, even when he was still in the orphanage.

\emph{'Now, if only I had some MINOS, and this would be the best birthday dinner yet!'} He thought.

{``\em Ahem.''}

``I'd get that checked out if I were you.'' Haruto replied off handily as he took a large bite out of one of his meat buns. A second later, and he nearly chocked on his food as he turned sharply around to find he wasn't alone.

Lavender eyes stared back at him missing their irises. She was a Gento, but he'd swear on every God out there that he'd never seen Gento eyes quiet like that. And she was dressed right out of a history book with the most ornamental robes possible. A decorative picture of some kind of tree or something like that. Whatever it was, it was pretty and made of a material that he'd never seen before. \emph{'Man that looks heavy...'} He thought, but unable to shake the nagging feeling that \emph{this} was what the \emph{Sh\`{a}ngd\`{i}} would wear, and likely very pricey.

Honestly, she was the most beautiful girl he'd every seen, and she couldn't have been any older than him. ``Ahhh... Hi?'' He growled out roughly, his throat raw from his coughing fit earlier. Hand held out with his nicest looking onigiri, ``Ahh, did you want some?''

Her eyes buzzed with movement, swirling little dots within a pool of lavender as she tentatively took the proffered onigiri.

``Thank you.'' Her voice was soft, but strong. Haruto replied with a goofy smile. ``Do you often climb into strangers rooms?'' She asked before taking a small bite of the rice bun.

Haruto absentmindedly picked up the last two baozi, gobbing them down before he replied, ``Only when I'm on the run.''

She tilted her head slightly in answer. Her eyes covered in a slight haze that he'd have missed if he'd taken his eyes off hers for even a single second. It was weird, no one ever looked at him with such focus. An intensity without judgment. No silent hatred or fear.

``Hey, why aren't you in Solas?'' Haruto asked as he moved on to his yakitori.

She raised her eyebrow as if to ask the same question. So Haruto pointed to his face. ``This scares people.'' She looked on in disbelief as she silently finished her food. ``No, really. I'm not allowed to go for the public's safety.'' Holding out his last skewer to his new friend, she shifted slightly in place a clear indicator that she was finished.

Shrugging he downed the stick under her disapproving eyes before stuffing the last two onigiri into his mouth. ``Hey, I have manners, just not right now.'' Hopping up he looked around at the empty room. No windows, no clocks, no seats, no \emph{nothing}. Just a bed, a desk, and one dresser. If he didn't know any better he'd say she was in some kind of prison. ``Look since you're here for whatever unspoken reason.'' Haruto paused to let her answer, but she remained silent, ``I figure, I don't have much time to relax.''

She tilted her head forward acknowledgment just as his ears picked up movement further in the house. ``Hey, give me a hand up will you.'' Haruto asked as he grabbed his bag of jian dui, stuffing it back into his jacket.

His new friend moved toward the center, and laced her fingers together as she held them out ready for him to jump. Uncovering his hacked BISM, he caught his easily slipped back into the houses security network causing the solar panels to slid open. Grabbing his new friend by the shoulders, he tried not to get her expensive outfit dirty. No way would he be able to afford the cleaning bill.

``See ya around, Princess.'' Jumping up, he called over his shoulder.

On a whim, he looked down as the panels shut just in time to see her lips turn up in amusement.

\starbreak

\emph{Clink, clink!}

\emph{KLUNK!}

\emph{Ping, ping!}

\emph{Ka-caaww!}

The sounds of battle surrounded Aeliana as she was being pulled further and further into Solar Plaza. The ship's speaker system being put to work as the large Halo screens flashed screens from the Celebration of the Heaven parade in space. She turned her head longingly at one such screen, but was easily tugged further. Floating red spheres in between Halo screens morphed into a fearsome looking dragon as they run.

``Roaarrr!!!'' Its voice echoed after them as it turned from red to different shades of red and orange as if it were on fire. When she was smaller, she'd cling to her father's hand hoping for any other animal. Now, the sight of the flaming dragon brought a smile to her face as he friend continued to tug her on.

She could see other spheres morphing along the Plaza.  Different kinds of birds long since lost to time, feline animals that she'd only ever seen in her history videos. Mostly, the sphere this close to the center of the Plaza showed the twelve animals of the ancient Sh\={e}ngxi\`{a}o; the rat, the ox, the tiger, the rabbit, the dragon, the snake, the horse, the goat, the monkey, the rooster, the dog, and the pig. But further out, a more diverse set of animals showed. 

That had always been her favorite part of the Moon Festival. Learning about new beast from the habitable worlds they passed. The animals that still live that, if she wanted to, could actually see. But very few people were huddled around them, or even running along the Plaza. No, most every sensible native of KTS Kanopos was seated around a large Halo screen watching the parade excitement happening in space. \emph{Which is exactly what I should be doing.}

``Ilia! We're missing it!'' Aeliana whined as she tugged softly on the hand in her own. The artificial light had already dimmed for the evening viewing. As her first official Moon Festival where she was old enough to attend without the watchful gaze of her parents, she didn't want to be the only one missing it! \emph{'The parade's the best part!'} She thought angrily, tugging a little harder on her friend's hand.

``Don't worry, Aeliana, we're almost there.'' Ilia replied with a kind smile as she gently tugged her faster into the night.

``Where?'' Aeliana questioned pointing to nearby empty seats near the Halo screens they kept passing. The parade had started more than ten minutes ago. She could catch glimpse of the artfully decorated giant ZenKZ as they clashed on screen. At this rate, they'd miss \emph{everything}! \emph{'It's not like we can watch in the observatory deck.'} She thought, \emph{'That was for the Sakr\'{a} and his family only.'}

``The best spot in the house, of course!'' Ilia replied with a large grin on her face. Aeliana didn't return it. But followed along a little faster as they turned down a corridor leaving Solas Plaza behind and...

``Oh...''\ Aeliana blinked in surprise to find a large crowd surrounding the Commander's Halo screen that she'd only heard about. \emph{'I thought this was for emergencies only...'} At nearly a hundred times as large as the largest screen in the Plaza, the Commander's Halo was something else entirely.

A couple of people turned as Ilia pushed her way through the crowd, but ignored them with one look at her friend's ceremonial robes. Looking at their own robes, Aeliana realized why.

\emph{'So, this is where the clans watch the parade.'} Everywhere she turned, she could see the different clans all in their sections. It was a little unnerving, but soon enough they were in the Amur section, and people were parting before them.

``There!'' Ilia exclaimed as she pulled Aeliana forward and to the front of crowd. The Commander's screen was more impressive up close. The level of detail was impressive, she'd never seen the Gento ZenKZ like this before. Fairy lights below her caught her attention to a little stage that must have been set up for this event. For now, there was only the props with nine humanoid shaped statues encircling a smaller one and nothing else. \emph{'I wonder if I've missed the show?'} Action on the big screen stole her attention once more. 

``Amazing...''\ Aeliana trailed off in wander as the Battle of the Forgotten Fruit unfolded before her. She could see the intricate details of the Moon Goddess for the first time. The heavy look of the relics the ZenKZ wear lined with a pattern that had the look of power in it. It was awe inspiring.

``The best seats, like I said.'' Ilia replied with a self satisfying grin on her face. Aeliana wouldn't even be sad to tell her she was right later. Letting her hand go, Aeliana held on to the railing as she looked on in excitement.

``Uh huh.'' Aeliana agreed.

``Pays to be best friends with an heir to a clan, does't it?'' Ilia whispered in her ear causing Aeliana to nearly jump out of her SKIM.

Sighing she rolled her eyes, ``Yeah, because that's why we're friends.'' Ilia smiled back before turning her attention to the re-enactment ahead. Aeliana looked at her for a moment more, wishfully. This would probably be the last time they got to hang out like this. Her parents having vetoed going to KANP just because Ilia was going. 

\emph{'Why do I have to have a reason of my own. Just because it's dangerous? If Ilia can risk her life being a pilot, shouldn't I be allowed too, as well?'} She held back a sigh. Now that they were ten, it was time to get serious. She knew that. Knew that as her parents only child, she couldn't just do whatever she wanted without a good reason. Her family wasn't just anyone in the merchant guild but the biggest civilian guild masters of the Jade Empire. And while her parents wouldn't make her follow in their footsteps, they were right in this. Being a ZenKZ pilot wasn't an easy route, filled with danger and uncertainty. If she went to KANP, it would be for her and no one else. \emph{'Besides, a merchant's life won't be so bad.'}

Turning back to the screen, Aeliana shook such heavy thoughts from her mind. Today would be for today. Tomorrow would come soon enough.

The Moon Goddess moved into the pray position as the smaller ZenKZ surrounded her as the story continued to unfold. ``It's piloted by the Gento clan head.'' Ilia added softly. Aeliana was grateful for the commentary as her friend knew her constant desire for gaining knowledge. ``They only put all those old relics on it for this show. And that one,''\ Ilia pointed to a slightly smaller ZenKZ covered in nearly as much relic gear as the Moon Goddess that seemed to be leading the small army of the Gento ZenKZ. ``That one is lead by the Head of the Keepers, which just so happens to be the clan head's identical twin brother.''

Aeliana nodded at the new information. Not being from one of the twelve pilot clans, she had no reason to know any of this. \emph{'Although, I suppose I'd learn at KANP.'} She thought as the screen flashed in movement as the story continued. She knew it well.

Set back on their ancient ancestral planet, when the strong held power and the Gods still fought amongst each other well before her people had traversed the stars. Here, their ancestors had but one champion, the Moon Goddess. She alone stood for the people having lived amongst them for years had grown to love them as her own. But power was the only thing that commanded those realms, so she fought. Leaning her strength to push back the mighty forces trying to take their land.

But even with all her strength and cunning they were losing. So, she prayed to her father, the Father of the Gods, and he told her of the Forgotten Fruit. But their foes were not to be out done. So they summoned their God, the betrayer, to help. At that point the Halo screen showed a dark ZenKZ ten times the size of the Moon Goddess. The lights flashed and the ZenKZ swept his hand across the battle field destroying everything he touched. Aeliana instinctively reached out for her friend.

``Don't worry. I won't let anything hurt you.'' Ilia replied softly giving a firm squeeze to Aeliana's hand. Aeliana was grateful even though she knew, she \emph{knew} the dark God was nothing more than an illusion. Even so, she still had nightmares of the ZenKZ every once in a while, which was an improvement from the very first time she'd laid eyes on him.

For weeks, she'd had nightmares having to sleep in her parents bed. Her parents had made the wise decision to avoid this part of the parade for the following two years. And while that was more than four years ago, the sight of that dark God, so easily killing still frighten her.

Pulling her eyes away from the screen, she caught movement below. On the stage, the small statue in the middle slowly began to move. Slow and methodical it weaved around the stage distracting her from the monster on the screen. \emph{'A dance?'}

``That's the heir.'' Ilia whispered.

Aeliana looked on with a new light, so \emph{this} was the Gento heir. She wore an ancient looking battle kimono that wouldn't have been out of place at the Emperor's palace, but the material moved strangely. Heavy almost. ``It looks heavy.'' She voiced aloud.

Ilia snorted in response, ``Oh, you bet it is. Something like 100 kg in total. At least, that's what Kur-ram said anyway.'' Ilia shrugged as if to say take that with a grain of salt, but Aeliana didn't have anything against Kur-ram, so she figured he was probably correct. ``Anyway, this is the first year she's been apart of the parade. Pretty exciting actually.''

Aeliana nodded as they watched the heir finish her elegant dance. Sliding into place as if she really were a statue. It was than that Aeliana realized that this whole time the heir no older than herself had been holding her position since before they had arrived. The knowledge was unsettling.

A grinding sound from the stage brought her attention to the other nine statues as they started to move. ``Wow, those are people too!''

``Yeah, and just as heavy. Nobles of the Gento clan or something like that I think. I fell asleep during that lesson, but Kenta's mom is cool like that.'' Ilia trailed off before turning with a grin at Aeliana, ``But wait, this gets way better.'' Her smile was secretive as she continued, ``They don't show this part on the Halos in the Plaza.''

Sure enough, Aeliana only saw the hateful God destroying the Gento might. The fight for the Forgotten Fruit. But Aeliana knew it wouldn't last, the Moon Goddess was getting stronger with every passing second. \emph{'And now I know why.'} She thought looking down at the moving Gento Clan as they seemed to be gaining strength of their own. Soft chanting starting to pick up as the stage lit up in ancient symbols.

The Moon Goddess began to glow, never moving an inch even as the hateful God grew closer. The chanting grew louder as the symbols burned itself into the stage itself. \emph{'Stone? Where did they get that much rock?'} She thought as the nine Gento nobles moved in sync. Their voices somehow vibrating in the air. Aeliana could feel the power within the words. Coursing through that air, moving through her. Nine people should not have been able to do that, but they did. The sound being a deafening roar.

The power tangible in the air as the Moon Goddess glowed an other worldly light. {``\em Hu-haa!''} The sound crescendoing into nothingness leaving the arena in silence, but not for long. It was than the Moon Goddess came alive. Her relics taking on a quality that lead Aeliana to believe that they were more than decoration. For the Goddess was stronger, \emph{faster}, than before.

Aeliana was taken with the screen as the Moon Goddess danced. She knew this dance from year before, but now it was different. Now it meant more, because this was the same dance the young heir had just performed not even five minutes ago.

With her knew strength, the dark God stood no chance, and Aeliana cheered with the crowd as the Goddess vanquished her foes in an explosion of fireworks. ``Yatta!'' Aeliana cheered at the top of her lungs as fireworks both on the screen and around her light up the ship. Ilia laugh in excitement beside her as if they'd never seen the exact same show many times before. Holding her friend's hand tightly, Aeliana couldn't help her grin. The victory on the screen was as much hers as it was the whole of KTS Kanopos.

All too soon the Moon Goddess was finishing going back into her pray pose to thank her Father for the knowledge of the Forgotten Fruit. Aeliana watched as she always did the end, as the Gento General bowed to his warriors. She knew that in a few second the Moon Goddess would bow too, but was surprised to see movement again on the stage. Without missing a beat, the nine nobles all bowed as one to the center of the stage, to the heir. Low and steady they held the same position as the ZenKZ General. A second later, the heir too bowed low, moving for the first time since her dance concluded. And when all head were lowered, the Moon Goddess bowed to the Mighty Tree, and took the fruit for herself.

\emph{'Well that makes more sense now.'} Aeliana thought.

``Hey, Ilia. If this is the first time the heir has been here, who did her part?'' Aeliana asked.

``No one. It was just a long pause, kind of boring really.'' Ilia replied.

Aeliana looked back at the screen. The beauty of the Moon Goddess ZenKZ-D taking on a new light for her. A new story, but... Aeliana's eyes found the small figure of the Gento heir as she slowly stood. Never before had she thought someone her age could be that powerful, that sure of herself. Before her was a \emph{pilot}. No, not just any pilot, but the next pilot for the Moon Goddess. Suddenly, Aeliana felt a sharp ting of jealousy. She had never wanted to pilot a ZenKZ before, but seeing this beauty, translated as it was in person. To truly see the body, the pilot, behind the scene, Aeliana wanted that. \emph{She} wanted to be the beautiful, powerful, fearless pilot. She wanted that power, that strength.

\emph{'I want to pilot the Moon Goddess.'} She thought with a passion. \emph{'No. I want to pilot a ZenKZ more powerful, more elegant than the Moon Goddess. I want that, and I don't care how long or hard it takes.'} And for the first time, she'd never wanting anything so strongly.

%%  LocalWords:  wasn Yosh Gento couldn hadn Ahhh Ahh aren haaaaa ng
%%  LocalWords:  KLUNK Ka caaww Roaarrr ngxi Sakr KANP weren ngd Kur
%%  LocalWords:  Hu haa wouldn didn
