\documentclass[12pt, openany]{memoir}
\usepackage[utf8]{inputenc}
\usepackage[TS1,T1]{fontenc}
\usepackage{titlesec}
\usepackage{indentfirst}
\usepackage{cmtt}
%% \usepackage{hyperref}
\chapterstyle{dash}
\DoubleSpacing
\renewcommand{\afterchaptertitle}{\par\nobreak\vskip0.5\baselineskip}
\newcommand{\starbreak}{
  \fancybreak{* * * * * *}
}

%%%%%%%%%%%%%%  Title Page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*{\titleJT}{\begingroup
  \begin{vplace}[0.7]
  \centering\Large
  {\scshape Hacker Files: Moon Princess}\\
  {\scshape by}\\
  KJ Benjamin\\
  Approx 120,000 words\\
  \end{vplace}
  \endgroup}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\begin{titlingpage}
  \pagestyle{empty}
  \titleJT
\end{titlingpage}
\chapter*{Synopsis}
[Try not to fail]
  On KTS Kanopos, people are separated into those who are part of the Clans and those who are Clanless. Here on this massive battleship, there is nothing more important than becoming a Pilot for the Jade Empire. And as Helian Aeliana, heir to the infamous Guild, is finding out, it doesn't matter how smart, clever, or hard working you are. If you're not from the Clans, then your destined for a life as a Tech. But with lofty dreams of becoming a Pilot to rival the Moon Princess, she has every reason to believe she'll have to fall back on the family business.

  The infamous prankster, H\={e}id\`{o}ng Haruto, doesn't know there's any life outside of being a Pilot. He doesn't care if he's got the lowest scores in KANP either, he'll become a Pilot even if he has to make his own ZenKZ. But that won't get him into the ever elusive OCI program. And without it he'll forever be without his best friend, who just happens to be the heir to the most powerful Clan on Kanopos.

  Together, Aeliana and Haruto, two unlikely friends, have to find a way to beat the odds. And if worst comes to worst, cheat. Now, if only Kanopos would stay together long enough for either of them to achieve their goals, because for them failure isn't an option.

\include{chaps/01}
\include{chaps/02}
\include{chaps/03}
\include{chaps/04}
\include{chaps/05}
\include{chaps/06}
\include{chaps/07}
\include{chaps/08}

\include{chaps/09}
\include{chaps/10}
\include{chaps/11}
\include{chaps/12}
\include{chaps/13}
\include{chaps/14}
\include{chaps/15}
\include{chaps/16}
%% \include{chaps/chapter17}

\end{document}

%%  LocalWords:  doesn KANP OCI isn
%% Special markers: \.{h} \u{n} \v{q} \H{r} \d{v} \b{x} \i \j \ae \OE \l \o \ss ?` !'
